### 2025-02-04 writing/manuscript.tex
update day 1

\documentclass[11pt,a4paper,oneside]{article}
\linespread{1.5}
\usepackage{amsmath,amsthm,amssymb,amsfonts,adjustbox,bm}
\usepackage{geometry}
\usepackage{threeparttable}
%\usepackage[dvipsnames]{xcolor}
\usepackage{mathtools}
\usepackage{refstyle}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{eurosym}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{bbm}
\usepackage{subcaption}
\usepackage{caption}
\captionsetup{width=.8\textwidth}
\usepackage[section]{placeins}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{changepage}
\usepackage{float}
\usepackage[natbibapa]{apacite}
\usepackage{threeparttable}
\newcommand{\footremember}[2]{%
   \footnote{#2}
    \newcounter{#1}
    \setcounter{#1}{\value{footnote}}%
}
\newcommand{\footrecall}[1]{%
    \footnotemark[\value{#1}]%
} 
\usepackage{lineno}
\makeatletter
\def\makeLineNumberLeft{%
  \linenumberfont\llap{\hb@xt@\linenumberwidth{\LineNumber\hss}\hskip\linenumbersep}% left line number
  \hskip\columnwidth% skip over column of text
  \rlap{\hskip\linenumbersep\hb@xt@\linenumberwidth{\hss\LineNumber}}\hss}% right line number
\leftlinenumbers% Re-issue [left] option
\makeatother

\usepackage{blindtext}

\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue,breaklinks]{hyperref}

\title{Peer skill identification and social class:
Evidence from a referral field experiment\footnote{We obtained Institutional Review Board approvals from NYU Abu Dhabi (HRPP 2024-50) and the University of Luxembourg (ERP 24–028). The study design was preregistered in the OSF Registries prior to data collection (see \url{https://doi.org/10.17605/OSF.IO/V9T3W}).} }
% \\ \large Experimental Design \\
% \title{Skills, Inequality, and Referrals}
\author{Manuel Munoz\footremember{liser}{Luxembourg Institute of Socio-Economic Research}, Ernesto Reuben\footnote{Division of Social Science, New York University Abu Dhabi} \footrecall{liser}, Reha Tuncer\footnote{University of Luxembourg}}  
% \footnote{Center for Behavioral Institutional Design at New York University Abu Dhabi} 
\begin{document}
\linenumbers 
% HERE FOR LINES
\maketitle

\section*{Abstract}
asd
\medskip \\
\textbf{JEL Classification:} C93, D03, D83, J24 \\
\textbf{Keywords:} productivity beliefs, referrals, field experiment, skill identification, social class

% Problem: Labor markets increasingly value both cognitive and social skills, but firms struggle to identify these skills in candidates. Referrals are a common hiring tool, but their effectiveness across different skill types and potential social class biases remain unclear.
% Method: Using a field experiment with 849 university students, we study how well peers identify cognitive and social skills of their classmates.
% Key Results: Students effectively identify cognitive skills but struggle with social skills. Limited evidence of social class bias in referrals.
% Implications: Referrals may be more effective for identifying certain types of skills than others.
% We study how well referrals help screening for the two types of worker skills within the same network and compare the differential skill identification ability of referrers.

\section{Introduction}

\section{Background and Setting} \label{s2}

\section{Design} \label{s3}

\section{Results} \label{s5}

\section{Conclusion} \label{s6}

\pagebreak

\bibliographystyle{apacite}

\bibliography{referrals}    
\pagebreak

\appendix \label{appendix-all}
\renewcommand{\thefigure}{A.\arabic{figure}}
\setcounter{figure}{0}

\section{Additional Figures and Tables}

\subsection{Additional Figures}

\pagebreak

\section{Experiment} \label{instructions}
\renewcommand{\thefigure}{B.\arabic{figure}}
\textit{We include the English version of the instructions used in Qualtrics. Participansts saw the Spanish version. Horizontal lines in the text indicate page breaks and clarifiying comments are inside brackets.}

\section*{Consent}
You have been invited to participate in this decision-making study. This study is directed by [omitted for anonymous review] and organized with the support of the Social Bee Lab (Social Behavior and Experimental Economics Laboratory) at UNAB.

\vspace{5mm}

\noindent In this study, we will pay \textbf{one (1)} out of every \textbf{ten (10)} participants, who will be randomly selected. Each selected person will receive a fixed payment of \textbf{70,000} (seventy thousand pesos) for completing the study. Additionally, they can earn up to \textbf{270,000} (two hundred and seventy thousand pesos), depending on their decisions. So, in total, if you are selected to receive payment, you can earn up to \textbf{340,000} (three hundred and forty thousand pesos) for completing this study.

\vspace{5mm}

\noindent If you are selected, you can claim your payment at any Banco de Bogotá office by presenting your ID. Your participation in this study is voluntary and you can leave the study at any time. If you withdraw before completing the study, you will not receive any payment.

\vspace{5mm}

\noindent The estimated duration of this study is 20 minutes.

\vspace{5mm}

\noindent  The purpose of this study is to understand how people make decisions. For this, we will use administrative information from the university such as the SABER 11 test scores of various students (including you). Your responses will not be shared with anyone and your participation will not affect your academic records. To maintain strict confidentiality, the research results will not be associated at any time with information that could personally identify you.

\vspace{5mm}

\noindent There are no risks associated with your participation in this study beyond everyday risks. However, if you wish to report any problems, you can contact Professor [omitted for anonymous review]. For questions related to your rights as a research study participant, you can contact the IRB office of [omitted for anonymous review].

\vspace{5mm}

\noindent By selecting the option ``I want to participate in the study" below, you give your consent to participate in this study and allow us to compare your responses with some administrative records from the university.

\begin{itemize}
  \item I want to participate in the study [advances to next page]
  \item I do not want to participate in the study
\end{itemize}

\noindent\rule{\textwidth}{1pt}

\section*{Student Information}

Please write your student code.
In case you are enrolled in more than one program simultaneously, write the code of the first program you entered:

\vspace{5mm}

\noindent[Student ID code]

\vspace{5mm}

\noindent What semester are you currently in?

\vspace{5mm}

\noindent[Slider ranging from 1 to 11]

\noindent\rule{\textwidth}{1pt}

\vspace{5mm}

\noindent[Random assignment to treatment or control]

\section*{Instructions}

The instructions for this study are presented in the following video. Please watch it carefully. We will explain your participation and how earnings are determined if you are selected to receive payment.

\vspace{5mm}

\noindent[Treatment-specific instructions in video format]

\vspace{5mm}

\noindent If you want to read the text of the instructions narrated in the video, press the ``Read instruction text" button. Also know that in each question, there will be a button with information that will remind you if that question has earnings and how it is calculated, in case you have any doubts.

\begin{itemize}
  \item I want to read the instructions text [text version below]
\end{itemize}

\noindent\rule{\textwidth}{1pt}

\vspace{5mm}

In this study, you will respond to three types of questions. First, are the belief questions. For belief questions, we will use as reference the results of the SABER 11 test that you and other students took to enter the university, focused on three areas of the exam: mathematics, reading, and English.

\vspace{5mm}

\noindent For each area, we will take the scores of all university students and order them from lowest to highest. We will then group them into 100 percentiles. The percentile is a position measure that indicates the percentage of students with an exam score that is above or below a value.

\vspace{5mm}

\noindent For example, if your score in mathematics is in the 20th percentile, it means that 20 percent of university students have a score lower than yours and the remaining 80 percent have a higher score. A sample belief question is: ``compared to university students, in what percentile is your score for mathematics?"

\vspace{5mm}

\noindent If your answer is correct, you can earn 20 thousand pesos. We say your answer is correct if the difference between the percentile you suggest and the actual percentile of your score is not greater than 7 units. For example, if you have a score that is in the 33rd percentile and you say it is in the 38th, the answer is correct because the difference is less than 7. But if you answer that it is in the 41st, the difference is greater than 7 and the answer is incorrect.

\vspace{5mm}

\noindent The second type of questions are recommendation questions and are also based on the mathematics, reading, and English areas of the SABER 11 test. We will ask you to think about the students with whom you have taken or are taking classes, to recommend from among them the person you consider best at solving problems similar to those on the SABER 11 test.

\vspace{5mm}

\noindent When you start typing the name of your recommended person, the computer will show suggestions with the full name, program, and university entry year of different students. Choose the person you want to recommend. If the name doesn't appear, check that you are writing it correctly. Do not use accents and use `n' instead of `ñ'. If it still doesn't appear, it may be because that person is not enrolled this semester or because they did not take the SABER 11 test. In that case, recommend someone else.

\vspace{5mm}

\noindent You can earn up to 250,000 pesos for your recommendation. We will multiply your recommended person's score by 100 pesos if they are in the first 50 percentiles. We will multiply it by 500 pesos if your recommended person's score is between the 51st and 65th percentile. If it is between the 66th and 80th percentile, we will multiply your recommended person's score by 1000 pesos. If the score is between the 81st and 90th percentile, you earn 1500 pesos multiplied by your recommended person's score. And if the score is between the 91st and 100th percentile, we will multiply your recommended person's score by 2500 pesos to determine the earnings.

\vspace{5mm}

\noindent The third type of questions are information questions and focus on aspects of your personal life or your relationship with the people you have recommended.

\subsection*{Earnings}

Now we will explain who gets paid for participating and how the earnings for this study are assigned. The computer will randomly select one out of every 10 participants to pay for their responses. For selected individuals, the computer will randomly choose one of the three areas, and from that chosen area, it will pay for one of the belief questions.

\vspace{5mm}

\noindent Similarly, the computer will randomly select one of the three areas to pay for one of the recommendation questions.

\vspace{5mm}

\noindent \textbf{Additionally, if you are selected to receive payment, your recommended person in the  chosen area will receive a fixed payment of 100 thousand pesos.} [Only seen if assigned to the treatment]

\vspace{5mm}

\noindent Each person selected to receive payment for this study can earn: up to 20 thousand pesos for one of the belief questions, up to 250 thousand pesos for one of the recommendation questions, and a fixed payment of 70 thousand pesos for completing the study.

\vspace{5mm}

\noindent Selected individuals can earn up to 340 thousand pesos.

\noindent\rule{\textwidth}{1pt}

\vspace{5mm}

\noindent [Participants go through all three Subject Areas in randomized order]

\section*{Subject Areas}

\subsection*{Critical Reading}
For this section, we will use as reference the Critical Reading test from SABER 11, which evaluates the necessary competencies to understand, interpret, and evaluate texts that can be found in everyday life and in non-specialized academic fields.

\vspace{5mm}

\noindent [Clicking shows the example question from SABER 11 below]

\vspace{5mm}

\noindent Although the democratic political tradition dates back to ancient Greece, political thinkers did not address the democratic cause until the 19th century. Until then, democracy had been rejected as the government of the ignorant and unenlightened masses. Today it seems that we have all become democrats without having solid arguments in favor. Liberals, conservatives, socialists, communists, anarchists, and even fascists have rushed to proclaim the virtues of democracy and to show their democratic credentials (Andrew Heywood). According to the text, which political positions identify themselves as democratic?

\begin{itemize}
  \item Only political positions that are not extremist
  \item The most recent political positions historically
  \item The majority of existing political positions
  \item The totality of possible political currents
\end{itemize}

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\subsection*{Mathematics}
This section references the Mathematics test from SABER 11, which evaluates people's competencies to face situations that can be resolved using certain mathematical tools.

\vspace{5mm}

\noindent [Clicking shows the example question from SABER 11 below]

\vspace{5mm}

\noindent A person living in Colombia has investments in dollars in the United States and knows that the exchange rate of the dollar against the Colombian peso will remain constant this month, with 1 dollar equivalent to 2,000 Colombian pesos. Their investment, in dollars, will yield profits of 3\% in the same period. A friend assures them that their profits in pesos will also be 3\%. Their friend's statement is:

\begin{itemize}
    \item Correct. The proportion in which the investment increases in dollars is the same as in pesos.
    \item Incorrect. The exact value of the investment should be known.
    \item Correct. 3\% is a fixed proportion in either currency.
    \item Incorrect. 3\% is a larger increase in Colombian pesos.
\end{itemize}

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\subsection*{English}
This section uses the English test from SABER 11 as a reference, which evaluates that the person demonstrates their communicative abilities in reading and language use in this language.

\vspace{5mm}

\noindent [Clicking shows the example question from SABER 11 below]

\vspace{5mm}

\noindent Complete the conversations by marking the correct option.
    \begin{itemize}
        \item Conversation 1: I can't eat a cold sandwich. It is horrible!
        \begin{itemize}
            \item I hope so.
            \item I agree.
            \item I am not.
        \end{itemize}
        \item Conversation 2: It rained a lot last night!
        \begin{itemize}
            \item Did you accept?
            \item Did you understand?
            \item Did you sleep?
        \end{itemize}
    \end{itemize}

\noindent\rule{\textwidth}{1pt}

\vspace{5mm}

\noindent [Following parts are identical for all Subject Areas and are not repeated here for brevity]

\subsection*{Your Score}

Compared to university students, in which percentile do you think your [\textbf{Subject Area}] test score falls (1 is the lowest percentile and 100 the highest)?

\vspace{5mm}

\noindent [Clicking shows the explanations below]

\vspace{5mm}

\noindent How is a percentile calculated?

\vspace{5mm}

\noindent A percentile is a position measurement. To calculate it, we take the test scores for all students currently enrolled in the university and order them from lowest to highest. The percentile value you choose refers to the percentage of students whose score is below yours. For example, if you choose the 20th percentile, you're indicating that 20\% of students have a score lower than yours and the remaining 80\% have a score higher than yours.

\vspace{5mm}

\noindent What can I earn for this question?

\vspace{5mm}

\noindent For your answer, you can earn \textbf{20,000 (twenty thousand) PESOS}, but only if the difference between your response and the correct percentile is less than 7. For example, if the percentile where your score falls is 33 and you respond with 38 (or 28), the difference is 5 and the answer is considered correct. But if you respond with 41 or more (or 25 or less), for example, the difference would be greater than 7 and the answer is incorrect.

\vspace{5mm}

\noindent Please move the sphere to indicate which percentile you think your score falls in:

\vspace{5mm}

\noindent[Slider with values from 0 to 100]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\subsection*{Recommendation}

Among the people with whom you have taken any class at the university, who is your recommendation for the [\textbf{Subject Area}] test? Please write that person's name in the box below:

\vspace{5mm}

\noindent \textbf{\textcolor{red}{Important:}} \textbf{You will not be considered for payment unless the recommended person is someone with whom you have taken at least one class during your studies.}

\vspace{5mm}

\noindent Your response is only a recommendation for the purposes of this study and we will \textbf{not} contact your recommended person at any time.

\vspace{5mm}

\noindent [Clicking shows the explanations below]

\vspace{5mm}

\noindent Who can I recommend?

\vspace{5mm}

\noindent Your recommendation \textbf{must} be someone with whom you have taken (or are taking) a class. If not, your answer will not be considered for payment. The person you recommend will not be contacted or receive any benefit from your recommendation.

\vspace{5mm}

\noindent As you write, you will see up to 7 suggested student names containing the letters you have entered. The more you write, the more accurate the suggestions will be. Please write \textbf{without} accents and use the letter `n' instead of `ñ'. If the name of the person you're writing doesn't appear, it could be because you made an error while writing the name.

\vspace{5mm}

\noindent If the name is correct and still doesn't appear, it could be because the student is not enrolled this semester or didn't take the SABER 11 test. In that case, you must recommend someone else.

\vspace{5mm}

\noindent My earnings for this question?

\vspace{5mm}

\noindent For your recommendation, you could receive earnings of up to 250,000 (two hundred and fifty thousand) PESOS. The earnings are calculated based on your recommendation's score and the percentile of that score compared to other UNAB students, as follows:

\begin{itemize}
  \item We will multiply your recommendation's score by \$100 (one hundred) pesos if it's between the 1st and 50th percentiles
  \item We will multiply your recommendation's score by \$500 (five hundred) pesos if it's between the 51st and 65th percentiles
  \item We will multiply your recommendation's score by \$1000 (one thousand) pesos if it's between the 66th and 80th percentiles
  \item We will multiply your recommendation's score by \$1500 (one thousand five hundred) pesos if it's between the 81st and 90th percentiles
  \item We will multiply your recommendation's score by \$2500 (two thousand five hundred) pesos if it's between the 91st and 100th percentiles
\end{itemize}

\vspace{5mm}

\noindent This is illustrated in the image below:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.65\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/bonus_structure.png}
    \caption{Earnings for recommendation questions}
    \label{fig:earnings}
\end{figure}

\vspace{5mm}

\noindent For example, if your recommendation got 54 points and the score is in the 48th percentile, you could earn 54x100 = 5400 PESOS. But, if the same score of 54 points were in the 98th percentile, you could earn 54x2500 = 135,000 PESOS.

\vspace{5mm}

\noindent [Text field with student name suggestions popping up as participant types]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\subsection*{Relationship with your recommendation}
How close is your relationship with your recommendedation: ``[Name of the student selected from earlier]"? (0 indicates you are barely acquaintances and 10 means you are very close)

\vspace{5mm}

\noindent [Slider with values from 0 to 10]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\subsection*{Your recommendation's score}
Compared to university students, in which percentile do you think [Name of the student selected from earlier]'s score falls in the [\textbf{Subject Area}] test (1 is the lowest percentile and 100 the highest)?

\vspace{5mm}

\noindent [Clicking shows the explanations below]

\vspace{5mm}

\noindent How is a percentile calculated?

\vspace{5mm}

\noindent A percentile is a position measurement. To calculate it, we take the test scores for all students currently enrolled in the university and order them from lowest to highest. The percentile value you choose refers to the percentage of students whose score is below yours. For example, if you choose the 20th percentile, you're indicating that 20\% of students have a score lower than yours and the remaining 80\% have a score higher than yours.

\vspace{5mm}

\noindent What can I earn for this question?

\vspace{5mm}

\noindent For your answer, you can earn \textbf{20,000 (twenty thousand) PESOS}, but only if the difference between your response and the correct percentile is less than 7. For example, if the percentile where your recommended person's score falls is 33 and you respond with 38 (or 28), the difference is 5 and the answer is considered correct. But if you respond with 41 or more (or 25 or less), for example, the difference would be greater than 7 and the answer is incorrect.

\vspace{5mm}

\noindent  Please move the sphere to indicate which percentile you think your recommended person's score falls in:

\vspace{5mm}

\noindent[Slider with values from 0 to 100]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\section*{Demographic Information}

What is the highest level of education achieved by your father?

\vspace{5mm}

\noindent [Primary, High School, University, Graduate Studies, Not Applicable]

\vspace{5mm}

\noindent What is the highest level of education achieved by your mother?

\vspace{5mm}

\noindent [Primary, High School, University, Graduate Studies, Not Applicable]

\vspace{5mm}

\noindent Please indicate the socio-economic group to which your family belongs:

\vspace{5mm}

\noindent [Group A (Strata 1 or 2), Group B (Strata 3 or 4), Group C (Strata 5 or 6)]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\section*{UNAB Students Distribution}
Thinking about UNAB students, in your opinion, what percentage belongs to each socio-economic group? The total must sum to 100\%:

\vspace{5mm}

\noindent [Group A (Strata 1 or 2) percentage input area]

\noindent [Group B (Strata 3 or 4) percentage input area]

\noindent [Group C (Strata 5 or 6) percentage input area]

\noindent [Shows sum of above percentages]

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\section*{End of the Experiment}
Thank you for participating in this study.

\vspace{5mm}

\noindent If you are chosen to receive payment for your participation, you will receive a confirmation to your UNAB email and a link to fill out a form with your information. The process of processing payments is done through Nequi and takes approximately 15 business days, counted from the day of your participation.

\vspace{5mm}

\noindent [Clicking shows the explanations below]

\vspace{5mm}

\noindent Who gets paid and how is it decided?

\vspace{5mm}

\noindent The computer will randomly select one out of every ten participants in this study to be paid for their
decisions.

\vspace{5mm}

\noindent For selected individuals, the computer will randomly select one area: mathematics, reading, or English, and from that area will select one of the belief questions. If the answer to that question is correct, the participant will receive 20,000 pesos.

\vspace{5mm}

\noindent The computer will randomly select an area (mathematics, critical reading, or English) to pay for one of the recommendation questions. The area chosen for the recommendation question is independent of the area chosen for the belief question. The computer will take one of the two recommendations you have made for the chosen area. Depending on your recommendation's score, you could win up to 250,000 pesos.

\vspace{5mm}

\noindent Additionally, people selected to receive payment for their participation will have a fixed earnings of 70,000 pesos for completing the study.

\vspace{5mm}

\noindent\rule{\textwidth}{1pt}

\section*{Participation}
In the future, we will conduct studies similar to this one where people can earn money for their participation. The participation in these studies is by invitation only. Please indicate if you are interested in being invited to other studies similar to this one:

\vspace{5mm}

\noindent [Yes, No]

\end{document}

### 2025-02-07 writing/manuscript.tex
update day 2

@@
 \section{Results} \label{s5}
+
+\begin{table}[H]
+  \caption{Summary Statistics by Treatment Status}
+  \centering
+  \begin{tabular}{lccc}
+  \hline
+  & Control & Treatment & $p$ \\
+  \hline
+  GPA (z-score) & 0.126 & 0.187 & 0.393 \\
+  & (0.959) & (0.963) & \\
+  [1ex]
+  Reading Score (z-score) & 0.212 & 0.320 & 0.116 \\
+  & (0.892) & (0.969) & \\
+  [1ex]
+  Math Score (z-score) & 0.285 & 0.307 & 0.753 \\
+  & (0.900) & (0.978) & \\
+  [1ex]
+  Tie Strength & 3.982 & 3.923 & 0.892 \\
+  & (6.041) & (5.613) & \\
+  [1ex]
+  Estrato & 1.670 & 1.693 & 0.623 \\
+  & (0.633) & (0.633) & \\
+  [1ex]
+  Age & 20.576 & 20.733 & 0.380 \\
+  & (2.410) & (2.423) & \\
+  [1ex]
+  Female & 0.529 & 0.531 & 0.947 \\
+  & (0.500) & (0.500) & \\
+  \hline
+  Observations & 382 & 352 & \\
+  \hline
+  \end{tabular}
+  \label{tab:treatment_stats}
+  \end{table}
+
+\begin{table}[H]
+  \caption{Summary Statistics for Choice Set and Nominated Peers}
+  \centering
+  \begin{tabular}{lcccc}
+  \hline
+  & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
+  \cline{2-5}
+  & Choice Set & Nominated & Choice Set & Nominated \\
+  \hline
+  GPA (z-score) & -0.140 & 0.579 & -0.147 & 0.580 \\
+  & (0.981) & (0.994) & (0.983) & (0.998) \\
+  [1ex]
+  Reading Score (z-score) & 0.167 & 0.547 & 0.166 & 0.501 \\
+  & (0.902) & (0.883) & (0.903) & (0.910) \\
+  [1ex]
+  Math Score (z-score) & 0.202 & 0.513 & 0.206 & 0.624 \\
+  & (0.883) & (0.918) & (0.885) & (0.941) \\
+  [1ex]
+  Tie Strength & 3.222 & 14.467 & 3.217 & 13.822 \\
+  & (4.625) & (9.382) & (4.632) & (9.291) \\
+  [1ex]
+  Estrato & 1.817 & 1.738 & 1.811 & 1.725 \\
+  & (0.672) & (0.648) & (0.672) & (0.647) \\
+  [1ex]
+  Age & 20.942 & 20.501 & 20.958 & 20.490 \\
+  & (2.180) & (2.698) & (2.187) & (2.559) \\
+  [1ex]
+  Female & 0.524 & 0.562 & 0.520 & 0.428 \\
+  & (0.499) & (0.497) & (0.500) & (0.495) \\
+  \hline
+  Observations & 128,847 & 673 & 128,150 & 669 \\
+  \hline
+  \end{tabular}
+  \label{tab:stats_by_area}
+  \end{table}
 

### 2025-02-18 writing/manuscript.tex
update descriptives

--- 2025-02-04 writing/manuscript.tex
@@
 
-\title{Peer skill identification and social class:
+\title{Project ICFES:
 Evidence from a referral field experiment\footnote{We obtained Institutional Review Board approvals from NYU Abu Dhabi (HRPP 2024-50) and the University of Luxembourg (ERP 24–028).
@@
 \section*{Abstract}
-asd
+Lorem Ipsum \citep{beaman_job_2018}
 \medskip \\
@@
 \section{Results} \label{s5}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Selection into the experiment}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{Admin Data}} & \multicolumn{1}{c}{\textbf{Sample}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\
+  \midrule
+  Reading score (z-score) & 0.000 & 0.264 & 0.000 \\
+  Math score (z-score) & 0.000 & 0.295 & 0.000 \\
+  GPA (z-score) & 0.000 & 0.156 & 0.000 \\
+  Low-SES & 0.343 & 0.410 & 0.000 \\
+  Female & 0.567 & 0.530 & 0.060 \\
+  Age & 21.154 & 20.651 & 0.000 \\
+  \midrule
+  Observations & 4,417 & 734 & 5,151 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares characteristics between the full administrative sample and the experimental sample.
+$p$-values for binary outcomes (Low-SES, Female) are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+All reported \textit{p}-values are two-tailed.
+GPA and test scores are standardized to have mean zero and standard deviation one in the administrative sample.
+  \end{tablenotes}
+  \label{tab:selection}
+  \end{threeparttable}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Balance between treatments}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
+  \toprule
+    & \multicolumn{1}{c}{\textbf{Baseline}} & \multicolumn{1}{c}{\textbf{Bonus}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\ 
+  \midrule
+  Reading score (z-score) & 0.212 & 0.320 & \multicolumn{1}{c}{0.116} \\
+  Math score (z-score) & 0.285 & 0.307 & \multicolumn{1}{c}{0.753} \\
+  GPA (z-score) & 0.126 & 0.187 & \multicolumn{1}{c}{0.393} \\
+  \# connections & 346.80 & 353.75 & \multicolumn{1}{c}{0.574} \\
+  Tie strength & 3.665 & 3.565 & \multicolumn{1}{c}{0.798} \\
+  Low-SES & 0.419 & 0.401 & \multicolumn{1}{c}{0.615} \\
+  Female & 0.529 & 0.531 & \multicolumn{1}{c}{0.947} \\
+  Age & 20.576 & 20.733 & \multicolumn{1}{c}{0.380} \\
+  \midrule
+  Observations & 382 & 352 & 734 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table presents balance tests between \textbf{Baseline} and \textbf{Bonus} conditions.
+$p$-values for binary outcomes are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+All reported \textit{p}-values are two-tailed.
+GPA and test scores are standardized to have mean zero and standard deviation one in the administrative sample.
+Tie strength refers to the number of classes taken together.
+\# connections refers to the number of indiviuduals in referrer choice sets, otherwise called the ``network degree''.
+Low-SES is a binary variable indicating the share of participants in estrato 1 or 2.
+  \end{tablenotes}
+  \label{tab:balance}
+  \end{threeparttable}
+  \end{table}
+
+  \begin{table}[H]
+    \centering
+    \begin{threeparttable}
+    \caption{Summary statistics for referred and not referred}
+    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
+    \toprule
+    & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
+    \cmidrule{2-5}
+    & Not Referred & Referred & Not Referred & Referred \\
+    \midrule
+    Reading score (z-score) & 0.165 & 0.547 & 0.164 & 0.501 \\
+    & (0.003) & (0.034) & (0.003) & (0.035) \\
+    [1ex]
+    Math score (z-score) & 0.201 & 0.513 & 0.204 & 0.624 \\
+    & (0.002) & (0.035) & (0.002) & (0.036) \\
+    [1ex]
+    GPA (z-score) & -0.144 & 0.579 & -0.151 & 0.580 \\
+    & (0.003) & (0.038) & (0.003) & (0.039) \\
+    Tie strength & 3.163 & 14.467 & 3.161 & 13.822 \\
+    & (0.013) & (0.362) & (0.013) & (0.359) \\
+    [1ex]
+    Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
+    & (0.001) & (0.019) & (0.001) & (0.019) \\
+    [1ex]
+    Female & 0.524 & 0.562 & 0.520 & 0.428 \\
+    & (0.001) & (0.019) & (0.001) & (0.019) \\
+    [1ex]
+    Age & 20.945 & 20.501 & 20.961 & 20.490 \\
+    & (0.006) & (0.104) & (0.006) & (0.099) \\
+    \midrule
+    Observations & 128,174 & 673 & 127,481 & 669 \\
+    \bottomrule
+    \end{tabular*}
+    \begin{tablenotes}[flushleft]
+    \footnotesize
+    \item[] \textit{Note:} Standard errors in parentheses.
+All scores are standardized (z-scores).
+Tie strength measures the number of courses taken together.
+Low-SES indicates the share of participants in estrato 1 or 2.
+\# connections represents the size of the choice set.
+    \end{tablenotes}
+    \label{tab:stats_by_area}
+    \end{threeparttable}
+  \end{table}
+
+  \begin{table}[H]
+    \caption{Math Referrals by own SES and Treatment}
+    \centering
+    \begin{tabular}{lcccc}
+    \hline
+    & \multicolumn{2}{c}{Baseline} & \multicolumn{2}{c}{Bonus} \\
+    \cline{2-5}
+    & Choice Set & Nominated & Choice Set & Nominated \\
+    \hline
+    Low-SES & 0.358 & 0.483 & 0.368 & 0.508 \\
+    Middle-SES & 0.527 & 0.595 & 0.517 & 0.527 \\
+    High-SES  & 0.202 & 0.161 & 0.196 & 0.259 \\
+    \hline
+    Observations & 65,103 & 348 & 62,378 & 321 \\
+    \hline
+    \end{tabular}
+    \label{tab:social_class_nominations}
+\end{table}
+
+\begin{table}[H]
+    \caption{Verbal Referrals by own SES and Treatment}
+    \centering
+    \begin{tabular}{lcccc}
+    \hline
+    & \multicolumn{2}{c}{Baseline} & \multicolumn{2}{c}{Bonus} \\
+    \cline{2-5}
+    & Choice Set & Nominated & Choice Set & Nominated \\
+    \hline
+    Low-SES  & 0.365 & 0.464 & 0.370 & 0.554 \\
+    Middle-SES & 0.527 & 0.570 & 0.513 & 0.512 \\
+    High-SES & 0.199 & 0.200 & 0.192 & 0.310 \\
+    \hline
+    Observations & 66,674 & 351 & 61,500 & 322 \\
+    \hline
+    \end{tabular}
+    \label{tab:social_class_nominations_verbal}
+\end{table}
 
@@
 
-In this study, you will respond to three types of questions.
+\noindent In this study, you will respond to three types of questions.
 First, are the belief questions.

### 2025-03-05 writing/manuscript.tex
update march

@@
 \section{Results} \label{s5}
+
+\subsection{Descriptives}
 
@@
 Low-SES indicates the share of participants in estrato 1 or 2.
-\# connections represents the size of the choice set.
     \end{tablenotes}
@@
 
+  \begin{figure}[H]
+    \centering
+    \caption{Distribution of performance by subject}\label{performance}
+    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
+    \begin{tablenotes}
+      \footnotesize
+      \item[] \textit{Note:} This figure displays the average standardized math and reading z-scores across socioeconomic status groups.
+We test differences between math and reading scores within each SES group using paired t-tests.
+No statistically significant differences were found between subjects for Low SES ($p$ = 0.495), Middle SES ($p$ = 0.734), or High SES students ($p$ = 0.124).
+While math scores are consistently higher than reading scores across all groups, these differences do not reach statistical significance.
+The data shows a clear socioeconomic gradient, with performance improving as SES increases for both subjects.
+    \end{tablenotes}
+  \end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \caption{Distribution of top decile performers by subject}\label{topdecile}
+    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/strata_scores.png}
+    \begin{tablenotes}
+      \footnotesize
+      \item[] \textit{Note:} This figure displays the percentage of participants across SES who score in the top decile for math and reading.
+We test differences between math and reading proportions within each SES group using two-sample tests of proportions and find no statistically significant differences ($p > 0.28$).
+Middle-SES students show the highest representation in the top decile for both subjects in the sample.
+    \end{tablenotes}
+  \end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \caption{Availability of SES groups}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
+        \caption{Referral Rates}
+        \label{fig:baseline_ses}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_shares.png}
+        \caption{Academic Performance of Referrals}
+        \label{fig:baseline_topses}
+    \end{subfigure}
+    \label{fig:baseline_combinedses}
+    \caption*{\footnotesize\textit{Note:} The figure on the left displays the availability of each SES group by SES backgrounds.
+Two-sample tests of proportions show all differences across SES groups are statistically significant ($p <$ 0.001).
+Low-SES students have 9.6 percentage points more connections with Low-SES peers than High-SES students do (36.5\% vs 26.8\%).
+In constrast, high-SES students have 6.3 percentage points more connections with High-SES peers than Low-SES students do (19.7\% vs 13.4\%).
+    }
+  \end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \caption{Baseline Referral Patterns by SES}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
+        \caption{Referral Rates}
+        \label{fig:tie_ses}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
+        \caption{Academic Performance of Referrals}
+        \label{fig:tie_topses}
+    \end{subfigure}
+    \label{fig:tie_combinedses}
+    \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata.
+The right panel shows the availability of top decile performers within each SES group.}
+  \end{figure}
+
+\pagebreak
+
+  \begin{figure}[H]
+    \centering
+    \caption{Baseline Referral Patterns by SES}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_rates.png}
+        \caption{Referral Rates}
+        \label{fig:baseline_rates}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
+        \caption{Academic Performance of Referrals}
+        \label{fig:baseline_performance}
+    \end{subfigure}
+    \label{fig:baseline_combined}
+    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across socioeconomic strata in the baseline condition.
+The right panel shows the average standardized math and reading scores of referred students by referrer's SES.}
+  \end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \caption{Treatment Effects on Referral Patterns}
+    \label{fig:treat_combined}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
+        \caption{Changes in Referral Rates}
+        \label{fig:treat_rates}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
+        \caption{Changes in Academic Performance of Referrals}
+        \label{fig:treat_performance}
+    \end{subfigure}
+    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
+The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Treatment Effects on Tie Strength}
+  \label{fig:treat_combined2}
+  \begin{subfigure}[t]{0.49\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
+      \caption{Changes in Referral Rates}
+      \label{fig:tietreat_rates}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.49\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
+      \caption{Changes in Academic Performance of Referrals}
+      \label{fig:tietreat_performance}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
+The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
+\end{figure}
+
   \begin{table}[H]
-    \caption{Math Referrals by own SES and Treatment}
+    \caption{SES shares by SES and referral status}
     \centering
@@
     \cline{2-5}
-    & Choice Set & Nominated & Choice Set & Nominated \\
+    & Not Referred & Referred & Not Referred & Referred \\
     \hline
-    Low-SES & 0.358 & 0.483 & 0.368 & 0.508 \\
-    Middle-SES & 0.527 & 0.595 & 0.517 & 0.527 \\
-    High-SES  & 0.202 & 0.161 & 0.196 & 0.259 \\
+    Low-SES & 0.361 & 0.473 & 0.368 & 0.531 \\
+    Middle-SES & 0.527 & 0.583 & 0.515 & 0.520 \\
+    High-SES & 0.201 & 0.180 & 0.193 & 0.286 \\
     \hline
-    Observations & 65,103 & 348 & 62,378 & 321 \\
+    Observations & 131,777 & 699 & 123,878 & 643 \\
     \hline
     \end{tabular}
-    \label{tab:social_class_nominations}
+    \label{tab:social_class_nominations_combined}
+ \end{table}
+
+%  \begin{table}[H]
+%   \caption{SES shares by academic measure}
+%   \centering
+%   \begin{tabular}{lcccc}
+%   \hline
+%   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
+%   \cline{2-5}
+%   & Referred & Top Decile & Referred & Top Decile \\
+%   \hline
+%   Low-SES & 0.495 & 0.301 & 0.505 & 0.318 \\
+%   Middle-SES & 0.562 & 0.460 & 0.541 & 0.445 \\
+%   High-SES & 0.207 & 0.239 & 0.254 & 0.237 \\
+%   \hline
+%   Observations & 275 & 385 & 283 & 355 \\
+%   \hline
+%   \end{tabular}
+%   \label{tab:ses_shares_by_measure}
+%   \end{table}
+
+\begin{table}[H]
+  \caption{SES shares in Verbal}
+  \centering
+  \begin{tabular}{lcccc}
+  \hline
+  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
+  \cline{4-5}
+  & & & Baseline & Bonus \\
+  \hline
+  Low-SES & 0.301 & 0.398 & 0.483 & 0.508 \\
+  Middle-SES & 0.460 & 0.438 & 0.595 & 0.527 \\
+  High-SES & 0.239 & 0.282 & 0.161 & 0.259 \\
+  \hline
+  Observations & 385 & 25,196 & 147 & 128 \\
+  \hline
+  \end{tabular}
+  \label{tab:ses_shares_verbal}
   \end{table}
@@
   \begin{table}[H]
-    \caption{Verbal Referrals by own SES and Treatment}
+  \caption{SES shares in Math}
   \centering
@@
   \hline
-    & \multicolumn{2}{c}{Baseline} & \multicolumn{2}{c}{Bonus} \\
-    \cline{2-5}
-    & Choice Set & Nominated & Choice Set & Nominated \\
+  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
+  \cline{4-5}
+  & & & Baseline & Bonus \\
   \hline
-    Low-SES  & 0.365 & 0.464 & 0.370 & 0.554 \\
-    Middle-SES & 0.527 & 0.570 & 0.513 & 0.512 \\
-    High-SES & 0.199 & 0.200 & 0.192 & 0.310 \\
+  Low-SES & 0.318 & 0.398 & 0.464 & 0.554 \\
+  Middle-SES & 0.445 & 0.428 & 0.570 & 0.512 \\
+  High-SES & 0.237 & 0.278 & 0.200 & 0.310 \\
   \hline
-    Observations & 66,674 & 351 & 61,500 & 322 \\
+  Observations & 355 & 23,883 & 153 & 130 \\
   \hline
   \end{tabular}
-    \label{tab:social_class_nominations_verbal}
+  \label{tab:ses_shares_math}
+  \end{table}
+
+    \begin{table}[H]
+      \caption{Verbal performance (z-score) of Referred Students}
+      \centering
+      \begin{tabular}{lccc}
+      \hline
+      & Baseline & Bonus & Total \\
+      \hline
+      Low-SES & 0.644 & 0.383 & 0.513 \\
+      Middle-SES & 0.551 & 0.509 & 0.530 \\
+      High-SES & 0.705 & 0.820 & 0.763 \\
+      \hline
+      Observations & 351 & 322 & 673 \\
+      \hline
+      \end{tabular}
+      \label{tab:performance_verbal}
+      \end{table}
+
+      \begin{table}[H]
+      \caption{Math performance (z-score) of Referred Students }
+      \centering
+      \begin{tabular}{lccc}
+      \hline
+      & Baseline & Bonus & Total \\
+      \hline
+      Low-SES & 0.560 & 0.483 & 0.521 \\
+      Middle-SES & 0.683 & 0.647 & 0.665 \\
+      High-SES & 0.921 & 0.836 & 0.879 \\
+      \hline
+      Observations & 348 & 321 & 669 \\
+      \hline
+      \end{tabular}
+      \label{tab:performance_math}
       \end{table}

### 2025-03-14 writing/manuscript.tex
post ernesto visit march 1

@@
   \midrule
-  Reading score (z-score) & 0.000 & 0.264 & 0.000 \\
-  Math score (z-score) & 0.000 & 0.295 & 0.000 \\
-  GPA (z-score) & 0.000 & 0.156 & 0.000 \\
+  Reading score & 62.651 & 65.183 & 0.000 \\
+  Math score & 63.973 & 67.477 & 0.000 \\
+  GPA & 3.958 & 4.012 & 0.000 \\
   Low-SES & 0.343 & 0.410 & 0.000 \\
+  Med-SES & 0.505 & 0.499 & 0.763 \\
+  High-SES & 0.153 & 0.091 & 0.000 \\
   Female & 0.567 & 0.530 & 0.060 \\
@@
   \item[] \textit{Note:} This table compares characteristics between the full administrative sample and the experimental sample.
-$p$-values for binary outcomes (Low-SES, Female) are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+$p$-values for binary outcomes (Low-SES, Med-SES, High-SES, Female) are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
 All reported \textit{p}-values are two-tailed.
-GPA and test scores are standardized to have mean zero and standard deviation one in the administrative sample.
   \end{tablenotes}
@@
   \midrule
-  Reading score (z-score) & 0.212 & 0.320 & \multicolumn{1}{c}{0.116} \\
-  Math score (z-score) & 0.285 & 0.307 & \multicolumn{1}{c}{0.753} \\
-  GPA (z-score) & 0.126 & 0.187 & \multicolumn{1}{c}{0.393} \\
-  \# connections & 346.80 & 353.75 & \multicolumn{1}{c}{0.574} \\
-  Tie strength & 3.665 & 3.565 & \multicolumn{1}{c}{0.798} \\
+  Reading score & 64.712 & 65.693 & \multicolumn{1}{c}{0.134} \\
+  Math score & 67.366 & 67.597 & \multicolumn{1}{c}{0.780} \\
+  GPA & 4.003 & 4.021 & \multicolumn{1}{c}{0.445} \\
+  \# connections & 173.40 & 176.88 & \multicolumn{1}{c}{0.574} \\
+  Tie strength & 3.939 & 3.719 & \multicolumn{1}{c}{0.443} \\
   Low-SES & 0.419 & 0.401 & \multicolumn{1}{c}{0.615} \\
+  Med-SES & 0.492 & 0.506 & \multicolumn{1}{c}{0.714} \\
+  High-SES & 0.089 & 0.094 & \multicolumn{1}{c}{0.824} \\
   Female & 0.529 & 0.531 & \multicolumn{1}{c}{0.947} \\
@@
 All reported \textit{p}-values are two-tailed.
-GPA and test scores are standardized to have mean zero and standard deviation one in the administrative sample.
 Tie strength refers to the number of classes taken together.
 \# connections refers to the number of indiviuduals in referrer choice sets, otherwise called the ``network degree''.
-Low-SES is a binary variable indicating the share of participants in estrato 1 or 2.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
   \end{tablenotes}
@@
   \begin{threeparttable}
-    \caption{Summary statistics for referred and not referred}
-    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
+  \caption{Distribution of referrals by area}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \toprule
+  Area & Only one referral & Both areas & Total \\
+  \midrule
+  Verbal & 65 & 608 & 673 \\
+  Math & 61 & 608 & 669 \\
+  \midrule
+  Total & 126 & 1,216 & 1,342 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas.
+"Only one referral" indicates individuals who made referrals exclusively in that area.
+"Both areas" shows individuals who made referrals in both verbal and math areas.
+The majority of referrers (608) made referrals in both areas.
+  \end{tablenotes}
+  \label{tab:referral_distribution}
+  \end{threeparttable}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Summary statistics for network members by nomination status}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
   \toprule
   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
-    \cmidrule{2-5}
+  \cmidrule{2-3} \cmidrule{4-5}
   & Not Referred & Referred & Not Referred & Referred \\
   \midrule
-    Reading score (z-score) & 0.165 & 0.547 & 0.164 & 0.501 \\
-    & (0.003) & (0.034) & (0.003) & (0.035) \\
+  Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
+  & (0.003) & (0.039) & (0.003) & (0.040) \\
   [1ex]
-    Math score (z-score) & 0.201 & 0.513 & 0.204 & 0.624 \\
-    & (0.002) & (0.035) & (0.002) & (0.036) \\
+  Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
+  & (0.003) & (0.042) & (0.003) & (0.043) \\
   [1ex]
-    GPA (z-score) & -0.144 & 0.579 & -0.151 & 0.580 \\
-    & (0.003) & (0.038) & (0.003) & (0.039) \\
-    Tie strength & 3.163 & 14.467 & 3.161 & 13.822 \\
-    & (0.013) & (0.362) & (0.013) & (0.359) \\
+  GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
+  & (0.003) & (0.041) & (0.003) & (0.041) \\
+  [1ex]
+  Tie strength z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
+  & (0.003) & (0.091) & (0.003) & (0.090) \\
   [1ex]
@@
   & (0.001) & (0.019) & (0.001) & (0.019) \\
+  [1ex]
+  Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
+  & (0.001) & (0.019) & (0.001) & (0.019) \\
+  [1ex]
+  High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
+  & (0.001) & (0.012) & (0.001) & (0.012) \\
   [1ex]
@@
   \item[] \textit{Note:} Standard errors in parentheses.
-All scores are standardized (z-scores).
-Tie strength measures the number of courses taken together.
-Low-SES indicates the share of participants in estrato 1 or 2.
+GPA, test scores, and tie strength are standardized at the network level.
+For each referrer's network, we first calculated the mean and standard deviation of each measure.
+We then computed the average of these means and standard deviations across all referrers.
+Each individual's score was standardized using these network-level statistics.
+The standardization formula is $z = (x - \bar{x}_{network}) / \sigma_{network}$, where $\bar{x}_{network}$ and $\sigma_{network}$ are the average of network means and standard deviations, respectively.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
+Tie strength measures the number of connections between individuals.
   \end{tablenotes}
-    \label{tab:stats_by_area}
+  \label{tab:stats_by_nomination}
   \end{threeparttable}
@@
 
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Comparison of math and verbal scores by SES group and data source}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc}
+  \toprule
+  & \multicolumn{3}{c}{Math} & \multicolumn{3}{c}{Verbal} \\
+  \cmidrule{2-4} \cmidrule{5-7}
+  & Network & Admin & Sample & Network & Admin & Sample \\
+  \midrule
+  Low-SES & 66.976 & 61.653 & 67.813 & 64.738 & 60.974 & 66.058 \\
+  & (0.052) & (0.346) & (0.694) & (0.043) & (0.274) & (0.574) \\
+  [1ex]
+  Mid-SES & 65.627 & 64.531 & 66.859 & 63.685 & 63.154 & 64.779 \\
+  & (0.039) & (0.224) & (0.580) & (0.032) & (0.183) & (0.436) \\
+  [1ex]
+  High-SES & 67.781 & 67.330 & 70.610 & 64.966 & 64.892 & 66.397 \\
+  & (0.077) & (0.416) & (1.295) & (0.063) & (0.341) & (1.214) \\
+  \midrule
+  Observations & 128,150 & 4,415 & 669 & 128,847 & 4,403 & 673 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} Standard errors in parentheses.
+The table presents mean scores with standard errors for math and verbal tests across the entire network, the admin data, and the sample.
+Admin data consistently shows lower scores than both network and the sample across all SES groups consistent with selection, with the largest gaps occurring for the Low-SES.
+Differences between network and sample scores are generally smaller than those between either and the admin data.
+  \end{tablenotes}
+  \label{tab:ses_scores_comparison}
+  \end{threeparttable}
+\end{table}
+
 \begin{figure}[H]
   \centering
-    \caption{Distribution of performance by subject}\label{performance}
+  \caption{Participant network size and tie strength by time spent at UNAB}\label{connections_class}
+  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/connection_class.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average number of connections for referrers in blue and the average number of classes they have taken together with their connections in green across semesters spent at UNAB.
+The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
+  \end{tablenotes}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
+  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the percentage share of individuals across three dimensions.
+First bar shows referrers in the top decile for math and reading based on admin data.
+Second bar is the share of top decile in their networks.
+Third column shows the share of top decile among the referrals made.
+We test differences between proportions across these three groups using two-sample tests of proportions.
+For both math and reading scores, the differences between Sample and Network ($p<0.001$), Sample and Referrals ($p<0.005$), and Network and Referrals ($p<0.001$) are all statistically significant.
+  \end{tablenotes}
+\end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \caption{Participant network performance by subject and SES}\label{performance}
     \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
@@
       \footnotesize
-      \item[] \textit{Note:} This figure displays the average standardized math and reading z-scores across socioeconomic status groups.
-We test differences between math and reading scores within each SES group using paired t-tests.
-No statistically significant differences were found between subjects for Low SES ($p$ = 0.495), Middle SES ($p$ = 0.734), or High SES students ($p$ = 0.124).
-While math scores are consistently higher than reading scores across all groups, these differences do not reach statistical significance.
-The data shows a clear socioeconomic gradient, with performance improving as SES increases for both subjects.
+      \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES.
+We test differences between math and reading scores within using paired $t$-tests.
+For both math and reading scores, differences between Low and Middle SES ($p < 0.001$), Low and High SES ($p < 0.001$), and Middle and High SES ($p = 0.001$) are all statistically significant.
     \end{tablenotes}
@@
 
-  \begin{figure}[H]
-    \centering
-    \caption{Distribution of top decile performers by subject}\label{topdecile}
-    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/strata_scores.png}
-    \begin{tablenotes}
-      \footnotesize
-      \item[] \textit{Note:} This figure displays the percentage of participants across SES who score in the top decile for math and reading.
+  % \begin{figure}[H]
+  %   \centering
+  %   \caption{Distribution of top decile performers by subject}\label{topdecile}
+  %   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/strata_scores.png}
+  %   \begin{tablenotes}
+  %     \footnotesize
+  %     \item[] \textit{Note:} This figure displays the percentage of participants across SES who score in the top decile for math and reading.
 We test differences between math and reading proportions within each SES group using two-sample tests of proportions and find no statistically significant differences ($p > 0.28$).
 Middle-SES students show the highest representation in the top decile for both subjects in the sample.
-    \end{tablenotes}
-  \end{figure}
+  %   \end{tablenotes}
+  % \end{figure}
 
@@
     \centering
-    \caption{Availability of SES groups}
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
-        \caption{Referral Rates}
+    \caption{Participant network composition by SES}
+    \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
     \label{fig:baseline_ses}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_shares.png}
-        \caption{Academic Performance of Referrals}
-        \label{fig:baseline_topses}
-    \end{subfigure}
-    \label{fig:baseline_combinedses}
-    \caption*{\footnotesize\textit{Note:} The figure on the left displays the availability of each SES group by SES backgrounds.
-Two-sample tests of proportions show all differences across SES groups are statistically significant ($p <$ 0.001).
-Low-SES students have 9.6 percentage points more connections with Low-SES peers than High-SES students do (36.5\% vs 26.8\%).
-In constrast, high-SES students have 6.3 percentage points more connections with High-SES peers than Low-SES students do (19.7\% vs 13.4\%).
+    \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES.
+We test differences in proportions of peer connections across SES groups using two-sample tests of proportions.
+All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections.
+These patterns reveal strong homophily in network formation across all SES groups.
     }

### 2025-03-18 writing/manuscript.tex
figures update

@@
   \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas.
-"Only one referral" indicates individuals who made referrals exclusively in that area.
-"Both areas" shows individuals who made referrals in both verbal and math areas.
+``Only one referral'' indicates individuals who made referrals exclusively in that area.
+``Both areas'' shows individuals who made referrals in both verbal and math areas.
 The majority of referrers (608) made referrals in both areas.
@@
   & (0.001) & (0.012) & (0.001) & (0.012) \\
-  [1ex]
-  Female & 0.524 & 0.562 & 0.520 & 0.428 \\
-  & (0.001) & (0.019) & (0.001) & (0.019) \\
-  [1ex]
-  Age & 20.945 & 20.501 & 20.961 & 20.490 \\
-  & (0.006) & (0.104) & (0.006) & (0.099) \\
+  % [1ex]
+  % Female & 0.524 & 0.562 & 0.520 & 0.428 \\
+  % & (0.001) & (0.019) & (0.001) & (0.019) \\
+  % [1ex]
+  % Age & 20.945 & 20.501 & 20.961 & 20.490 \\
+  % & (0.006) & (0.104) & (0.006) & (0.099) \\
   \midrule
@@
   \centering
+  \caption{Effect of the Bonus on Referrals}
+  \begin{subfigure}[t]{0.7\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
+      \caption{Reading}  
+      \label{fig:reading_combined}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.7\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
+      \caption{Math}
+      \label{fig:math_combined}
+  \end{subfigure}
+  \label{fig:both_combined}
+  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
+We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$).
+The bottom panel shows the average standardized math and tie strength of referrals across conditions.
+We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$).
+For both math and reading, referred students }
+\end{figure}
+
+\begin{figure}[H]
+  \centering
   \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
@@
     \footnotesize
-    \item[] \textit{Note:} This figure displays the percentage share of individuals across three dimensions.
-First bar shows referrers in the top decile for math and reading based on admin data.
-Second bar is the share of top decile in their networks.
+    \item[] \textit{Note:} This figure displays the percentage share of top decile individuals according to the admin data across three dimensions.
+First bar shows referrers in the sample of participants.
+Second bar is the share of top decile individuals in their networks.
 Third column shows the share of top decile among the referrals made.
@@
   \centering
+  \caption{Participant network composition by SES}
+  \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
+  \label{fig:tie_ses}
+  \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
+We test differences in standardized tie strength across SES groups using two-sample $t$-tests.
+All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$).
+The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.
+These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
+\end{figure}
+
+%   \begin{figure}[H]
+%     \centering
+%     \caption{Baseline Referral Patterns by SES}
+%     \begin{subfigure}[t]{0.49\textwidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
+%         \caption{Referral Rates}
+%         \label{fig:tie_ses}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[t]{0.49\textwidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
+%         \caption{Academic Performance of Referrals}
+%         \label{fig:tie_topses}
+%     \end{subfigure}
+%     \label{fig:tie_combinedses}
+%     \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata.
+The right panel shows the availability of top decile performers within each SES group.}
+%   \end{figure}
+
+\pagebreak
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Participant network composition by SES}
+%   \includegraphics[width=\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/combined_baseline.png}
+%   \label{fig:baseline_combined}
+%   \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
+We test differences in z-score tie strength across SES groups using two-sample $t$-tests.
+All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$).
+The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.
+These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
+% \end{figure}
+
+  \begin{figure}[H]
+    \centering
     \caption{Baseline Referral Patterns by SES}
@@
       \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
-        \caption{Referral Rates}
-        \label{fig:tie_ses}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
-        \caption{Academic Performance of Referrals}
-        \label{fig:tie_topses}
-    \end{subfigure}
-    \label{fig:tie_combinedses}
-    \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata.
-The right panel shows the availability of top decile performers within each SES group.}
-  \end{figure}
-
-\pagebreak
-
-  \begin{figure}[H]
-    \centering
-    \caption{Baseline Referral Patterns by SES}
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_rates.png}
+        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_referral_distribution.png}
         \caption{Referral Rates}  
@@
         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
-        \caption{Academic Performance of Referrals}
+        \caption{Referral Performance}
         \label{fig:baseline_performance}
@@
     \label{fig:baseline_combined}
-    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across socioeconomic strata in the baseline condition.
-The right panel shows the average standardized math and reading scores of referred students by referrer's SES.}
+    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across SES in the baseline condition.
+We test differences in SES shares across SES groups using two-sample tests of proportions.
+All differences are statistically significant ($p < 0.1$).
+The right panel shows the average standardized math and reading scores of referred students by referrer's SES.
+We test differences in z-scores across SES groups using two-sample $t$-tests and find no statistically significant differences in reading scores across SES groups (all $p > 0.36$).
+For math scores, we observe marginally significant differences between Low and High SES students ($p = 0.08$) and between Middle and High SES students ($p = 0.18$), with High SES referring peers with higher math performance.}
   \end{figure}
@@
     \centering
-    \caption{Treatment Effects on Referral Patterns}
+    \caption{Effect of the Bonus}
     \label{fig:treat_combined}
@@
         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
-        \caption{Changes in Academic Performance of Referrals}
+        \caption{Changes in Referral Performance}
         \label{fig:treat_performance}
     \end{subfigure}
-    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
-The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
+    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across SES.
+We test differences in SES shares across conditions using two-sample tests of proportions.
+For Low-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.034$).
+For Middle-SES, only the change in referral share of High-SES is statistically significant ($p = 0.027$).
+For High-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.059$).
+The right panel shows the differences in math and reading z-scores across SES.
+We test differences in SES shares across conditions using two-sample $t$-tests.
+For both reading and math scores, the only statistically significant difference is in the reading scores for Low-SES ($p = 0.026$).}
 \end{figure}
@@
   \centering
-  \caption{Treatment Effects on Tie Strength}
+  \caption{Effect of the Bonus on Tie Strength}
   \label{fig:treat_combined2}
@@
       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
-      \caption{Changes in Academic Performance of Referrals}
+      \caption{Changes in Referral Performance}
       \label{fig:tietreat_performance}
@@
 \end{figure}
-
-  \begin{table}[H]
-    \caption{SES shares by SES and referral status}
-    \centering
-    \begin{tabular}{lcccc}
-    \hline
-    & \multicolumn{2}{c}{Baseline} & \multicolumn{2}{c}{Bonus} \\
-    \cline{2-5}
-    & Not Referred & Referred & Not Referred & Referred \\
-    \hline
-    Low-SES & 0.361 & 0.473 & 0.368 & 0.531 \\
-    Middle-SES & 0.527 & 0.583 & 0.515 & 0.520 \\
-    High-SES & 0.201 & 0.180 & 0.193 & 0.286 \\
-    \hline
-    Observations & 131,777 & 699 & 123,878 & 643 \\
-    \hline
-    \end{tabular}
-    \label{tab:social_class_nominations_combined}
- \end{table}
-
-%  \begin{table}[H]
-%   \caption{SES shares by academic measure}
-%   \centering
-%   \begin{tabular}{lcccc}
-%   \hline
-%   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
-%   \cline{2-5}
-%   & Referred & Top Decile & Referred & Top Decile \\
-%   \hline
-%   Low-SES & 0.495 & 0.301 & 0.505 & 0.318 \\
-%   Middle-SES & 0.562 & 0.460 & 0.541 & 0.445 \\
-%   High-SES & 0.207 & 0.239 & 0.254 & 0.237 \\
-%   \hline
-%   Observations & 275 & 385 & 283 & 355 \\
-%   \hline
-%   \end{tabular}
-%   \label{tab:ses_shares_by_measure}
-%   \end{table}
-
-\begin{table}[H]
-  \caption{SES shares in Verbal}
-  \centering
-  \begin{tabular}{lcccc}
-  \hline
-  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
-  \cline{4-5}
-  & & & Baseline & Bonus \\
-  \hline
-  Low-SES & 0.301 & 0.398 & 0.483 & 0.508 \\
-  Middle-SES & 0.460 & 0.438 & 0.595 & 0.527 \\
-  High-SES & 0.239 & 0.282 & 0.161 & 0.259 \\
-  \hline
-  Observations & 385 & 25,196 & 147 & 128 \\
-  \hline
-  \end{tabular}
-  \label{tab:ses_shares_verbal}
-  \end{table}
-
-  \begin{table}[H]
-  \caption{SES shares in Math}
-  \centering
-  \begin{tabular}{lcccc}
-  \hline
-  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
-  \cline{4-5}
-  & & & Baseline & Bonus \\
-  \hline
-  Low-SES & 0.318 & 0.398 & 0.464 & 0.554 \\
-  Middle-SES & 0.445 & 0.428 & 0.570 & 0.512 \\
-  High-SES & 0.237 & 0.278 & 0.200 & 0.310 \\
-  \hline
-  Observations & 355 & 23,883 & 153 & 130 \\
-  \hline
-  \end{tabular}
-  \label{tab:ses_shares_math}
-  \end{table}
-
-    \begin{table}[H]
-      \caption{Verbal performance (z-score) of Referred Students}
-      \centering
-      \begin{tabular}{lccc}
-      \hline
-      & Baseline & Bonus & Total \\
-      \hline
-      Low-SES & 0.644 & 0.383 & 0.513 \\
-      Middle-SES & 0.551 & 0.509 & 0.530 \\
-      High-SES & 0.705 & 0.820 & 0.763 \\
-      \hline
-      Observations & 351 & 322 & 673 \\
-      \hline
-      \end{tabular}
-      \label{tab:performance_verbal}
-      \end{table}
-
-      \begin{table}[H]
-      \caption{Math performance (z-score) of Referred Students }
-      \centering
-      \begin{tabular}{lccc}
-      \hline
-      & Baseline & Bonus & Total \\
-      \hline
-      Low-SES & 0.560 & 0.483 & 0.521 \\
-      Middle-SES & 0.683 & 0.647 & 0.665 \\
-      High-SES & 0.921 & 0.836 & 0.879 \\
-      \hline
-      Observations & 348 & 321 & 669 \\
-      \hline
-      \end{tabular}
-      \label{tab:performance_math}
-      \end{table}
 

### 2025-03-21 writing/manuscript.tex
first look regression analysis

@@
   \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$).
 The bottom panel shows the average standardized math and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$).
-For both math and reading, referred students }
+We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
+For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
 \end{figure}
@@
       \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES.
-We test differences between math and reading scores within using paired $t$-tests.
-For both math and reading scores, differences between Low and Middle SES ($p < 0.001$), Low and High SES ($p < 0.001$), and Middle and High SES ($p = 0.001$) are all statistically significant.
+We test differences between scores across SES using paired $t$-tests.
+For both math and reading scores, all differences between SES groups are statistically significant (all $p \leq 0.001$).
     \end{tablenotes}
@@
 All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections.
-These patterns reveal strong homophily in network formation across all SES groups.
     }
@@
 All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$).
-The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.
-These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
+The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.}
 \end{figure}

### 2025-03-24 writing/manuscript.tex
prep for meet 1

@@
 
+\begin{figure}[H]
+  \centering
+  \caption{Performance by Tie Strength and SES}
+  \includegraphics[width=0.85\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/tie_combined.png}
+  \label{fig:tie_score_ses}
+  \caption*{\footnotesize\textit{Note:} This figure shows local polynomial regressions of network math and reading z-scores by social tie strength across socioeconomic status groups with 95\% confidence intervals.
+Higher SES have steeper positive relationships between tie strength and the average performance those in their network across reading and math scores.}
+\end{figure}
+
     \section{Conclusion} \label{s6}

### 2025-05-20 writing/manuscript.tex
first draft -introduction

@@
 
+\pagebreak
 \section{Introduction}
+Equally qualified individuals in the labor market may face very different outcomes depending on their socioeconomic status (SES).
+A key driver of inequality according to  sociologists is due to differences in social capital (e.g., Bourdieu).
+A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
+In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{\textcolor{red}{fill in citaiton sociology reading from slides}}.
+
+Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a vivid labor market application where the role of differences in social capital becomes evident.
+As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022social_a}.\footnote{Chetty and colleagues suggests the share of high-SES connections among low-SES networks as the definition of social capital, as it correlates so strongly with labor market income.} This implies referrals will reflect differences in network structures even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
+
+Yet, in case of gender, evidence shows referrals may be biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions \citep{beaman_job_2018,hederos2025gender}.
+A similar bias against low-SES may further exacerbate outcomes of low-SES individuals in the labor market: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we can be confident that referral hiring disadvantages low-SES.
+The empirical question we answer is whether there is a bias against low-SES once we account for the network SES compositon in a controlled setting.
+
+In this study, we focus on the role of SES in referrals by investigating whether individuals who are asked to refer someone tend to refer a candidate of their own SES.
+We also explore potential mechanisms behind referral patterns under different incentives.
+To this end, we conducted a lab-in-the-field experiment with 734 participants in a Colombian university where different SES groups mix together.
+Participants were instructed to refer a qualified student for tasks similar to the Math and Reading parts of the national university entry exam (akin to SAT).
+To incentivize participants to refer qualified candidates, we set earnings dependent on referred candidates' actual university entry exam scores.
+
+Referral hiring in the labor market range form formal referral program at firm asking employees to refer to simply passing on job opportunities between network members \citep{topa2019social}.
+As participants in our study are students at the university referring based on exam scores, we abstract away from formal referral programs with defined job openings.
+Our setting instead resembles situations where contacts share opportunities with each other.
+This also eliminates reputational concerns as there is no firm, which play a largers role in the labor market compared to our setting.
+At the same time, national university entry exam scores are objective, widely accepted measures of ability, and referrers in our setting possess accurate information about these signals.
 

### 2025-05-21 writing/manuscript.tex
first draft progress #2

--- 2025-03-24 writing/manuscript.tex
@@
 
+\pagebreak
 \section{Introduction}
+Equally qualified individuals may face very different labor market outcomes depending on their socioeconomic status (SES).
+A key driver of this inequality according to sociologists is due to differences in social capital (e.g., Bourdieu).
+A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
+In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.
+\textcolor{red}{fill in citaiton sociology reading from slides}}
+
+Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a common labor market practice where the role of differences in social capital becomes evident.
+As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022social_a}.\footnote{Chetty and colleagues suggests the share of high-SES connections among low-SES networks as the definition of social capital, as it correlates so strongly with labor market income.} Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
+
+Evidence shows referrals are biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
+A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we expect referral hiring to disadvantagee low-SES.
+The empirical question we answer is whether there is a bias against low-SES once we account for the network SES compositon in a controlled setting.
+
+In this study, we focus on the role of SES in referrals by investigating whether individuals who are asked to refer someone tend to refer a candidate of their own SES.
+We also explore potential mechanisms behind referral patterns under different incentives.
+To this end, we conducted a lab-in-the-field experiment with 734 participants in a Colombian university where different SES groups mix together.
+Participants were instructed to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent of SAT in US system).
+To incentivize participants to refer qualified candidates, we set earnings dependent on referred candidates' actual university entry exam scores.
+
+Referral hiring in the labor market range form formal referral program at firm asking employees to refer to simply passing on job opportunities between network members \citep{topa2019social}.
+As participants in our study are students at the university referring based on exam scores, we abstract away from formal referral programs with defined job openings.
+Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action.
+This also eliminates reputational concerns as there is no firm (see for example \citet{witte2021workers,bandiera2009social}).
+At the same time, referring based on national university entry exam scores are still objective, widely accepted measures of ability, and we show evidence that referrers in our setting possess accurate information about these signals.
+
+We find no evidence that referrals are biased against low-SES after network SES compositions are accounted for.
+Networks of high- and low-SES participants show SES-homophily, and both groups are connected at higher rates with their own SES group than what would be at random given actual group shares at the university.
+Controlling for these, however, only low-SES students displayed same-SES homophily in referrals.
+Our treatment randomized participants across different incentives.
+We provide evidence that adding a substantial monetary bonus (\$25) for the referred candidate on top of the pay-for-performance incentives did not change the referral behavior we observed.
+
+Same-SES bias is strongest among low-SES,
 

### 2025-06-02 writing/manuscript.tex
writing draft 1

--- 2025-03-24 writing/manuscript.tex
@@
 % \title{Skills, Inequality, and Referrals}
-\author{Manuel Munoz\footremember{liser}{Luxembourg Institute of Socio-Economic Research}, Ernesto Reuben\footnote{Division of Social Science, New York University Abu Dhabi} \footrecall{liser}, Reha Tuncer\footnote{University of Luxembourg}}
+\author{Manuel Munoz,\footremember{liser}{Luxembourg Institute of Socio-Economic Research} Ernesto Reuben,\footnote{Division of Social Science, New York University Abu Dhabi} \footrecall{liser} Reha Tuncer\footnote{University of Luxembourg}}
 % \footnote{Center for Behavioral Institutional Design at New York University Abu Dhabi} 
@@
 
+\pagebreak
 \section{Introduction}
+Equally qualified individuals may face very different labor market outcomes depending on their socioeconomic status (SES).
+A key driver of this inequality is due to differences in social capital,\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} with recent empirical work characterizing its most important facet as the “share of high-SES friends among individuals with low-SES” because it correlates strongly with labor market income \citep{chetty2022social_a}.
+A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
+In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.
+\textcolor{red}{fill in citaiton sociology reading from slides}}
+
+Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a common labor market practice which makes evident the role of differences in social capital.
+As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022social_a}.
+Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
+
+Evidence shows referrals can be biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
+A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we expect referral hiring to disadvantagee low-SES.
+The empirical question we answer is whether there is a bias against low-SES once we account for the network SES compositon in a controlled setting.
+
+In this study, we focus on the role of SES in referrals by investigating whether individuals who are asked to refer someone tend to refer a same-SES candidate.
+We also explore potential mechanisms behind referral patterns under different incentives.
+To this end, we conducted a lab-in-the-field experiment with 734 participants in a Colombian university where different SES groups mix together.
+Participants were instructed to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent of SAT in US system).
+To incentivize participants to refer qualified candidates, we set earnings dependent on referred candidates' actual university entry exam scores.
+
+Referral hiring in the labor market can range from firm-level formal referral programs asking employees to bring candidates to simply passing on job opportunities between network members \citep{topa2019social}.
+As participants in our study are students at the university referring based on exam scores, we abstract away from formal referral programs with defined job openings.
+Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action.
+This also eliminates reputational concerns as there is no firm (see for example \citet{witte2021workers,bandiera2009social}).
+At the same time, national university entry exam scores are still objective, widely accepted measures of ability, and we show evidence that referrers in our setting possess accurate information about these signals.
+
+We find strong evidence that networks of high- and low-SES participants exhibit SES-homophily.
+Both groups are connected at higher rates with their own SES group than what would be at random given actual group shares at the university (Figure \ref{availability_lses}).
+As students take more courses together within the same program, their networks dwindle in size (Figures \ref{share_same_program_by_tie} and \ref{conns_by_tie}), and become more homogenous in SES-shares (Figure \ref{share_same_ses_by_tie}).
+We identify selection into academic programs as a key mechanism.
+The private university where our study takes place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
+These result in programs with very large cost differences within the same university (Figure \ref{fees_with_boxplot}).
+We find that average yearly fees paid increase with SES, and the high-SES share in the most expensive program at the university, medicine, drives the network segregation across SES (Figure \ref{ses_distribution_by_fees}).
+
+Do segregated networks account for all the differences in SES referral rates across SES groups?
+Same-SES referrals are 17\% more common than is suggested by referrer networks.
+High- and low-SES referrers under refer each other by 50\%.
+Yet, controlling for networks, our results suggest only low-SES students show significant same-SES homophily in referrals.
+Regardless of SES, referrals identify highly able individuals, and are characterized by a very high number of courses taken together.
+The latter underlies the impact of program selection in referrals, where the smaller and more homogenous choice sets come into play.
+Our treatment randomized participants across two different incentive schemes by adding a substantial monetary bonus (\$25) for the referred candidate on top of the pay-for-performance incentives.
+We provide evidence that treatment incentives did not change the referral behavior across the same-SES referral rate, the number of courses taken together with the referral candidate, and the candidate's exam scores.
+
+This paper extends various the literature
+
+The remainder of the paper is organized as follows.
+Section 2 begins with the background and setting in Colombia.
+In Section 3 we present the design of the experiment.
+In Section 4 we describe the data and procedures.
+Section 5 discusses the results of the experiment.
+Section 6 concludes.
+The Appendix presents additional tables and figures as well as the experiment instructions.
+
+\begin{figure}[H]
+  \centering
+  \caption{Effect of the Bonus on Referrals}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/availability_lses.png}
+      \caption{Reading}  
+      \label{availability_lses}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/share_same_ses_by_tie.png}
+      \caption{Math}
+      \label{share_same_ses_by_tie}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
+The bottom panel shows the average standardized math and tie strength of referrals across conditions.
+We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
+For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Effect of the Bonus on Referrals}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/share_same_program_by_tie.png}
+      \caption{Reading}  
+      \label{share_same_program_by_tie}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/conns_by_tie.png}
+      \caption{Math}
+      \label{conns_by_tie}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
+The bottom panel shows the average standardized math and tie strength of referrals across conditions.
+We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
+For both math and reading, treatment causes no significant changes in referral performance or tie strength.
+considering the net average monthly wage stands at \$350 and minimum legal wage is at \$200 in 2025}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Effect of the Bonus on Referrals}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/fees_with_boxplot.png}
+      \caption{Reading}  
+      \label{fees_with_boxplot}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/ses_distribution_by_fees.png}
+      \caption{Math}
+      \label{ses_distribution_by_fees}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
+The bottom panel shows the average standardized math and tie strength of referrals across conditions.
+We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
+For both math and reading, treatment causes no significant changes in referral performance or tie strength.
+considering the net average monthly wage stands at \$350 and minimum legal wage is at \$200 in 2025}
+\end{figure}
 

### 2025-06-03 writing/manuscript.tex
draft 2

@@
 \section{Introduction}
-Equally qualified individuals may face very different labor market outcomes depending on their socioeconomic status (SES).
-A key driver of this inequality is due to differences in social capital,\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} with recent empirical work characterizing its most important facet as the “share of high-SES friends among individuals with low-SES” because it correlates strongly with labor market income \citep{chetty2022social_a}.
+Equally qualified individuals may face very different labor market outcomes depending on their socioeconomic status \citep{stansbury2024class}.
+A key driver of this inequality is due to differences in social capital,\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} with recent empirical work characterizing its most important facet as the “share of high-SES friends among individuals with low-SES” as it correlates strongly with labor market income \citep{chetty2022na}.
 A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
@@
 Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a common labor market practice which makes evident the role of differences in social capital.
-As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022social_a}.
+As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
 Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
 
-Evidence shows referrals can be biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
-A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we expect referral hiring to disadvantagee low-SES.
+Yet, experimental evidence shows referrals can be biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
+A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we should expect referral hiring to further disadvantagee low-SES.
 The empirical question we answer is whether there is a bias against low-SES once we account for the network SES compositon in a controlled setting.
 
-In this study, we focus on the role of SES in referrals by investigating whether individuals who are asked to refer someone tend to refer a same-SES candidate.
-We also explore potential mechanisms behind referral patterns under different incentives.
-To this end, we conducted a lab-in-the-field experiment with 734 participants in a Colombian university where different SES groups mix together.
+In this study, we study inequalities related to SES combining a university-wide cross-sectional network data set comprising over 4,500 students in which classroom interactions are recorded along with individual attributes.
+We focus on the role of SES in referrals by experimentally investigating whether individuals who are asked to refer a peer tend to refer a same-SES candidate.
+We also explore potential mechanisms behind referral patterns by randomizing participants into two different incentive structures.
+To this end, we conducted a lab-in-the-field experiment with 734 students in a Colombian university.
 Participants were instructed to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent of SAT in US system).
@@
 Referral hiring in the labor market can range from firm-level formal referral programs asking employees to bring candidates to simply passing on job opportunities between network members \citep{topa2019social}.
-As participants in our study are students at the university referring based on exam scores, we abstract away from formal referral programs with defined job openings.
+As our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
 Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action.
-This also eliminates reputational concerns as there is no firm (see for example \citet{witte2021workers,bandiera2009social}).
+This eliminates reputational concerns as there is no firm (see for example \citet{witte2021workers,bandiera2009social}).
 At the same time, national university entry exam scores are still objective, widely accepted measures of ability, and we show evidence that referrers in our setting possess accurate information about these signals.
 
-We find strong evidence that networks of high- and low-SES participants exhibit SES-homophily.
+In a university setting, class attendance provides essential opportunities for face-to-face interaction between students.
+On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.
+On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
+Our setting is ideal to study these opposing forces: First, The very high level of income inequality and existence of deeply rooted historical groups in Colombia makes SES differences extremely visible in access to tertiary education, where the rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
+Yet, thanks to the particular standing of the institution we have chosen for this study (Figure \ref{school_quality_income}), different SES groups including both low- and high-SES mix together in this university.
+
+We find strong evidence that networks of high- and low-SES participants exhibit same-SES bias.
 Both groups are connected at higher rates with their own SES group than what would be at random given actual group shares at the university (Figure \ref{availability_lses}).
@@
 We identify selection into academic programs as a key mechanism.
-The private university where our study takes place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
+The private university where our study took place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
 These result in programs with very large cost differences within the same university (Figure \ref{fees_with_boxplot}).
-We find that average yearly fees paid increase with SES, and the high-SES share in the most expensive program at the university, medicine, drives the network segregation across SES (Figure \ref{ses_distribution_by_fees}).
+We find that average yearly fee paid per student increases with SES, and the high-SES share in the most expensive program at the university, medicine, drives the network segregation across SES (Figure \ref{ses_distribution_by_fees}).
 
@@
 considering the net average monthly wage stands at \$350 and minimum legal wage is at \$200 in 2025}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Participant network size and tie strength by time spent at UNAB}\label{school_quality_income}
+  \includegraphics[width=0.6\linewidth]{../figures/school_quality_income.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average number of connections for referrers in blue and the average number of classes they have taken together with their connections in green across semesters spent at UNAB.
+The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
+Figure reproduced from \citep{fergusson2021distincion}
+  \end{tablenotes}
 \end{figure}

### 2025-06-04 writing/manuscript.tex
draft 3 intro lit rev

@@
 A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
-In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.
-\textcolor{red}{fill in citaiton sociology reading from slides}}
+In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.}
 
@@
 
-Yet, experimental evidence shows referrals can be biased under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
+Yet, experimental evidence shows referrals can be biased even under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
 A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we should expect referral hiring to further disadvantagee low-SES.
@@
 As our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
-Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action.
-This eliminates reputational concerns as there is no firm (see for example \citet{witte2021workers,bandiera2009social}).
-At the same time, national university entry exam scores are still objective, widely accepted measures of ability, and we show evidence that referrers in our setting possess accurate information about these signals.
+Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action and without revealing the identity of the referrer.
+This eliminates reputational concerns as there is no hiring firm, and puts a lower bound on the expected reciprocity for the referrer in combination with pay-for-performance incentives \citep{witte2021workers,bandiera2009social}.
+At the same time, referring based on university entry exam scores are still an objective, widely accepted measure of ability, and we show evidence that referrers in our setting not only possess accurate information about these signals but are also able to screen more productive individuals from their university network.
 
 In a university setting, class attendance provides essential opportunities for face-to-face interaction between students.
-On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.
-On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
+On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, account for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citet{fergusson2021desigualdad}.} On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
 Our setting is ideal to study these opposing forces: First, The very high level of income inequality and existence of deeply rooted historical groups in Colombia makes SES differences extremely visible in access to tertiary education, where the rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
-Yet, thanks to the particular standing of the institution we have chosen for this study (Figure \ref{school_quality_income}), different SES groups including both low- and high-SES mix together in this university.
+Yet, thanks to the particular standing of the institution we have chosen for this study (Figure \ref{school_quality_income}), all SES groups including both low- and high-SES mix together in this university.
+Second, using administrative data, we are able to reconstruct 734 participants' complete university network based on the number of common courses they have taken together with other students.
+This allows directly identifying the individual characteristics of those getting referrals among all possible candidates, as well as descriptive characterizations of similarity (e.g., in same-SES share) in student networks as a function of the number of classes taken.
 
@@
 Do segregated networks account for all the differences in SES referral rates across SES groups?
-Same-SES referrals are 17\% more common than is suggested by referrer networks.
-High- and low-SES referrers under refer each other by 50\%.
-Yet, controlling for networks, our results suggest only low-SES students show significant same-SES homophily in referrals.
-Regardless of SES, referrals identify highly able individuals, and are characterized by a very high number of courses taken together.
-The latter underlies the impact of program selection in referrals, where the smaller and more homogenous choice sets come into play.
+Although same-SES referrals are 17\% more common than is suggested by referrer networks, controlling for these, we find no general SES-bias against beyond what is attribuable to network composition.
+Regardless of SES, participants refer productive individuals, and referred candidates are characterized by a very high number of courses taken together.
+The latter underlies the impact of program selection, where smaller and more homogenous parts of the networks are activated for referrals made in our setting.
 Our treatment randomized participants across two different incentive schemes by adding a substantial monetary bonus (\$25) for the referred candidate on top of the pay-for-performance incentives.
@@
 
-This paper extends various the literature
+This paper contributes to the literature on referral experiments by solving the challenge of observing the entire referral network.
+Earlier research could only make observe referrals made across different incentive structures or experimental instructions and make according conclusions.
+For example, when participants are paid on the basis of their referred candidate's productivity instead of receiving a fixed finder's fee \citep{beaman_who_2012}, or when participants are restrictred to refer either a male or female candidate instead of freely \citep{beaman_job_2018}.
+\citet{pallais_why_2016} recruited a random sample of nonreferred workers to compare with referred ones, but none of the previous studies could provide a direct comparison of the referral choice set with those who were selected by participants.
+Closest to our work is the work of \citet{hederos2025gender}, who elicited friendship networks by asking referrers to name 5 friends.
+Their findings suggest only half of those who were referred were from the elicited friendship network, and thus is not a complete observation of the referral choice set.
+Although commonplace, censored elicitation methods also result in underestimating network effects \citep{griffith2022jle} and may suffer from biases in recall.
+We are able to take our analysis one step further by asking for referrals from the enrollment network, where we have complete information on every single connection that may or may not get a referral.
+This allows us to neatly separate the effect of the network composition from any potential biases stemming from the referral procedure itself.
+
+ Second, we contribute to the earlier work on SES-biases in referrals.
+To our knowledge, \citet{diaz_peer_2025} are the first to study SES-biases in referals.
+Drawing from a similar sample from the same institution, they focus on referrals from first year students made within mixed-program classrooms, and find no evidence for an aggregate bias against low-SES.
+We also find no aggregate bias against low-SES in referrals.
+Our setup differs as we sample from students who completed their first year and impose no limits on referring from a classroom.
+This has several implications: We find that referrals in our setup go to individuals within the same program, and that programs have different SES-shares which become more even more accentuated as students take more courses together.
+While networks in our sample drive inequality in referral outcomes because of the institional environment, we have no reason to believe networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
+
+Finally, we contribute to the growing literature on SES differences in the labor market, expliciting the role of networks as a driver of inequality.
+\citet{stansbury2024class} find that low-SES researchers coauthor more often with other low-SES, and have networks that have lower values which can explain why
 

### 2025-06-05 writing/manuscript.tex
draft 4 update

@@
 
-\title{Project ICFES:
-Evidence from a referral field experiment\footnote{We obtained Institutional Review Board approvals from NYU Abu Dhabi (HRPP 2024-50) and the University of Luxembourg (ERP 24–028).
-The study design was preregistered in the OSF Registries prior to data collection (see \url{https://doi.org/10.17605/OSF.IO/V9T3W}).} }
+\title{Class differences in social networks: Evidence from a referral experiment}
 % \\ \large Experimental Design \\
@@
 In a university setting, class attendance provides essential opportunities for face-to-face interaction between students.
-On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, account for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citet{fergusson2021desigualdad}.} On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
+On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, accounting for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citet{fergusson2021desigualdad}.} On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
 Our setting is ideal to study these opposing forces: First, The very high level of income inequality and existence of deeply rooted historical groups in Colombia makes SES differences extremely visible in access to tertiary education, where the rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
@@
 This paper contributes to the literature on referral experiments by solving the challenge of observing the entire referral network.
-Earlier research could only make observe referrals made across different incentive structures or experimental instructions and make according conclusions.
+Earlier research could only compare referrals made across different incentive structures or experimental instructions and make according conclusions.
 For example, when participants are paid on the basis of their referred candidate's productivity instead of receiving a fixed finder's fee \citep{beaman_who_2012}, or when participants are restrictred to refer either a male or female candidate instead of freely \citep{beaman_job_2018}.
@@
 
- Second, we contribute to the earlier work on SES-biases in referrals.
-To our knowledge, \citet{diaz_peer_2025} are the first to study SES-biases in referals.
-Drawing from a similar sample from the same institution, they focus on referrals from first year students made within mixed-program classrooms, and find no evidence for an aggregate bias against low-SES.
+Second, we build upon to the earlier work on SES-biases in referrals.
+To our knowledge, the first to study SES-biases in referals are \citet{diaz_peer_2025}, and our study is conceptually the closest to theirs.
+Drawing from a similar sample from the same institution, \citet{diaz_peer_2025} focus on referrals from first year students made within mixed-program classrooms, and find no evidence for an aggregate bias against low-SES.
 We also find no aggregate bias against low-SES in referrals.
@@
 This has several implications: We find that referrals in our setup go to individuals within the same program, and that programs have different SES-shares which become more even more accentuated as students take more courses together.
-While networks in our sample drive inequality in referral outcomes because of the institional environment, we have no reason to believe networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
+While networks drive inequality in referral outcomes because of the institional environment in our sample, we have no reason to believe first year student networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
+Following the recent evidence, implementing more mixed-program courses which allow for across-SES mixing can be a clear policy goal \citep{alan2023troeasa,rohrer2021po}.
 
@@
 The remainder of the paper is organized as follows.
-Section 2 begins with the background and setting in Colombia.
-In Section 3 we present the design of the experiment.
-In Section 4 we describe the data and procedures.
-Section 5 discusses the results of the experiment.
-Section 6 concludes.
+Section \ref{s2} begins with the background and setting in Colombia.
+In Section \ref{s3} we present the design of the experiment.
+In Section \ref{s4} we describe the data and procedures.
+Section \ref{s5} discusses the results of the experiment.
+Section \ref{s6} concludes.
 The Appendix presents additional tables and figures as well as the experiment instructions.
@@
   \centering
-  \caption{Effect of the Bonus on Referrals}
+  \caption{Networks of SES groups and same-SES segregation}
   \begin{subfigure}[t]{0.49\textwidth}
@@
       \includegraphics[width=\linewidth]{../figures/availability_lses.png}
-      \caption{Reading}  
+      \caption{SES networks}  
       \label{availability_lses}
@@
       \includegraphics[width=\linewidth]{../figures/share_same_ses_by_tie.png}
-      \caption{Math}
+      \caption{Same-SES share}
       \label{share_same_ses_by_tie}
   \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
-The bottom panel shows the average standardized math and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
-For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
+  \caption*{\footnotesize\textit{Note:} The left panel compares the network shares of SES groups in the networks of low-, middle-, and high-SES.
+Horizontal lines plot the university-wide shares of each SES group.
+While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
+The right panel shows the average share of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
+Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.}
 \end{figure}
@@
   \centering
-  \caption{Effect of the Bonus on Referrals}
+  \caption{Network characteristics and courses taken together}
   \begin{subfigure}[t]{0.49\textwidth}
@@
       \includegraphics[width=\linewidth]{../figures/share_same_program_by_tie.png}
-      \caption{Reading}  
+      \caption{Same-program share}  
       \label{share_same_program_by_tie}
@@
       \includegraphics[width=\linewidth]{../figures/conns_by_tie.png}
-      \caption{Math}
+      \caption{Network size}
       \label{conns_by_tie}
   \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
-The bottom panel shows the average standardized math and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
-For both math and reading, treatment causes no significant changes in referral performance or tie strength.
-considering the net average monthly wage stands at \$350 and minimum legal wage is at \$200 in 2025}
+  \caption*{\footnotesize\textit{Note:} The left panel illustrates the share of connections within the same program as a function of the number of courses taken together.
+The right panel shows the average network size as a function of the number of courses taken together.
+Taking more than 5 courses together with a network member means on average 90\% chance to be in the same program.
+Similarly, past 5 courses together, the average network size dwindles by 80\%, from more than 220 individuals to below 50.
+  }
 \end{figure}
@@
   \centering
-  \caption{Effect of the Bonus on Referrals}
+  \caption{University programs by yearly fee and SES distribution}
   \begin{subfigure}[t]{0.49\textwidth}
@@
       \includegraphics[width=\linewidth]{../figures/fees_with_boxplot.png}
-      \caption{Reading}  
+      \caption{Programs sorted by fee}  
       \label{fees_with_boxplot}
@@
       \includegraphics[width=\linewidth]{../figures/ses_distribution_by_fees.png}
-      \caption{Math}
+      \caption{SES distribution by program fee}
       \label{ses_distribution_by_fees}
   \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
-The bottom panel shows the average standardized math and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
-For both math and reading, treatment causes no significant changes in referral performance or tie strength.
-considering the net average monthly wage stands at \$350 and minimum legal wage is at \$200 in 2025}
+  \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of programs at the university by their average yearly fee.
+The right panel illustrates the distribution of each SES group across programs sorted by fee.
+As of 2025 net average monthly wage is around \$350 and the minimum legal wage is at \$200.
+The average yearly fee of programs stands at \$3000, and medicine is an extreme outlier at \$6000.
+Distributions of SES groups across programs show the majority of low-SES select into programs with below average cost, while high-SES select into programs with above average cost.
+Medicine accounts for a third of all high-SES students at this university.}
 \end{figure}
@@
   \centering
-  \caption{Participant network size and tie strength by time spent at UNAB}\label{school_quality_income}
+  \caption{Income, performance, and university choice in Colombia}\label{school_quality_income}
   \includegraphics[width=0.6\linewidth]{../figures/school_quality_income.png}
@@
     \footnotesize
-    \item[] \textit{Note:} This figure displays the average number of connections for referrers in blue and the average number of classes they have taken together with their connections in green across semesters spent at UNAB.
-The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
-Figure reproduced from \citep{fergusson2021distincion}
+    \item[] \textit{Note:} This figure shows the average score national university entry exam by family income and type of higher education instition.
+With average student score in the 65-70 band, the private university where we conducted this experiment caters to low- and high-SES students.
+Figure reproduced from \citet{fergusson2021distincion}.
   \end{tablenotes}
@@
 
+Our study takes place at UNAB, a medium-sized private university in Bucaramanga, Colombia with approximately 6,000 enrolled students.
+The university's student body is remarkably diverse with about 35\% of the students classified as low-SES, and 15\% high-SES.
+Diversity at this institution provides a unique research setting as Colombian society is highly unequal and generally characterized by limited interaction between social classes, with different socioeconomic groups separated by education and geographic residence.\footnote{Colombia has consistently ranked as one of the most unequal countries in Latin America \citep{barretoherrera2024regional}, with the richest decile earning 50 times more than the poorest decile \citep{comisioneconomicaparaamericalatinayel2023}.
+This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
+103]{hudson_colombia_2010}, with UNAB representing one of the few environments where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
+
+In 1994, Colombia introduced a nationwide classification system dividing the population into 6 strata based on housing characteristics and neighborhood amenities.\footnote{Initially designed for utility subsidies from higher strata (5 and 6) to support lower strata (1 to 3), it now extends to university fees and social program eligibility.
+Stratum 4 neither receives subsidies nor pays extra taxes.
+This stratification system largely aligns with and potentially reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.} We use this classification as the measure of SES in our experiment: Students in strata 1 to 2 are categorized as low-SES, strata 3 to 4 as middle-SES and those in strata 5 to 6 as high-SES.
+
+We invited via email all 4,417 UNAB students who had at the time of recruitment completed their first year at the university to participate in our experiment.
+837 students who joined (19\%) display large variations in terms of their academic programs and SES.
+This setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are casually documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
+
 \section{Design} \label{s3}
+
+\section{Sample, Incentives, and Procedure} \label{s4}
 
@@
 
-  \begin{figure}[H]
-    \centering
-    \caption{Participant network performance by subject and SES}\label{performance}
-    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
-    \begin{tablenotes}
-      \footnotesize
-      \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES.
+  % \begin{figure}[H]
+  %   \centering
+  %   \caption{Participant network performance by subject and SES}\label{performance}
+  %   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
+  %   \begin{tablenotes}
+  %     \footnotesize
+  %     \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES.
 We test differences between scores across SES using paired $t$-tests.
 For both math and reading scores, all differences between SES groups are statistically significant (all $p \leq 0.001$).
-    \end{tablenotes}
-  \end{figure}
+  %   \end{tablenotes}
+  % \end{figure}
 
@@
 
-  \begin{figure}[H]
-    \centering
-    \caption{Participant network composition by SES}
-    \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
-    \label{fig:baseline_ses}
-    \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES.
+%   \begin{figure}[H]
+%     \centering
+%     \caption{Participant network composition by SES}
+%     \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
+%     \label{fig:baseline_ses}
+%     \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES.
 We test differences in proportions of peer connections across SES groups using two-sample tests of proportions.
 All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections.
-    }
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Participant network composition by SES}
-  \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
-  \label{fig:tie_ses}
-  \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
+%     }
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Participant network composition by SES}
+%   \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
+%   \label{fig:tie_ses}
+%   \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
 We test differences in standardized tie strength across SES groups using two-sample $t$-tests.
@@
 The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.}
-\end{figure}
+% \end{figure}
 
@@
 
-  \begin{figure}[H]
-    \centering
-    \caption{Baseline Referral Patterns by SES}
-    \begin{subfigure}[t]{0.49\textwidth}
-      \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_referral_distribution.png}
-        \caption{Referral Rates}  
-        \label{fig:baseline_rates}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{0.49\textwidth}
-      \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
-        \caption{Referral Performance}
-        \label{fig:baseline_performance}
-    \end{subfigure}
-    \label{fig:baseline_combined}
-    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across SES in the baseline condition.
+  % \begin{figure}[H]
+  %   \centering
+  %   \caption{Baseline Referral Patterns by SES}
+  %   \begin{subfigure}[t]{0.49\textwidth}
+  %     \centering
+  %       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_referral_distribution.png}
+  %       \caption{Referral Rates}  
+  %       \label{fig:baseline_rates}
+  %   \end{subfigure}
+  %   \hfill
+  %   \begin{subfigure}[t]{0.49\textwidth}
+  %     \centering
+  %       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
+  %       \caption{Referral Performance}
+  %       \label{fig:baseline_performance}
+  %   \end{subfigure}
+  %   \label{fig:baseline_combined}
+  %   \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across SES in the baseline condition.
 We test differences in SES shares across SES groups using two-sample tests of proportions.
@@
 For math scores, we observe marginally significant differences between Low and High SES students ($p = 0.08$) and between Middle and High SES students ($p = 0.18$), with High SES referring peers with higher math performance.}
-  \end{figure}
-
-  \begin{figure}[H]
-    \centering
-    \caption{Effect of the Bonus}
-    \label{fig:treat_combined}
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
-        \caption{Changes in Referral Rates}
-        \label{fig:treat_rates}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
-        \caption{Changes in Referral Performance}
-        \label{fig:treat_performance}
-    \end{subfigure}
-    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across SES.
+  % \end{figure}
+
+%   \begin{figure}[H]
+%     \centering
+%     \caption{Effect of the Bonus}
+%     \label{fig:treat_combined}
+%     \begin{subfigure}[t]{0.49\textwidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
+%         \caption{Changes in Referral Rates}
+%         \label{fig:treat_rates}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[t]{0.49\textwidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
+%         \caption{Changes in Referral Performance}
+%         \label{fig:treat_performance}
+%     \end{subfigure}
+%     \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across SES.
 We test differences in SES shares across conditions using two-sample tests of proportions.
@@
 For both reading and math scores, the only statistically significant difference is in the reading scores for Low-SES ($p = 0.026$).}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Effect of the Bonus on Tie Strength}
-  \label{fig:treat_combined2}
-  \begin{subfigure}[t]{0.49\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
-      \caption{Changes in Referral Rates}
-      \label{fig:tietreat_rates}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{0.49\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
-      \caption{Changes in Referral Performance}
-      \label{fig:tietreat_performance}
-  \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Effect of the Bonus on Tie Strength}
+%   \label{fig:treat_combined2}
+%   \begin{subfigure}[t]{0.49\textwidth}
+%       \centering
+%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
+%       \caption{Changes in Referral Rates}
+%       \label{fig:tietreat_rates}
+%   \end{subfigure}
+%   \hfill
+%   \begin{subfigure}[t]{0.49\textwidth}
+%       \centering
+%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
+%       \caption{Changes in Referral Performance}
+%       \label{fig:tietreat_performance}
+%   \end{subfigure}
+%   \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
 The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Performance by Tie Strength and SES}
-  \includegraphics[width=0.85\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/tie_combined.png}
-  \label{fig:tie_score_ses}
-  \caption*{\footnotesize\textit{Note:} This figure shows local polynomial regressions of network math and reading z-scores by social tie strength across socioeconomic status groups with 95\% confidence intervals.
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Performance by Tie Strength and SES}
+%   \includegraphics[width=0.85\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/tie_combined.png}
+%   \label{fig:tie_score_ses}
+%   \caption*{\footnotesize\textit{Note:} This figure shows local polynomial regressions of network math and reading z-scores by social tie strength across socioeconomic status groups with 95\% confidence intervals.
 Higher SES have steeper positive relationships between tie strength and the average performance those in their network across reading and math scores.}
-\end{figure}
+% \end{figure}
 

### 2025-06-06 writing/manuscript.tex
draft update 5
design, sample, procedure

@@
 \section{Introduction}
-Equally qualified individuals may face very different labor market outcomes depending on their socioeconomic status \citep{stansbury2024class}.
-A key driver of this inequality is due to differences in social capital,\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} with recent empirical work characterizing its most important facet as the “share of high-SES friends among individuals with low-SES” as it correlates strongly with labor market income \citep{chetty2022na}.
-A lack of social capital means a lack of access to individuals with influential (higher paid) jobs and job opportunities.
+Equally qualified individuals face different labor market outcomes depending on their socioeconomic status \citep{stansbury2024class}.
+A key driver of this inequality is due to differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Because it correlates strongly with labor market income, the most important facet of social capital is the share of high-SES connections among low-SES individuals \citep{chetty2022na}.
+A lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.
 In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.}
@@
 Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a common labor market practice which makes evident the role of differences in social capital.
-As referrals must orginate from the networks of referrers, the composition of referrer networks becomes a crucial channel that may propagate inequality: Similar individuals across socio-demographic characteristics tend to form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
+As referrals originate from the networks of referrers, the composition of referrer networks becomes a crucial channel that propagates inequality: Similar individuals across socio-demographic characteristics form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
 Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
@@
 A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we should expect referral hiring to further disadvantagee low-SES.
-The empirical question we answer is whether there is a bias against low-SES once we account for the network SES compositon in a controlled setting.
+
+The empirical question we answer in this paper is whether referrers are biased against low-SES peers after accounting for differences in the network SES compositon.
+We also evaluate the causal impact of two different incentive structures on referral behavior.
 
@@
 This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
-103]{hudson_colombia_2010}, with UNAB representing one of the few environments where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
+103]{hudson_colombia_2010}, and UNAB represents one of the few environments where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
 
@@
 We invited via email all 4,417 UNAB students who had at the time of recruitment completed their first year at the university to participate in our experiment.
-837 students who joined (19\%) display large variations in terms of their academic programs and SES.
+837 students who joined (19\%) vary in terms of their academic programs, SES, and progress in their studies.
 This setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are casually documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
@@
 
-\section{Sample, Incentives, and Procedure} \label{s4}
-
-\section{Results} \label{s5}
-
-\subsection{Descriptives}
-
-\begin{table}[H]
+We designed an experiment to assess peer referral behavior from an SES perspective and to causally evaluate the effect of different incentive structures on referrals.
+The study design consists of a single online experiment organized at the university level (see Figure \ref{timeline}).
+The instructions are provided in Appendix \ref{instructions}.
+
+\begin{figure}[H]
+\centering
+\caption{Experiment Timeline}\label{timeline}
+\includegraphics[width=\linewidth]{../figures/timeline.jpg}
+\begin{tablenotes}
+\footnotesize
+\item[] \textit{Note:} Participants first report beliefs about their own national university entry exam performance, then recommend peers for each academic area.
+In the final part, they report beliefs about their recommendations' performance and provide demographic information.
+This order is implemented for all participants.
+\end{tablenotes}
+\end{figure}
+
+\subsection{Productivity measures}
+To establish an objective basis for referral productivity, we use national university entry exam scores (SABER 11).
+These scores provide pre-existing, comparable measures of ability across two domains relevant for the labor market.
+By using existing administrative data, we eliminate the need for additional testing and ensure that all eligible students have comparable productivity measures.
+The scores we use in this experiment comprise of critical reading and mathematics parts.
+
+Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history).
+This measures students' ability to comprehend and critically evaluate written material.
+Mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
+This captures quantitative reasoning and problem-solving abilities.
+
+For each area, we calculate percentile rankings based on the distribution of scores among all currently enrolled UNAB students, providing a standardized measure of relative performance within the university population.
+
+\subsection{Referral task}
+After eliciting beliefs about their own performance, participants engage in incentivized peer recommendations.
+For both test areas (critical reading and mathematics), participants recommend one peer they believe excels in that domain.
+We first present an example question from the relevant test area to clarify what skills are being assessed.
+Participants then type the name of their recommended peer, with the system providing autocomplete suggestions from enrolled students who have taken the test (see Figure \ref{interface}).
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral task interface}\label{interface}
+  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/interface.png}
+  \begin{tablenotes} 
+    \footnotesize
+    \item[] \textit{Note:} This illustration shows how the system provides suggestions from enrolled students with their program and year of study from the administrative database.
+  \end{tablenotes}
+\end{figure}
+
+Participants can only recommend students with whom they have taken at least one class during their university studies.
+This requirement ensures that referrals are based on actual peer interactions and overlap with the enrollment network that we construct.
+The order in which participants make recommendations across the two areas is randomized.
+
+We incentivize referrals using a productivity-based payment scheme.
+Referrers earn increasing monetary rewards as the percentile ranking of their recommendation increases (see Figure \ref{piece_rate_by_score}).
+We multiply the piece rate coefficient associated to the percentile rank with the actual test scores of the recommendation to calculate earnings.
+This payment structure provides strong incentives to screen for highly ranked peers, with potential earnings up to \$60 per recommendation.\footnote{Due to the selection into the university, the actual test score distribution has limited variance.
+Below a certain threshold students cannot qualify for the institution and choose a lower ranked university, and above a certain threshold they have better options to choose from.}
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral incentives}\label{piece_rate_by_score}
+  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/piece_rate_by_score.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure shows how the piece rate coefficient increases as a function of the referral ranking in the university, providing incrementally higher rewards for higher ranked peers.
+  \end{tablenotes}
+\end{figure}
+
+\subsection{Treatment variation}
+We implement a between-subjects treatment that varies whether the recommended peer also receives payment.
+In the \textbf{Baseline} treatment, only the referrer can earn money based on their recommendation's productivity.
+The \textbf{Bonus} treatment adds an additional fixed payment of \$25 to any peer who is recommended in the randomly selected area for payment.
+This payment is independent of the peer's actual productivity (see Figure \ref{tab:treatments}).
+
+\begin{table}[htbp]
   \centering
   \begin{threeparttable}
-  \caption{Selection into the experiment}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
+  \caption{Payment structure by treatment}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l c c @{}}
   \toprule
-  & \multicolumn{1}{c}{\textbf{Admin Data}} & \multicolumn{1}{c}{\textbf{Sample}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\
+  & \multicolumn{1}{c}{\textbf{Baseline}} & \multicolumn{1}{c}{\textbf{Bonus}} \\
   \midrule
-  Reading score & 62.651 & 65.183 & 0.000 \\
-  Math score & 63.973 & 67.477 & 0.000 \\
-  GPA & 3.958 & 4.012 & 0.000 \\
-  Low-SES & 0.343 & 0.410 & 0.000 \\
-  Med-SES & 0.505 & 0.499 & 0.763 \\
-  High-SES & 0.153 & 0.091 & 0.000 \\
-  Female & 0.567 & 0.530 & 0.060 \\
-  Age & 21.154 & 20.651 & 0.000 \\
-  \midrule
-  Observations & 4,417 & 734 & 5,151 \\
+  Referrer (sender) & Productivity-based & Productivity-based \\
+  Recommendation (receiver) & No payment  & Fixed reward  \\
   \bottomrule
   \end{tabular*}
-  \begin{tablenotes}[flushleft]
-  \footnotesize
-  \item[] \textit{Note:} This table compares characteristics between the full administrative sample and the experimental sample.
-$p$-values for binary outcomes (Low-SES, Med-SES, High-SES, Female) are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
-All reported \textit{p}-values are two-tailed.
-  \end{tablenotes}
-  \label{tab:selection}
+  \label{tab:treatments}
   \end{threeparttable}
 \end{table}
+
+Participants are informed about their treatment condition before making recommendations through both video and text instructions.
+The treatment is assigned at the individual level, allowing us to compare referral outcomes across conditions.
+
+\subsection{Belief elicitation}
+We elicit incentivized beliefs at two points in the experiment.
+First, before making referrals, participants report their beliefs about their own percentile ranking in each test area.
+Second, after making each referral, participants report their beliefs about their recommendedation's percentile ranking.
+For both belief elicitation tasks, participants earn \$5 if their guess is within 7 percentiles of the true value.
+This tolerance level is expected to balance precision with the difficulty of the task.
+
+% participants report the closeness of their relationship with each recommended peer on a 0-10 scale.
+This allows us to examine whether social proximity influences referral decisions and accuracy.
+.
+Finally, participants estimate the distribution of university students across these SES groups, providing insight into their perceptions of the university-wide SES distribution.
+
+\section{Sample, Incentives, and Procedure} \label{s4}
+We invited all 4,417 UNAB students who had at the time of recruitment completed their first year at the university to participate in our experiment.
+A total of 837 students took part in the data collection with a 19\% response rate.
+Our final sample consists of 734 individuals who referred peers with whom they have taken at least one class together, resulting in an 88\% success rate for the sample.
+We randomly allocated half of the participants into either \textbf{Baseline} or \textbf{Bonus} treatments.
+Table \ref{tab:balance} presents key demographic characteristics and academic performance indicators across treatments (see Appendix Table \ref{tab:selection} for selection).
+The sample is well-balanced between the \textbf{Baseline} and \textbf{Quota} conditions and we observe no statistically significant differences in any of the reported variables (all \textit{p} values $> 0.1$).
+Our sample is characterized by a majority of middle-SES students with about one-tenth of the sample being high-SES students.
+The test scores and GPA distributions are balanced.
+Participants have taken on average 3.8 courses together with their connections and the average network consists of 175 peers.
 
@@
   GPA & 4.003 & 4.021 & \multicolumn{1}{c}{0.445} \\
-  \# connections & 173.40 & 176.88 & \multicolumn{1}{c}{0.574} \\
-  Tie strength & 3.939 & 3.719 & \multicolumn{1}{c}{0.443} \\
+  Connections & 173.40 & 176.88 & \multicolumn{1}{c}{0.574} \\
+  Courses taken & 3.939 & 3.719 & \multicolumn{1}{c}{0.443} \\
   Low-SES & 0.419 & 0.401 & \multicolumn{1}{c}{0.615} \\
@@
   High-SES & 0.089 & 0.094 & \multicolumn{1}{c}{0.824} \\
-  Female & 0.529 & 0.531 & \multicolumn{1}{c}{0.947} \\
-  Age & 20.576 & 20.733 & \multicolumn{1}{c}{0.380} \\
   \midrule
-  Observations & 382 & 352 & 734 \\
+  N & 382 & 352 & 734 \\
   \bottomrule
@@
 All reported \textit{p}-values are two-tailed.
-Tie strength refers to the number of classes taken together.
-\# connections refers to the number of indiviuduals in referrer choice sets, otherwise called the ``network degree''.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
+Reading and math scores are in original scale units out of 100.
+GPA is grade point average out of 5.
+Connections refers to the average number of network members.
+Low-SES, Med-SES, and High-SES indicate SES categories based on strata.
   \end{tablenotes}
@@
 \end{table}
+
+The experiment was conducted online through Qualtrics, with participants recruited from active UNAB students who have SABER 11 scores in the administrative records.
+To manage budget constraints while maintaining sufficient incentives, we randomly selected one in ten participants for payment.
+Selected participants received a fixed payment of \$17 for completion, plus potential earnings from one randomly selected belief question (up to \$5) and one randomly selected recommendation question (up to \$60), for maximum total earnings of \$82.
+The random selection of payment part ensured that participants had incentives to exert effort across all tasks rather than focusing on a single part.
+Payment processing occured through online banking platform Nequi within 15 business days of participation.
+
+\textcolor{cyan}{Data collection occurred during the last two weeks of April 2024.
+Our local partner at UNAB coordinated scheduled classroom visits and recruited research assistants to administer the experiment.
+Students present in class on the scheduled visit dates participated.
+Each classroom visit constituted a separate session.
+There were in total 35 sessions.
+Participants accessed the Qualtrics-based experiment using their smartphones during these visits.
+The median time to complete the survey was 20 minutes, with a compensation of \$26 for 117 lottery winners.}
+
+\section{Results} \label{s5}
+
+\subsection{Descriptives}
 
@@
 
-\subsection{Additional Figures}
+\subsection*{Additional Figures}
+\pagebreak
+\subsection*{Additional Tables}
+\renewcommand{\thetable}{A.\arabic{table}}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Selection into the experiment}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{University}} & \multicolumn{1}{c}{\textbf{Sample}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\
+  \midrule
+  Reading score & 62.651 & 65.183 & 0.000 \\
+  Math score & 63.973 & 67.477 & 0.000 \\
+  GPA & 3.958 & 4.012 & 0.000 \\
+  Low-SES & 0.343 & 0.410 & 0.000 \\
+  Med-SES & 0.505 & 0.499 & 0.763 \\
+  High-SES & 0.153 & 0.091 & 0.000 \\
+  Female & 0.567 & 0.530 & 0.060 \\
+  Age & 21.154 & 20.651 & 0.000 \\
+  \midrule
+  Observations & 4,417 & 734 & 5,151 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares characteristics between the university and the experimental sample.
+$p$-values for binary outcomes (Low-SES, Med-SES, High-SES, Female) are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+All reported \textit{p}-values are two-tailed.
+  \end{tablenotes}
+  \label{tab:selection}
+  \end{threeparttable}
+\end{table}
 

### 2025-06-10 writing/manuscript.tex
draft progress - results

@@
   \centering
-  \caption{Networks of SES groups and same-SES segregation}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/availability_lses.png}
-      \caption{SES networks}  
-      \label{availability_lses}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/share_same_ses_by_tie.png}
-      \caption{Same-SES share}
-      \label{share_same_ses_by_tie}
-  \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The left panel compares the network shares of SES groups in the networks of low-, middle-, and high-SES.
-Horizontal lines plot the university-wide shares of each SES group.
-While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
-The right panel shows the average share of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
-Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \caption{Network characteristics and courses taken together}
@@
 This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
-103]{hudson_colombia_2010}, and UNAB represents one of the few environments where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
+103]{hudson_colombia_2010}, and UNAB represents one of the few environments in Colombia where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
 
@@
 
-We invited via email all 4,417 UNAB students who had at the time of recruitment completed their first year at the university to participate in our experiment.
+We invited via email all 4,417 UNAB undergraduate students who had at the time of recruitment completed their first year at the university to participate in our experiment.
 837 students who joined (19\%) vary in terms of their academic programs, SES, and progress in their studies.
 This setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are casually documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
+
+Undergraduate programs at UNAB are spread across two semesters, with each individual course lasting one semester.
+Students take between 5 to 7 courses per semester, with programs lasting anywhere between 4 to 12 semesters (2 to 6 years).
+Medicine, the largest program by size at UNAB, lasts for 12 semesters, followed by engineering programs at 10 semesters.
+Most remaining programs lasting for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4.
 
@@
   \begin{threeparttable}
-  \caption{Payment structure by treatment}
+  \caption{Incentive structure by treatment}
   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l c c @{}}
@@
 Table \ref{tab:balance} presents key demographic characteristics and academic performance indicators across treatments (see Appendix Table \ref{tab:selection} for selection).
-The sample is well-balanced between the \textbf{Baseline} and \textbf{Quota} conditions and we observe no statistically significant differences in any of the reported variables (all \textit{p} values $> 0.1$).
+The sample is well-balanced between the \textbf{Baseline} and \textbf{Bonus} conditions and we observe no statistically significant differences in any of the reported variables (all \textit{p} values $> 0.1$).
 Our sample is characterized by a majority of middle-SES students with about one-tenth of the sample being high-SES students.
 The test scores and GPA distributions are balanced.
-Participants have taken on average 3.8 courses together with their connections and the average network consists of 175 peers.
+On average, participants took 3.8 courses together with their network, and the average network consisted of 175 peers.
 
@@
 
-\subsection{Descriptives}
+\subsection{Network characteristics}
+We begin by describing the characteristic features of the ``enrollment network'' for all participants.
+This data set pairwise associates every participant in our sample with another university student if they have taken at least one course together at the time of the data collection.
+By doing so, we construct the entire referral choice set for participants.
+We include in this data set both the participant's and their potential candidate's individual characterics, as well as the number of common courses they have taken together.
+In Figure \ref{connections_class}, we describe the evolution of the enrollment network across the average number of network connections in network and the number of common courses taken with network members as participants progress through semesters.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by time spent at UNAB}\label{connections_class}
+  \includegraphics[width=0.6\linewidth]{../figures/connections.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average number of connections in blue and the average number of classes they have taken together with their connections in grey across semesters spent.
+The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
+  \end{tablenotes}
+\end{figure}
+
+Are enrollment networks different across SES groups?
+We look at how the number of connections (network size) and number of courses taken together (tie strength) change across SES groups in Figure \ref{connections_by_ses}.
+Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, ``denser'' networks.
+Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03, p = .003$ and $t = 2.49, p = .013$, respectively), but high-SES take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20, p < .001$).
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by time spent at UNAB}\label{connections_by_ses}
+  \includegraphics[width=0.6\linewidth]{../figures/connections_by_ses.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average number of connections and the average number of classes taken together across SES groups.
+The data shows a decrease in the number of connections with SES, and an associated increase in the number of classes taken together.
+  \end{tablenotes}
+\end{figure}
+
+What are diversity related consequences of SES-driven differences across networks?
+In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).
+Our results suggest at the network-level, SES groups form connections that mirror the overall university composition, with no significant deviations from expected proportions based on random sorting (all proportion tests have $p > 0.1$ across SES group comparisons).
+Each SES group connects with low, middle, and high SES peers at rates statistically indistinguishable from what would be expected given the demographic composition of the university.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network shares of SES groups}\label{availability_lses}
+  \includegraphics[width=0.6\linewidth]{../figures/availability_lses.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES.
+Horizontal lines plot the university-wide shares of each SES group.
+While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
+  \end{tablenotes}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by time spent at UNAB}\label{share_same_ses_by_tie}
+  \includegraphics[width=0.6\linewidth]{../figures/share_same_ses_by_tie.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average share of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
+Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.
+  \end{tablenotes}
+\end{figure}
 
@@
   \centering
-  \caption{Participant network size and tie strength by time spent at UNAB}\label{connections_class}
-  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/connection_class.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure displays the average number of connections for referrers in blue and the average number of classes they have taken together with their connections in green across semesters spent at UNAB.
-The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
-  \end{tablenotes}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \caption{Effect of the Bonus on Referrals}

### 2025-06-11 writing/manuscript.tex
draft 1 progress - results suite

@@
   \centering
-  \caption{Network characteristics and courses taken together}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/share_same_program_by_tie.png}
-      \caption{Same-program share}  
-      \label{share_same_program_by_tie}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/conns_by_tie.png}
-      \caption{Network size}
-      \label{conns_by_tie}
-  \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The left panel illustrates the share of connections within the same program as a function of the number of courses taken together.
-The right panel shows the average network size as a function of the number of courses taken together.
-Taking more than 5 courses together with a network member means on average 90\% chance to be in the same program.
-Similarly, past 5 courses together, the average network size dwindles by 80\%, from more than 220 individuals to below 50.
-  }
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{University programs by yearly fee and SES distribution}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/fees_with_boxplot.png}
-      \caption{Programs sorted by fee}  
-      \label{fees_with_boxplot}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.49\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{../figures/ses_distribution_by_fees.png}
-      \caption{SES distribution by program fee}
-      \label{ses_distribution_by_fees}
-  \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of programs at the university by their average yearly fee.
-The right panel illustrates the distribution of each SES group across programs sorted by fee.
-As of 2025 net average monthly wage is around \$350 and the minimum legal wage is at \$200.
-The average yearly fee of programs stands at \$3000, and medicine is an extreme outlier at \$6000.
-Distributions of SES groups across programs show the majority of low-SES select into programs with below average cost, while high-SES select into programs with above average cost.
-Medicine accounts for a third of all high-SES students at this university.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \caption{Income, performance, and university choice in Colombia}\label{school_quality_income}
@@
 \section{Sample, Incentives, and Procedure} \label{s4}
-We invited all 4,417 UNAB students who had at the time of recruitment completed their first year at the university to participate in our experiment.
+We invited all 4,417 UNAB undergraduate students who had at the time of recruitment completed their first year at the university to participate in our experiment.
 A total of 837 students took part in the data collection with a 19\% response rate.
@@
 
-The experiment was conducted online through Qualtrics, with participants recruited from active UNAB students who have SABER 11 scores in the administrative records.
+The experiment was conducted online through Qualtrics, with participants recruited from active UNAB students.
 To manage budget constraints while maintaining sufficient incentives, we randomly selected one in ten participants for payment.
 Selected participants received a fixed payment of \$17 for completion, plus potential earnings from one randomly selected belief question (up to \$5) and one randomly selected recommendation question (up to \$60), for maximum total earnings of \$82.
-The random selection of payment part ensured that participants had incentives to exert effort across all tasks rather than focusing on a single part.
+The average time to complete the survey was 30 minutes, with an average compensation of \$80 for one in ten participants randomly selected for payment.
 Payment processing occured through online banking platform Nequi within 15 business days of participation.
-
-\textcolor{cyan}{Data collection occurred during the last two weeks of April 2024.
-Our local partner at UNAB coordinated scheduled classroom visits and recruited research assistants to administer the experiment.
-Students present in class on the scheduled visit dates participated.
-Each classroom visit constituted a separate session.
-There were in total 35 sessions.
-Participants accessed the Qualtrics-based experiment using their smartphones during these visits.
-The median time to complete the survey was 20 minutes, with a compensation of \$26 for 117 lottery winners.}
 
@@
 
+\subsection{SES diversity in networks}
 What are diversity related consequences of SES-driven differences across networks?
@@
 
-\begin{figure}[H]
-  \centering
-  \caption{Network size and courses taken together by time spent at UNAB}\label{share_same_ses_by_tie}
+At the same time, low-SES students connect with other low-SES students at significantly higher rates than high-SES students connect with low-SES students ($z = 2.05, p = .041$), while high-SES students show a marginally significant tendency to connect more with other high-SES students than low-SES students do ($z = -1.66, p = .098$).
+All other cross-group comparisons show no significant differences (all $p > .30$).
+Taken together, while our results show some SES segregation at group level for the extremes, these are balanced out, and do not point to problematic tendencies at the network-level.
+
+So far we have looked at the entire network without considering the intensity of connections between students.
+In our network data set, this variable amounts to the number of classes taken together with peers.
+As we will see in the next section, referrals go to peers with whom participants have taken a lot of courses with \textcolor{red}{on average XX}, implying the intensity of the connection matters.
+We begin by dissecting what the intensity means in our context.
+As students take more courses together, the proportion of peers from the same academic program quickly goes beyond 95\% (see Figure \ref{share_same_program_by_tie}).
+Similarly, the average network size drops very quickly from above 210 to around 25 (see Figure \ref{conns_by_tie}).
+Both results indicate that actual referral considerations orginate from a much smaller pool of individuals from the same academic program.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network characteristics and courses taken together}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/share_same_program_by_tie.png}
+      \caption{Same-program share}  
+      \label{share_same_program_by_tie}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \centering
+      \includegraphics[width=\linewidth]{../figures/conns_by_tie.png}
+      \caption{Network size}
+      \label{conns_by_tie}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} The left panel illustrates the share of connections within the same program as a function of the number of courses taken together.
+The right panel shows the average network size as a function of the number of courses taken together.
+Taking more than 5 courses together with a network member means on average 90\% chance to be in the same program.
+Similarly, past 5 courses together, the average network size dwindles by 80\%, from more than 210 individuals to below 50.
+  }
+\end{figure}
+
+\subsection{SES diversity in networks}
+What are the diversity implications of increasing the intensity of connections between students?
+As students take more courses together with peers, the share of same-SES peers in the networks of low- and high-SES increases while the share of middle-SES declines (see Figure \ref{share_same_ses_by_tie}).
+Both increases are substantial, amounting to 50\% for high-, and 30\% for low-SES.
+Combining these with the earlier result that beyond 5 courses taken together network members are almost entirely within the same program, these suggest program selection may have strong consequences for SES diversity in our setting.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by courses taken}\label{share_same_ses_by_tie}
   \includegraphics[width=0.6\linewidth]{../figures/share_same_ses_by_tie.png}
@@
     \footnotesize
-    \item[] \textit{Note:} This figure displays the average share of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
+    \item[] \textit{Note:} This figure illustrates the shares of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
 Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.
@@
 \end{figure}
+
+\subsection{Program selection and SES diversity}
+Academic programs at this university are priced based on how much they cost, and typically less than 5\% of students receive any kind of scholarship \citep{diaz_peer_2025}.
+Based on these, we first calculate how much every program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
+Considering that net minimum montly wage stands at \$200 and the average Colombian salary around \$350, the cost difference between programs are large enough to make an impact of program selection.
+Is it the case that SES groups select into programs with financial considerations?
+
+\begin{figure}[H]
+  \centering
+  \caption{Programs sorted by fee}\label{fees_with_boxplot}
+  \includegraphics[width=0.6\linewidth]{../figures/fees_with_boxplot.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure illustrates the distribution of programs at the university by their average yearly fee.
+The average yearly fee stands at \$3000, and medicine is an outlier at \$6000.
+  \end{tablenotes}
+\end{figure}
+
+We look at how SES groups are distributed across programs to see evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
+Indeed, low-SES select into more affordable programs, followed by middle-SES.
+High-SES sort almost exclusively in above average costing programs, with a third of students selecting into medicine and creating a very skewed distribution.
+With this finding, program selection could be the reason why low- and high-SES networks tend to segregate as the number of courses taken increases.
+The next section characterizes the referrals, and we will return to the diversity implications of program selection once we understand how referrals were made.
+
+\begin{figure}[H]
+  \centering
+  \caption{Programs sorted by fee}\label{ses_distribution_by_fees}
+  \includegraphics[width=0.6\linewidth]{../figures/ses_distribution_by_fees.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure illustrates the distribution of each SES group across programs sorted by fee.
+the majority of low-SES select into programs with below average cost, while high-SES select into programs with above average cost.
+Medicine accounts for a third of all high-SES students at this university.
+  \end{tablenotes}
+\end{figure}
+
+\subsection{Characterizing referrals}
+
+We observe 1342 referrals in our final data set.
+More than 90\% of these consist from participants referring for both areas of the national entry exam, as can be seen in Table \ref{tab:referral_distribution}.
 
@@
   \toprule
-  Area & Only one referral & Both areas & Total \\
+  Area & Only one area & Both areas & Total \\
   \midrule
@@
   \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas.
-``Only one referral'' indicates individuals who made referrals exclusively in that area.
+``Only one area'' indicates individuals who made referrals exclusively for one area of the exam.
 ``Both areas'' shows individuals who made referrals in both verbal and math areas.
@@
 \end{table}
+
+What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network?
 
@@
 
+\subsection{Effect of the Bonus treatment}
+
+\subsection{SES diversity in ex post referral choice sets}
+At the median number of courses taken together for referrals, the effects of network segregation on SES diversity becomes clear (see Figure \ref{t15availability}) 
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by courses taken}\label{t15availability}
+  \includegraphics[width=0.6\linewidth]{../figures/t15availability.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure illustrates the shares of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
+Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.
+  \end{tablenotes}
+\end{figure}
+
 \begin{table}[H]

### 2025-06-16 writing/manuscript.tex
v0 - results ctd.

@@
 % \title{Skills, Inequality, and Referrals}
-\author{Manuel Munoz,\footremember{liser}{Luxembourg Institute of Socio-Economic Research} Ernesto Reuben,\footnote{Division of Social Science, New York University Abu Dhabi} \footrecall{liser} Reha Tuncer\footnote{University of Luxembourg}}
+\author{Manuel Munoz\footremember{liser}{Luxembourg Institute of Socio-Economic Research}, Ernesto Reuben\footnote{Division of Social Science, New York University Abu Dhabi} \footrecall{liser}, Reha Tuncer\footnote{University of Luxembourg}}
 % \footnote{Center for Behavioral Institutional Design at New York University Abu Dhabi} 
@@
 In our network data set, this variable amounts to the number of classes taken together with peers.
-As we will see in the next section, referrals go to peers with whom participants have taken a lot of courses with \textcolor{red}{on average XX}, implying the intensity of the connection matters.
+As we will see in the next section, referrals go to peers with whom participants have taken on average 14 courses courses with, implying the intensity of the connection matters.
 We begin by dissecting what the intensity means in our context.
 As students take more courses together, the proportion of peers from the same academic program quickly goes beyond 95\% (see Figure \ref{share_same_program_by_tie}).
-Similarly, the average network size drops very quickly from above 210 to around 25 (see Figure \ref{conns_by_tie}).
+Similarly, the average network size drops very quickly from above 210 to below 50 (see Figure \ref{conns_by_tie}).
 Both results indicate that actual referral considerations orginate from a much smaller pool of individuals from the same academic program.
@@
 Indeed, low-SES select into more affordable programs, followed by middle-SES.
-High-SES sort almost exclusively in above average costing programs, with a third of students selecting into medicine and creating a very skewed distribution.
+High-SES sort almost exclusively in above average costing programs, with a third of students selecting into medicine and creating a very skewed distribution \textcolor{red}{KS test here}.
 With this finding, program selection could be the reason why low- and high-SES networks tend to segregate as the number of courses taken increases.
-The next section characterizes the referrals, and we will return to the diversity implications of program selection once we understand how referrals were made.
+The next section characterizes the referrals, and we will return to the diversity implications of program selection once we propose an understanding of how referrals were made.
 
@@
 
-We observe 1342 referrals in our final data set.
-More than 90\% of these consist from participants referring for both areas of the national entry exam, as can be seen in Table \ref{tab:referral_distribution}.
+We observe 1342 referrals from our 734 participants in our final data set.
+More than 90\% of these consist from participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
+While each participant made one referral for Math and Reading parts of the exam, we pool these referrals in our main analysis and look at averages as there is no difference in terms of referral SES compositions between exam areas (see Appendix Table \ref{tab:referral_area}).
+
+What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network?
+Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students.
+First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
+This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties.
+While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
+The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers within same program (93\%).
+
+\begin{figure}[H]
+  \centering
+  \caption{Courses taken together with network members and referrals}\label{tie_hist}
+  \includegraphics[width=0.6\linewidth]{../figures/tie_hist.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the distributions of the number of courses taken together between referrers and their network members (orange) versus referrers and their chosen referral recipients (dark blue) for all 734 participants.
+75\% of referral recipients having taken more than 7.5 courses together with the referrer, compared to only 25\% of network members.
+The distributions are significantly different (Kolmogorov-Smirnov test $D = 33.37$, $p < 0.001$).
+  \end{tablenotes}
+\end{figure}
+
+Second, we examine entry exam score differences between referred students and the broader network.
+Referrals go to peers with an average score of 69.5 points, compared to 64.5 points for other network members (see Figure \ref{other_score_hist}).
+This difference of 5 points is significant ($t = 18.97$, $p < 0.001$), indicating that referrers choose higher-performing peers.
+While the median referral recipient scores 71.0 points, the median network member scores 65.1 points.
+The interquartile range for referrals spans from 65.5 to 75.0 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
+
+\begin{figure}[H]
+  \centering
+  \caption{Entry exam scores of network members and referrals}\label{other_score_hist}
+  \includegraphics[width=0.6\linewidth]{../figures/other_score_hist.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the distributions of entry exam scores (Math and Reading average) between referrers' network members (orange) versus their chosen referral recipients (dark blue) for all 734 participants.
+75\% of referral recipients score above 65.5 points compared to only 25\% of network members scoring above 66.9 points.
+The distributions are significantly different (Kolmogorov-Smirnov test $D = 71.16$, $p < 0.001$).
+  \end{tablenotes}
+\end{figure}
+
+Third, we examine the overall SES-compositions in referral selection.
+Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Table \ref{tab:ses_composition}).
+This over-representation of 4.3 pp.
+is marginally significant ($z = -1.70$, $p = 0.088$), suggesting a small overall tendency to favor low-SES peers.
+For middle-SES students, referrals constitute 51.0\% versus 51.4\% network representation (difference: -0.5 pp., $z = 0.17$, $p = 0.863$).
+High-SES referrals account for 11.1\% compared to 14.9\% network share, a significant under-representation of 3.8 pp.
+($z = 2.17$, $p = 0.030$).
+These findings indicate that referral selection in general modestly deviates from proportional representation, with referrers showing a slight preference for lower-SES at the expense of high-SES peers relative to their network shares.
 
@@
   \begin{threeparttable}
-  \caption{Distribution of referrals by area}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \caption{SES composition: network shares versus referral rates}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
   \toprule
-  Area & Only one area & Both areas & Total \\
+   & \multicolumn{1}{c}{\textbf{Network average}} & \multicolumn{1}{c}{\textbf{Referrals}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\ 
   \midrule
-  Verbal & 65 & 608 & 673 \\
-  Math & 61 & 608 & 669 \\
+  Low-SES & 33.7\% & 37.9\% & 0.088 \\
+  Mid-SES & 51.4\% & 51.0\% & 0.863 \\
+  High-SES & 14.9\% & 11.1\% & 0.030 \\
   \midrule
-  Total & 126 & 1,216 & 1,342 \\
+  N & 734 & 734 & \\
   \bottomrule
@@
   \footnotesize
-  \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas.
-``Only one area'' indicates individuals who made referrals exclusively for one area of the exam.
-``Both areas'' shows individuals who made referrals in both verbal and math areas.
-The majority of referrers (608) made referrals in both areas.
-  \end{tablenotes}
-  \label{tab:referral_distribution}
+  \item[] \textit{Note:} This table compares the average SES compositions of referrer enrollment networks and actual referral choices.
+$p$-values are from two-sample proportion tests.
+Network percentages represent the average SES group shares across individual networks.
+Referral percentages represent the actual SES distribution of chosen referrals.
+  \end{tablenotes}
+  \label{tab:ses_composition}
   \end{threeparttable}
@@
 
-What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network?
+\textcolor{red}{to do: 1- SES composition by SES, 2- expost choice sets 3- effect of the bonus 4- bias regression }
+
+Table \ref{tab:stats_by_nomination}
 
@@
   \begin{threeparttable}
-  \caption{Summary statistics for network members by nomination status}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
+  \caption{Summary statistics for network members by referral status}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
   \toprule
-  & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
-  \cmidrule{2-3} \cmidrule{4-5}
-  & Not Referred & Referred & Not Referred & Referred \\
+  & \multicolumn{1}{c}{\textbf{\textcolor{red}{Not Referred - to remove}}} & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
   \midrule
-  Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
-  & (0.003) & (0.039) & (0.003) & (0.040) \\
-  [1ex]
-  Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
-  & (0.003) & (0.042) & (0.003) & (0.043) \\
-  [1ex]
-  GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
-  & (0.003) & (0.041) & (0.003) & (0.041) \\
-  [1ex]
-  Tie strength z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
-  & (0.003) & (0.091) & (0.003) & (0.090) \\
-  [1ex]
-  Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
-  & (0.001) & (0.019) & (0.001) & (0.019) \\
-  [1ex]
-  Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
-  & (0.001) & (0.019) & (0.001) & (0.019) \\
-  [1ex]
-  High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
-  & (0.001) & (0.012) & (0.001) & (0.012) \\
-  % [1ex]
-  % Female & 0.524 & 0.562 & 0.520 & 0.428 \\
-  % & (0.001) & (0.019) & (0.001) & (0.019) \\
-  % [1ex]
-  % Age & 20.945 & 20.501 & 20.961 & 20.490 \\
-  % & (0.006) & (0.104) & (0.006) & (0.099) \\
+  Reading score & 64.212 & 68.044 & 67.180 & 0.063 \\
+  Math score & 66.361 & 71.119 & 70.240 & 0.143 \\
+  GPA & 3.909 & 4.158 & 4.148 & 0.583 \\
+  Tie strength & 3.162 & 14.062 & 14.236 & 0.732 \\
+  Low-SES & 0.336 & 0.366 & 0.393 & 0.304 \\
+  Med-SES & 0.514 & 0.548 & 0.468 & 0.004 \\
+  High-SES & 0.150 & 0.086 & 0.138 & 0.002 \\
   \midrule
-  Observations & 128,174 & 673 & 127,481 & 669 \\
+  Observations & 255,655 & 699 & 643 \\
   \bottomrule
@@
   \footnotesize
-  \item[] \textit{Note:} Standard errors in parentheses.
+  \item[] \textit{Note:} P-values are from two-sample t-tests with unequal variances for continuous variables and two-sample tests of proportions for binary variables, comparing Baseline Referred vs Bonus Referred groups.
+Reading and math scores are raw test scores.
+GPA is the grade point average.
+Tie strength measures the weighted frequency of contact between individuals.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
+Not Referred includes all network members who were not nominated for referral.
+Baseline Referred and Bonus Referred include only those network members who were actually nominated for referral in each treatment condition.
+  \end{tablenotes}
+  \label{tab:stats_by_nomination}
+  \end{threeparttable}
+\end{table}
+
+% \begin{table}[H]
+%   \centering
+%   \begin{threeparttable}
+%   \caption{Summary statistics for network members by referral status}
+%   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
+%   \toprule
+%   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
+%   \cmidrule{2-3} \cmidrule{4-5}
+%   & Not Referred & Referred & Not Referred & Referred \\
+%   \midrule
+%   Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
+%   & (0.003) & (0.039) & (0.003) & (0.040) \\
+%   [1ex]
+%   Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
+%   & (0.003) & (0.042) & (0.003) & (0.043) \\
+%   [1ex]
+%   GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
+%   & (0.003) & (0.041) & (0.003) & (0.041) \\
+%   [1ex]
+%   Courses taken z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
+%   & (0.003) & (0.091) & (0.003) & (0.090) \\
+%   [1ex]
+%   Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
+%   & (0.001) & (0.019) & (0.001) & (0.019) \\
+%   [1ex]
+%   Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
+%   & (0.001) & (0.019) & (0.001) & (0.019) \\
+%   [1ex]
+%   High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
+%   & (0.001) & (0.012) & (0.001) & (0.012) \\
+%   % [1ex]
+%   % Female & 0.524 & 0.562 & 0.520 & 0.428 \\
+%   % & (0.001) & (0.019) & (0.001) & (0.019) \\
+%   % [1ex]
+%   % Age & 20.945 & 20.501 & 20.961 & 20.490 \\
+%   % & (0.006) & (0.104) & (0.006) & (0.099) \\
+%   \midrule
+%   Observations & 128,174 & 673 & 127,481 & 669 \\
+%   \bottomrule
+%   \end{tabular*}
+%   \begin{tablenotes}[flushleft]
+%   \footnotesize
+%   \item[] \textit{Note:} Standard errors in parentheses.
 GPA, test scores, and tie strength are standardized at the network level.
@@
 Tie strength measures the number of connections between individuals.
-  \end{tablenotes}
-  \label{tab:stats_by_nomination}
-  \end{threeparttable}
-\end{table}
+%   \end{tablenotes}
+%   \label{tab:stats_by_nomination}
+%   \end{threeparttable}
+% \end{table}
 
@@
   \midrule
-  Observations & 4,417 & 734 & 5,151 \\
+  Observations & 4,417 & 734 &  \\
   \bottomrule
@@
   \label{tab:selection}
+  \end{threeparttable}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Distribution of referrals by area}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \toprule
+  Area & Only one area & Both areas & Total \\
+  \midrule
+  Verbal & 65 & 608 & 673 \\
+  Math & 61 & 608 & 669 \\
+  \midrule
+  Total & 126 & 1,216 & 1,342 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas.
+``Only one area'' indicates individuals who made referrals exclusively for one area of the exam.
+``Both areas'' shows individuals who made referrals in both verbal and math areas.
+The majority of referrers (608) made referrals in both areas.
+  \end{tablenotes}
+  \label{tab:referral_distribution}
+  \end{threeparttable}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Referral characteristics by academic area}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
+  \toprule
+   & \multicolumn{1}{c}{\textbf{Reading}} & \multicolumn{1}{c}{\textbf{Math}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\ 
+  \midrule
+  Reading score & 67.85 & 67.41 & 0.348 \\
+  Math score & 70.04 & 71.36 & 0.029 \\
+  Low-SES & 37\% & 38\% & 0.714 \\
+  Med-SES & 51\% & 51\% & 0.829 \\
+  High-SES & 11\% & 11\% & 0.824 \\
+  \midrule
+  N & 673 & 669 &  \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares characteristics of referred students by referrer's academic area (verbal vs.
+math).
+$p$-values are from two-sample t-tests with unequal variances.
+Math area participants refer peers with significantly higher math performance ($p = 0.029$), while no significant differences exist for reading scores or SES composition across areas.
+  \end{tablenotes}
+  \label{tab:referral_area}
   \end{threeparttable}

### 2025-06-17 writing/manuscript.tex
v0 results ctd.

@@
 What are diversity related consequences of SES-driven differences across networks?
-In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).
-Our results suggest at the network-level, SES groups form connections that mirror the overall university composition, with no significant deviations from expected proportions based on random sorting (all proportion tests have $p > 0.1$ across SES group comparisons).
-Each SES group connects with low, middle, and high SES peers at rates statistically indistinguishable from what would be expected given the demographic composition of the university.
+In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means in networks.
+However, it is important to note that these are not independent observations across the network - the reason these estimates are so precise is because most people are seemingly connected with similar others, creating systematic patterns that reduce variance.
+For this reason we choose not reporting test results in this section and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
+Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.
 
@@
     \footnotesize
-    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES.
+    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants.
 Horizontal lines plot the university-wide shares of each SES group.
@@
 
-At the same time, low-SES students connect with other low-SES students at significantly higher rates than high-SES students connect with low-SES students ($z = 2.05, p = .041$), while high-SES students show a marginally significant tendency to connect more with other high-SES students than low-SES students do ($z = -1.66, p = .098$).
-All other cross-group comparisons show no significant differences (all $p > .30$).
-Taken together, while our results show some SES segregation at group level for the extremes, these are balanced out, and do not point to problematic tendencies at the network-level.
+At the same time, we observe much larger differences between SES groups in how they connect on average with others.
+Low-SES students connect with other low-SES students at higher rates than middle-SES students (38.4\% vs 31.4\%) and high-SES students (38.4\% vs 25.1\%).
+Conversely, high-SES students connect more with other high-SES students than both low-SES students (20.4\% vs 12.6\%) and middle-SES students (20.4\% vs 15.8\%).
+Middle-SES students are in between the two extreme patterns, connecting with middle-SES peers at higher rates than low-SES students (52.9\% vs 49.0\%) but lower rates than high-SES students (52.9\% vs 54.5\%).
+These findings indicate SES-based network segregation, with same-SES homophily patterns across groups.
 
@@
 In our network data set, this variable amounts to the number of classes taken together with peers.
-As we will see in the next section, referrals go to peers with whom participants have taken on average 14 courses courses with, implying the intensity of the connection matters.
+As we will see in the next section, referrals go to peers with whom participants have taken on average 14 courses with, implying the intensity of the connection matters.
 We begin by dissecting what the intensity means in our context.
@@
 Similarly, the average network size drops very quickly from above 210 to below 50 (see Figure \ref{conns_by_tie}).
-Both results indicate that actual referral considerations orginate from a much smaller pool of individuals from the same academic program.
+Both results indicate that actual referral considerations originate from a much smaller pool of individuals from the same academic program.
 
@@
 
-\subsection{SES diversity in networks}
 What are the diversity implications of increasing the intensity of connections between students?
@@
 We look at how SES groups are distributed across programs to see evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
-Indeed, low-SES select into more affordable programs, followed by middle-SES.
-High-SES sort almost exclusively in above average costing programs, with a third of students selecting into medicine and creating a very skewed distribution \textcolor{red}{KS test here}.
+Indeed, low-SES students select into more affordable programs, followed by middle-SES students.
+High-SES students sort almost exclusively into above-average costing programs, with a third selecting into medicine and creating a very skewed distribution.
+The distributions are significantly different across all pairwise comparisons: low-SES vs.
+middle-SES (Kolmogorov-Smirnov test $D=33.89$, $p<0.001$), low-SES vs.
+high-SES ($D=31.31$, $p<0.001$), and middle-SES vs.
+high-SES ($D=31.31$, $p<0.001$).
 With this finding, program selection could be the reason why low- and high-SES networks tend to segregate as the number of courses taken increases.
@@
 More than 90\% of these consist from participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
-While each participant made one referral for Math and Reading parts of the exam, we pool these referrals in our main analysis and look at averages as there is no difference in terms of referral SES compositions between exam areas (see Appendix Table \ref{tab:referral_area}).
+While each participant made one referral for Math and Reading parts of the exam, we pool these referrals in our main analysis and look at averages as there is no difference in terms of referral SES compositions between the two exam areas (see Appendix Table \ref{tab:referral_area}).
 
@@
 This difference of 5 points is significant ($t = 18.97$, $p < 0.001$), indicating that referrers choose higher-performing peers.
-While the median referral recipient scores 71.0 points, the median network member scores 65.1 points.
-The interquartile range for referrals spans from 65.5 to 75.0 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
+While the median referral recipient scores 71 points, the median network member scores 65.1 points.
+The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
 
@@
 Third, we examine the overall SES-compositions in referral selection.
-Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Table \ref{tab:ses_composition}).
-This over-representation of 4.3 pp.
-is marginally significant ($z = -1.70$, $p = 0.088$), suggesting a small overall tendency to favor low-SES peers.
-For middle-SES students, referrals constitute 51.0\% versus 51.4\% network representation (difference: -0.5 pp., $z = 0.17$, $p = 0.863$).
-High-SES referrals account for 11.1\% compared to 14.9\% network share, a significant under-representation of 3.8 pp.
-($z = 2.17$, $p = 0.030$).
-These findings indicate that referral selection in general modestly deviates from proportional representation, with referrers showing a slight preference for lower-SES at the expense of high-SES peers relative to their network shares.
-
-\begin{table}[H]
-  \centering
-  \begin{threeparttable}
-  \caption{SES composition: network shares versus referral rates}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcc c@{}}
-  \toprule
-   & \multicolumn{1}{c}{\textbf{Network average}} & \multicolumn{1}{c}{\textbf{Referrals}} & \multicolumn{1}{c}{\textit{\textbf{p}}} \\ 
-  \midrule
-  Low-SES & 33.7\% & 37.9\% & 0.088 \\
-  Mid-SES & 51.4\% & 51.0\% & 0.863 \\
-  High-SES & 14.9\% & 11.1\% & 0.030 \\
-  \midrule
-  N & 734 & 734 & \\
-  \bottomrule
-  \end{tabular*}
-  \begin{tablenotes}[flushleft]
-  \footnotesize
-  \item[] \textit{Note:} This table compares the average SES compositions of referrer enrollment networks and actual referral choices.
-$p$-values are from two-sample proportion tests.
-Network percentages represent the average SES group shares across individual networks.
-Referral percentages represent the actual SES distribution of chosen referrals.
-  \end{tablenotes}
-  \label{tab:ses_composition}
-  \end{threeparttable}
-\end{table}
+Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Figure \ref{fig:all_referral_rates}).
+This represents a modest over-representation of 4.3 percentage points.
+For middle-SES students, referrals constitute 51.0\% versus 51.4\% network representation, showing virtually no difference (-0.5 pp.).
+High-SES referrals account for 11.1\% compared to 14.9\% network share, an under-representation of 3.8 percentage points.
+While these patterns suggest some deviation from proportional representation - with slight over-referral to low-SES peers and under-referral to high-SES peers - the magnitudes are relatively modest.
+Overall, referral compositions are largely balanced and closely mirror the underlying network structure, with the largest deviation being less than 5 percentage points for any SES group.
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral patterns compared to network composition}
+  \label{fig:all_referral_rates}
+  \includegraphics[width=0.8\linewidth]{../figures/all_referral_rates.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray).
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
 
@@
 
-Table \ref{tab:stats_by_nomination}
-
-\begin{table}[H]
-  \centering
-  \begin{threeparttable}
-  \caption{Summary statistics for network members by referral status}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
-  \toprule
-  & \multicolumn{1}{c}{\textbf{\textcolor{red}{Not Referred - to remove}}} & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
-  \midrule
-  Reading score & 64.212 & 68.044 & 67.180 & 0.063 \\
-  Math score & 66.361 & 71.119 & 70.240 & 0.143 \\
-  GPA & 3.909 & 4.158 & 4.148 & 0.583 \\
-  Tie strength & 3.162 & 14.062 & 14.236 & 0.732 \\
-  Low-SES & 0.336 & 0.366 & 0.393 & 0.304 \\
-  Med-SES & 0.514 & 0.548 & 0.468 & 0.004 \\
-  High-SES & 0.150 & 0.086 & 0.138 & 0.002 \\
-  \midrule
-  Observations & 255,655 & 699 & 643 \\
-  \bottomrule
-  \end{tabular*}
-  \begin{tablenotes}[flushleft]
-  \footnotesize
-  \item[] \textit{Note:} P-values are from two-sample t-tests with unequal variances for continuous variables and two-sample tests of proportions for binary variables, comparing Baseline Referred vs Bonus Referred groups.
-Reading and math scores are raw test scores.
-GPA is the grade point average.
-Tie strength measures the weighted frequency of contact between individuals.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
-Not Referred includes all network members who were not nominated for referral.
-Baseline Referred and Bonus Referred include only those network members who were actually nominated for referral in each treatment condition.
-  \end{tablenotes}
-  \label{tab:stats_by_nomination}
-  \end{threeparttable}
-\end{table}
+Fourth, we examine referral patterns by referrer SES to identify potential SES biases across groups.
+Figure \ref{fig:all_ses_referral_rates} reveals mixed patterns of deviation from network composition that vary by referrer SES.
+Most patterns show modest deviations from network composition, with differences typically ranging from 1-6 percentage points.
+However, at the very extremes, meaning low-SES to high-SES connections and vice versa, we observe the the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
+Low-SES referrers show the strongest same-SES preference, referring 12.9 percentage points more to low-SES students than their network composition would suggest, while under-referring to high-SES recipients by 6.3 percentage points.
+Conversely, high-SES referrers under-refer to low-SES students by 10.9 percentage points compared to their network composition.
+Middle-SES referrers show the most balanced patterns, with deviations generally under 3 percentage points across all recipient groups.
+These findings indicate that cross-SES referral patterns - particularly between the most socioeconomically distant groups - show the largest departures from network availability, suggesting that when SES differences are most pronounced, referral behavior diverges most from underlying network structure.
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral patterns by referrer SES compared to network composition}
+  \label{fig:all_ses_referral_rates}
+  \includegraphics[width=0.8\linewidth]{../figures/all_ses_referral_rates.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray) for each SES group.
+The panels show referral patterns for low-SES (left), middle-SES (center), and high-SES referrers (right).
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
 
@@
 
+Table \ref{tab:stats_by_nomination}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Summary statistics for network members by referral status}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{\textcolor{red}{Not Referred - to remove}}} & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
+  \midrule
+  Reading score & 64.212 & 68.044 & 67.180 & 0.063 \\
+  Math score & 66.361 & 71.119 & 70.240 & 0.143 \\
+  GPA & 3.909 & 4.158 & 4.148 & 0.583 \\
+  Tie strength & 3.162 & 14.062 & 14.236 & 0.732 \\
+  Low-SES & 0.336 & 0.366 & 0.393 & 0.304 \\
+  Med-SES & 0.514 & 0.548 & 0.468 & 0.004 \\
+  High-SES & 0.150 & 0.086 & 0.138 & 0.002 \\
+  \midrule
+  Observations & 255,655 & 699 & 643 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} P-values are from two-sample t-tests with unequal variances for continuous variables and two-sample tests of proportions for binary variables, comparing Baseline Referred vs Bonus Referred groups.
+Reading and math scores are raw test scores.
+GPA is the grade point average.
+Tie strength measures the weighted frequency of contact between individuals.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
+Not Referred includes all network members who were not nominated for referral.
+Baseline Referred and Bonus Referred include only those network members who were actually nominated for referral in each treatment condition.
+  \end{tablenotes}
+  \label{tab:stats_by_nomination}
+  \end{threeparttable}
+\end{table}
+
 \subsection{SES diversity in ex post referral choice sets}

### 2025-06-18 writing/manuscript.tex
Update results v0
Expanded Stata scripts to refine SES and referral analyses, including new logic for summarizing referral characteristics by treatment and SES, and updated regression specifications. Revised manuscript to clarify SES terminology, add new tables and figures, and provide detailed discussion of treatment effects, referral choice sets, and SES bias. Minor corrections to table labels and figure captions for clarity and consistency.

@@
   Low-SES & 0.419 & 0.401 & \multicolumn{1}{c}{0.615} \\
-  Med-SES & 0.492 & 0.506 & \multicolumn{1}{c}{0.714} \\
+  Middle-SES & 0.492 & 0.506 & \multicolumn{1}{c}{0.714} \\
   High-SES & 0.089 & 0.094 & \multicolumn{1}{c}{0.824} \\
   \midrule
-  N & 382 & 352 & 734 \\
+  Observations & 382 & 352 & 734 \\
   \bottomrule
@@
   \centering
-  \caption{Network size and courses taken together by time spent at UNAB}\label{connections_class}
+  \caption{Network size and courses taken together by time spent at the university}\label{connections_class}
   \includegraphics[width=0.6\linewidth]{../figures/connections.png}
@@
   \centering
-  \caption{Network size and courses taken together by time spent at UNAB}\label{connections_by_ses}
+  \caption{Network size and courses taken together by SES}\label{connections_by_ses}
   \includegraphics[width=0.6\linewidth]{../figures/connections_by_ses.png}
@@
 
-\subsection{SES diversity in networks}
+\subsection{SES diversity in networks}\label{s:ses-diversity}
 What are diversity related consequences of SES-driven differences across networks?
-In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means in networks.
-However, it is important to note that these are not independent observations across the network - the reason these estimates are so precise is because most people are seemingly connected with similar others, creating systematic patterns that reduce variance.
-For this reason we choose not reporting test results in this section and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
+In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
+However, it is important to note that these are not independent observations for each network.
+Estimates are precise because each network is a draw with replacement from the same pool of university population.
+Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
+For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
 Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.
@@
     \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants.
-Horizontal lines plot the university-wide shares of each SES group.
+Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
 While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
@@
 More than 90\% of these consist from participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
-While each participant made one referral for Math and Reading parts of the exam, we pool these referrals in our main analysis and look at averages as there is no difference in terms of referral SES compositions between the two exam areas (see Appendix Table \ref{tab:referral_area}).
+While participants made one referral for Math and Reading parts of the exam, about 70\% of these referrals went to two separate individuals.
+We compare the outcomes across areas for unique referrals in Appendix Table \ref{tab:referral_by_area} and all referrals in Appendix Table \ref{tab:referral_area}.
+In both cases, we find no meaningful differences between referrals made Math or Reading areas of the entry exam.
+As referrals in both exam areas come from the same referrer network, we pool referrals per  participant and report their average in terms of outcomes in our main analysis to avoid unintentionally increasing the statistical power of our tests when making comparisions.
 
@@
 
-Third, we examine the overall SES-compositions in referral selection.
+\subsection{Effect of the Bonus treatment}
+
+Do referred individuals have different outcomes across treatments?
+We compare the performance, number of courses taken together, and SES shares of referred individuals between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
+While performance of referrals across Reading, Math, and GPA are similar across treatments, middle- and high-SES shares have significant differences.
+We find that referrals under the \textbf{Bonus} condition referred a higher proportion of high-SES individuals (13.5\% vs 8.8\%, $p=0.041$) and a lower proportion of middle-SES individuals on average (47.0\% vs 53.7\%, $p=0.072$).
+However, these differences do not appear to stem from systematic behavioral changes by any particular SES group of referrers, and the overall patterns remain largely consistent across treatments.
+The similarities in academic performance and number of courses taken together suggest that the core selection criteria, i.e., academic merit and social proximity, remain unchanged between conditions.
+For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Characteristics of referrals by treatment condition}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
+  \midrule
+  Reading score & 67.806 & 67.210 & 0.308 \\
+  Math score & 70.784 & 70.155 & 0.406 \\
+  GPA & 4.155 & 4.149 & 0.799 \\
+  Courses taken & 13.840 & 14.065 & 0.723 \\
+  Low-SES & 0.376 & 0.395 & 0.593 \\
+  Middle-SES & 0.537 & 0.470 & 0.072 \\
+  High-SES & 0.088 & 0.135 & 0.041 \\
+  \midrule
+  Observations & 382 & 352 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares the characteristics of network members who were referred under baseline vs bonus treatment conditions.
+$p$-values for binary outcomes are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+All reported \textit{p}-values are two-tailed.
+Reading and math scores are raw test scores out of 100.
+GPA is grade point average out of 5.
+Courses taken is the number of courses participant has taken  with their referral.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1-2, 3-4, or 5-6, respectively.
+Both columns include only network members who were actually nominated for referral in each treatment condition.
+  \end{tablenotes}
+  \label{tab:referral_by_treatment}
+  \end{threeparttable}
+\end{table}
+
+\subsection{Referral SES composition}
+We first examine the overall SES-compositions in referral selection.
 Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Figure \ref{fig:all_referral_rates}).
@@
   \label{fig:all_referral_rates}
-  \includegraphics[width=0.8\linewidth]{../figures/all_referral_rates.png}
+  \includegraphics[width=0.6\linewidth]{../figures/all_referral_rates.png}
   \begin{tablenotes}
@@
 
-\textcolor{red}{to do: 1- SES composition by SES, 2- expost choice sets 3- effect of the bonus 4- bias regression }
-
-Fourth, we examine referral patterns by referrer SES to identify potential SES biases across groups.
+Then, we examine referral patterns by referrer SES to identify potential SES biases across groups.
 Figure \ref{fig:all_ses_referral_rates} reveals mixed patterns of deviation from network composition that vary by referrer SES.
 Most patterns show modest deviations from network composition, with differences typically ranging from 1-6 percentage points.
-However, at the very extremes, meaning low-SES to high-SES connections and vice versa, we observe the the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
+However, at the very extremes, i.e., low-SES to high-SES connections and vice versa, we observe the the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
 Low-SES referrers show the strongest same-SES preference, referring 12.9 percentage points more to low-SES students than their network composition would suggest, while under-referring to high-SES recipients by 6.3 percentage points.
@@
   \label{fig:all_ses_referral_rates}
-  \includegraphics[width=0.8\linewidth]{../figures/all_ses_referral_rates.png}
+  \includegraphics[width=0.6\linewidth]{../figures/all_ses_referral_rates.png}
   \begin{tablenotes}
@@
 
-\subsection{Effect of the Bonus treatment}
-
-Table \ref{tab:stats_by_nomination}
-
-\begin{table}[H]
-  \centering
-  \begin{threeparttable}
-  \caption{Summary statistics for network members by referral status}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccc}
-  \toprule
-  & \multicolumn{1}{c}{\textbf{\textcolor{red}{Not Referred - to remove}}} & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
-  \midrule
-  Reading score & 64.212 & 68.044 & 67.180 & 0.063 \\
-  Math score & 66.361 & 71.119 & 70.240 & 0.143 \\
-  GPA & 3.909 & 4.158 & 4.148 & 0.583 \\
-  Tie strength & 3.162 & 14.062 & 14.236 & 0.732 \\
-  Low-SES & 0.336 & 0.366 & 0.393 & 0.304 \\
-  Med-SES & 0.514 & 0.548 & 0.468 & 0.004 \\
-  High-SES & 0.150 & 0.086 & 0.138 & 0.002 \\
-  \midrule
-  Observations & 255,655 & 699 & 643 \\
-  \bottomrule
-  \end{tabular*}
-  \begin{tablenotes}[flushleft]
-  \footnotesize
-  \item[] \textit{Note:} P-values are from two-sample t-tests with unequal variances for continuous variables and two-sample tests of proportions for binary variables, comparing Baseline Referred vs Bonus Referred groups.
-Reading and math scores are raw test scores.
-GPA is the grade point average.
-Tie strength measures the weighted frequency of contact between individuals.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
-Not Referred includes all network members who were not nominated for referral.
-Baseline Referred and Bonus Referred include only those network members who were actually nominated for referral in each treatment condition.
-  \end{tablenotes}
-  \label{tab:stats_by_nomination}
-  \end{threeparttable}
-\end{table}
-
-\subsection{SES diversity in ex post referral choice sets}
-At the median number of courses taken together for referrals, the effects of network segregation on SES diversity becomes clear (see Figure \ref{t15availability}) 
+\subsection{Ex post referral choice sets}
+
+We now shed more light on the referral behavior after having characterized how referrals were made.
+Particularly interesting is that referrals go to peers with whom the median participant took 12 courses, with an average of 14.
+By restricting the networks for courses taken above the median, we can get a snapshot of how the referral choice set actually looked for participants before making referral decisions.
+As discussed in Section \ref{s:ses-diversity}, taking more courses with network members increases the share of same-SES individuals for both low- and high-SES students, and we had explored program selection as a potential mechanism.
+In Figure \ref{t15availability}, we show the effects of network segregation on \textit{ex post} referral choice sets for each SES group.
+Network compositions above the median number of courses taken reveal strong segregation effects: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
+Conversely, high-SES are  under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
+At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
+High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% population share ($+12.5$ pp.).
+Middle-SES networks remain relatively balanced and closely track population proportions across all SES groups.
+Taken together, these suggest observed referral rates of SES groups may follow the network compostions above median number of courses taken together.
+We will test this formally by setting up a choice model where we can take into account individual differences in network compositions across SES, and try to identify SES biases that go beyond SES groups' availability in the choice sets.
+
 \begin{figure}[H]
@@
     \footnotesize
-    \item[] \textit{Note:} This figure illustrates the shares of same-SES connections for low-, middle-, and high-SES as a function of the average number of courses taken together with network members.
-Low- and high-SES networks both become more homogenous as the average number of courses taken together with their connections increase.
-  \end{tablenotes}
-\end{figure}
+    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants above the median number of courses taken together with peers.
+Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+Low- and high-SES networks both become same-SES dominated at the expense of each other while middle-SES networks remain balanced.
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
+
+\subsection{Identifying the SES bias in referrals}
+
+\textcolor{red}{regression time!}
 
@@
   Low-SES & 0.343 & 0.410 & 0.000 \\
-  Med-SES & 0.505 & 0.499 & 0.763 \\
+  Middle-SES & 0.505 & 0.499 & 0.763 \\
   High-SES & 0.153 & 0.091 & 0.000 \\
@@
   \toprule
-  Area & Only one area & Both areas & Total \\
+  \textbf{Area} & \textbf{Only one area} & \textbf{Both areas} & \textbf{Total} \\
   \midrule
@@
   \begin{threeparttable}
+  \caption{Referral characteristics by exam area (unique referrals only)}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{Reading}} & \multicolumn{1}{c}{\textbf{Math}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
+  \midrule
+  Reading score & 67.733 & 67.126 & 0.252 \\
+  Math score & 69.339 & 71.151 & 0.008 \\
+  GPA & 4.136 & 4.136 & 0.987 \\
+  Courses taken & 13.916 & 13.019 & 0.123 \\
+  Low-SES & 0.372 & 0.385 & 0.666 \\
+  Med-SES & 0.526 & 0.518 & 0.801 \\
+  High-SES & 0.103 & 0.097 & 0.781 \\
+  \midrule
+  Observations & 487 & 483 &  \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares characteristics of uniquely referred students by entry exam area for the referral (verbal vs.
+math).
+$p$-values are from two-sample t-tests with unequal variances.
+Referrals in Math area go to peers with significantly higher math scores ($p = 0.008$), while we find no significant differences for Reading scores, GPA, courses taken, or SES composition for referrals across the two areas.
+Excluding referrals going to the same individuals does not change the outcomes for referrals compared to Appendix Table \ref{tab:referral_area}
+  \end{tablenotes}
+  \label{tab:referral_by_area}
+  \end{threeparttable}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
   \caption{Referral characteristics by academic area}
@@
   Math score & 70.04 & 71.36 & 0.029 \\
+  GPA & 4.153 & 4.153 & 0.984 \\ 
+  Courses taken & 14.467 & 13.822 & 0.206 \\
   Low-SES & 37\% & 38\% & 0.714 \\
-  Med-SES & 51\% & 51\% & 0.829 \\
+  Middle-SES & 51\% & 51\% & 0.829 \\
   High-SES & 11\% & 11\% & 0.824 \\
   \midrule
-  N & 673 & 669 &  \\
+  Observations & 673 & 669 &  \\
   \bottomrule
@@
   \footnotesize
-  \item[] \textit{Note:} This table compares characteristics of referred students by referrer's academic area (verbal vs.
+  \item[] \textit{Note:} This table compares characteristics of referred students by entry exam area for the referral (verbal vs.
 math).
 $p$-values are from two-sample t-tests with unequal variances.
-Math area participants refer peers with significantly higher math performance ($p = 0.029$), while no significant differences exist for reading scores or SES composition across areas.
+Referrals in Math area go to peers with significantly higher math scores ($p = 0.029$), while we find no significant differences for Reading scores, GPA, courses taken, or SES composition for referrals across the two areas.
   \end{tablenotes}

### 2025-06-19 writing/manuscript.tex
Revise regression models and update manuscript text
Expanded Stata regression scripts to include program and SES interactions, added new variables, and restructured model specifications for clarity. Updated manuscript.tex to clarify SES diversity analysis, referral characteristics, and regression modeling approach, including a new description and formula for the conditional logit model.

@@
 However, it is important to note that these are not independent observations for each network.
-Estimates are precise because each network is a draw with replacement from the same pool of university population.
+Estimates are precise because each network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group.
 Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
@@
 While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
-The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers within same program (93\%).
+The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with high social proximity and within same program (93\%).
 
@@
 
-\textcolor{red}{regression time!}
+We model a single referral outcome from candidates that are mutually exclusive, where our the dependent variable outcome is multinomial distributed.
+Our design leverages the enrollment network to generate dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for all referral candidates, and not just the chosen alternative.
+Using a conditional logit model with these data, we can identify whether SES groups have an aggregate bias each other:
+
+\begin{align*}
+            \Pr(\text{Refer}_{ij} = 1) = \Lambda\left(\beta_1 \text{SES}_j + \beta_2 \text{Courses}_j + \beta_3 \text{Score}_{ij} + \beta_4 \text{Courses}_j \times \text{Score}_{ij} + \alpha_i\right)
+        \end{align*}
+
+“The income coefficients of , , and mean that, relative to the probability of beach fishing, an increase in income leads to a decrease in the probability of charter boat and pier fishing and an increase in the probability of private boat fishing”
 

### 2025-06-20 writing/manuscript.tex
Revise SES bias analysis and update regression code
Expanded the SES bias section in the manuscript to provide a more detailed explanation of the conditional logit model, identification assumptions, and interpretation of results. Added new tables and updated the narrative to reflect additional model specifications and findings. Updated Stata regression script to comment out old models, introduce new model specifications, and output results for each specification. Data and auxiliary files were updated accordingly.

@@
 We model a single referral outcome from candidates that are mutually exclusive, where our the dependent variable outcome is multinomial distributed.
-Our design leverages the enrollment network to generate dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for all referral candidates, and not just the chosen alternative.
-Using a conditional logit model with these data, we can identify whether SES groups have an aggregate bias each other:
-
-\begin{align*}
-            \Pr(\text{Refer}_{ij} = 1) = \Lambda\left(\beta_1 \text{SES}_j + \beta_2 \text{Courses}_j + \beta_3 \text{Score}_{ij} + \beta_4 \text{Courses}_j \times \text{Score}_{ij} + \alpha_i\right)
-        \end{align*}
-
-“The income coefficients of , , and mean that, relative to the probability of beach fishing, an increase in income leads to a decrease in the probability of charter boat and pier fishing and an increase in the probability of private boat fishing”
+Our design leverages the enrollment network to generate dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
+Using a conditional logit model on these data, we can identify whether an SES group has an aggregate bias controlling for each individual's unique enrollment network composition.
+
+We follow an additive random utility model framework where individual $i$ and alternative $j$ have utility $U_{ij}$ that is the sum of a deterministic component, $V_{ij}$, that depends on regressors and unknown parameters, and an unobserved random component $\varepsilon_{ij}$:
+
+We observe the outcome $y_i = j$ if alternative $j$ has the highest utility of the alternatives.
+The probability that the outcome for individual $i$ is alternative $j$, conditional on the regressors, is:
+
+\begin{align}
+p_{ij} = \Pr(y_i = j) = \Pr(U_{ij} \geq U_{ik}), \quad \text{for all } k
+\end{align}
+
+The CL model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
+
+\begin{align}
+p_{ij} = \frac{\exp(x'_{ij} \beta)}{\sum_{l \in C_i} \exp(x'_{il} \beta)}, \quad j \in C_i
+\end{align}
+
+where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referees that vary across alternatives.
+
+In our context, individual $i$ chooses to refer candidate $j$ from their enrollment network $C_i$.
+The alternative-specific regressors include SES and entry exam scores of the referral candidate, and the number of courses taken together with the participant making the referral.
+Conditional logit structure eliminates participant-specific factors that might influence both network formation and referral decisions, allowing us to identify preferences within each participant's realized network.
+
+For causal identification of SES bias, we require two identifying assumptions. Specifically:
+
+\begin{enumerate}
+    \item \textbf{Conditional exogeneity}: Both SES and the number of courses taken together could be endogenous due to program selection.
+High-SES students sort into expensive programs while low-SES students choose affordable programs, creating systematic SES variation across enrollment networks.
+Similarly, the number of courses taken together reflects program selection decisions that may correlate with unobserved referral preferences.
+However, conditional on the realized enrollment network, the remaining variation in both SES and the number of courses taken together across referral candidates must be independent of unobserved factors affecting referral decisions.
+In the robustness checks, we show that being in the same program with the referrer does not impact our SES bias estimates, although it reduces the coefficient on the number of courses taken together.
+
+    \item \textbf{Complete choice set specification and independence of irrelevant alternatives}: Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
+The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
+This concern does not apply to our setting because the design of our experiment ensures that choice sets are fixed by enrollment rather than arbitrary inclusion/exclusion of alternatives that create IIA violations.
+\end{enumerate}
+
+Under these assumptions, the conditional logit framework controls for individual heterogeneity in program selection (absorbed by conditioning on choice sets), selection into programs based on observable characteristics (through alternative-specific variables), and choice set composition effects (through the multinomial structure).
+Therefore, $\beta$ should identify the causal effect of referral candidate SES on referral probability, holding constant the number of courses taken together and the entry exam scores of candidates.
+A significant coefficient will then indicate taste-based discrimination.
+
+We pool participants by their SES group, and estimate the above described conditional fixed effects logit model once for low-, middle-, and high-SES referrers.
+We standardize entry exam scores and the number of courses taken together at the individual network level.
+For each referrer's network, we first calculate the mean and standard deviation for both measures.
+We then compute the average of these means and standard deviations across all 734 referrers.
+Each referral candidate's entry exam score and the number of courses they haven taken with the referrer is standardized using these network-level statistics.
+The standardization formula is $z_{i} = (x - \bar{X}_{i}) / \sigma_{i}$, where $\bar{X}_{i}$ and $\sigma_{i}$ are the average of network means and standard deviations for $C_{i}$.
+
+We describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
+To begin with, the variance explained by all three models are extremely low, suggesting the role of potential SES biases in referrals that go beyond the network structure must be limited.
+Regardless, controlling for network composition, low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
+In contrast, we find that high-SES participants are less likely to refer other low-SES, relative to the probability of referring middle-SES peers.
 
@@
 \begin{threeparttable}
-  \caption{Comparison of math and verbal scores by SES group and data source}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc}
+\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
 \toprule
-  & \multicolumn{3}{c}{Math} & \multicolumn{3}{c}{Verbal} \\
-  \cmidrule{2-4} \cmidrule{5-7}
-  & Network & Admin & Sample & Network & Admin & Sample \\
-  \midrule
-  Low-SES & 66.976 & 61.653 & 67.813 & 64.738 & 60.974 & 66.058 \\
-  & (0.052) & (0.346) & (0.694) & (0.043) & (0.274) & (0.574) \\
-  [1ex]
-  Mid-SES & 65.627 & 64.531 & 66.859 & 63.685 & 63.154 & 64.779 \\
-  & (0.039) & (0.224) & (0.580) & (0.032) & (0.183) & (0.436) \\
-  [1ex]
-  High-SES & 67.781 & 67.330 & 70.610 & 64.966 & 64.892 & 66.397 \\
-  & (0.077) & (0.416) & (1.295) & (0.063) & (0.341) & (1.214) \\
-  \midrule
-  Observations & 128,150 & 4,415 & 669 & 128,847 & 4,403 & 673 \\
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES candidate & 0.453*** & -0.019 & -0.710** \\
+& (0.109) & (0.098) & (0.333) \\
+High-SES candidate & -0.584*** & -0.255* & 0.001 \\
+& (0.211) & (0.145) & (0.261) \\
+\midrule
+$\chi^2$ & 33.47 & 3.18 & 4.94 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
 \bottomrule
@@
 \footnotesize
-  \item[] \textit{Note:} Standard errors in parentheses.
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
+A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that stronger social connections substantially increase the probability of referral.
+The high $\chi^2$ statistics suggest that these models explain considerably more variance than specifications without this control, highlighting the importance of courses taken together in referral decisions.
+Nevertheless, low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
+This same-SES bias is not observed among middle-SES or high-SES referrers, who also display no statistically significant bias toward low-SES candidates.
+None referrer group shows a positive bias for high-SES candidates relative to middle-SES candidates.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity-extended}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES candidate & 0.348*** & -0.064 & -0.489 \\
+& (0.123) & (0.115) & (0.337) \\
+High-SES candidate & -0.366 & -0.165 & -0.140 \\
+& (0.223) & (0.157) & (0.286) \\
+Courses taken (z-score) & 0.856*** & 0.931*** & 1.049*** \\
+& (0.035) & (0.037) & (0.126) \\
+\midrule
+$\chi^2$ & 626.15 & 636.10 & 71.43 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+We add standardized entry exam scores (Math and Reading average) as a second control variable and describe our results in Table \ref{tab:ses-heterogeneity-scores}.
+A one standard deviation increase in the entry exam score proves highly significant across all models, with coefficients ranging from 0.587 to 0.883.
+This shows merit-based considerations due to the incentive structure of the experiment remained central to referral decisions.
+The slightly higher $\chi^2$ statistics compared to the earlier specification suggests that entry exam scores improve model fit.
+The inclusion of standardized entry exam scores strengthens SES biases.
+Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES .
+Middle-SES referrers, previously showing no SES bias, now show marginal negative bias agaisnt high-SES.
+Finally, high-SES referrers exhibit marginal negative bias against low-SES candidates.
+
+The evidence of a biases becoming significant when controlling for entry exam scores has a nuanced interpretation.
+While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students.
+Controlling for performance thus removes this positive selection and reveals the ``pure'' SES bias that was previously underestimated by above average performance of low-SES.
+Vice versa, high-SES in low-SES networks perform 0.12 standard deviations better than middle-SES students.
+The same bias was underestimated as high-SES candidates' better performance relative to middle-SES in the same networks provided a meritocratic justification for getting more referrals.
+Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of - and counter to - performance-based considerations.
+What makes interpretation difficult is that while biased against low-SES, high-SES referrers do not under any specification display a positive bias towards their in-group.
+For this final reason, we do not dig any further in this direction.\textcolor{red}{add tests if you want}
+
+To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specificaiton.
+For low-SES referrers, the joint test remains highly significant across all three specifications ($\chi^2 = 10.20$, $p = 0.006$ in the final model), indicating persistent SES bias across all specifications.
+In contrast, middle-SES referrers display no significant joint SES bias in any specification, with the test becoming increasingly non-significant as controls are added ($\chi^2 = 4.13$, $p = 0.127$ in the final model).
+High-SES referrers similarly show no significant joint SES bias across all three models ($\chi^2 = 4.28$, $p = 0.118$ in the final model).
+These results suggest that SES bias in referrals is primarily driven by low-SES.
+There is no sufficient evidence to conclude that middle- and high-SES referrers systematically discriminate against other-SES peers once we take into account the large differences in their network compositions due to program selection.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group with academic performance controls}\label{tab:ses-heterogeneity-scores}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES candidate & 0.242** & -0.159 & -0.600* \\
+& (0.123) & (0.114) & (0.327) \\
+High-SES candidate& -0.445** & -0.274* & -0.345 \\
+& (0.222) & (0.157) & (0.287) \\
+Courses taken (z-score) & 0.859*** & 0.948*** & 1.043*** \\
+& (0.036) & (0.038) & (0.118) \\
+Entry exam (candidate z-score) & 0.607*** & 0.587*** & 0.883*** \\
+& (0.052) & (0.047) & (0.111) \\
+\midrule
+$\chi^2$ & 789.87 & 756.06 & 120.54 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+% \begin{table}[H]
+%   \centering
+%   \begin{threeparttable}
+%   \caption{Comparison of math and verbal scores by SES group and data source}
+%   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc}
+%   \toprule
+%   & \multicolumn{3}{c}{Math} & \multicolumn{3}{c}{Verbal} \\
+%   \cmidrule{2-4} \cmidrule{5-7}
+%   & Network & Admin & Sample & Network & Admin & Sample \\
+%   \midrule
+%   Low-SES & 66.976 & 61.653 & 67.813 & 64.738 & 60.974 & 66.058 \\
+%   & (0.052) & (0.346) & (0.694) & (0.043) & (0.274) & (0.574) \\
+%   [1ex]
+%   Mid-SES & 65.627 & 64.531 & 66.859 & 63.685 & 63.154 & 64.779 \\
+%   & (0.039) & (0.224) & (0.580) & (0.032) & (0.183) & (0.436) \\
+%   [1ex]
+%   High-SES & 67.781 & 67.330 & 70.610 & 64.966 & 64.892 & 66.397 \\
+%   & (0.077) & (0.416) & (1.295) & (0.063) & (0.341) & (1.214) \\
+%   \midrule
+%   Observations & 128,150 & 4,415 & 669 & 128,847 & 4,403 & 673 \\
+%   \bottomrule
+%   \end{tabular*}
+%   \begin{tablenotes}[flushleft]
+%   \footnotesize
+%   \item[] \textit{Note:} Standard errors in parentheses.
 The table presents mean scores with standard errors for math and verbal tests across the entire network, the admin data, and the sample.
@@
 Differences between network and sample scores are generally smaller than those between either and the admin data.
-  \end{tablenotes}
-  \label{tab:ses_scores_comparison}
-  \end{threeparttable}
-\end{table}
-
-\begin{figure}[H]
-  \centering
-  \caption{Effect of the Bonus on Referrals}
-  \begin{subfigure}[t]{0.7\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
-      \caption{Reading}  
-      \label{fig:reading_combined}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.7\textwidth}
-    \centering
-      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
-      \caption{Math}
-      \label{fig:math_combined}
-  \end{subfigure}
-  \label{fig:both_combined}
-  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
+%   \end{tablenotes}
+%   \label{tab:ses_scores_comparison}
+%   \end{threeparttable}
+% \end{table}
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Effect of the Bonus on Referrals}
+%   \begin{subfigure}[t]{0.7\textwidth}
+%     \centering
+%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
+%       \caption{Reading}  
+%       \label{fig:reading_combined}
+%   \end{subfigure}
+%   \begin{subfigure}[t]{0.7\textwidth}
+%     \centering
+%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
+%       \caption{Math}
+%       \label{fig:math_combined}
+%   \end{subfigure}
+%   \label{fig:both_combined}
+%   \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
 The bottom panel shows the average standardized math and tie strength of referrals across conditions.
@@
 For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
-  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure displays the percentage share of top decile individuals according to the admin data across three dimensions.
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
+%   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
+%   \begin{tablenotes}
+%     \footnotesize
+%     \item[] \textit{Note:} This figure displays the percentage share of top decile individuals according to the admin data across three dimensions.
 First bar shows referrers in the sample of participants.
@@
 For both math and reading scores, the differences between Sample and Network ($p<0.001$), Sample and Referrals ($p<0.005$), and Network and Referrals ($p<0.001$) are all statistically significant.
-  \end{tablenotes}
-\end{figure}
+%   \end{tablenotes}
+% \end{figure}
 

### 2025-06-23 writing/manuscript.tex
Add robustness checks and performance analysis by SES
Introduced a new Stata script and figure for performance by SES (f_perf_kde.do, sample_performance.png), and updated regression scripts to include program controls in robustness checks. Manuscript expanded with a robustness check section, new table for program controls, and additional discussion and results on SES bias, network structure, and performance. Cleaned up commented code in Stata scripts and made minor text clarifications.

@@
 \begin{enumerate}
-    \item \textbf{Conditional exogeneity}: Both SES and the number of courses taken together could be endogenous due to program selection.
+    \item \textbf{Conditional exogeneity.} SES and the number of courses taken together could be endogenous due to program selection.
 High-SES students sort into expensive programs while low-SES students choose affordable programs, creating systematic SES variation across enrollment networks.
@@
 
-    \item \textbf{Complete choice set specification and independence of irrelevant alternatives}: Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
+    \item \textbf{Complete choice sets and independence of irrelevant alternatives.}: Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
 The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
@@
 The evidence of a biases becoming significant when controlling for entry exam scores has a nuanced interpretation.
-While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students.
+While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students (see Appendix Table \ref{tab:network_connections}).
 Controlling for performance thus removes this positive selection and reveals the ``pure'' SES bias that was previously underestimated by above average performance of low-SES.
@@
 What makes interpretation difficult is that while biased against low-SES, high-SES referrers do not under any specification display a positive bias towards their in-group.
-For this final reason, we do not dig any further in this direction.\textcolor{red}{add tests if you want}
+For this final reason, we do not dig any further in this direction.
 
@@
 $\chi^2$ & 789.87 & 756.06 & 120.54 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\section{Robustness check}
+
+Does the number of courses taken together have an independent effect which goes beyond identifying peers in the same academic program?
+To evaluate this question we leverage our administrative data, and identify peers within the same program: In each individual network we observe the case-specific academic program for the participant making the referral and alternative-specific academic program for each referral candidate.
+We add this new variable in our specification and describe our findings in Table \ref{tab:ses-heterogeneity-program}.
+Being in the same academic program has a substantial positive effect on referral likelihood, with coefficients ranging from 1.257 to 2.198 across all referrer SES groups.
+This confirms that program affiliation serves as a strong predictor of referral decisions, reflecting increased familiarity.
+Our comparison of interest is the point estimate for the standardized number of courses taken.
+Across all three referrer groups, the standardized number of courses taken together maintains its statistical significance after controlling for same program membership.
+The coefficient magnitudes are expectedly smaller compared to specifications without program controls (ranging from 0.688 to 0.930) as the newly added variable is a moderator: Matching academic programs leads to taking more courses together.
+The remaining estimates in our model prove robust to the inclusion of the same-program variable with little change in point estimates.
+The persistence of statistical significance (all $p < 0.001$) suggests that the number of courses taken together has an independent effect on referral decisions.
+To sum, our measure of tie strength seems to capture meaningful social interaction patterns that lead to referrals, and go beyond simply identifying matching academic programs.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group with program controls}\label{tab:ses-heterogeneity-program}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES candidate & 0.236** & -0.140 & -0.567* \\
+& (0.119) & (0.111) & (0.331) \\
+High-SES candidate& -0.421* & -0.249 & -0.383 \\
+& (0.220) & (0.158) & (0.281) \\
+Entry exam (candidate z-score) & 0.623*** & 0.590*** & 0.892*** \\
+& (0.054) & (0.048) & (0.114) \\
+Courses taken (z-score) & 0.688*** & 0.760*** & 0.930*** \\
+& (0.032) & (0.035) & (0.119) \\
+Same program & 2.074*** & 2.198*** & 1.257*** \\
+& (0.215) & (0.185) & (0.467) \\
+\midrule
+$\chi^2$ & 865.35 & 981.99 & 135.47 \\
 Observations & 110,142 & 127,088 & 19,767 \\
@@
     \section{Conclusion} \label{s6}
+  In this paper, we study whether SES groups are biased toward one another beyond what is attribuable to differences in their networks, and the effects of different incentive structures on referral behavior.
+Through a lab-in-the-field experiment that leverages enrollment networks at a socially diverse university, we find that the SES biases in referrals orginate mostly from network structures, and referrals under perfomance-pay incentives do not exacerbate existing SES inequalities.
+
+  Our findings reveal that enrollment networks are suprisingly segregated and referrals from these networks reflect closely the choice sets of the referrers.
+We identify a potential mechanism for the observed differences in network structures: Low-SES students select into more affordable programs, and program selection plays a major part in segregating SES groups where low- and high-SES take more courses with their own SES group.
+Consequently, referrals come almost exclusively from the same academic program as the referrer, limiting the SES-diversity of their choice sets.
+Regardless of the bonus for the referral candidate, participants also pick higher performing peers with whom they have taken many courses together.
+We find that only low-SES referrers exhibit a same-SES bias.
+These suggest that the underlying network structure plays a crucial role in referrals, where institutional action can remedy the network segregation.
+
+  These results complement the broader literature where much of the bias in referrals can be attribuable to the ``practical'' choice sets of the referrers.
+While previous work demonstrates that about half of referrals come from a smaller, elicited network of close friends \citep{hederos2025gender}, we go the other way and use administartive data to construct a complete network which presumably includes close social relationships at the institional level.
+Having access to the complete network thus eliminates any potential for under or overestimating taste-based biases \citep{griffith2022jle}.
+Under performance-pay incentives, referrers identify productive others regardless of addtional financial rewards for the referral candidate.
+Still, the lack of a treatment effect suggessts that in both incentive structures referrers pick close ties, shifting the  responsability to institional actors to create diverse environments where cross-SES social interaction can take place more frequently and allow more diversity in networks.
+
+  Looking forward, to achieve SES equality in opportunity institions can play  a crucial role in higher education.
+Universities are already a setting in which low-SES get exposed to typically a higher than population share of higher-SES individuals than at other settings \citep{chetty2022n}.
+Yet, segregation within the higher educations institions remain a source for SES inequality.
+If low-SES peers never get to interact in meaningful ways with higher-SES, e.g., by taking courses together, the premise of social mobility thorough social channels remain severly under exploited.
+Future studies should work on ways to reduce SES segregation in collabration with instititons, where having access to complete enrollment networks in addition to the typical friendship elcitation methods could help identfying the exact overlap between the two distinct apporaches.
 
@@
   \label{tab:referral_area}
+  \end{threeparttable}
+  \end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Average entry exam z-scores by SES network connections}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc@{}}
+  \toprule
+   & \multicolumn{3}{c}{\textbf{Network average for SES group}} \\
+  \cmidrule(lr){2-4}
+  \textbf{Referrer SES} & \textbf{Low} & \textbf{Middle} & \textbf{High} \\ 
+  \midrule
+  Low & 0.086 & -0.018 & 0.144 \\
+  Middle & 0.186 & 0.023 & 0.215 \\
+  High & 0.204 & 0.064 & 0.285 \\
+  \midrule
+  All & -0.361 & -0.078 & 0.169 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table shows average (Math and Reading) standardized entry exam scores for individuals of different SES levels (rows) when connected to peers of specific SES levels (columns).
+The ``All'' row shows the overall average scores across all participant SES levels when connected to each network SES type.
+Higher values indicate better academic performance in SD's.
+  \end{tablenotes}
+  \label{tab:network_connections}
   \end{threeparttable}

### 2025-06-24 writing/manuscript.tex
v1 chapter 3

@@
 \usepackage{blindtext}
-
 \usepackage[colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue,breaklinks]{hyperref}
+
+% \pdfcompresslevel=0
+% \pdfobjcompresslevel=0
 
@@
 \section*{Abstract}
-Lorem Ipsum \citep{beaman_job_2018}
+Economic connectivity, defined as the share of high-SES connections in one's network, is a strong correlate of labor market income.
+Yet, low-SES individuals are typically at a disadvantage when it comes to knowing the right people.
+Referral hiring leverages networks and make explicit the role of economic connectivity where taste-based biases could further exacerbate low-SES outcomes.
+We conduct a field experiment with 734 university students to study the network compositions of different SES groups.
+We leverage enrollment networks to identify all potential referral candidates and conduct an incentivized referral exercise to reveal SES biases within these choice sets.
+We find that the university enrollment networks are highly segregated, with low-SES and high-SES individuals having a higher share of same-SES connections in their networks due to program selection (12\% and 31\% respectively).
+When considering ex post actualized choice sets for the observed referrals, the segregation becomes worse: Low-SES individuals connect with other low-SES individuals at rates 30\% higher than the university share, while high-SES individuals connect with other high-SES individuals at rates 55\% higher than the university share.
+Yet, we find no bias against low-SES individuals once we account for network structures.
+We randomly assign half of the participants to a condition where their referral candidate receives a fixed bonus on top of pay-for-performance referral incentives.
+We find that additional incentives for the referral candidate do not change social proximity with the referral nor the referral quality.
+Our findings suggest that systematic segregation patterns in networks that alter choice sets matter more than taste-based SES biases in referrals, and highlight the potential for institutional action in promoting SES diversity.
 \medskip \\
-\textbf{JEL Classification:} C93, D03, D83, J24 \\
-\textbf{Keywords:} productivity beliefs, referrals, field experiment, skill identification, social class
-
-% Problem: Labor markets increasingly value both cognitive and social skills, but firms struggle to identify these skills in candidates.
-Referrals are a common hiring tool, but their effectiveness across different skill types and potential social class biases remain unclear.
-% Method: Using a field experiment with 849 university students, we study how well peers identify cognitive and social skills of their classmates.
-% Key Results: Students effectively identify cognitive skills but struggle with social skills. Limited evidence of social class bias in referrals.
-% Implications: Referrals may be more effective for identifying certain types of skills than others.
-% We study how well referrals help screening for the two types of worker skills within the same network and compare the differential skill identification ability of referrers.
+\textbf{JEL Classification:} C93, J71, D85, Z13 \\
+\textbf{Keywords:} social capital, social networks, referral hiring, socioeconomic status, field experiment
 
@@
 \section{Introduction}
-Equally qualified individuals face different labor market outcomes depending on their socioeconomic status \citep{stansbury2024class}.
-A key driver of this inequality is due to differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Because it correlates strongly with labor market income, the most important facet of social capital is the share of high-SES connections among low-SES individuals \citep{chetty2022na}.
-A lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.
-In economic terms, it implies having worse outcomes when using one's network to find jobs conditional on the capacity on leveraging one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.}
-
-Referral hiring, the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities, is a common labor market practice which makes evident the role of differences in social capital.
-As referrals originate from the networks of referrers, the composition of referrer networks becomes a crucial channel that propagates inequality: Similar individuals across socio-demographic characteristics form connections at higher rates \citep{mcpherson2001birds}, making across SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
-Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure, i.e., referring at random from one's network according to some productivity criteria.
-
-Yet, experimental evidence shows referrals can be biased even under substantial pay-for-performance incentives beyond what is attribuable to differences in network compositions, at least for the case of gender \citep{beaman_job_2018,hederos2025gender}.
-A similar bias against low-SES may further exacerbate outcomes of low-SES individuals: If job information are in the hands of a select few high-SES which low-SES have already limited network access to (social capital hypothesis), and high-SES referrers are biased against low-SES, referring other high-SES at higher rates than their network composition, we should expect referral hiring to further disadvantagee low-SES.
-
-The empirical question we answer in this paper is whether referrers are biased against low-SES peers after accounting for differences in the network SES compositon.
+Equally qualified individuals in terms of productivity face different labor market outcomes based on their socioeconomic status \citep{stansbury2024class}.
+This persistent inequality undermines meritocratic ideals and represents a substantial barrier to economic mobility.
+A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectivity, defined as the share of high-SES connections among low-SES individuals, is the most important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
+In this sense, a lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.
+It implies having worse outcomes when using one's network to find jobs conditional on the capacity to leverage one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.}
+
+Referral hiring—the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities—is a common labor market practice that makes differences in social capital evident.\footnote{Referrals solve some frictions in the search and matching process and benefit both job-seekers and employers.
+As a consequence, referral candidates get hired more often, have lower turnover, and earn higher wages \citep{brown2016informal,dustmann2016referral,friebel2023employee}.} Since referrals originate from the networks of referrers, the composition of referrer networks becomes a crucial channel that propagates inequality.
+Similar individuals across socio-demographic characteristics form connections at higher rates \citep{mcpherson2001birds}, making across-SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
+Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure—that is, even when referring randomly from one's network according to some productivity criteria.
+
+Yet, experimental evidence shows referrals can be biased even under substantial pay-for-performance incentives beyond what is attributable to differences in network compositions, at least in the case of gender \citep{beaman_job_2018,hederos2025gender}.
+A similar bias against low-SES individuals may further exacerbate their outcomes.
+If job information is in the hands of a select few high-SES individuals to whom low-SES individuals already have limited network access due to their lack of economic connectivity, and high-SES referrers are biased against low-SES individuals—referring other high-SES individuals at higher rates than their network composition would suggest—we should expect referral hiring to further disadvantage low-SES individuals.
+
+The empirical question we answer in this paper is whether referrers exhibit bias against low-SES peers after accounting for differences in network SES composition.
 We also evaluate the causal impact of two different incentive structures on referral behavior.
 
-In this study, we study inequalities related to SES combining a university-wide cross-sectional network data set comprising over 4,500 students in which classroom interactions are recorded along with individual attributes.
+In this study, we examine inequalities related to SES by curating a university-wide network dataset comprising over 4,500 students for whom classroom interactions are recorded along with individual attributes.
 We focus on the role of SES in referrals by experimentally investigating whether individuals who are asked to refer a peer tend to refer a same-SES candidate.
 We also explore potential mechanisms behind referral patterns by randomizing participants into two different incentive structures.
-To this end, we conducted a lab-in-the-field experiment with 734 students in a Colombian university.
-Participants were instructed to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent of SAT in US system).
-To incentivize participants to refer qualified candidates, we set earnings dependent on referred candidates' actual university entry exam scores.
+To this end, we conducted a lab-in-the-field experiment with 734 students at a Colombian university.
+We instructed participants to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent to the SAT in the US system).
+To incentivize participants to refer qualified candidates during the experiment, we set earnings to depend on referred candidates' actual university entry exam scores.
 
 Referral hiring in the labor market can range from firm-level formal referral programs asking employees to bring candidates to simply passing on job opportunities between network members \citep{topa2019social}.
-As our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
-Our setting instead resembles situations where contacts share opportunities with each other without the need for the referred candidate to take any action and without revealing the identity of the referrer.
-This eliminates reputational concerns as there is no hiring firm, and puts a lower bound on the expected reciprocity for the referrer in combination with pay-for-performance incentives \citep{witte2021workers,bandiera2009social}.
-At the same time, referring based on university entry exam scores are still an objective, widely accepted measure of ability, and we show evidence that referrers in our setting not only possess accurate information about these signals but are also able to screen more productive individuals from their university network.
+Since our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
+Our setting instead resembles situations where contacts share opportunities with each other without requiring the referred candidate to take any action and without revealing the referrer's identity.
+This eliminates reputational concerns since there is no hiring employer.
+It also establishes a lower bound on the expected reciprocity for the referrer when combined with pay-for-performance incentives \citep{witte2021workers,bandiera2009social}.
+At the same time, referring based on university entry exam scores is still an objective, widely accepted measure of ability.
+We show evidence that referrers in our setting not only possess accurate information about these signals but can also screen more productive individuals from their university network.
 
 In a university setting, class attendance provides essential opportunities for face-to-face interaction between students.
-On the one hand, this reduces network segregation by providing ample opportunities to meet across-SES, because of the exposure to an equal or higher level of high-SES compared to the population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, accounting for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citet{fergusson2021desigualdad}.} On the other hand, as students take more and more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}, which should drive the high- and low-SES networks to segregate.
-Our setting is ideal to study these opposing forces: First, The very high level of income inequality and existence of deeply rooted historical groups in Colombia makes SES differences extremely visible in access to tertiary education, where the rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
-Yet, thanks to the particular standing of the institution we have chosen for this study (Figure \ref{school_quality_income}), all SES groups including both low- and high-SES mix together in this university.
-Second, using administrative data, we are able to reconstruct 734 participants' complete university network based on the number of common courses they have taken together with other students.
-This allows directly identifying the individual characteristics of those getting referrals among all possible candidates, as well as descriptive characterizations of similarity (e.g., in same-SES share) in student networks as a function of the number of classes taken.
+This is a powerful force that reduces network segregation by providing ample opportunities to meet across SES groups, because of exposure to an equal or higher level of high-SES individuals compared to the general population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, accounting for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citep{fergusson2021desigualdad}.} The very high level of income inequality in Colombia makes SES differences extremely visible in access to tertiary education, where rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
+However, in the particular institutional setting we have chosen for this study, different SES groups mix at this university, allowing us to focus on SES diversity within the institution.
+At the same time, as students take more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}.
+This is an opposite force that drives high- and low-SES networks to segregate.
+We observe the net effect of these two opposing forces using administrative data and construct class attendance (enrollment) networks for 734 participants based on the number of common courses they have taken together with other students.
+This allows us to directly identify aggregate characterizations of different SES groups' network compositions as a function of courses taken (e.g., in same-SES share), as well as the individual characteristics of network members who receive referrals among all possible candidates.
 
 We find strong evidence that networks of high- and low-SES participants exhibit same-SES bias.
-Both groups are connected at higher rates with their own SES group than what would be at random given actual group shares at the university (Figure \ref{availability_lses}).
-As students take more courses together within the same program, their networks dwindle in size (Figures \ref{share_same_program_by_tie} and \ref{conns_by_tie}), and become more homogenous in SES-shares (Figure \ref{share_same_ses_by_tie}).
-We identify selection into academic programs as a key mechanism.
-The private university where our study took place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
-These result in programs with very large cost differences within the same university (Figure \ref{fees_with_boxplot}).
-We find that average yearly fee paid per student increases with SES, and the high-SES share in the most expensive program at the university, medicine, drives the network segregation across SES (Figure \ref{ses_distribution_by_fees}).
-
-Do segregated networks account for all the differences in SES referral rates across SES groups?
-Although same-SES referrals are 17\% more common than is suggested by referrer networks, controlling for these, we find no general SES-bias against beyond what is attribuable to network composition.
+On average, both groups connect with their own SES group at higher rates than would occur randomly given actual group shares at the university (12\% for low-SES and 31\% for high-SES).
+As students take more courses together within the same program, their networks dwindle in size and become even more homogeneous in SES shares.
+At 12 courses together (the median number of courses taken together among referrals), the same-SES share increases to 30\% above the university share for low-SES students and 55\% above for high-SES students.
+We identify selection into academic programs as a key mechanism explaining this phenomenon: The private university where our study took place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
+This results in programs with very large cost differences within the same university, with some programs costing up to six times the cheapest one.
+We find that the average yearly fee paid per student increases with SES, and the high-SES share in the most expensive program at the university—medicine—drives a large part of the network segregation across SES groups.
+
+Do segregated networks account for the differences in SES referral rates across SES groups?
+Same-SES referrals are 17\% more common than referrer networks suggest.
+Controlling for differences in network compositions, we find that the entirety of the bias is driven by low-SES referrers.
+We find no bias against low-SES peers beyond what is attributable to differences in network composition.
 Regardless of SES, participants refer productive individuals, and referred candidates are characterized by a very high number of courses taken together.
-The latter underlies the impact of program selection, where smaller and more homogenous parts of the networks are activated for referrals made in our setting.
+The latter underlies the impact of program selection on the intensity of social interaction, where participants activate smaller and more homogeneous parts of their networks for making referrals.
 Our treatment randomized participants across two different incentive schemes by adding a substantial monetary bonus (\$25) for the referred candidate on top of the pay-for-performance incentives.
-We provide evidence that treatment incentives did not change the referral behavior across the same-SES referral rate, the number of courses taken together with the referral candidate, and the candidate's exam scores.
-
-This paper contributes to the literature on referral experiments by solving the challenge of observing the entire referral network.
-Earlier research could only compare referrals made across different incentive structures or experimental instructions and make according conclusions.
-For example, when participants are paid on the basis of their referred candidate's productivity instead of receiving a fixed finder's fee \citep{beaman_who_2012}, or when participants are restrictred to refer either a male or female candidate instead of freely \citep{beaman_job_2018}.
-\citet{pallais_why_2016} recruited a random sample of nonreferred workers to compare with referred ones, but none of the previous studies could provide a direct comparison of the referral choice set with those who were selected by participants.
-Closest to our work is the work of \citet{hederos2025gender}, who elicited friendship networks by asking referrers to name 5 friends.
-Their findings suggest only half of those who were referred were from the elicited friendship network, and thus is not a complete observation of the referral choice set.
-Although commonplace, censored elicitation methods also result in underestimating network effects \citep{griffith2022jle} and may suffer from biases in recall.
-We are able to take our analysis one step further by asking for referrals from the enrollment network, where we have complete information on every single connection that may or may not get a referral.
-This allows us to neatly separate the effect of the network composition from any potential biases stemming from the referral procedure itself.
-
-Second, we build upon to the earlier work on SES-biases in referrals.
-To our knowledge, the first to study SES-biases in referals are \citet{diaz_peer_2025}, and our study is conceptually the closest to theirs.
-Drawing from a similar sample from the same institution, \citet{diaz_peer_2025} focus on referrals from first year students made within mixed-program classrooms, and find no evidence for an aggregate bias against low-SES.
-We also find no aggregate bias against low-SES in referrals.
+We provide evidence that treatment incentives did not change referral behavior across the same-SES referral rate, the number of courses taken together with the referral candidate, and the candidate's exam scores.
+We interpret the lack of differences in the number of courses taken together as further evidence that referrals go to strong social ties across both treatments regardless of the incentive structure.\footnote{This follows directly from earlier evidence showing that referrals tend to go to strong ties, i.e., close friends and/or family members \citep{gee2017social,kramarz2014strong,wang2013marriage}.}
+
+Our main empirical contribution to the experimental referral literature is our observation of the entire network that characterizes the referral choice set.
+Earlier research compares referrals made across different incentive structures and makes inferences about the counterfactual.
+For example, \citet{beaman_who_2012} compared referrers paid based on their referred candidate's productivity instead of receiving a fixed finder's fee, and \citet{beaman_job_2018} compared referrers who were restricted to refer either a male or female candidate instead of choosing freely.
+While \citet{pallais_why_2016} recruited a random sample of non-referred workers for comparison with referred ones, none of the previous studies could identify the entire referral choice set and provide a direct comparison to those who were referred by the participants.
+Observing the entire network allows us to identify biases in referrals in a more natural way, without imposing restrictions on the choice sets.
+A similar approach to ours is \citet{hederos2025gender}, who elicited friendship networks by asking referrers to name 5 close friends.
+Their findings suggest only half of those who were referred were from the elicited friendship network, and thus represent an incomplete observation of the entire referral choice set.
+We take our analysis one step further by requesting referrals from the enrollment network, where we have complete information on every single connection that may or may not receive a referral.
+This allows us to neatly separate the effect of network composition from any potential biases stemming from the referral procedure itself.
+
+Second, we build upon the earlier work on inequalities in referrals and the role of SES differences.
+The reliance of labor markets on referrals, coupled with homophily in social networks, can lead to persistent inequalities in wages and employment \citep{montgomery_social_1991,calvo2004effects,bolte_role_2021}.
+The premise of these models is that referrals exhibit homophily, so that employees are more likely to refer workers of their own race, gender, SES, etc.
+Supporting evidence shows that low-SES individuals have networks with lower shares of high-SES individuals, which partly explains why they have worse labor market outcomes \citep{stansbury2024class,chetty2022na}.
+We contribute by separately identifying the role of network homophily (the tendency to connect with similar others) and referral homophily (the tendency to refer similar others).
+Our results suggest that network homophily, rather than referral homophily, drives SES inequality in our setting.
+
+To our knowledge, \citet{diaz_peer_2025} are the first to study SES biases in referrals, and our study is conceptually the closest to theirs.
+Drawing from a similar sample at the same institution, \citet{diaz_peer_2025} focus on referrals from first-year students made within mixed-program classrooms and find no evidence for an aggregate bias against low-SES individuals.
+We also find no aggregate bias against low-SES individuals in referrals beyond what is attributable to differences in network structure.
 Our setup differs as we sample from students who completed their first year and impose no limits on referring from a classroom.
-This has several implications: We find that referrals in our setup go to individuals within the same program, and that programs have different SES-shares which become more even more accentuated as students take more courses together.
-While networks drive inequality in referral outcomes because of the institional environment in our sample, we have no reason to believe first year student networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
-Following the recent evidence, implementing more mixed-program courses which allow for across-SES mixing can be a clear policy goal \citep{alan2023troeasa,rohrer2021po}.
-
-Finally, we contribute to the growing literature on SES differences in the labor market, expliciting the role of networks as a driver of inequality.
-\citet{stansbury2024class} find that low-SES researchers coauthor more often with other low-SES, and have networks that have lower values which can explain why
+This has several implications: We find that referrals in our setup go to individuals within the same program, and that programs have different SES shares which become even more accentuated as students take more courses together.
+While networks drive inequality in referral outcomes because of the institutional environment in our sample, we have no reason to believe first-year student networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
+Our findings suggest that implementing more mixed-program courses that allow for across-SES mixing should be a clear policy goal to reduce segregation \citep{alan2023troeasa,rohrer2021po}.
 
@@
 In Section \ref{s4} we describe the data and procedures.
-Section \ref{s5} discusses the results of the experiment.
-Section \ref{s6} concludes.
+Section \ref{s5} discusses the results of the experiment and Section \ref{s6} introduces robustness checks.
+Section \ref{s7} concludes.
 The Appendix presents additional tables and figures as well as the experiment instructions.
+
+\section{Background and Setting} \label{s2}
+
+Our study takes place at UNAB, a medium-sized private university in Bucaramanga, Colombia with approximately 6,000 enrolled undergraduate students.
+The university's student body is remarkably diverse, with about 35\% of students classified as low-SES and 15\% as high-SES.
+This diversity at UNAB provides a unique research setting.
+Colombian society is highly unequal and generally characterized by limited interaction between social classes, with different socioeconomic groups separated by education and geographic residence.\footnote{Colombia has consistently ranked as one of the most unequal countries in Latin America \citep{barretoherrera2024regional}, with the richest decile earning 50 times more than the poorest decile \citep{comisioneconomicaparaamericalatinayel2023}.
+This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
+103]{hudson_colombia_2010}.
+UNAB represents one of the few environments in Colombia where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
 
@@
     \footnotesize
-    \item[] \textit{Note:} This figure shows the average score national university entry exam by family income and type of higher education instition.
+    \item[] \textit{Note:} This figure shows the average score national university entry exam by monthly family income and type of higher education institution.
 With average student score in the 65-70 band, the private university where we conducted this experiment caters to low- and high-SES students.
@@
 
-\section{Background and Setting} \label{s2}
-
-Our study takes place at UNAB, a medium-sized private university in Bucaramanga, Colombia with approximately 6,000 enrolled students.
-The university's student body is remarkably diverse with about 35\% of the students classified as low-SES, and 15\% high-SES.
-Diversity at this institution provides a unique research setting as Colombian society is highly unequal and generally characterized by limited interaction between social classes, with different socioeconomic groups separated by education and geographic residence.\footnote{Colombia has consistently ranked as one of the most unequal countries in Latin America \citep{barretoherrera2024regional}, with the richest decile earning 50 times more than the poorest decile \citep{comisioneconomicaparaamericalatinayel2023}.
-This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
-103]{hudson_colombia_2010}, and UNAB represents one of the few environments in Colombia where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
-
-In 1994, Colombia introduced a nationwide classification system dividing the population into 6 strata based on housing characteristics and neighborhood amenities.\footnote{Initially designed for utility subsidies from higher strata (5 and 6) to support lower strata (1 to 3), it now extends to university fees and social program eligibility.
+To operationalize SES in our study, we rely on Colombia's established classification system.
+In 1994, Colombia introduced a nationwide system that divides the population into 6 strata based on housing characteristics and neighborhood amenities.\footnote{Initially designed for utility subsidies from higher strata (5 and 6) to support lower strata (1 to 3), it now extends to university fees and social program eligibility.
 Stratum 4 neither receives subsidies nor pays extra taxes.
-This stratification system largely aligns with and potentially reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.} We use this classification as the measure of SES in our experiment: Students in strata 1 to 2 are categorized as low-SES, strata 3 to 4 as middle-SES and those in strata 5 to 6 as high-SES.
-
-We invited via email all 4,417 UNAB undergraduate students who had at the time of recruitment completed their first year at the university to participate in our experiment.
-837 students who joined (19\%) vary in terms of their academic programs, SES, and progress in their studies.
-This setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are casually documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
-
+This stratification system largely aligns with and potentially reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.} We use this classification as our measure of SES in the experiment.
+Students in strata 1 to 2 are categorized as low-SES, strata 3 to 4 as middle-SES, and those in strata 5 to 6 as high-SES.
+
+For our experiment, we invited via email all 4,417 UNAB undergraduate students who had completed their first year at the university at the time of recruitment.
+The 837 students who joined (19\%) vary in terms of their academic programs, SES, and progress in their studies.
+This experimental setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are causally documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
+
+The institutional setup at UNAB sets up the social contact structure and facilitates the network analysis.
 Undergraduate programs at UNAB are spread across two semesters, with each individual course lasting one semester.
@@
 Medicine, the largest program by size at UNAB, lasts for 12 semesters, followed by engineering programs at 10 semesters.
-Most remaining programs lasting for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4.
+Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
 
@@
 By using existing administrative data, we eliminate the need for additional testing and ensure that all eligible students have comparable productivity measures.
-The scores we use in this experiment comprise of critical reading and mathematics parts.
+The scores we use in this experiment consist of critical reading and mathematics parts.
 
@@
 \subsection{Referral task}
+Building on these productivity measures, our main experimental task involves peer recommendations.
 After eliciting beliefs about their own performance, participants engage in incentivized peer recommendations.
@@
 Participants can only recommend students with whom they have taken at least one class during their university studies.
-This requirement ensures that referrals are based on actual peer interactions and overlap with the enrollment network that we construct.
+This requirement ensures that referrals are based on actual peer interactions and overlaps with the enrollment network that we construct.
 The order in which participants make recommendations across the two areas is randomized.
 
-We incentivize referrals using a productivity-based payment scheme.
+We incentivize referrals using a productivity-based payment scheme that rewards participants for recommending highly ranked peers.
 Referrers earn increasing monetary rewards as the percentile ranking of their recommendation increases (see Figure \ref{piece_rate_by_score}).
-We multiply the piece rate coefficient associated to the percentile rank with the actual test scores of the recommendation to calculate earnings.
-This payment structure provides strong incentives to screen for highly ranked peers, with potential earnings up to \$60 per recommendation.\footnote{Due to the selection into the university, the actual test score distribution has limited variance.
+This payment structure provides strong incentives to screen for highly ranked peers, with potential earnings up to \$60 per recommendation.
+We multiply the piece rate coefficient associated with the percentile rank by the actual test scores of the recommendation to calculate earnings.\footnote{Due to the selection into the university, the actual test score distribution has limited variance.
 Below a certain threshold students cannot qualify for the institution and choose a lower ranked university, and above a certain threshold they have better options to choose from.}
@@
 \subsection{Treatment variation}
+To examine how different incentive structures affect referral behavior, we implement a treatment that varies payment to recommended peers.
 We implement a between-subjects treatment that varies whether the recommended peer also receives payment.
@@
 \subsection{Belief elicitation}
+To understand participants' information and expectations, we collect incentivized beliefs at key points.
 We elicit incentivized beliefs at two points in the experiment.
 First, before making referrals, participants report their beliefs about their own percentile ranking in each test area.
-Second, after making each referral, participants report their beliefs about their recommendedation's percentile ranking.
+Second, after making each referral, participants report their beliefs about their recommendation's percentile ranking.
 For both belief elicitation tasks, participants earn \$5 if their guess is within 7 percentiles of the true value.
@@
 \section{Sample, Incentives, and Procedure} \label{s4}
-We invited all 4,417 UNAB undergraduate students who had at the time of recruitment completed their first year at the university to participate in our experiment.
-A total of 837 students took part in the data collection with a 19\% response rate.
-Our final sample consists of 734 individuals who referred peers with whom they have taken at least one class together, resulting in an 88\% success rate for the sample.
-We randomly allocated half of the participants into either \textbf{Baseline} or \textbf{Bonus} treatments.
+We invited all 4,417 UNAB undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
+A total of 837 students participated in the data collection, yielding a 19\% response rate.
+Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together, resulting in an 88\% success rate for the sample.
+We randomly allocated participants to either \textbf{Baseline} or \textbf{Bonus} treatments.
+
 Table \ref{tab:balance} presents key demographic characteristics and academic performance indicators across treatments (see Appendix Table \ref{tab:selection} for selection).
@@
 The test scores and GPA distributions are balanced.
-On average, participants took 3.8 courses together with their network, and the average network consisted of 175 peers.
+On average, participants had taken 3.8 courses together with members of their network, and the average network consisted of 175 peers.
 
@@
 The experiment was conducted online through Qualtrics, with participants recruited from active UNAB students.
-To manage budget constraints while maintaining sufficient incentives, we randomly selected one in ten participants for payment.
-Selected participants received a fixed payment of \$17 for completion, plus potential earnings from one randomly selected belief question (up to \$5) and one randomly selected recommendation question (up to \$60), for maximum total earnings of \$82.
-The average time to complete the survey was 30 minutes, with an average compensation of \$80 for one in ten participants randomly selected for payment.
-Payment processing occured through online banking platform Nequi within 15 business days of participation.
+To ensure data quality while managing costs, we randomly selected one in ten participants for payment.
+Selected participants received a fixed payment of \$17 for completion, plus potential earnings from one randomly selected belief question (up to \$5) and one randomly selected recommendation question (up to \$60).
+This structure resulted in maximum total earnings of \$82.
+The average time to complete the survey was 30 minutes, with an average compensation of \$80 for the one in ten participants randomly selected for payment.
+Payment processing occurred through online banking platform Nequi within 15 business days of participation.
 
@@
 \subsection{Network characteristics}
-We begin by describing the characteristic features of the ``enrollment network'' for all participants.
-This data set pairwise associates every participant in our sample with another university student if they have taken at least one course together at the time of the data collection.
+We begin by describing the key features of the enrollment network for all participants.
+This network connects every participant in our sample with another university student if they have taken at least one course together at the time of data collection.
 By doing so, we construct the entire referral choice set for participants.
-We include in this data set both the participant's and their potential candidate's individual characterics, as well as the number of common courses they have taken together.
-In Figure \ref{connections_class}, we describe the evolution of the enrollment network across the average number of network connections in network and the number of common courses taken with network members as participants progress through semesters.
+We include in this dataset both the participant's and their potential candidate's individual characteristics, as well as the number of common courses they have taken together.
+Figure \ref{connections_class} describes the evolution of the enrollment network across the average number of network connections and the number of common courses taken with network members as participants progress through semesters.
 
@@
 
+Having established the overall network structure, we now examine differences across SES groups.
 Are enrollment networks different across SES groups?
 We look at how the number of connections (network size) and number of courses taken together (tie strength) change across SES groups in Figure \ref{connections_by_ses}.
-Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, ``denser'' networks.
-Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03, p = .003$ and $t = 2.49, p = .013$, respectively), but high-SES take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20, p < .001$).
+Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, denser networks.
+Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03, p = .003$ and $t = 2.49, p = .013$, respectively), but high-SES students take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20, p < .001$).
 
@@
 \subsection{SES diversity in networks}\label{s:ses-diversity}
-What are diversity related consequences of SES-driven differences across networks?
-In terms of network compositions, SES groups may connect at different rates with other SES groups than at random (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
+What are the diversity-related consequences of SES-driven differences across networks?
+In terms of network compositions, SES groups may connect with other SES groups at different rates than would occur randomly (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
 However, it is important to note that these are not independent observations for each network.
@@
 
-At the same time, we observe much larger differences between SES groups in how they connect on average with others.
+At the same time, we observe much larger differences between SES groups in their connection patterns with other groups.
 Low-SES students connect with other low-SES students at higher rates than middle-SES students (38.4\% vs 31.4\%) and high-SES students (38.4\% vs 25.1\%).
@@
 
+Having examined basic network composition, we now turn to connection intensity.
 So far we have looked at the entire network without considering the intensity of connections between students.
-In our network data set, this variable amounts to the number of classes taken together with peers.
-As we will see in the next section, referrals go to peers with whom participants have taken on average 14 courses with, implying the intensity of the connection matters.
+In our network dataset, this variable amounts to the number of classes taken together with peers.
+As we will see in the next section, referrals go to peers with whom participants have taken an average of 14 courses, implying the intensity of the connection matters.
 We begin by dissecting what the intensity means in our context.
@@
 
-What are the diversity implications of increasing the intensity of connections between students?
+This raises an important question: What are the diversity implications of increased connection intensity between students?
 As students take more courses together with peers, the share of same-SES peers in the networks of low- and high-SES increases while the share of middle-SES declines (see Figure \ref{share_same_ses_by_tie}).
@@
 \subsection{Program selection and SES diversity}
-Academic programs at this university are priced based on how much they cost, and typically less than 5\% of students receive any kind of scholarship \citep{diaz_peer_2025}.
-Based on these, we first calculate how much every program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
-Considering that net minimum montly wage stands at \$200 and the average Colombian salary around \$350, the cost difference between programs are large enough to make an impact of program selection.
+To understand the mechanisms driving these patterns, we examine program selection.
+Academic programs at this university use cost-based pricing, and typically less than 5\% of students receive any kind of scholarship \citep{diaz_peer_2025}.
+Based on this, we first calculate how much every program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
+Considering that net minimum monthly wage stands at \$200 and the average Colombian salary around \$350, the cost differences between programs are large enough to make an impact on program selection.
 Is it the case that SES groups select into programs with financial considerations?
@@
 
-We look at how SES groups are distributed across programs to see evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
+We examine how SES groups are distributed across programs to identify evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
 Indeed, low-SES students select into more affordable programs, followed by middle-SES students.
@@
 
-We observe 1342 referrals from our 734 participants in our final data set.
-More than 90\% of these consist from participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
+We observe 1,342 referrals from our 734 participants in our final dataset.
+More than 90\% of these consist of participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
 While participants made one referral for Math and Reading parts of the exam, about 70\% of these referrals went to two separate individuals.
 We compare the outcomes across areas for unique referrals in Appendix Table \ref{tab:referral_by_area} and all referrals in Appendix Table \ref{tab:referral_area}.
-In both cases, we find no meaningful differences between referrals made Math or Reading areas of the entry exam.
-As referrals in both exam areas come from the same referrer network, we pool referrals per  participant and report their average in terms of outcomes in our main analysis to avoid unintentionally increasing the statistical power of our tests when making comparisions.
+In both cases, we find no meaningful differences between referrals made for Math or Reading areas of the entry exam.
+As referrals in both exam areas come from the same referrer network, we pool referrals per participant and report their averages in our main analysis to avoid inflating statistical power in our comparisons.
 
@@
 Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students.
+
 First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
@@
 However, these differences do not appear to stem from systematic behavioral changes by any particular SES group of referrers, and the overall patterns remain largely consistent across treatments.
-The similarities in academic performance and number of courses taken together suggest that the core selection criteria, i.e., academic merit and social proximity, remain unchanged between conditions.
+The similarities in academic performance and number of courses taken together suggest that the core selection criteria—academic merit and social proximity—remain unchanged between conditions.
 For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
@@
 \subsection{Referral SES composition}
-We first examine the overall SES-compositions in referral selection.
+We first examine the overall SES compositions in referral selection.
 Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Figure \ref{fig:all_referral_rates}).
@@
 High-SES referrals account for 11.1\% compared to 14.9\% network share, an under-representation of 3.8 percentage points.
-While these patterns suggest some deviation from proportional representation - with slight over-referral to low-SES peers and under-referral to high-SES peers - the magnitudes are relatively modest.
+While these patterns suggest some deviation from proportional representation—with slight over-referral to low-SES peers and under-referral to high-SES peers—the magnitudes are relatively modest.
 Overall, referral compositions are largely balanced and closely mirror the underlying network structure, with the largest deviation being less than 5 percentage points for any SES group.
@@
 Most patterns show modest deviations from network composition, with differences typically ranging from 1-6 percentage points.
-However, at the very extremes, i.e., low-SES to high-SES connections and vice versa, we observe the the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
+However, at the very extremes—low-SES to high-SES connections and vice versa—we observe the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
 Low-SES referrers show the strongest same-SES preference, referring 12.9 percentage points more to low-SES students than their network composition would suggest, while under-referring to high-SES recipients by 6.3 percentage points.
@@
 Middle-SES referrers show the most balanced patterns, with deviations generally under 3 percentage points across all recipient groups.
-These findings indicate that cross-SES referral patterns - particularly between the most socioeconomically distant groups - show the largest departures from network availability, suggesting that when SES differences are most pronounced, referral behavior diverges most from underlying network structure.
+Cross-SES referral patterns, particularly between the most socioeconomically distant groups, show the largest departures from network availability.
+These results suggest that referral behavior diverges most from underlying network structure when SES differences are most pronounced.
 
@@
 Network compositions above the median number of courses taken reveal strong segregation effects: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
-Conversely, high-SES are  under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
+Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
 At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
@@
 Middle-SES networks remain relatively balanced and closely track population proportions across all SES groups.
-Taken together, these suggest observed referral rates of SES groups may follow the network compostions above median number of courses taken together.
+Taken together, these suggest observed referral rates of SES groups may follow the network compositions above median number of courses taken together.
 We will test this formally by setting up a choice model where we can take into account individual differences in network compositions across SES, and try to identify SES biases that go beyond SES groups' availability in the choice sets.
@@
 
-We model a single referral outcome from candidates that are mutually exclusive, where our the dependent variable outcome is multinomial distributed.
-Our design leverages the enrollment network to generate dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
+To formally test for SES bias beyond network composition, we employ a choice modeling approach.
+We model a single referral outcome from mutually exclusive candidates, where our dependent variable outcome is multinomial distributed.
+Our design leverages the enrollment network to generate a dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
 Using a conditional logit model on these data, we can identify whether an SES group has an aggregate bias controlling for each individual's unique enrollment network composition.
@@
 
-The CL model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
+The conditional logit model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
 
@@
 
-where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referees that vary across alternatives.
-
+where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referral candidates that vary across alternatives.
 In our context, individual $i$ chooses to refer candidate $j$ from their enrollment network $C_i$.
@@
 
-    \item \textbf{Complete choice sets and independence of irrelevant alternatives.}: Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
+    \item \textbf{Complete choice sets and independence of irrelevant alternatives.} Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
 The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
@@
 We then compute the average of these means and standard deviations across all 734 referrers.
-Each referral candidate's entry exam score and the number of courses they haven taken with the referrer is standardized using these network-level statistics.
+Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these network-level statistics.
 The standardization formula is $z_{i} = (x - \bar{X}_{i}) / \sigma_{i}$, where $\bar{X}_{i}$ and $\sigma_{i}$ are the average of network means and standard deviations for $C_{i}$.
 
-We describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
+We now present our empirical findings and describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
 To begin with, the variance explained by all three models are extremely low, suggesting the role of potential SES biases in referrals that go beyond the network structure must be limited.
@@
 
+Next, we include social proximity controls in our analysis.
 We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
@@
 This same-SES bias is not observed among middle-SES or high-SES referrers, who also display no statistically significant bias toward low-SES candidates.
-None referrer group shows a positive bias for high-SES candidates relative to middle-SES candidates.
+No referrer group shows a positive bias for high-SES candidates relative to middle-SES candidates.
 
@@
 The inclusion of standardized entry exam scores strengthens SES biases.
-Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES .
-Middle-SES referrers, previously showing no SES bias, now show marginal negative bias agaisnt high-SES.
+Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES.
+Middle-SES referrers, previously showing no SES bias, now show marginal negative bias against high-SES.
 Finally, high-SES referrers exhibit marginal negative bias against low-SES candidates.
 
-The evidence of a biases becoming significant when controlling for entry exam scores has a nuanced interpretation.
+The evidence of a bias becoming significant when controlling for entry exam scores has a nuanced interpretation.
 While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students (see Appendix Table \ref{tab:network_connections}).
@@
 
-To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specificaiton.
+To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specification.
 For low-SES referrers, the joint test remains highly significant across all three specifications ($\chi^2 = 10.20$, $p = 0.006$ in the final model), indicating persistent SES bias across all specifications.
@@
 
-\section{Robustness check}
-
-Does the number of courses taken together have an independent effect which goes beyond identifying peers in the same academic program?
-To evaluate this question we leverage our administrative data, and identify peers within the same program: In each individual network we observe the case-specific academic program for the participant making the referral and alternative-specific academic program for each referral candidate.
+\section{Robustness check} \label{s6}
+
+Does the number of courses taken together have an independent effect that goes beyond identifying peers in the same academic program?
+To evaluate this question we leverage our administrative data, and identify peers within the same program: In each individual network we observe the participant-specific academic program for the participant making the referral and alternative-specific academic program for each referral candidate.
 We add this new variable in our specification and describe our findings in Table \ref{tab:ses-heterogeneity-program}.
@@
 The coefficient magnitudes are expectedly smaller compared to specifications without program controls (ranging from 0.688 to 0.930) as the newly added variable is a moderator: Matching academic programs leads to taking more courses together.
-The remaining estimates in our model prove robust to the inclusion of the same-program variable with little change in point estimates.
+The remaining estimates in our model remain robust to the inclusion of the same-program variable with little change in point estimates.
 The persistence of statistical significance (all $p < 0.001$) suggests that the number of courses taken together has an independent effect on referral decisions.
@@
 
-% \begin{table}[H]
-%   \centering
-%   \begin{threeparttable}
-%   \caption{Comparison of math and verbal scores by SES group and data source}
-%   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc}
-%   \toprule
-%   & \multicolumn{3}{c}{Math} & \multicolumn{3}{c}{Verbal} \\
-%   \cmidrule{2-4} \cmidrule{5-7}
-%   & Network & Admin & Sample & Network & Admin & Sample \\
-%   \midrule
-%   Low-SES & 66.976 & 61.653 & 67.813 & 64.738 & 60.974 & 66.058 \\
-%   & (0.052) & (0.346) & (0.694) & (0.043) & (0.274) & (0.574) \\
-%   [1ex]
-%   Mid-SES & 65.627 & 64.531 & 66.859 & 63.685 & 63.154 & 64.779 \\
-%   & (0.039) & (0.224) & (0.580) & (0.032) & (0.183) & (0.436) \\
-%   [1ex]
-%   High-SES & 67.781 & 67.330 & 70.610 & 64.966 & 64.892 & 66.397 \\
-%   & (0.077) & (0.416) & (1.295) & (0.063) & (0.341) & (1.214) \\
-%   \midrule
-%   Observations & 128,150 & 4,415 & 669 & 128,847 & 4,403 & 673 \\
-%   \bottomrule
-%   \end{tabular*}
-%   \begin{tablenotes}[flushleft]
-%   \footnotesize
-%   \item[] \textit{Note:} Standard errors in parentheses.
-The table presents mean scores with standard errors for math and verbal tests across the entire network, the admin data, and the sample.
-Admin data consistently shows lower scores than both network and the sample across all SES groups consistent with selection, with the largest gaps occurring for the Low-SES.
-Differences between network and sample scores are generally smaller than those between either and the admin data.
-%   \end{tablenotes}
-%   \label{tab:ses_scores_comparison}
-%   \end{threeparttable}
-% \end{table}
-
-% \begin{figure}[H]
-%   \centering
-%   \caption{Effect of the Bonus on Referrals}
-%   \begin{subfigure}[t]{0.7\textwidth}
-%     \centering
-%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
-%       \caption{Reading}  
-%       \label{fig:reading_combined}
-%   \end{subfigure}
-%   \begin{subfigure}[t]{0.7\textwidth}
-%     \centering
-%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
-%       \caption{Math}
-%       \label{fig:math_combined}
-%   \end{subfigure}
-%   \label{fig:both_combined}
-%   \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions.
-The bottom panel shows the average standardized math and tie strength of referrals across conditions.
-We test differences in across conditions using two-sample $t$-tests and find no meaningful differences.
-For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%   \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
-%   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
-%   \begin{tablenotes}
-%     \footnotesize
-%     \item[] \textit{Note:} This figure displays the percentage share of top decile individuals according to the admin data across three dimensions.
-First bar shows referrers in the sample of participants.
-Second bar is the share of top decile individuals in their networks.
-Third column shows the share of top decile among the referrals made.
-We test differences between proportions across these three groups using two-sample tests of proportions.
-For both math and reading scores, the differences between Sample and Network ($p<0.001$), Sample and Referrals ($p<0.005$), and Network and Referrals ($p<0.001$) are all statistically significant.
-%   \end{tablenotes}
-% \end{figure}
-
-  % \begin{figure}[H]
-  %   \centering
-  %   \caption{Participant network performance by subject and SES}\label{performance}
-  %   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
-  %   \begin{tablenotes}
-  %     \footnotesize
-  %     \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES.
-We test differences between scores across SES using paired $t$-tests.
-For both math and reading scores, all differences between SES groups are statistically significant (all $p \leq 0.001$).
-  %   \end{tablenotes}
-  % \end{figure}
-
-  % \begin{figure}[H]
-  %   \centering
-  %   \caption{Distribution of top decile performers by subject}\label{topdecile}
-  %   \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/strata_scores.png}
-  %   \begin{tablenotes}
-  %     \footnotesize
-  %     \item[] \textit{Note:} This figure displays the percentage of participants across SES who score in the top decile for math and reading.
-We test differences between math and reading proportions within each SES group using two-sample tests of proportions and find no statistically significant differences ($p > 0.28$).
-Middle-SES students show the highest representation in the top decile for both subjects in the sample.
-  %   \end{tablenotes}
-  % \end{figure}
-
-%   \begin{figure}[H]
-%     \centering
-%     \caption{Participant network composition by SES}
-%     \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
-%     \label{fig:baseline_ses}
-%     \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES.
-We test differences in proportions of peer connections across SES groups using two-sample tests of proportions.
-All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections.
-%     }
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%   \caption{Participant network composition by SES}
-%   \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
-%   \label{fig:tie_ses}
-%   \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
-We test differences in standardized tie strength across SES groups using two-sample $t$-tests.
-All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$).
-The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.}
-% \end{figure}
-
-%   \begin{figure}[H]
-%     \centering
-%     \caption{Baseline Referral Patterns by SES}
-%     \begin{subfigure}[t]{0.49\textwidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
-%         \caption{Referral Rates}
-%         \label{fig:tie_ses}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[t]{0.49\textwidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
-%         \caption{Academic Performance of Referrals}
-%         \label{fig:tie_topses}
-%     \end{subfigure}
-%     \label{fig:tie_combinedses}
-%     \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata.
-The right panel shows the availability of top decile performers within each SES group.}
-%   \end{figure}
-
 \pagebreak
 
-% \begin{figure}[H]
-%   \centering
-%   \caption{Participant network composition by SES}
-%   \includegraphics[width=\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/combined_baseline.png}
-%   \label{fig:baseline_combined}
-%   \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES.
-We test differences in z-score tie strength across SES groups using two-sample $t$-tests.
-All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$).
-The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.
-These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
-% \end{figure}
-
-  % \begin{figure}[H]
-  %   \centering
-  %   \caption{Baseline Referral Patterns by SES}
-  %   \begin{subfigure}[t]{0.49\textwidth}
-  %     \centering
-  %       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_referral_distribution.png}
-  %       \caption{Referral Rates}  
-  %       \label{fig:baseline_rates}
-  %   \end{subfigure}
-  %   \hfill
-  %   \begin{subfigure}[t]{0.49\textwidth}
-  %     \centering
-  %       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
-  %       \caption{Referral Performance}
-  %       \label{fig:baseline_performance}
-  %   \end{subfigure}
-  %   \label{fig:baseline_combined}
-  %   \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across SES in the baseline condition.
-We test differences in SES shares across SES groups using two-sample tests of proportions.
-All differences are statistically significant ($p < 0.1$).
-The right panel shows the average standardized math and reading scores of referred students by referrer's SES.
-We test differences in z-scores across SES groups using two-sample $t$-tests and find no statistically significant differences in reading scores across SES groups (all $p > 0.36$).
-For math scores, we observe marginally significant differences between Low and High SES students ($p = 0.08$) and between Middle and High SES students ($p = 0.18$), with High SES referring peers with higher math performance.}
-  % \end{figure}
-
-%   \begin{figure}[H]
-%     \centering
-%     \caption{Effect of the Bonus}
-%     \label{fig:treat_combined}
-%     \begin{subfigure}[t]{0.49\textwidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
-%         \caption{Changes in Referral Rates}
-%         \label{fig:treat_rates}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[t]{0.49\textwidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
-%         \caption{Changes in Referral Performance}
-%         \label{fig:treat_performance}
-%     \end{subfigure}
-%     \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across SES.
-We test differences in SES shares across conditions using two-sample tests of proportions.
-For Low-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.034$).
-For Middle-SES, only the change in referral share of High-SES is statistically significant ($p = 0.027$).
-For High-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.059$).
-The right panel shows the differences in math and reading z-scores across SES.
-We test differences in SES shares across conditions using two-sample $t$-tests.
-For both reading and math scores, the only statistically significant difference is in the reading scores for Low-SES ($p = 0.026$).}
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%   \caption{Effect of the Bonus on Tie Strength}
-%   \label{fig:treat_combined2}
-%   \begin{subfigure}[t]{0.49\textwidth}
-%       \centering
-%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
-%       \caption{Changes in Referral Rates}
-%       \label{fig:tietreat_rates}
-%   \end{subfigure}
-%   \hfill
-%   \begin{subfigure}[t]{0.49\textwidth}
-%       \centering
-%       \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
-%       \caption{Changes in Referral Performance}
-%       \label{fig:tietreat_performance}
-%   \end{subfigure}
-%   \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline).
-The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%   \caption{Performance by Tie Strength and SES}
-%   \includegraphics[width=0.85\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/tie_combined.png}
-%   \label{fig:tie_score_ses}
-%   \caption*{\footnotesize\textit{Note:} This figure shows local polynomial regressions of network math and reading z-scores by social tie strength across socioeconomic status groups with 95\% confidence intervals.
-Higher SES have steeper positive relationships between tie strength and the average performance those in their network across reading and math scores.}
-% \end{figure}
-
-    \section{Conclusion} \label{s6}
-  In this paper, we study whether SES groups are biased toward one another beyond what is attribuable to differences in their networks, and the effects of different incentive structures on referral behavior.
-Through a lab-in-the-field experiment that leverages enrollment networks at a socially diverse university, we find that the SES biases in referrals orginate mostly from network structures, and referrals under perfomance-pay incentives do not exacerbate existing SES inequalities.
-
-  Our findings reveal that enrollment networks are suprisingly segregated and referrals from these networks reflect closely the choice sets of the referrers.
-We identify a potential mechanism for the observed differences in network structures: Low-SES students select into more affordable programs, and program selection plays a major part in segregating SES groups where low- and high-SES take more courses with their own SES group.
+\section{Conclusion} \label{s7}
+In this paper, we study whether SES groups are biased toward one another beyond what is attributable to differences in their networks, and the effects of different incentive structures on referral behavior.
+Through a lab-in-the-field experiment that leverages enrollment networks at a socially diverse university, we find that the SES biases in referrals originate mostly from network structures, and referrals under performance-pay incentives do not exacerbate existing SES inequalities.
+
+Our findings reveal that enrollment networks are surprisingly segregated and referrals from these networks reflect closely the choice sets of the referrers.
+We identify program selection as the key mechanism driving this segregation.
+Low-SES students select into more affordable programs, and program selection plays a major part in segregating SES groups where low- and high-SES take more courses with their own SES group.
 Consequently, referrals come almost exclusively from the same academic program as the referrer, limiting the SES-diversity of their choice sets.
@@
 We find that only low-SES referrers exhibit a same-SES bias.
-These suggest that the underlying network structure plays a crucial role in referrals, where institutional action can remedy the network segregation.
-
-  These results complement the broader literature where much of the bias in referrals can be attribuable to the ``practical'' choice sets of the referrers.
-While previous work demonstrates that about half of referrals come from a smaller, elicited network of close friends \citep{hederos2025gender}, we go the other way and use administartive data to construct a complete network which presumably includes close social relationships at the institional level.
+These findings suggest that the underlying network structure plays a crucial role in referrals, where institutional action can remedy the network segregation.
+
+These results complement the broader literature where much of the bias in referrals can be attributable to the ``practical'' choice sets of the referrers.
+While previous work demonstrates that about half of referrals come from a smaller, elicited network of close friends \citep{hederos2025gender}, we go the other way and use administrative data to construct a complete network which presumably includes close social relationships at the institutional level.
 Having access to the complete network thus eliminates any potential for under or overestimating taste-based biases \citep{griffith2022jle}.
-Under performance-pay incentives, referrers identify productive others regardless of addtional financial rewards for the referral candidate.
-Still, the lack of a treatment effect suggessts that in both incentive structures referrers pick close ties, shifting the  responsability to institional actors to create diverse environments where cross-SES social interaction can take place more frequently and allow more diversity in networks.
-
-  Looking forward, to achieve SES equality in opportunity institions can play  a crucial role in higher education.
+Under performance-pay incentives, referrers identify productive others regardless of additional financial rewards for the referral candidate.
+Still, the lack of a treatment effect suggests that in both incentive structures referrers pick close ties, shifting the responsibility to institutional actors to create diverse environments where cross-SES social interaction can take place more frequently and allow more diversity in networks.
+
+These findings have policy implications.
+Looking forward, institutions can play a crucial role in achieving SES equality of opportunity in higher education.
 Universities are already a setting in which low-SES get exposed to typically a higher than population share of higher-SES individuals than at other settings \citep{chetty2022n}.
-Yet, segregation within the higher educations institions remain a source for SES inequality.
-If low-SES peers never get to interact in meaningful ways with higher-SES, e.g., by taking courses together, the premise of social mobility thorough social channels remain severly under exploited.
-Future studies should work on ways to reduce SES segregation in collabration with instititons, where having access to complete enrollment networks in addition to the typical friendship elcitation methods could help identfying the exact overlap between the two distinct apporaches.
+Yet, segregation within the higher education institutions remain a source for SES inequality.
+If low-SES peers never get to interact in meaningful ways with higher-SES, e.g., by taking courses together, the premise of social mobility through social channels remains severely underexploited.
+Future studies should work on ways to reduce SES segregation in collaboration with institutions, where having access to complete enrollment networks in addition to the typical friendship elicitation methods could help identifying the exact overlap between the two distinct approaches.
 

### 2025-07-28 writing/manuscript.tex
v1.1
Chapter 3 to-do: fix background and setting, change order results, streamline language, rewrite introduction and conclusion

@@
 \usepackage{threeparttable}
+
+\makeatletter
+\NAT@longnamesfalse
+\makeatother
+
 \newcommand{\footremember}[2]{%
@@
 
+% fast compile
 % \pdfcompresslevel=0
@@
 
-Our study takes place at UNAB, a medium-sized private university in Bucaramanga, Colombia with approximately 6,000 enrolled undergraduate students.
-The university's student body is remarkably diverse, with about 35\% of students classified as low-SES and 15\% as high-SES.
-This diversity at UNAB provides a unique research setting.
-Colombian society is highly unequal and generally characterized by limited interaction between social classes, with different socioeconomic groups separated by education and geographic residence.\footnote{Colombia has consistently ranked as one of the most unequal countries in Latin America \citep{barretoherrera2024regional}, with the richest decile earning 50 times more than the poorest decile \citep{comisioneconomicaparaamericalatinayel2023}.
-This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
-103]{hudson_colombia_2010}.
-UNAB represents one of the few environments in Colombia where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
+Our experiment took place in Colombia, a country that consistently ranks among the most unequal in Latin America.
+The richest decile of Colombians earn 50 times more than the poorest decile \citep{barretoherrera2024regional,comisioneconomicaparaamericalatinayel2023}.
+This economic disparity creates profound differences in outcomes across SES groups in terms of education, geographic residence, language, manners, and social networks \citep{fergusson2021distincion, angulo2012movilidad,garcia2015loteria}.
+While these patterns are not atypical and exist elsewhere \citep{chetty2022na}, Colombia's pronounced inequality makes class-based differences particularly visible.
+This combination of economic, educational, and cultural segregation provides an ideal setting to study SES biases in referral selection.
+
+We rely on Colombia's established estrato classification system to operationalize SES in our study.
+In 1994, Colombia introduced a nationwide system that divides the population into six strata based on  ``similar social and economic characteristics'' \citep[p.
+102]{hudson_colombia_2010}.
+Designed for utility subsidies from higher strata to support lower strata, the system aligns with and reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.
+It is widely used by policymakers and in official statistics \citep{fergusson2021desigualdad}.
+Using the estrato system, we categorize students in strata 1-2 as low-SES, strata 3-4 as middle-SES, and strata 5-6 as high-SES.
+The institutional recognition and widespread use of this system makes Colombia methodologically advantageous for studying SES-based phenomena.
+
+Colombia's educational segregation typically prevents meaningful interaction between socioeconomic groups, as wealthy families attending exclusive private schools while poorer families access lower-quality public or private institutions \citep{fergusson2021distincion}.
+However, non-elite private universities like our partner institution are outliers to this pattern.
+They attract students across the socioeconomic spectrum, unlike elite private institutions that serve primarily high-SES students or public universities that serve mainly low-SES students (see Figure \ref{school_quality_income}).\footnote{Despite significant financial barriers, many low- and middle-SES families pay for private university education for their children \citep[p.
+103]{hudson_colombia_2010}.} Our study takes place at a medium-sized private university in Colombia with approximately 6,000 enrolled undergraduate students.
+Its student body is diverse, comprising approximately 35\% low-SES, 50\% middle-SES, and 15\% high-SES students.
+\footnote{In contrast, government statistics reveal less than 5\% of the population is high-SES \citep[p.
+103]{hudson_colombia_2010}.} This diversity solves the fundamental problem of providing opportunities for different SES groups to meet and interact within the same institutional framework.
+
+\textcolor{orange}{decide what to do here: Beyond providing opportunities for meeting across SES groups (cross-SES contact), the partner university also creates conditions for contact on equal status.
+First, all students at the university pay the same fees based on their program choice, and typically less than 5\% of students receive any scholarship.
+The student body is also relatively homogeneous along other demographic dimensions, being mostly urban and having similar university entry exam scores \textcolor{red}{ADD NUMBERS}.
+According to contact theory, meaningful interaction between groups is most likely to reduce bias when members have equal status within the contact situation \citep{allport1954nature,pettigrew2006meta}.
+The combination of SES diversity and equal institutional status makes this setting particularly well-suited for identifying pure socioeconomic biases in referral behavior, as other potential sources of differentiation are minimized.}
 

### 2025-07-29 writing/manuscript.tex
v1.1.1

--- 2025-06-24 writing/manuscript.tex
@@
 
-Our study takes place at UNAB, a medium-sized private university in Bucaramanga, Colombia with approximately 6,000 enrolled undergraduate students.
-The university's student body is remarkably diverse, with about 35\% of students classified as low-SES and 15\% as high-SES.
-This diversity at UNAB provides a unique research setting.
-Colombian society is highly unequal and generally characterized by limited interaction between social classes, with different socioeconomic groups separated by education and geographic residence.\footnote{Colombia has consistently ranked as one of the most unequal countries in Latin America \citep{barretoherrera2024regional}, with the richest decile earning 50 times more than the poorest decile \citep{comisioneconomicaparaamericalatinayel2023}.
-This economic disparity is reflected by a highly stratified society with significant class inequalities and limited class mobility \citep{angulo2012movilidad,garcia2015loteria}.} Despite significant financial barriers, many lower and middle-SES families prioritize university education for their children \citep[p.
-103]{hudson_colombia_2010}.
-UNAB represents one of the few environments in Colombia where sustained inter-SES contact occurs naturally (see Figure \ref{school_quality_income}).
+Our experiment took place in Colombia, a country that consistently ranks highly in terms of economic inequality.
+The richest decile of Colombians earn 50 times more than the poorest decile \citep{barretoherrera2024regional,comisioneconomicaparaamericalatinayel2023}.
+This economic disparity creates profound differences in outcomes across SES groups in terms of education, geographic residence, language, manners, and social networks \citep{garciavillegas2021dimension, angulo2012movilidad,garcia2015loteria}.
+While these patterns are not atypical and exist elsewhere, Colombia's pronounced inequality makes economic, educational, and cultural differences across SES particularly visible and thus provides an ideal setting to study SES biases in referral selection.
+
+We rely on Colombia's established estrato classification system to measure SES in our study.
+In 1994, Colombia introduced a nationwide system that divides the population into six strata based on  ``similar social and economic characteristics'' \citep[p.
+102]{hudson_colombia_2010}.
+Designed for utility subsidies from higher strata to support lower strata, the system aligns with and reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.
+It is widely used by policymakers and in official statistics \citep{fergusson2021desigualdad}.
+Using the estrato system, we categorize students in strata 1-2 as low-SES, strata 3-4 as middle-SES, and strata 5-6 as high-SES.
+
+Colombia's educational segregation typically prevents meaningful interaction between socioeconomic groups, as wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
+Our study takes place in a non-elite private university which attracts students across the socioeconomic spectrum: The university's student body comprises 35\% low-SES, 50\% middle-SES, and 15\% high-SES students.\footnote{Government statistics reveal less than 5\% of the population is high-SES \citep[p.
+103]{hudson_colombia_2010}.} This diversity provides opportunities for different SES groups to meet and interact within the same institutional framework.
+
+The partner university creates conditions for contact on equal status.
+All students pay the same fees based on their program choices, and less than 5\% of students receive scholarships.
+The student body is mostly urban and has comparable university entry exam scores due to the entrance exam \textcolor{red}{ADD NUMBERS}.
+These additional factors make our setting appropriate to study the effects of contact on intergroup discrimination.
+
+% These factors typically facilitate reducing bias between interacting groups \citep{allport1954nature,rao2019familiarity,mousa2020building,lowe2021types}
+
+% For our experiment, we invited via email all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment.
+These students vary in terms of their academic programs \textcolor{red}{ADD NUMBERS}, SES \textcolor{red}{ADD NUMBERS}, and progress in their studies \textcolor{red}{ADD NUMBERS}.
+
+% Undergraduate students take between 5 to 7 courses per semester, with programs lasting anywhere between 4 to 12 semesters (2 to 6 years).
+Medicine, the largest program by size at the university, lasts for 12 semesters, followed by engineering programs at 10 semesters.
+Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
+
+% 837 students joined the experiment (19\%).
 
@@
 
-To operationalize SES in our study, we rely on Colombia's established classification system.
-In 1994, Colombia introduced a nationwide system that divides the population into 6 strata based on housing characteristics and neighborhood amenities.\footnote{Initially designed for utility subsidies from higher strata (5 and 6) to support lower strata (1 to 3), it now extends to university fees and social program eligibility.
-Stratum 4 neither receives subsidies nor pays extra taxes.
-This stratification system largely aligns with and potentially reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.} We use this classification as our measure of SES in the experiment.
-Students in strata 1 to 2 are categorized as low-SES, strata 3 to 4 as middle-SES, and those in strata 5 to 6 as high-SES.
-
-For our experiment, we invited via email all 4,417 UNAB undergraduate students who had completed their first year at the university at the time of recruitment.
-The 837 students who joined (19\%) vary in terms of their academic programs, SES, and progress in their studies.
-This experimental setup provides a unique opportunity for collaborative inter-class contact on equal status, whose positive effects on reducing discrimination are causally documented \citep{rao2019familiarity, mousa2020building,lowe2021types}.
-
-The institutional setup at UNAB sets up the social contact structure and facilitates the network analysis.
-Undergraduate programs at UNAB are spread across two semesters, with each individual course lasting one semester.
-Students take between 5 to 7 courses per semester, with programs lasting anywhere between 4 to 12 semesters (2 to 6 years).
-Medicine, the largest program by size at UNAB, lasts for 12 semesters, followed by engineering programs at 10 semesters.
-Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
-
 \section{Design} \label{s3}
-
-We designed an experiment to assess peer referral behavior from an SES perspective and to causally evaluate the effect of different incentive structures on referrals.
-The study design consists of a single online experiment organized at the university level (see Figure \ref{timeline}).
-The instructions are provided in Appendix \ref{instructions}.
+We designed an online experiment to assess peer referral selection from an SES perspective and to evaluate the causal effect of providing a bonus to referral candidates.
+The experimental design consisted of two incentivized tasks administered in the following sequence to all participants: First, participants completed belief elicitation tasks about their own performance on the national university entry exam.
+Second, they completed the main referral task, nominating peers based on exam performance in two academic areas.
+Finally, participants reported beliefs about their referrals' performance and provided demographic information.
+This structure allowed us to measure both the accuracy of participants' beliefs and their referral behavior under controlled incentive conditions.
+Figure \ref{timeline} shows the experimental timeline, and detailed instructions are provided in Appendix \ref{instructions}.
 
@@
 \centering
-\caption{Experiment Timeline}\label{timeline}
+\caption{Experimental Timeline}\label{timeline}
 \includegraphics[width=\linewidth]{../figures/timeline.jpg}
@@
 \footnotesize
-\item[] \textit{Note:} Participants first report beliefs about their own national university entry exam performance, then recommend peers for each academic area.
-In the final part, they report beliefs about their recommendations' performance and provide demographic information.
-This order is implemented for all participants.
+\item[] \textit{Note:} Participants first reported beliefs about their own university entry exam performance, then made referrals for each academic area, and finally reported beliefs about their referrals' performance and provided demographics.
 \end{tablenotes}
@@
 
-\subsection{Productivity measures}
-To establish an objective basis for referral productivity, we use national university entry exam scores (SABER 11).
-These scores provide pre-existing, comparable measures of ability across two domains relevant for the labor market.
-By using existing administrative data, we eliminate the need for additional testing and ensure that all eligible students have comparable productivity measures.
-The scores we use in this experiment consist of critical reading and mathematics parts.
-
-Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history).
-This measures students' ability to comprehend and critically evaluate written material.
-Mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
-This captures quantitative reasoning and problem-solving abilities.
-
-For each area, we calculate percentile rankings based on the distribution of scores among all currently enrolled UNAB students, providing a standardized measure of relative performance within the university population.
+\subsection{Performance measures}
+To establish an objective basis for referral performance, we use national university entry exam scores (SABER 11).
+All Colombian high school students take the SABER 11 exam at the end of their final year as a requirement for university admission.
+These scores provide pre-existing, comparable measures of performance.
+By using existing administrative data, we also ensure that all eligible students have comparable performance measures.
+
+The SABER 11 exam consists of five areas (critical reading, mathematics, natural sciences, social sciences, and English).
+We focus on critical reading and mathematics as these represent fundamental skills most relevant across academic programs and future employment.
+Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history), while mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
+These together capture performance in comprehending and critically evaluating written material as well as reasoning and problem-solving abilities.
+
+For each area, we calculate percentile rankings based on the distribution of scores among all currently enrolled students, providing a standardized measure of relative performance within the university population.
 
 \subsection{Referral task}
-Building on these productivity measures, our main experimental task involves peer recommendations.
-After eliciting beliefs about their own performance, participants engage in incentivized peer recommendations.
-For both test areas (critical reading and mathematics), participants recommend one peer they believe excels in that domain.
-We first present an example question from the relevant test area to clarify what skills are being assessed.
-Participants then type the name of their recommended peer, with the system providing autocomplete suggestions from enrolled students who have taken the test (see Figure \ref{interface}).
+The main experimental task involves making referrals among peers.
+For both exam areas (critical reading and mathematics), participants refer one peer they believe excels in that area.
+We provide an example question from the relevant exam area to clarify the skills that are being assessed.
+Participants type the name of their preferred candidate to make a referral.
+To avoid issues with recall, the interface provides autocomplete name and program suggestions from the administrative database (see Figure \ref{interface}).
 
@@
 
-Participants can only recommend students with whom they have taken at least one class during their university studies.
-This requirement ensures that referrals are based on actual peer interactions and overlaps with the enrollment network that we construct.
-The order in which participants make recommendations across the two areas is randomized.
-
-We incentivize referrals using a productivity-based payment scheme that rewards participants for recommending highly ranked peers.
-Referrers earn increasing monetary rewards as the percentile ranking of their recommendation increases (see Figure \ref{piece_rate_by_score}).
-This payment structure provides strong incentives to screen for highly ranked peers, with potential earnings up to \$60 per recommendation.
-We multiply the piece rate coefficient associated with the percentile rank by the actual test scores of the recommendation to calculate earnings.\footnote{Due to the selection into the university, the actual test score distribution has limited variance.
+Participants can only refer students with whom they have taken at least one class during their university studies.
+This requirement ensures that referrals are based on actual peer interactions.
+We randomize the order in which participants make referrals across the two exam areas.
+
+We incentivize referrals using a piece rate payment structure.
+Referrers earn increasing payments as the percentile ranking of their recommendation increases (see Figure \ref{piece_rate_by_score}).
+We multiply the piece rate coefficient associated with the percentile rank by the actual exam scores of the recommendation to calculate earnings.
+This payment structure provides strong incentives to refer highly ranked peers with potential earnings going up to \$60 per referral.
+\footnote{Note that due to the selection into the university, the actual exam score distribution has limited variance.
 Below a certain threshold students cannot qualify for the institution and choose a lower ranked university, and above a certain threshold they have better options to choose from.}
@@
 
-\subsection{Treatment variation}
-To examine how different incentive structures affect referral behavior, we implement a treatment that varies payment to recommended peers.
-We implement a between-subjects treatment that varies whether the recommended peer also receives payment.
-In the \textbf{Baseline} treatment, only the referrer can earn money based on their recommendation's productivity.
-The \textbf{Bonus} treatment adds an additional fixed payment of \$25 to any peer who is recommended in the randomly selected area for payment.
-This payment is independent of the peer's actual productivity (see Figure \ref{tab:treatments}).
+\subsection{Bonus Treatment}
+To examine how different incentive structures affect referral selection, we randomly assign a fixed bonus payment for students who get a referral.
+In the \textbf{Baseline} treatment, only the referrer can earn money based on their referral's performance.
+The \textbf{Bonus} treatment adds an additional fixed payment of \$25 to the peer who gets the referral.
+This payment is independent of the referred candidate's actual performance (see Table \ref{tab:treatments}).
 
@@
   \midrule
-  Referrer (sender) & Productivity-based & Productivity-based \\
-  Recommendation (receiver) & No payment  & Fixed reward  \\
+  Referrer (sender) & Performance-based & Performance-based \\
+  Referral (receiver) & No payment  & Fixed reward  \\
   \bottomrule
@@
 
-Participants are informed about their treatment condition before making recommendations through both video and text instructions.
-The treatment is assigned at the individual level, allowing us to compare referral outcomes across conditions.
+We use a between-subjects design and randomly assign half our participants to the \textbf{Bonus} treatment.
+This allows us to causally identify the effect of the bonus on referral selection.
+Participants learn whether their referral gets the fixed bonus before making referral decisions.
 
 \subsection{Belief elicitation}
-To understand participants' information and expectations, we collect incentivized beliefs at key points.
-We elicit incentivized beliefs at two points in the experiment.
-First, before making referrals, participants report their beliefs about their own percentile ranking in each test area.
-Second, after making each referral, participants report their beliefs about their recommendation's percentile ranking.
-For both belief elicitation tasks, participants earn \$5 if their guess is within 7 percentiles of the true value.
-This tolerance level is expected to balance precision with the difficulty of the task.
+We collect two sets of incentivized beliefs to assess the accuracy of participants' knowledge about exam performance.
+Participants first report beliefs about their own percentile ranking in the university for each exam area.
+After making referrals, participants report their beliefs about their referrals' percentile ranking in the university.
+For both belief elicitation tasks, participants earn \$5 per correct belief if their guess is within 7 percentiles of the true value.
+This margin of error is designed to balance precision with the difficulty of the task.
 
@@
 \section{Sample, Incentives, and Procedure} \label{s4}
-We invited all 4,417 UNAB undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
-A total of 837 students participated in the data collection, yielding a 19\% response rate.
+We invited all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
+A total of 837 students participated in the data collection (19\% response rate).
 Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together, resulting in an 88\% success rate for the sample.
@@
 
-The experiment was conducted online through Qualtrics, with participants recruited from active UNAB students.
+The experiment was conducted online through Qualtrics, with participants recruited from active students.
 To ensure data quality while managing costs, we randomly selected one in ten participants for payment.
-Selected participants received a fixed payment of \$17 for completion, plus potential earnings from one randomly selected belief question (up to \$5) and one randomly selected recommendation question (up to \$60).
+Selected participants received a fixed payment of \$17 for completion.
+They also received potential earnings from one randomly selected belief question (up to \$5) and one randomly selected referral question (up to \$60).
 This structure resulted in maximum total earnings of \$82.
 The average time to complete the survey was 30 minutes, with an average compensation of \$80 for the one in ten participants randomly selected for payment.
-Payment processing occurred through online banking platform Nequi within 15 business days of participation.
+Payment processing occurred through bank transfer within 15 business days of participation.
 
@@
   \midrule
-  Reading score & 62.651 & 65.183 & 0.000 \\
-  Math score & 63.973 & 67.477 & 0.000 \\
-  GPA & 3.958 & 4.012 & 0.000 \\
-  Low-SES & 0.343 & 0.410 & 0.000 \\
+  Reading score & 62.651 & 65.183 & $<0.001$ \\
+  Math score & 63.973 & 67.477 & $<0.001$ \\
+  GPA & 3.958 & 4.012 & $<0.001$ \\
+  Low-SES & 0.343 & 0.410 & $<0.001$ \\
   Middle-SES & 0.505 & 0.499 & 0.763 \\
-  High-SES & 0.153 & 0.091 & 0.000 \\
-  Female & 0.567 & 0.530 & 0.060 \\
-  Age & 21.154 & 20.651 & 0.000 \\
+  High-SES & 0.153 & 0.091 & $<0.001$ \\
+  Female & 0.567 & 0.530 & $<0.001$ \\
+  Age & 21.154 & 20.651 & $<0.001$ \\
   \midrule

### 2025-07-30 writing/manuscript.tex
v1.1.2
Chapter 3 to-do: streamline language, rewrite introduction and conclusion

@@
 
-\section{Design} \label{s3}
+We construct enrollment networks using administrative data to map social connections at the university.
+For each participant, we identify all other undergraduate students with whom they have taken at least one course and create their individual network of university connections.
+The size of this network depends on how many different students a participant has encountered through coursework, while the intensity of connection is measured by the number of courses taken together.
+This approach provides a complete picture of each participant's social environment at the university, including detailed characteristics (i.e., SES, academic program, performance) for both the participant and every person in their network.
+
+\textcolor{cyan}{why don't we introduce number of programs and student count here as background?}
+
+\section{Empirical Specification} \label{s3}
+
+To formally test for SES bias, we use a choice modeling approach.
+We observe a single referral outcome from mutually exclusive candidates.
+Our design leverages the enrollment network to generate a dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
+Using a conditional logit model, we can identify whether an SES group has an aggregate bias controlling for each individual's unique enrollment network composition.
+
+We follow an additive random utility model framework where individual $i$ and alternative $j$ have utility $U_{ij}$ that is the sum of a deterministic component, $V_{ij}$, that depends on regressors and unknown parameters, and an unobserved random component $\varepsilon_{ij}$:
+
+We observe the outcome $y_i = j$ if alternative $j$ has the highest utility of the alternatives.
+The probability that the outcome for individual $i$ is alternative $j$, conditional on the regressors, is:
+
+\begin{align}
+p_{ij} = \Pr(y_i = j) = \Pr(U_{ij} \geq U_{ik}), \quad \text{for all } k
+\end{align}
+
+The conditional logit model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
+
+\begin{align}
+p_{ij} = \frac{\exp(x'_{ij} \beta)}{\sum_{l \in C_i} \exp(x'_{il} \beta)}, \quad j \in C_i
+\end{align}
+
+where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referral candidates that vary across alternatives.
+In our context, individual $i$ chooses to refer candidate $j$ from their enrollment network $C_i$.
+The alternative-specific regressors include SES and entry exam scores of the referral candidate, and the number of courses taken together with the participant making the referral.
+Conditional logit structure eliminates participant-specific factors that might influence both network formation and referral decisions, allowing us to identify preferences within each participant's realized network.
+
+For causal identification of SES bias, we require two identifying assumptions. Specifically:
+
+\begin{enumerate}
+    \item \textbf{Conditional exogeneity.} SES and the number of courses taken together could be endogenous due to program selection.
+High-SES students sort into expensive programs while low-SES students choose affordable programs, creating systematic SES variation across enrollment networks.
+Similarly, the number of courses taken together reflects program selection decisions that may correlate with unobserved referral preferences.
+However, conditional on the realized enrollment network, the remaining variation in both SES and the number of courses taken together across referral candidates must be independent of unobserved factors affecting referral decisions.
+In the robustness checks, we show that being in the same program with the referrer does not impact our SES bias estimates, although it reduces the coefficient on the number of courses taken together.
+
+    \item \textbf{Complete choice sets and independence of irrelevant alternatives.} Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
+The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
+This concern does not apply to our setting because the design of our experiment ensures that choice sets are fixed by enrollment rather than arbitrary inclusion/exclusion of alternatives that create IIA violations.
+\end{enumerate}
+
+Under these assumptions, the conditional logit framework controls for individual heterogeneity in program selection (absorbed by conditioning on choice sets), selection into programs based on observable characteristics (through alternative-specific variables), and choice set composition effects (through the multinomial structure).
+Therefore, $\beta$ should identify the causal effect of referral candidate SES on referral probability, holding constant the number of courses taken together and the entry exam scores of candidates.
+A significant coefficient will then indicate taste-based discrimination.
+
+We pool participants by their SES group, and estimate the above described conditional fixed effects logit model once for low-, middle-, and high-SES referrers.
+We standardize entry exam scores and the number of courses taken together at the individual network level.
+For each referrer's network, we first calculate the mean and standard deviation for both measures.
+We then compute the average of these means and standard deviations across all 734 referrers.
+Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these network-level statistics.
+The standardization formula is $z_{i} = (x - \bar{X}_{i}) / \sigma_{i}$, where $\bar{X}_{i}$ and $\sigma_{i}$ are the average of network means and standard deviations for $C_{i}$.
+
+\section{Design} \label{s4}
 We designed an online experiment to assess peer referral selection from an SES perspective and to evaluate the causal effect of providing a bonus to referral candidates.
-The experimental design consisted of two incentivized tasks administered in the following sequence to all participants: First, participants completed belief elicitation tasks about their own performance on the national university entry exam.
+The experimental design consisted of two incentivized tasks administered in the following sequence: First, participants completed belief elicitation tasks about their own performance on the national university entry exam.
 Second, they completed the main referral task, nominating peers based on exam performance in two academic areas.
@@
 All Colombian high school students take the SABER 11 exam at the end of their final year as a requirement for university admission.
-These scores provide pre-existing, comparable measures of performance.
+The scores from this exam provide pre-existing, comparable measures of performance.
 By using existing administrative data, we also ensure that all eligible students have comparable performance measures.
 
-The SABER 11 exam consists of five areas (critical reading, mathematics, natural sciences, social sciences, and English).
-We focus on critical reading and mathematics as these represent fundamental skills most relevant across academic programs and future employment.
-Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history), while mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
+The exam consists of five areas (critical reading, mathematics, natural sciences, social sciences, and English).
+We focus on critical reading and mathematics as these represent two independent and fundemental skills.
+Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history).
+Mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
 These together capture performance in comprehending and critically evaluating written material as well as reasoning and problem-solving abilities.
@@
 \subsection{Referral task}
-The main experimental task involves making referrals among peers.
+The main task involves making referrals among peers.
 For both exam areas (critical reading and mathematics), participants refer one peer they believe excels in that area.
@@
 We incentivize referrals using a piece rate payment structure.
-Referrers earn increasing payments as the percentile ranking of their recommendation increases (see Figure \ref{piece_rate_by_score}).
-We multiply the piece rate coefficient associated with the percentile rank by the actual exam scores of the recommendation to calculate earnings.
+Referrers earn increasing payments as the percentile ranking of their referral increases (see Figure \ref{piece_rate_by_score}).
+We multiply the piece rate coefficient associated with the percentile rank by the actual exam scores of the referral to calculate earnings.
 This payment structure provides strong incentives to refer highly ranked peers with potential earnings going up to \$60 per referral.
@@
 To examine how different incentive structures affect referral selection, we randomly assign a fixed bonus payment for students who get a referral.
-In the \textbf{Baseline} treatment, only the referrer can earn money based on their referral's performance.
+In the \textbf{Baseline} treatment, only the participants can earn money based on their referral's performance.
 The \textbf{Bonus} treatment adds an additional fixed payment of \$25 to the peer who gets the referral.
-This payment is independent of the referred candidate's actual performance (see Table \ref{tab:treatments}).
+This payment is independent of the referral's actual performance (see Table \ref{tab:treatments}).
 
@@
 
-\section{Sample, Incentives, and Procedure} \label{s4}
+\section{Sample, Incentives, and Procedure} \label{s5}
 We invited all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
 A total of 837 students participated in the data collection (19\% response rate).
-Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together, resulting in an 88\% success rate for the sample.
+Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together (88\% success rate).
 We randomly allocated participants to either \textbf{Baseline} or \textbf{Bonus} treatments.
@@
 \subsection{Network characteristics}
-We begin by describing the key features of the enrollment network for all participants.
-This network connects every participant in our sample with another university student if they have taken at least one course together at the time of data collection.
-By doing so, we construct the entire referral choice set for participants.
-We include in this dataset both the participant's and their potential candidate's individual characteristics, as well as the number of common courses they have taken together.
-Figure \ref{connections_class} describes the evolution of the enrollment network across the average number of network connections and the number of common courses taken with network members as participants progress through semesters.
+We begin by describing the key features of the enrollment networks.
+On average, participants connect with 175 other students, and take an average of 3.62 courses together.
+Figure \ref{connections_class} shows how network characteristics vary by students' time at the university: both the number of connections (network size) and the number of courses taken together (connection intensity) change as participants progress through their studies.
 
@@
     \footnotesize
-    \item[] \textit{Note:} This figure displays the average number of connections in blue and the average number of classes they have taken together with their connections in grey across semesters spent.
-The data shows an increase in the number of classes taken together as students progress in their programs, with the connections peaking around 7 semesters and dropping as certain students finish their bachelor's.
+    \item[] \textit{Note:} 
+    This figure displays the average number of connections in blue and the average number of courses taken together with connections in grey across semesters completed.
+Network size (nb.
+of connections) peaks around 7 semesters before declining as students graduate.
+Connection intensity (nb.
+of courses taken) has an increasing trend.
   \end{tablenotes}
@@
 
-Having established the overall network structure, we now examine differences across SES groups.
-Are enrollment networks different across SES groups?
-We look at how the number of connections (network size) and number of courses taken together (tie strength) change across SES groups in Figure \ref{connections_by_ses}.
-Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, denser networks.
-Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03, p = .003$ and $t = 2.49, p = .013$, respectively), but high-SES students take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20, p < .001$).
-
-\begin{figure}[H]
-  \centering
-  \caption{Network size and courses taken together by SES}\label{connections_by_ses}
-  \includegraphics[width=0.6\linewidth]{../figures/connections_by_ses.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure displays the average number of connections and the average number of classes taken together across SES groups.
-The data shows a decrease in the number of connections with SES, and an associated increase in the number of classes taken together.
-  \end{tablenotes}
-\end{figure}
-
-\subsection{SES diversity in networks}\label{s:ses-diversity}
-What are the diversity-related consequences of SES-driven differences across networks?
-In terms of network compositions, SES groups may connect with other SES groups at different rates than would occur randomly (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
-However, it is important to note that these are not independent observations for each network.
-Estimates are precise because each network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group.
-Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
-For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
-Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.
-
-\begin{figure}[H]
-  \centering
-  \caption{Network shares of SES groups}\label{availability_lses}
-  \includegraphics[width=0.6\linewidth]{../figures/availability_lses.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants.
-Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
-While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
-  \end{tablenotes}
-\end{figure}
-
-At the same time, we observe much larger differences between SES groups in their connection patterns with other groups.
-Low-SES students connect with other low-SES students at higher rates than middle-SES students (38.4\% vs 31.4\%) and high-SES students (38.4\% vs 25.1\%).
-Conversely, high-SES students connect more with other high-SES students than both low-SES students (20.4\% vs 12.6\%) and middle-SES students (20.4\% vs 15.8\%).
-Middle-SES students are in between the two extreme patterns, connecting with middle-SES peers at higher rates than low-SES students (52.9\% vs 49.0\%) but lower rates than high-SES students (52.9\% vs 54.5\%).
-These findings indicate SES-based network segregation, with same-SES homophily patterns across groups.
-
-Having examined basic network composition, we now turn to connection intensity.
-So far we have looked at the entire network without considering the intensity of connections between students.
-In our network dataset, this variable amounts to the number of classes taken together with peers.
-As we will see in the next section, referrals go to peers with whom participants have taken an average of 14 courses, implying the intensity of the connection matters.
-We begin by dissecting what the intensity means in our context.
-As students take more courses together, the proportion of peers from the same academic program quickly goes beyond 95\% (see Figure \ref{share_same_program_by_tie}).
-Similarly, the average network size drops very quickly from above 210 to below 50 (see Figure \ref{conns_by_tie}).
-Both results indicate that actual referral considerations originate from a much smaller pool of individuals from the same academic program.
+We now examine how connection intensity relates to network size and composition.
+First, if two students take more courses together, it is very likely that they are in the same academic program.
+We plot this relationship in Figure \ref{share_same_program_by_tie}: As students take more than 5 courses together, the share of students in their enrollment network from the same academic program quickly exceeds 90\%.
+Second, because students sort into specialized academic programs, increases in courses taken together should result in decreases in connections.
+We plot this relationship in Figure \ref{conns_by_tie}: As students take more than 5 courses together, the size of their enrollment network drops dramatically from above 210 to below 50.
+These patterns reveal that while participants' overall networks are large with relatively few courses taken together on average, they spend most of their time at the university within smaller, more intensive groups of peers from the same academic program.
 
@@
 
+\subsection{Referral characteristics}
+
+Participants made one referral for math and one referral for the reading part of the university entry exam from their enrollment networks.
+We observe 1,342 referrals from 734 participants in our final dataset.
+More than 90\% of these consist of participants referring for both exam areas (see Appendix Table \ref{tab:referral_distribution}).
+About 70\% of these referrals go to two separate individuals.
+We compare the outcomes across exam areas for referrals only going to separate individuals in Appendix Table \ref{tab:referral_by_area} and all referrals in Appendix Table \ref{tab:referral_area}.
+In both cases, we find no meaningful differences between referrals made for Math or Reading areas of the entry exam.
+As referrals in both exam areas come from the same enrollment network, we pool referrals per participant and report their averages in our main analysis to avoid inflating statistical power in our comparisons.
+
+What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network?
+Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students.
+
+First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
+This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties.
+While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
+The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with high social proximity.
+In addition, 93\% of referrals go to students within same program.
+
+\begin{figure}[H]
+  \centering
+  \caption{Courses taken together with network members and referrals}\label{tie_hist}
+  \includegraphics[width=0.6\linewidth]{../figures/tie_hist.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the distributions of the number of courses taken together between referrers and their network members (orange) versus referrers and their chosen referral recipients (dark blue) for all 734 participants.
+75\% of referral recipients take more than 7.5 courses together with the referrer, compared to only 25\% of network members.
+The distributions are significantly different (Kolmogorov-Smirnov test $D = 33.37$, $p < 0.001$).
+  \end{tablenotes}
+\end{figure}
+
+Second, we examine entry exam score differences between referred students and the broader network.
+Referrals go to peers with an average score of 69.5 points, compared to 64.5 points for other network members (see Figure \ref{other_score_hist}).
+This difference of 5 points is significant ($t = 18.97$, $p < 0.001$), indicating that referrers choose higher-performing peers.
+While the median referral recipient scores 71 points, the median network member scores 65.1 points.
+The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
+
+\begin{figure}[H]
+  \centering
+  \caption{Entry exam scores of network members and referrals}\label{other_score_hist}
+  \includegraphics[width=0.6\linewidth]{../figures/other_score_hist.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the distributions of entry exam scores (Math and Reading average) between referrers' network members (orange) versus their chosen referral recipients (dark blue) for all 734 participants.
+75\% of referral recipients score above 65.5 points compared to only 25\% of network members scoring above 66.9 points.
+The distributions are significantly different (Kolmogorov-Smirnov test $D = 71.16$, $p < 0.001$).
+  \end{tablenotes}
+\end{figure}
+
+\subsection{Effect of the Bonus treatment}
+
+Do referred individuals have different outcomes across treatments?
+We compare the performance, number of courses taken together, and SES shares of referred individuals between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
+While performance of referrals across Reading, Math, and GPA are similar across treatments, middle- and high-SES shares have significant differences.
+We find that referrals under the \textbf{Bonus} condition referred a higher proportion of high-SES individuals (13.5\% vs 8.8\%, $p=0.041$) and a lower proportion of middle-SES individuals on average (47.0\% vs 53.7\%, $p=0.072$).
+The similarities in academic performance and number of courses taken together suggest that performance and contact intensity drive referrals regardless of treatment.
+For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
+
+\begin{table}[H]
+  \centering
+  \begin{threeparttable}
+  \caption{Characteristics of referrals by treatment condition}
+  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
+  \toprule
+  & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
+  \midrule
+  Reading score & 67.806 & 67.210 & 0.308 \\
+  Math score & 70.784 & 70.155 & 0.406 \\
+  GPA & 4.155 & 4.149 & 0.799 \\
+  Courses taken & 13.840 & 14.065 & 0.723 \\
+  Low-SES & 0.376 & 0.395 & 0.593 \\
+  Middle-SES & 0.537 & 0.470 & 0.072 \\
+  High-SES & 0.088 & 0.135 & 0.041 \\
+  \midrule
+  Observations & 382 & 352 \\
+  \bottomrule
+  \end{tabular*}
+  \begin{tablenotes}[flushleft]
+  \footnotesize
+  \item[] \textit{Note:} This table compares the characteristics of network members who were referred under baseline vs bonus treatment conditions.
+$p$-values for binary outcomes are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
+All reported \textit{p}-values are two-tailed.
+Reading and math scores are raw test scores out of 100.
+GPA is grade point average out of 5.
+Courses taken is the number of courses participant has taken  with their referral.
+Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1-2, 3-4, or 5-6, respectively.
+Both columns include only network members who were actually nominated for referral in each treatment condition.
+  \end{tablenotes}
+  \label{tab:referral_by_treatment}
+  \end{threeparttable}
+\end{table}
+
+\subsection{Identifying the SES bias in referrals}
+
+We now present our empirical findings and describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
+To begin with, the variance explained by all three models are extremely low, suggesting the role of potential SES biases in referrals that go beyond the network structure must be limited.
+Regardless, controlling for network composition, low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
+In contrast, we find that high-SES participants are less likely to refer other low-SES, relative to the probability of referring middle-SES peers.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES referral & 0.453*** & -0.019 & -0.710** \\
+& (0.109) & (0.098) & (0.333) \\
+High-SES referral & -0.584*** & -0.255* & 0.001 \\
+& (0.211) & (0.145) & (0.261) \\
+\midrule
+$\chi^2$ & 33.47 & 3.18 & 4.94 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+Next, we include social proximity controls in our analysis.
+We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
+A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that intensity of contact substantially increase the probability of referral.
+The high $\chi^2$ statistics suggest that these models explain considerably more variance than specifications without this control, highlighting the predictive power of courses taken together in referral decisions.
+Nevertheless, low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
+This same-SES bias is not observed among middle-SES or high-SES referrers, who also display no statistically significant bias toward low-SES candidates.
+No referrer group shows a positive bias for high-SES candidates relative to middle-SES candidates.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity-extended}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES referral & 0.348*** & -0.064 & -0.489 \\
+& (0.123) & (0.115) & (0.337) \\
+High-SES referral & -0.366 & -0.165 & -0.140 \\
+& (0.223) & (0.157) & (0.286) \\
+Courses taken (z-score) & 0.856*** & 0.931*** & 1.049*** \\
+& (0.035) & (0.037) & (0.126) \\
+\midrule
+$\chi^2$ & 626.15 & 636.10 & 71.43 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring  from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+We add standardized entry exam scores (Math and Reading average) as a second control variable and describe our results in Table \ref{tab:ses-heterogeneity-scores}.
+A one standard deviation increase in the entry exam score proves highly significant across all models, with coefficients ranging from 0.587 to 0.883.
+This shows merit-based considerations due to the incentive structure of the experiment remained central to referral decisions.
+The slightly higher $\chi^2$ statistics compared to the earlier specification suggests that entry exam scores improve model fit.
+The inclusion of standardized entry exam scores strengthens SES biases.
+Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES.
+Middle-SES referrers, previously showing no SES bias, now show marginal negative bias against high-SES.
+Finally, high-SES referrers exhibit marginal negative bias against low-SES candidates.
+
+The evidence of a bias becoming significant when controlling for entry exam scores has a nuanced interpretation.
+While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students (see Appendix Table \ref{tab:network_connections}).
+Controlling for performance thus removes this positive selection and reveals the ``pure'' SES bias that was previously underestimated by above average performance of low-SES.
+Vice versa, high-SES in low-SES networks perform 0.12 standard deviations better than middle-SES students.
+The same bias was underestimated as high-SES candidates' better performance relative to middle-SES in the same networks provided a meritocratic justification for getting more referrals.
+Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of - and counter to - performance-based considerations.
+What makes interpretation difficult is that while biased against low-SES, high-SES referrers do not (under any specification) display a positive bias towards their in-group.
+For this final reason, we do not dig any further in this direction.
+
+To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specification.
+For low-SES referrers, the joint test remains highly significant across all three specifications ($\chi^2 = 10.20$, $p = 0.006$ in the final model), indicating persistent SES bias across all specifications.
+In contrast, middle-SES referrers display no significant joint SES bias in any specification, with the test becoming increasingly non-significant as controls are added ($\chi^2 = 4.13$, $p = 0.127$ in the final model).
+High-SES referrers similarly show no significant joint SES bias across all three models ($\chi^2 = 4.28$, $p = 0.118$ in the final model).
+These results suggest that SES bias in referrals is primarily driven by low-SES.
+There is no sufficient evidence to conclude that middle- and high-SES referrers systematically discriminate against other-SES peers.
+Naturally, this null result occurs once we take into account the potential differences in the network compositions of each SES group.
+In the next section, we explore the differences in the network compositions of different SES groups.
+
+\begin{table}[H]
+\centering
+\begin{threeparttable}
+\caption{SES bias in referral decisions by referrer SES group with academic performance controls}\label{tab:ses-heterogeneity-scores}
+\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
+\toprule
+& \multicolumn{3}{c}{Referrer SES} \\
+& Low & Middle & High \\
+& (1) & (2) & (3) \\
+\midrule
+Low-SES referral & 0.242** & -0.159 & -0.600* \\
+& (0.123) & (0.114) & (0.327) \\
+High-SES referral& -0.445** & -0.274* & -0.345 \\
+& (0.222) & (0.157) & (0.287) \\
+Courses taken (z-score) & 0.859*** & 0.948*** & 1.043*** \\
+& (0.036) & (0.038) & (0.118) \\
+Entry exam (referral z-score) & 0.607*** & 0.587*** & 0.883*** \\
+& (0.052) & (0.047) & (0.111) \\
+\midrule
+$\chi^2$ & 789.87 & 756.06 & 120.54 \\
+Observations & 110,142 & 127,088 & 19,767 \\
+Individuals & 301 & 366 & 67 \\
+\bottomrule
+\end{tabular*}
+\begin{tablenotes}[flushleft]
+\footnotesize
+\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
+* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
+Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
+Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
+All models include individual fixed effects that control for each referrer's choice set composition.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\subsection{SES diversity in networks}\label{s:ses-diversity}
+
+How do enrollment networks differ across SES groups?
+We look at how the number of connections (network size) and number of courses taken together (contact intensity) change across SES groups in Figure \ref{connections_by_ses}.
+Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, denser networks.
+Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03$, $p = 0.003$ and $t = 2.49$, $p = 0.013$, respectively), but high-SES students take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20$, $p < .001$).
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and courses taken together by SES}\label{connections_by_ses}
+  \includegraphics[width=0.6\linewidth]{../figures/connections_by_ses.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average number of connections and the average number of classes taken together across SES groups.
+The data shows a decrease in the number of connections with SES, and an associated increase in the number of classes taken together.
+  \end{tablenotes}
+\end{figure}
+
+What are the diversity-related consequences of SES-driven differences across networks?
+In terms of network compositions, SES groups may connect with other SES groups at different rates than would occur randomly (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
+However, it is important to note that these are not independent observations for each network.
+Estimates are precise because each network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group.
+Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
+For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
+Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network shares of SES groups}\label{availability_lses}
+  \includegraphics[width=0.8\linewidth]{../figures/combined_ses_network_composition.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants.
+Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
+  \end{tablenotes}
+\end{figure}
+
+We observe larger differences between SES groups in their connection patterns with other groups.
+Low-SES students connect with other low-SES students at higher rates than middle-SES students (38.4\% vs 31.4\%) and high-SES students (38.4\% vs 25.1\%).
+Conversely, high-SES students connect more with other high-SES students than both low-SES students (20.4\% vs 12.6\%) and middle-SES students (20.4\% vs 15.8\%).
+Middle-SES students are in between the two extreme patterns, connecting with middle-SES peers at higher rates than low-SES students (52.9\% vs 49.0\%) but lower rates than high-SES students (52.9\% vs 54.5\%).
+These findings indicate SES-based network segregation, with same-SES homophily patterns across groups.
+
 This raises an important question: What are the diversity implications of increased connection intensity between students?
@@
 To understand the mechanisms driving these patterns, we examine program selection.
-Academic programs at this university use cost-based pricing, and typically less than 5\% of students receive any kind of scholarship \citep{diaz_peer_2025}.
+Academic programs at this university use cost-based pricing, and typically less than 5\% of students receive any kind of scholarship.
 Based on this, we first calculate how much every program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
@@
 
-\subsection{Characterizing referrals}
-
-We observe 1,342 referrals from our 734 participants in our final dataset.
-More than 90\% of these consist of participants referring for both areas of the national entry exam (see Appendix Table \ref{tab:referral_distribution}).
-While participants made one referral for Math and Reading parts of the exam, about 70\% of these referrals went to two separate individuals.
-We compare the outcomes across areas for unique referrals in Appendix Table \ref{tab:referral_by_area} and all referrals in Appendix Table \ref{tab:referral_area}.
-In both cases, we find no meaningful differences between referrals made for Math or Reading areas of the entry exam.
-As referrals in both exam areas come from the same referrer network, we pool referrals per participant and report their averages in our main analysis to avoid inflating statistical power in our comparisons.
-
-What are the characteristics of the individuals who receive referrals, and how do they compare to others in the enrollment network?
-Because we have an entire pool of potential candidates with one referral chosen from it, we compare the distributions for our variables of interest between the referred and non-referred students.
-
-First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
-This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties.
-While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
-The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with high social proximity and within same program (93\%).
-
-\begin{figure}[H]
-  \centering
-  \caption{Courses taken together with network members and referrals}\label{tie_hist}
-  \includegraphics[width=0.6\linewidth]{../figures/tie_hist.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the distributions of the number of courses taken together between referrers and their network members (orange) versus referrers and their chosen referral recipients (dark blue) for all 734 participants.
-75\% of referral recipients having taken more than 7.5 courses together with the referrer, compared to only 25\% of network members.
-The distributions are significantly different (Kolmogorov-Smirnov test $D = 33.37$, $p < 0.001$).
-  \end{tablenotes}
-\end{figure}
-
-Second, we examine entry exam score differences between referred students and the broader network.
-Referrals go to peers with an average score of 69.5 points, compared to 64.5 points for other network members (see Figure \ref{other_score_hist}).
-This difference of 5 points is significant ($t = 18.97$, $p < 0.001$), indicating that referrers choose higher-performing peers.
-While the median referral recipient scores 71 points, the median network member scores 65.1 points.
-The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
-
-\begin{figure}[H]
-  \centering
-  \caption{Entry exam scores of network members and referrals}\label{other_score_hist}
-  \includegraphics[width=0.6\linewidth]{../figures/other_score_hist.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the distributions of entry exam scores (Math and Reading average) between referrers' network members (orange) versus their chosen referral recipients (dark blue) for all 734 participants.
-75\% of referral recipients score above 65.5 points compared to only 25\% of network members scoring above 66.9 points.
-The distributions are significantly different (Kolmogorov-Smirnov test $D = 71.16$, $p < 0.001$).
-  \end{tablenotes}
-\end{figure}
-
-\subsection{Effect of the Bonus treatment}
-
-Do referred individuals have different outcomes across treatments?
-We compare the performance, number of courses taken together, and SES shares of referred individuals between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
-While performance of referrals across Reading, Math, and GPA are similar across treatments, middle- and high-SES shares have significant differences.
-We find that referrals under the \textbf{Bonus} condition referred a higher proportion of high-SES individuals (13.5\% vs 8.8\%, $p=0.041$) and a lower proportion of middle-SES individuals on average (47.0\% vs 53.7\%, $p=0.072$).
-However, these differences do not appear to stem from systematic behavioral changes by any particular SES group of referrers, and the overall patterns remain largely consistent across treatments.
-The similarities in academic performance and number of courses taken together suggest that the core selection criteria—academic merit and social proximity—remain unchanged between conditions.
-For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
-
-\begin{table}[H]
-  \centering
-  \begin{threeparttable}
-  \caption{Characteristics of referrals by treatment condition}
-  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
-  \toprule
-  & \multicolumn{1}{c}{\textbf{Baseline Referred}} & \multicolumn{1}{c}{\textbf{Bonus Referred}} & \multicolumn{1}{c}{\textbf{\textit{p}}} \\
-  \midrule
-  Reading score & 67.806 & 67.210 & 0.308 \\
-  Math score & 70.784 & 70.155 & 0.406 \\
-  GPA & 4.155 & 4.149 & 0.799 \\
-  Courses taken & 13.840 & 14.065 & 0.723 \\
-  Low-SES & 0.376 & 0.395 & 0.593 \\
-  Middle-SES & 0.537 & 0.470 & 0.072 \\
-  High-SES & 0.088 & 0.135 & 0.041 \\
-  \midrule
-  Observations & 382 & 352 \\
-  \bottomrule
-  \end{tabular*}
-  \begin{tablenotes}[flushleft]
-  \footnotesize
-  \item[] \textit{Note:} This table compares the characteristics of network members who were referred under baseline vs bonus treatment conditions.
-$p$-values for binary outcomes are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
-All reported \textit{p}-values are two-tailed.
-Reading and math scores are raw test scores out of 100.
-GPA is grade point average out of 5.
-Courses taken is the number of courses participant has taken  with their referral.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1-2, 3-4, or 5-6, respectively.
-Both columns include only network members who were actually nominated for referral in each treatment condition.
-  \end{tablenotes}
-  \label{tab:referral_by_treatment}
-  \end{threeparttable}
-\end{table}
-
 \subsection{Referral SES composition}
-We first examine the overall SES compositions in referral selection.
+We now examine the overall SES compositions in referral selection.
 Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Figure \ref{fig:all_referral_rates}).
@@
 Middle-SES networks remain relatively balanced and closely track population proportions across all SES groups.
-Taken together, these suggest observed referral rates of SES groups may follow the network compositions above median number of courses taken together.
-We will test this formally by setting up a choice model where we can take into account individual differences in network compositions across SES, and try to identify SES biases that go beyond SES groups' availability in the choice sets.
+Taken together, these confirm that the observed referral rates of SES groups follow the network compositions above median number of courses taken together, except for the low-SES.
+We conclude that the referral choices in our setting are mainly driven by availability and performance.
 
@@
 \end{figure}
-
-\subsection{Identifying the SES bias in referrals}
-
-To formally test for SES bias beyond network composition, we employ a choice modeling approach.
-We model a single referral outcome from mutually exclusive candidates, where our dependent variable outcome is multinomial distributed.
-Our design leverages the enrollment network to generate a dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
-Using a conditional logit model on these data, we can identify whether an SES group has an aggregate bias controlling for each individual's unique enrollment network composition.
-
-We follow an additive random utility model framework where individual $i$ and alternative $j$ have utility $U_{ij}$ that is the sum of a deterministic component, $V_{ij}$, that depends on regressors and unknown parameters, and an unobserved random component $\varepsilon_{ij}$:
-
-We observe the outcome $y_i = j$ if alternative $j$ has the highest utility of the alternatives.
-The probability that the outcome for individual $i$ is alternative $j$, conditional on the regressors, is:
-
-\begin{align}
-p_{ij} = \Pr(y_i = j) = \Pr(U_{ij} \geq U_{ik}), \quad \text{for all } k
-\end{align}
-
-The conditional logit model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
-
-\begin{align}
-p_{ij} = \frac{\exp(x'_{ij} \beta)}{\sum_{l \in C_i} \exp(x'_{il} \beta)}, \quad j \in C_i
-\end{align}
-
-where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referral candidates that vary across alternatives.
-In our context, individual $i$ chooses to refer candidate $j$ from their enrollment network $C_i$.
-The alternative-specific regressors include SES and entry exam scores of the referral candidate, and the number of courses taken together with the participant making the referral.
-Conditional logit structure eliminates participant-specific factors that might influence both network formation and referral decisions, allowing us to identify preferences within each participant's realized network.
-
-For causal identification of SES bias, we require two identifying assumptions. Specifically:
-
-\begin{enumerate}
-    \item \textbf{Conditional exogeneity.} SES and the number of courses taken together could be endogenous due to program selection.
-High-SES students sort into expensive programs while low-SES students choose affordable programs, creating systematic SES variation across enrollment networks.
-Similarly, the number of courses taken together reflects program selection decisions that may correlate with unobserved referral preferences.
-However, conditional on the realized enrollment network, the remaining variation in both SES and the number of courses taken together across referral candidates must be independent of unobserved factors affecting referral decisions.
-In the robustness checks, we show that being in the same program with the referrer does not impact our SES bias estimates, although it reduces the coefficient on the number of courses taken together.
-
-    \item \textbf{Complete choice sets and independence of irrelevant alternatives.} Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
-The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
-This concern does not apply to our setting because the design of our experiment ensures that choice sets are fixed by enrollment rather than arbitrary inclusion/exclusion of alternatives that create IIA violations.
-\end{enumerate}
-
-Under these assumptions, the conditional logit framework controls for individual heterogeneity in program selection (absorbed by conditioning on choice sets), selection into programs based on observable characteristics (through alternative-specific variables), and choice set composition effects (through the multinomial structure).
-Therefore, $\beta$ should identify the causal effect of referral candidate SES on referral probability, holding constant the number of courses taken together and the entry exam scores of candidates.
-A significant coefficient will then indicate taste-based discrimination.
-
-We pool participants by their SES group, and estimate the above described conditional fixed effects logit model once for low-, middle-, and high-SES referrers.
-We standardize entry exam scores and the number of courses taken together at the individual network level.
-For each referrer's network, we first calculate the mean and standard deviation for both measures.
-We then compute the average of these means and standard deviations across all 734 referrers.
-Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these network-level statistics.
-The standardization formula is $z_{i} = (x - \bar{X}_{i}) / \sigma_{i}$, where $\bar{X}_{i}$ and $\sigma_{i}$ are the average of network means and standard deviations for $C_{i}$.
-
-We now present our empirical findings and describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
-To begin with, the variance explained by all three models are extremely low, suggesting the role of potential SES biases in referrals that go beyond the network structure must be limited.
-Regardless, controlling for network composition, low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
-In contrast, we find that high-SES participants are less likely to refer other low-SES, relative to the probability of referring middle-SES peers.
-
-\begin{table}[H]
-\centering
-\begin{threeparttable}
-\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity}
-\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
-\toprule
-& \multicolumn{3}{c}{Referrer SES} \\
-& Low & Middle & High \\
-& (1) & (2) & (3) \\
-\midrule
-Low-SES candidate & 0.453*** & -0.019 & -0.710** \\
-& (0.109) & (0.098) & (0.333) \\
-High-SES candidate & -0.584*** & -0.255* & 0.001 \\
-& (0.211) & (0.145) & (0.261) \\
-\midrule
-$\chi^2$ & 33.47 & 3.18 & 4.94 \\
-Observations & 110,142 & 127,088 & 19,767 \\
-Individuals & 301 & 366 & 67 \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}[flushleft]
-\footnotesize
-\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
-* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
-Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
-Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
-All models include individual fixed effects that control for each referrer's choice set composition.
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-Next, we include social proximity controls in our analysis.
-We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
-A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that stronger social connections substantially increase the probability of referral.
-The high $\chi^2$ statistics suggest that these models explain considerably more variance than specifications without this control, highlighting the importance of courses taken together in referral decisions.
-Nevertheless, low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
-This same-SES bias is not observed among middle-SES or high-SES referrers, who also display no statistically significant bias toward low-SES candidates.
-No referrer group shows a positive bias for high-SES candidates relative to middle-SES candidates.
-
-\begin{table}[H]
-\centering
-\begin{threeparttable}
-\caption{SES bias in referral decisions by referrer SES group}\label{tab:ses-heterogeneity-extended}
-\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
-\toprule
-& \multicolumn{3}{c}{Referrer SES} \\
-& Low & Middle & High \\
-& (1) & (2) & (3) \\
-\midrule
-Low-SES candidate & 0.348*** & -0.064 & -0.489 \\
-& (0.123) & (0.115) & (0.337) \\
-High-SES candidate & -0.366 & -0.165 & -0.140 \\
-& (0.223) & (0.157) & (0.286) \\
-Courses taken (z-score) & 0.856*** & 0.931*** & 1.049*** \\
-& (0.035) & (0.037) & (0.126) \\
-\midrule
-$\chi^2$ & 626.15 & 636.10 & 71.43 \\
-Observations & 110,142 & 127,088 & 19,767 \\
-Individuals & 301 & 366 & 67 \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}[flushleft]
-\footnotesize
-\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
-* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
-Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
-Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
-All models include individual fixed effects that control for each referrer's choice set composition.
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-We add standardized entry exam scores (Math and Reading average) as a second control variable and describe our results in Table \ref{tab:ses-heterogeneity-scores}.
-A one standard deviation increase in the entry exam score proves highly significant across all models, with coefficients ranging from 0.587 to 0.883.
-This shows merit-based considerations due to the incentive structure of the experiment remained central to referral decisions.
-The slightly higher $\chi^2$ statistics compared to the earlier specification suggests that entry exam scores improve model fit.
-The inclusion of standardized entry exam scores strengthens SES biases.
-Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES.
-Middle-SES referrers, previously showing no SES bias, now show marginal negative bias against high-SES.
-Finally, high-SES referrers exhibit marginal negative bias against low-SES candidates.
-
-The evidence of a bias becoming significant when controlling for entry exam scores has a nuanced interpretation.
-While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students (see Appendix Table \ref{tab:network_connections}).
-Controlling for performance thus removes this positive selection and reveals the ``pure'' SES bias that was previously underestimated by above average performance of low-SES.
-Vice versa, high-SES in low-SES networks perform 0.12 standard deviations better than middle-SES students.
-The same bias was underestimated as high-SES candidates' better performance relative to middle-SES in the same networks provided a meritocratic justification for getting more referrals.
-Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of - and counter to - performance-based considerations.
-What makes interpretation difficult is that while biased against low-SES, high-SES referrers do not under any specification display a positive bias towards their in-group.
-For this final reason, we do not dig any further in this direction.
-
-To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specification.
-For low-SES referrers, the joint test remains highly significant across all three specifications ($\chi^2 = 10.20$, $p = 0.006$ in the final model), indicating persistent SES bias across all specifications.
-In contrast, middle-SES referrers display no significant joint SES bias in any specification, with the test becoming increasingly non-significant as controls are added ($\chi^2 = 4.13$, $p = 0.127$ in the final model).
-High-SES referrers similarly show no significant joint SES bias across all three models ($\chi^2 = 4.28$, $p = 0.118$ in the final model).
-These results suggest that SES bias in referrals is primarily driven by low-SES.
-There is no sufficient evidence to conclude that middle- and high-SES referrers systematically discriminate against other-SES peers once we take into account the large differences in their network compositions due to program selection.
-
-\begin{table}[H]
-\centering
-\begin{threeparttable}
-\caption{SES bias in referral decisions by referrer SES group with academic performance controls}\label{tab:ses-heterogeneity-scores}
-\begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}}l c c c@{}}
-\toprule
-& \multicolumn{3}{c}{Referrer SES} \\
-& Low & Middle & High \\
-& (1) & (2) & (3) \\
-\midrule
-Low-SES candidate & 0.242** & -0.159 & -0.600* \\
-& (0.123) & (0.114) & (0.327) \\
-High-SES candidate& -0.445** & -0.274* & -0.345 \\
-& (0.222) & (0.157) & (0.287) \\
-Courses taken (z-score) & 0.859*** & 0.948*** & 1.043*** \\
-& (0.036) & (0.038) & (0.118) \\
-Entry exam (candidate z-score) & 0.607*** & 0.587*** & 0.883*** \\
-& (0.052) & (0.047) & (0.111) \\
-\midrule
-$\chi^2$ & 789.87 & 756.06 & 120.54 \\
-Observations & 110,142 & 127,088 & 19,767 \\
-Individuals & 301 & 366 & 67 \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}[flushleft]
-\footnotesize
-\item[] \textit{Note:} Individual-level clustered standard errors in parentheses.
-* $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$.
-Each column represents a separate conditional logit regression estimated on the subsample of referrers from the indicated SES group.
-Coefficients represent log-odds of referring candidates from the specified SES group relative to referring middle-SES candidates.
-All models include individual fixed effects that control for each referrer's choice set composition.
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
 
@@
 The persistence of statistical significance (all $p < 0.001$) suggests that the number of courses taken together has an independent effect on referral decisions.
-To sum, our measure of tie strength seems to capture meaningful social interaction patterns that lead to referrals, and go beyond simply identifying matching academic programs.
+To sum, our measure of contact intensity seems to capture meaningful social interaction patterns that lead to referrals, and go beyond simply identifying matching academic programs.
 
@@
 \midrule
-Low-SES candidate & 0.236** & -0.140 & -0.567* \\
+Low-SES referral & 0.236** & -0.140 & -0.567* \\
 & (0.119) & (0.111) & (0.331) \\
-High-SES candidate& -0.421* & -0.249 & -0.383 \\
+High-SES referral& -0.421* & -0.249 & -0.383 \\
 & (0.220) & (0.158) & (0.281) \\
-Entry exam (candidate z-score) & 0.623*** & 0.590*** & 0.892*** \\
+Entry exam (referral z-score) & 0.623*** & 0.590*** & 0.892*** \\
 & (0.054) & (0.048) & (0.114) \\

### 2025-07-31 writing/manuscript.tex
v1.1.3
Chapter 3 to-do: finish reorganizing results, streamline language, rewrite introduction and conclusion

@@
 \usepackage{threeparttable}
+\bibliographystyle{apacite}
 
@@
 We randomly assign half of the participants to a condition where their referral candidate receives a fixed bonus on top of pay-for-performance referral incentives.
-We find that additional incentives for the referral candidate do not change social proximity with the referral nor the referral quality.
+We find that additional incentives for the referral candidate do not change connection intensity with the referral nor the referral quality.
 Our findings suggest that systematic segregation patterns in networks that alter choice sets matter more than taste-based SES biases in referrals, and highlight the potential for institutional action in promoting SES diversity.
@@
 The remainder of the paper is organized as follows.
-Section \ref{s2} begins with the background and setting in Colombia.
-In Section \ref{s3} we present the design of the experiment.
-In Section \ref{s4} we describe the data and procedures.
-Section \ref{s5} discusses the results of the experiment and Section \ref{s6} introduces robustness checks.
-Section \ref{s7} concludes.
+Section \ref{BS} begins with the background and setting in Colombia.
+In Section \ref{ES} we present the empirical strategy and in Section \ref{Design} we present the design of the experiment.
+In Section \ref{SID} we describe the experimental sample, incentives and the procedure.
+Section \ref{Results} discusses the results of the experiment and Section \ref{Robustness} introduces robustness checks.
+Section \ref{Conclusion} concludes.
 The Appendix presents additional tables and figures as well as the experiment instructions.
 
-\section{Background and Setting} \label{s2}
-
+\section{Background and Setting} \label{BS}
+
+\subsection{Inequality and SES in Colombia}
 Our experiment took place in Colombia, a country that consistently ranks highly in terms of economic inequality.
@@
 This economic disparity creates profound differences in outcomes across SES groups in terms of education, geographic residence, language, manners, and social networks \citep{garciavillegas2021dimension, angulo2012movilidad,garcia2015loteria}.
-While these patterns are not atypical and exist elsewhere, Colombia's pronounced inequality makes economic, educational, and cultural differences across SES particularly visible and thus provides an ideal setting to study SES biases in referral selection.
+While these patterns are not atypical and exist elsewhere, Colombia's pronounced inequality makes economic, educational, and cultural differences across SES particularly visible.
 
@@
 
-Colombia's educational segregation typically prevents meaningful interaction between socioeconomic groups, as wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
-Our study takes place in a non-elite private university which attracts students across the socioeconomic spectrum: The university's student body comprises 35\% low-SES, 50\% middle-SES, and 15\% high-SES students.\footnote{Government statistics reveal less than 5\% of the population is high-SES \citep[p.
-103]{hudson_colombia_2010}.} This diversity provides opportunities for different SES groups to meet and interact within the same institutional framework.
-
-The partner university creates conditions for contact on equal status.
-All students pay the same fees based on their program choices, and less than 5\% of students receive scholarships.
-The student body is mostly urban and has comparable university entry exam scores due to the entrance exam \textcolor{red}{ADD NUMBERS}.
-These additional factors make our setting appropriate to study the effects of contact on intergroup discrimination.
-
-% These factors typically facilitate reducing bias between interacting groups \citep{allport1954nature,rao2019familiarity,mousa2020building,lowe2021types}
-
-% For our experiment, we invited via email all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment.
-These students vary in terms of their academic programs \textcolor{red}{ADD NUMBERS}, SES \textcolor{red}{ADD NUMBERS}, and progress in their studies \textcolor{red}{ADD NUMBERS}.
-
-% Undergraduate students take between 5 to 7 courses per semester, with programs lasting anywhere between 4 to 12 semesters (2 to 6 years).
-Medicine, the largest program by size at the university, lasts for 12 semesters, followed by engineering programs at 10 semesters.
-Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
-
-% 837 students joined the experiment (19\%).
+In higher education, Colombia's pronounced economic equality manifests itself by preventing meaningful interaction between SES groups.
+Wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
+Taken together, the unique ways in which economic inequality manifests itself in the Colombian higher educational setting provides the ideal conditions to study biases related to SES in referral selection.
 
@@
     \item[] \textit{Note:} This figure shows the average score national university entry exam by monthly family income and type of higher education institution.
-With average student score in the 65-70 band, the private university where we conducted this experiment caters to low- and high-SES students.
+With average student scores in the 65-70 band (see Appendix Figures \ref{math_hist} and \ref{reading_hist}), the private university where we conducted this experiment caters to low-, middle- and high-SES students.
 Figure reproduced from \citet{fergusson2021distincion}.
@@
 
-We construct enrollment networks using administrative data to map social connections at the university.
+\subsection{Partner institution and the enrollment network}
+
+Our study takes place in a non-elite private university which attracts students across the socioeconomic spectrum: The university's undergraduate student body comprises 35\% low-SES, 50\% middle-SES, and 15\% high-SES students.\footnote{Government statistics reveal less than 5\% of the population is high-SES \citep[p.
+103]{hudson_colombia_2010}.} This diversity provides opportunities for different SES groups to meet and interact within the same institutional framework.
+
+The opportunities for contact at the university are on equal status.
+All undergraduate students pay the same fees based on their program choices, and less than 5\% of undergraduate students receive scholarships.
+The student body is mostly urban ($>70$\%), not part of an ethnic minority ($>95$\%), and has comparable university entry exam scores (see Appendix Figures \ref{math_hist} and \ref{reading_hist}).
+These make our setting appropriate to study the effects of contact on intergroup discrimination.
+
+% These factors typically facilitate reducing bias between interacting groups \citep{allport1954nature,rao2019familiarity,mousa2020building,lowe2021types}
+
+% For our experiment, we invited via email all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment.
+These students vary in terms of their academic programs \textcolor{red}{ADD NUMBERS}, SES \textcolor{red}{ADD NUMBERS}, and progress in their studies \textcolor{red}{ADD NUMBERS}.
+
+Undergraduate students at the university choose among 32 different academic programs.
+Students take between 5 to 7 courses per semester, and programs last anywhere between 4 to 12 semesters (2 to 6 years).
+The majority (64\%) of students are enrolled in the 10 programs described in Appendix Figure \ref{program_share}.
+Medicine, the largest program by size at the university, lasts for 12 semesters, followed by engineering programs at 10 semesters.
+Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
+
+To map social connections at the university, we construct enrollment networks using administrative data.
 For each participant, we identify all other undergraduate students with whom they have taken at least one course and create their individual network of university connections.
@@
 
-\textcolor{cyan}{why don't we introduce number of programs and student count here as background?}
-
-\section{Empirical Specification} \label{s3}
-
-To formally test for SES bias, we use a choice modeling approach.
-We observe a single referral outcome from mutually exclusive candidates.
-Our design leverages the enrollment network to generate a dataset which includes alternative-specific variables for each referral decision, i.e., SES, courses taken together with the participant making the referral, as well as entry exam scores for not just the chosen alternative but all referral candidates.
-Using a conditional logit model, we can identify whether an SES group has an aggregate bias controlling for each individual's unique enrollment network composition.
-
-We follow an additive random utility model framework where individual $i$ and alternative $j$ have utility $U_{ij}$ that is the sum of a deterministic component, $V_{ij}$, that depends on regressors and unknown parameters, and an unobserved random component $\varepsilon_{ij}$:
-
-We observe the outcome $y_i = j$ if alternative $j$ has the highest utility of the alternatives.
-The probability that the outcome for individual $i$ is alternative $j$, conditional on the regressors, is:
+\section{Empirical Strategy} \label{ES}
+
+We use a conditional logit model to study SES biases in referral selection.
+Our dependent variable follows a multinomial distribution where referrer $i$ selects one candidate $j$ from their enrollment network for two exam areas.
+For each referrer, we observe all potential candidates, i.e, students they took at least one course with, along with their characteristics: SES, courses taken together with the referrer, entry exam scores.
+The conditional logit model with individual fixed effects takes the form:
 
 \begin{align}
-p_{ij} = \Pr(y_i = j) = \Pr(U_{ij} \geq U_{ik}), \quad \text{for all } k
+Y_{ij} = \alpha_i + \beta_1 \text{Referral SES}_{ij} + \beta_2 \text{Courses Together}_{ij} + \beta_2 \text{Referral Exam Score}_{ij} + \varepsilon_{ij}
 \end{align}
 
-The conditional logit model specifies that the probability of individual $i$ choosing alternative $j$ from choice set $C_i$ is given by:
-
-\begin{align}
-p_{ij} = \frac{\exp(x'_{ij} \beta)}{\sum_{l \in C_i} \exp(x'_{il} \beta)}, \quad j \in C_i
-\end{align}
-
-where $x_{ij}$ are alternative-specific regressors, i.e., characteristics of potential referral candidates that vary across alternatives.
-In our context, individual $i$ chooses to refer candidate $j$ from their enrollment network $C_i$.
-The alternative-specific regressors include SES and entry exam scores of the referral candidate, and the number of courses taken together with the participant making the referral.
-Conditional logit structure eliminates participant-specific factors that might influence both network formation and referral decisions, allowing us to identify preferences within each participant's realized network.
-
-For causal identification of SES bias, we require two identifying assumptions. Specifically:
-
-\begin{enumerate}
-    \item \textbf{Conditional exogeneity.} SES and the number of courses taken together could be endogenous due to program selection.
-High-SES students sort into expensive programs while low-SES students choose affordable programs, creating systematic SES variation across enrollment networks.
+where $Y_{ij} = 1$ if referrer $i$ selects candidate $j$, and 0 otherwise.
+The individual fixed effects $\alpha_i$ control for all referrer-specific factors that might influence both network formation and referral decisions.
+We set middle-SES as the base category, so $\beta_1$ is the log-odds estimate for referring low- and high-SES candidates relative to middle-SES.
+Continuous variables are standardized using means and standard deviations calculated by first computing network-level statistics for each referrer, then averaging across all 734 networks.\footnote{Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these sample-level statistics.
+The standardization formula is $z_{i} = (x_{i} - \bar{X}) / \sigma$, where $\bar{X}$ and $\sigma$ are the average mean and standard deviation across participant networks for the measure.} Because we observe two referrals from each referrer, we cluster standard errors at the referrer level to account for the potential correlation within these referral decisions.
+
+The key advantage of this approach is that by conditioning on each referrer's enrollment network, we eliminate selection bias from program choice and other factors that determine who appears in each person's choice set.
+The identifying variation comes from within-network differences in referral decisions, holding constant the pool of available candidates.
+
+We estimate separate models for each referrer SES group to estimate aggregate SES biases across socioeconomic groups.
+
+For causal identification, we require two assumptions.
+First, conditional exogeneity.
+SES and the number of courses taken together could be endogenous due to program selection.
+High-SES students sort into expensive programs while low-SES students choose affordable programs, creating SES variation across enrollment networks.
 Similarly, the number of courses taken together reflects program selection decisions that may correlate with unobserved referral preferences.
 However, conditional on the realized enrollment network, the remaining variation in both SES and the number of courses taken together across referral candidates must be independent of unobserved factors affecting referral decisions.
-In the robustness checks, we show that being in the same program with the referrer does not impact our SES bias estimates, although it reduces the coefficient on the number of courses taken together.
-
-    \item \textbf{Complete choice sets and independence of irrelevant alternatives.} Administrative data captures the complete enrollment network, with all peers who took at least one course with individual $i$ and represent the true choice set for referral decisions (unless participants have potential referral candidates with whom they never took classes).
-The independence of irrelevant alternatives (IIA) assumption requires that choices between any two alternatives be independent of other options in the choice set, which could be problematic if, e.g., peers within the same SES group are viewed as close substitutes.
-This concern does not apply to our setting because the design of our experiment ensures that choice sets are fixed by enrollment rather than arbitrary inclusion/exclusion of alternatives that create IIA violations.
-\end{enumerate}
-
-Under these assumptions, the conditional logit framework controls for individual heterogeneity in program selection (absorbed by conditioning on choice sets), selection into programs based on observable characteristics (through alternative-specific variables), and choice set composition effects (through the multinomial structure).
-Therefore, $\beta$ should identify the causal effect of referral candidate SES on referral probability, holding constant the number of courses taken together and the entry exam scores of candidates.
-A significant coefficient will then indicate taste-based discrimination.
-
-We pool participants by their SES group, and estimate the above described conditional fixed effects logit model once for low-, middle-, and high-SES referrers.
-We standardize entry exam scores and the number of courses taken together at the individual network level.
-For each referrer's network, we first calculate the mean and standard deviation for both measures.
-We then compute the average of these means and standard deviations across all 734 referrers.
-Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these network-level statistics.
-The standardization formula is $z_{i} = (x - \bar{X}_{i}) / \sigma_{i}$, where $\bar{X}_{i}$ and $\sigma_{i}$ are the average of network means and standard deviations for $C_{i}$.
-
-\section{Design} \label{s4}
+As a robustness check, we show that being in the same program with the referrer does not impact our SES bias estimates, although it reduces the coefficient estimate for the number of courses taken together.
+
+Second, the independence of irrelevant alternatives.
+This assumption could be violated if peers within the same SES group are viewed as close substitutes, where adding similar alternatives distorts choice probabilities.
+While this concern may have some validity in our setting,\footnote{Among participants making referrals to two different individuals, half refer to someone else from the same SES, suggesting potential substitutability within SES groups.} Alternative discrete choice models that relax IIA are computationally prohibitive given our large dataset.\footnote{Models such as nested logit become computationally intractable with over 250,000 observations across 734 individuals.} We therefore proceed with the conditional logit framework while acknowledging this limitation.
+
+\section{Design} \label{Design}
 We designed an online experiment to assess peer referral selection from an SES perspective and to evaluate the causal effect of providing a bonus to referral candidates.
@@
   \caption{Referral task interface}\label{interface}
-  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/interface.png}
+  \includegraphics[width=0.6\linewidth]{../figures/interface.png}
   \begin{tablenotes} 
@@
   \caption{Referral incentives}\label{piece_rate_by_score}
-  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/piece_rate_by_score.png}
+  \includegraphics[width=0.6\linewidth]{../figures/piece_rate_by_score.png}
   \begin{tablenotes}
@@
 
-\section{Sample, Incentives, and Procedure} \label{s5}
+\section{Sample, Incentives, and Procedure} \label{SID}
 We invited all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
@@
 
-\section{Results} \label{s5}
+\section{Results} \label{Results}
 
@@
 While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
-The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with high social proximity.
-In addition, 93\% of referrals go to students within same program.
+The interquartile range for referrals spans from 7.5 to 19.5 courses, compared to just 2.1 to 4.0 courses for the broader network, highlighting the concentration of referrals among peers with higher connection intensity.
+In addition, 93\% of referrals go to students in the same program as the referrer.
 
@@
 While the median referral recipient scores 71 points, the median network member scores 65.1 points.
-The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the clear concentration of referrals among higher performing peers.
+The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the  concentration of referrals among higher performing peers.
 
@@
 
-Next, we include social proximity controls in our analysis.
+Next, we include a control for connection intensity in our analysis.
 We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
@@
 
-\section{Robustness check} \label{s6}
+\section{Robustness check} \label{Robustness}
 
@@
 
-\section{Conclusion} \label{s7}
+\section{Conclusion} \label{Conclusion}
 In this paper, we study whether SES groups are biased toward one another beyond what is attributable to differences in their networks, and the effects of different incentive structures on referral behavior.
@@
 
-\bibliographystyle{apacite}
-
 \bibliography{referrals}    
@@
 \subsection*{Additional Figures}
+
+\begin{figure}[H]
+  \centering
+  \caption{Distribution of exam scores at the university }
+  \begin{subfigure}[t]{0.49\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/math_hist.png}
+      \caption{Math scores at the university}  
+      \label{math_hist}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/reading_hist.png}
+      \caption{Reading scores at the university}
+      \label{reading_hist}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} Reading scores (left panel) and math scores (right panel) show tight distributions with approximately 75\% of students falling within just 13-15 points of each other.
+  }
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Distribution of students across undergraduate programs}\label{program_share}
+  \includegraphics[width=0.6\linewidth]{../figures/program_share.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure shows the concentration of students across 32 undergraduate programs at the university.
+Students cluster around certain programs.
+The top 5 most popular programs (Medicine, Law, Biomedical Engineering, Pharmacy Technology, and Business Administration) account for 43\% of all undergraduates, and the top 10 most popular programs account for 63\% of students.
+  \end{tablenotes}
+\end{figure}
+
 \pagebreak
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/bonus_structure.png}
+    \includegraphics[width=0.65\textwidth]{../figures/bonus_structure.png}
     \caption{Earnings for recommendation questions}

### 2025-08-01 writing/manuscript.tex
v1.1.4
Chapter 3 to-do: streamline language, rewrite introduction+lit review and conclusion

@@
 In Section \ref{SID} we describe the experimental sample, incentives and the procedure.
-Section \ref{Results} discusses the results of the experiment and Section \ref{Robustness} introduces robustness checks.
+Section \ref{Results} discusses the results of the experiment and Section \ref{MandRC} discusses potential mechanisms and robustness checks.
 Section \ref{Conclusion} concludes.
@@
 Our dependent variable follows a multinomial distribution where referrer $i$ selects one candidate $j$ from their enrollment network for two exam areas.
-For each referrer, we observe all potential candidates, i.e, students they took at least one course with, along with their characteristics: SES, courses taken together with the referrer, entry exam scores.
+For each referrer, we observe all potential candidates, i.e, students they took at least one course with, along with their characteristics.
 The conditional logit model with individual fixed effects takes the form:
 
-\begin{align}
-Y_{ij} = \alpha_i + \beta_1 \text{Referral SES}_{ij} + \beta_2 \text{Courses Together}_{ij} + \beta_2 \text{Referral Exam Score}_{ij} + \varepsilon_{ij}
+\begin{align} \label{eq1}
+Y_{ij} = \alpha_i + \beta_{1} SES_{ij} + \beta_{2} X_{ij} + \varepsilon_{ij}
 \end{align}
@@
 where $Y_{ij} = 1$ if referrer $i$ selects candidate $j$, and 0 otherwise.
-The individual fixed effects $\alpha_i$ control for all referrer-specific factors that might influence both network formation and referral decisions.
 We set middle-SES as the base category, so $\beta_1$ is the log-odds estimate for referring low- and high-SES candidates relative to middle-SES.
-Continuous variables are standardized using means and standard deviations calculated by first computing network-level statistics for each referrer, then averaging across all 734 networks.\footnote{Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these sample-level statistics.
-The standardization formula is $z_{i} = (x_{i} - \bar{X}) / \sigma$, where $\bar{X}$ and $\sigma$ are the average mean and standard deviation across participant networks for the measure.} Because we observe two referrals from each referrer, we cluster standard errors at the referrer level to account for the potential correlation within these referral decisions.
+$X_{ij}$ includes the remaining characteristics of referral candidates in the enrollment network that improve model fit such as  entry exams scores and the number of courses taken together with the referrer.
+These continuous variables are standardized using means and standard deviations calculated by first computing network-level statistics for each referrer, then averaging across all 734 networks.\footnote{Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these sample-level statistics.
+The standardization formula is $z_{i} = (x_{i} - \bar{X}) / \sigma$, where $\bar{X}$ and $\sigma$ are the average mean and standard deviation across participant networks for the measure.} The individual fixed effects $\alpha_i$ control for all referrer-specific factors that might influence both network formation and referral decisions.
+Because we observe two referrals from each referrer, we cluster standard errors at the referrer level to account for the potential correlation within these referral decisions.
 
@@
 
-\subsection{Referral characteristics}
+\subsection{Referral characteristics} \label{RC}
 
@@
 
-Do referred individuals have different outcomes across treatments?
-We compare the performance, number of courses taken together, and SES shares of referred individuals between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
-While performance of referrals across Reading, Math, and GPA are similar across treatments, middle- and high-SES shares have significant differences.
-We find that referrals under the \textbf{Bonus} condition referred a higher proportion of high-SES individuals (13.5\% vs 8.8\%, $p=0.041$) and a lower proportion of middle-SES individuals on average (47.0\% vs 53.7\%, $p=0.072$).
-The similarities in academic performance and number of courses taken together suggest that performance and contact intensity drive referrals regardless of treatment.
+Do referrals across treatments have different outcomes?
+We compare the performance and the number of courses taken together with the referrer between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
+We find that the the number of courses taken together with referrer, as well as performance measures across Reading, Math, and GPA are similar across treatments.
+Taken together, the similarities in academic performance and contact intensity suggest these two factors drive referrals regardless of treatment.
 For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
@@
   Courses taken & 13.840 & 14.065 & 0.723 \\
-  Low-SES & 0.376 & 0.395 & 0.593 \\
-  Middle-SES & 0.537 & 0.470 & 0.072 \\
-  High-SES & 0.088 & 0.135 & 0.041 \\
   \midrule
@@
 Courses taken is the number of courses participant has taken  with their referral.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1-2, 3-4, or 5-6, respectively.
-Both columns include only network members who were actually nominated for referral in each treatment condition.
+Both columns only include network members who were referred in each treatment.
   \end{tablenotes}
@@
 
+\subsection{Referral SES composition}
+
+To motivate the SES related biases in referral selection, we now examine the overall SES composition of referrals compared to the average network availability.
+Descriptively, referral patterns largely mirror underlying network structure.\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
+However, it is important to note that these are not independent observations.
+Each enrollment network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group.
+Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
+For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Referrals to low-SES peers constitute 37.9\% of all referrals compared to 33.7\% network representation, middle-SES referrals account for 51.0\% versus 51.4\% network share, and high-SES referrals represent 11.1\% compared to 14.9\% network availability (see Figure \ref{fig:all_referral_rates}).
+The largest deviation is less than 5 percentage points for any SES group.
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral patterns compared to network composition}
+  \label{fig:all_referral_rates}
+  \includegraphics[width=0.6\linewidth]{../figures/all_referral_rates.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray).
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
+
+Examining patterns by referrer SES reveals larger deviations.
+Low-SES referrers have the largest same-SES deviation, referring 12.9 percentage points more to low-SES students than their network composition suggests, while high-SES referrers under-refer to low-SES students by 10.9 percentage points (see Figure \ref{fig:all_ses_referral_rates}).
+These descriptive findings suggest that referral behavior diverges most from underlying network structure when SES differences are most pronounced and motivate our formal analysis.
+
+\begin{figure}[H]
+  \centering
+  \caption{Referral patterns by referrer SES compared to network composition}
+  \label{fig:all_ses_referral_rates}
+  \includegraphics[width=0.6\linewidth]{../figures/all_ses_referral_rates.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray) for each SES group.
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
+
 \subsection{Identifying the SES bias in referrals}
 
-We now present our empirical findings and describe our first set of findings in Table \ref{tab:ses-heterogeneity}.
-To begin with, the variance explained by all three models are extremely low, suggesting the role of potential SES biases in referrals that go beyond the network structure must be limited.
-Regardless, controlling for network composition, low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
+We now analyze the results of the regression specification in Equation \ref{eq1} and describe our findings in Table \ref{tab:ses-heterogeneity}.
+We run three separate regressions, one for each referrer SES group, with a single regressor which is the referral candidate's SES.
+Controlling for network composition, we find that low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
 In contrast, we find that high-SES participants are less likely to refer other low-SES, relative to the probability of referring middle-SES peers.
@@
 
-Next, we include a control for connection intensity in our analysis.
+Next, we include a control for connection intensity.
 We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
 A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that intensity of contact substantially increase the probability of referral.
-The high $\chi^2$ statistics suggest that these models explain considerably more variance than specifications without this control, highlighting the predictive power of courses taken together in referral decisions.
+The high $\chi^2$ statistics suggest that the model with this regressor provides a better fit than a model without.
 Nevertheless, low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
@@
 
-We add standardized entry exam scores (Math and Reading average) as a second control variable and describe our results in Table \ref{tab:ses-heterogeneity-scores}.
-A one standard deviation increase in the entry exam score proves highly significant across all models, with coefficients ranging from 0.587 to 0.883.
+We then add standardized entry exam scores as a second control variable and describe our results in Table \ref{tab:ses-heterogeneity-scores}.
+A one standard deviation increase in the entry exam score (math and critical reading average) proves highly significant across all models, with coefficients ranging from 0.587 to 0.883.
 This shows merit-based considerations due to the incentive structure of the experiment remained central to referral decisions.
 The slightly higher $\chi^2$ statistics compared to the earlier specification suggests that entry exam scores improve model fit.
-The inclusion of standardized entry exam scores strengthens SES biases.
-Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES.
+The inclusion of standardized entry exam scores strengthens SES biases: Low-SES referrers maintain their same-SES bias, with now a significant negative bias against high-SES.
 Middle-SES referrers, previously showing no SES bias, now show marginal negative bias against high-SES.
@@
 While at the university-level, low-SES typically score lower in the entry exam, low-SES students appearing in high-SES networks are positively selected, scoring about 0.14 standard deviations higher than middle-SES students (see Appendix Table \ref{tab:network_connections}).
-Controlling for performance thus removes this positive selection and reveals the ``pure'' SES bias that was previously underestimated by above average performance of low-SES.
+Controlling for performance thus removes this positive selection and reveals the SES bias that was previously underestimated by above average performance of low-SES.
 Vice versa, high-SES in low-SES networks perform 0.12 standard deviations better than middle-SES students.
-The same bias was underestimated as high-SES candidates' better performance relative to middle-SES in the same networks provided a meritocratic justification for getting more referrals.
-Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of - and counter to - performance-based considerations.
-What makes interpretation difficult is that while biased against low-SES, high-SES referrers do not (under any specification) display a positive bias towards their in-group.
-For this final reason, we do not dig any further in this direction.
-
-To conclude, we conduct joint significance tests, testing whether low- and high-SES regression coefficients are jointly different from middle-SES for each regression specification.
-For low-SES referrers, the joint test remains highly significant across all three specifications ($\chi^2 = 10.20$, $p = 0.006$ in the final model), indicating persistent SES bias across all specifications.
-In contrast, middle-SES referrers display no significant joint SES bias in any specification, with the test becoming increasingly non-significant as controls are added ($\chi^2 = 4.13$, $p = 0.127$ in the final model).
-High-SES referrers similarly show no significant joint SES bias across all three models ($\chi^2 = 4.28$, $p = 0.118$ in the final model).
-These results suggest that SES bias in referrals is primarily driven by low-SES.
-There is no sufficient evidence to conclude that middle- and high-SES referrers systematically discriminate against other-SES peers.
-Naturally, this null result occurs once we take into account the potential differences in the network compositions of each SES group.
-In the next section, we explore the differences in the network compositions of different SES groups.
+The bias was underestimated as high-SES candidates' better performance relative to middle-SES increased referrals.
+Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of -- and counter to -- performance-based considerations.
+What makes a symmetric bias interpretation difficult is that while biased against low-SES, high-SES referrers do not (under any specification) display a positive bias towards their in-group.
+
+We conclude that the SES bias in referral selection is primarily driven by low-SES referrers who exhibit strong in-group preferences.
+Middle- and high-SES referrers show no systematic discrimination against other SES groups once we account for network composition and other relevant factors contributing to the referral decision.
+We will explore potential mechanisms that help explain this unexpected result.
 
@@
 
-\subsection{SES diversity in networks}\label{s:ses-diversity}
+\section{Potential Mechanisms and Robustness Checks } \label{MandRC}
+\subsection{SES diversity in networks} \label{s:ses-diversity}
 
@@
 What are the diversity-related consequences of SES-driven differences across networks?
-In terms of network compositions, SES groups may connect with other SES groups at different rates than would occur randomly (Figure \ref{availability_lses}).\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
-However, it is important to note that these are not independent observations for each network.
-Estimates are precise because each network is a draw with replacement from the same pool of university population, from which we calculate the proportion of SES groups per individual network, and take the average over an SES group.
-Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
-For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Our results reveal modest deviations from university-wide SES composition across groups.
-Low-SES students have networks with 38.4\% low-SES peers compared to the university average of 34.3\%, middle-SES students connect with 52.9\% middle-SES peers versus the university average of 50.5\%, and high-SES students show 20.4\% high-SES connections compared to the university average of 15.3\%.
+In terms of network compositions, participants could connect with other SES groups at different rates than would occur randomly depending on their own SES.
+We illustrate the average network shares conditional on referrer SES for low-SES in Figure \ref{connections_to_low_ses} and for high-SES in Figure \ref{connections_to_high_ses}.\footnote{For sake of brevity we omit middle-SES from this exposition.
+For the complete relationship, see Appendix Figure \ref{connections_by_ses_app}.} We observe modest deviations from university-wide SES shares in enrollment networks: Low-SES referrers have on average 38.4\% low-SES peers compared to the university average of 34.3\%, while high-SES referrers have 20.4\% high-SES connections compared to the university average of 15.3\%.
+
+We find larger differences when studying connections between SES groups: Low-SES referrers connect with other low-SES at much higher rates than high-SES referrers (38.4\% vs 25.1\%).
+Conversely, high-SES referrers connect more with other high-SES than low-SES referrers (20.4\% vs 12.6\%).
+Middle-SES referrers are in between the two extreme patterns, connecting with middle-SES at higher rates than low-SES referrers (52.9\% vs 49.0\%) but lower rates than high-SES referrers (52.9\% vs 54.5\%).
+These findings indicate SES-based segregation in networks, with same-SES homophily across groups.
 
@@
   \caption{Network shares of SES groups}\label{availability_lses}
-  \includegraphics[width=0.8\linewidth]{../figures/combined_ses_network_composition.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants.
-Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
-While the share of low-SES peers in the network decreases as the SES of the group increases, the share of high-SES peers in the network increases.
-  \end{tablenotes}
-\end{figure}
-
-We observe larger differences between SES groups in their connection patterns with other groups.
-Low-SES students connect with other low-SES students at higher rates than middle-SES students (38.4\% vs 31.4\%) and high-SES students (38.4\% vs 25.1\%).
-Conversely, high-SES students connect more with other high-SES students than both low-SES students (20.4\% vs 12.6\%) and middle-SES students (20.4\% vs 15.8\%).
-Middle-SES students are in between the two extreme patterns, connecting with middle-SES peers at higher rates than low-SES students (52.9\% vs 49.0\%) but lower rates than high-SES students (52.9\% vs 54.5\%).
-These findings indicate SES-based network segregation, with same-SES homophily patterns across groups.
-
-This raises an important question: What are the diversity implications of increased connection intensity between students?
+  \begin{subfigure}[t]{0.4\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/connections_to_low_ses.png}
+      \caption{Low-SES network share}  
+      \label{connections_to_low_ses}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.4\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/connections_to_high_ses.png}
+      \caption{High-SES network share}
+      \label{connections_to_high_ses}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES.
+Horizontal lines plot the university-wide shares of SES groups (Low: 35\%, High: 14\%).
+While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
+Error bars represent 95\% confidence intervals.
+}
+\end{figure}
+
+While same-SES students are connected more often with each other, so far we did not look at the consequences in terms of number of courses taken together with network members.
+What are the diversity implications of increased connection intensity between students?
 As students take more courses together with peers, the share of same-SES peers in the networks of low- and high-SES increases while the share of middle-SES declines (see Figure \ref{share_same_ses_by_tie}).
 Both increases are substantial, amounting to 50\% for high-, and 30\% for low-SES.
-Combining these with the earlier result that beyond 5 courses taken together network members are almost entirely within the same program, these suggest program selection may have strong consequences for SES diversity in our setting.
-
-\begin{figure}[H]
-  \centering
-  \caption{Network size and courses taken together by courses taken}\label{share_same_ses_by_tie}
+Considering that beyond 5 courses taken together network members are almost entirely within the same program, these suggest program selection may have strong consequences for SES diversity in our setting.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network size and connection intensity}\label{share_same_ses_by_tie}
   \includegraphics[width=0.6\linewidth]{../figures/share_same_ses_by_tie.png}
@@
 
+\subsection{SES diversity in referral choice sets}
+
+How did the referrer choice sets look like in practice?
+We combine our findings from network diversity and its relationship with connection intensity, together with referral selection.
+In Section \ref{RC}, we found that referrals went to peers with whom the median participant took 12 courses (average 14).
+By restricting the networks for courses taken above the median, we get an \textit{ex post} snapshot of referrer choice sets.
+
+We show the average network shares conditional on referrer SES and above median number of courses taken together for low-SES in Figure \ref{connections_to_low_ses_tie12} and for high-SES in Figure \ref{connections_to_high_ses_tie12}.\footnote{In Appendix Figure \ref{t15availability} we present the complete relationship including middle-SES.} Network compositions above the median number of courses taken reveal strong segregation effects in referral choice sets: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
+Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
+At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
+High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% population share ($+12.5$ pp.).
+Middle-SES networks remain relatively balanced and closely track population proportions.
+
+Put differently, in an environment where 1 out of 3 students are low-SES, the chance that low-SES are considered for a referral by high-SES at random is already less than 1/6.
+This confirms that low-SES and high-SES practically have non-overlapping networks despite having opportunities to meet on equal status students at the university.
+While referral selection being driven by availability and performance is positive, network segregation has such a large impact on diversity.
+We now explore program selection as a key driver.
+
+\begin{figure}[H]
+  \centering
+  \caption{Network shares of SES groups above median connection intensity}
+  \begin{subfigure}[t]{0.4\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/connections_to_low_ses_tie12.png}
+      \caption{Low-SES network share}  
+      \label{connections_to_low_ses_tie12}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.4\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/connections_to_high_ses_tie12.png}
+      \caption{High-SES network share}
+      \label{connections_to_high_ses_tie12}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES above the median number of courses taken together.
+Horizontal lines plot the university-wide shares of SES groups (Low: 35\%, High: 14\%).
+While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
+Error bars represent 95\% confidence intervals.
+}
+\end{figure}
+
 \subsection{Program selection and SES diversity}
-To understand the mechanisms driving these patterns, we examine program selection.
+
 Academic programs at this university use cost-based pricing, and typically less than 5\% of students receive any kind of scholarship.
-Based on this, we first calculate how much every program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
+Based on this, we first calculate how much every undergraduate program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
 Considering that net minimum monthly wage stands at \$200 and the average Colombian salary around \$350, the cost differences between programs are large enough to make an impact on program selection.
@@
   \centering
-  \caption{Programs sorted by fee}\label{fees_with_boxplot}
+  \caption{Undergraduate programs sorted by fee}\label{fees_with_boxplot}
   \includegraphics[width=0.6\linewidth]{../figures/fees_with_boxplot.png}
@@
 
-We examine how SES groups are distributed across programs to identify evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
+We then examine how SES groups are distributed across programs to identify evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
 Indeed, low-SES students select into more affordable programs, followed by middle-SES students.
@@
   \centering
-  \caption{Programs sorted by fee}\label{ses_distribution_by_fees}
+  \caption{SES distribution by program fee}\label{ses_distribution_by_fees}
   \includegraphics[width=0.6\linewidth]{../figures/ses_distribution_by_fees.png}
@@
 
-\subsection{Referral SES composition}
-We now examine the overall SES compositions in referral selection.
-Referrals to low-SES peers constitute 37.9\% of all referrals, compared to 33.7\% low-SES representation in individual networks (see Figure \ref{fig:all_referral_rates}).
-This represents a modest over-representation of 4.3 percentage points.
-For middle-SES students, referrals constitute 51.0\% versus 51.4\% network representation, showing virtually no difference (-0.5 pp.).
-High-SES referrals account for 11.1\% compared to 14.9\% network share, an under-representation of 3.8 percentage points.
-While these patterns suggest some deviation from proportional representation—with slight over-referral to low-SES peers and under-referral to high-SES peers—the magnitudes are relatively modest.
-Overall, referral compositions are largely balanced and closely mirror the underlying network structure, with the largest deviation being less than 5 percentage points for any SES group.
-
-\begin{figure}[H]
-  \centering
-  \caption{Referral patterns compared to network composition}
-  \label{fig:all_referral_rates}
-  \includegraphics[width=0.6\linewidth]{../figures/all_referral_rates.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray).
-Error bars represent 95\% confidence intervals.
-  \end{tablenotes}
-\end{figure}
-
-Then, we examine referral patterns by referrer SES to identify potential SES biases across groups.
-Figure \ref{fig:all_ses_referral_rates} reveals mixed patterns of deviation from network composition that vary by referrer SES.
-Most patterns show modest deviations from network composition, with differences typically ranging from 1-6 percentage points.
-However, at the very extremes—low-SES to high-SES connections and vice versa—we observe the largest discrepancies between network share (which were already biased toward same-SES connections to begin with) and referral rates.
-Low-SES referrers show the strongest same-SES preference, referring 12.9 percentage points more to low-SES students than their network composition would suggest, while under-referring to high-SES recipients by 6.3 percentage points.
-Conversely, high-SES referrers under-refer to low-SES students by 10.9 percentage points compared to their network composition.
-Middle-SES referrers show the most balanced patterns, with deviations generally under 3 percentage points across all recipient groups.
-Cross-SES referral patterns, particularly between the most socioeconomically distant groups, show the largest departures from network availability.
-These results suggest that referral behavior diverges most from underlying network structure when SES differences are most pronounced.
-
-\begin{figure}[H]
-  \centering
-  \caption{Referral patterns by referrer SES compared to network composition}
-  \label{fig:all_ses_referral_rates}
-  \includegraphics[width=0.6\linewidth]{../figures/all_ses_referral_rates.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray) for each SES group.
-The panels show referral patterns for low-SES (left), middle-SES (center), and high-SES referrers (right).
-Error bars represent 95\% confidence intervals.
-  \end{tablenotes}
-\end{figure}
-
-% \begin{table}[H]
-%   \centering
-%   \begin{threeparttable}
-%   \caption{Summary statistics for network members by referral status}
-%   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
-%   \toprule
-%   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
-%   \cmidrule{2-3} \cmidrule{4-5}
-%   & Not Referred & Referred & Not Referred & Referred \\
-%   \midrule
-%   Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
-%   & (0.003) & (0.039) & (0.003) & (0.040) \\
-%   [1ex]
-%   Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
-%   & (0.003) & (0.042) & (0.003) & (0.043) \\
-%   [1ex]
-%   GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
-%   & (0.003) & (0.041) & (0.003) & (0.041) \\
-%   [1ex]
-%   Courses taken z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
-%   & (0.003) & (0.091) & (0.003) & (0.090) \\
-%   [1ex]
-%   Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
-%   & (0.001) & (0.019) & (0.001) & (0.019) \\
-%   [1ex]
-%   Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
-%   & (0.001) & (0.019) & (0.001) & (0.019) \\
-%   [1ex]
-%   High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
-%   & (0.001) & (0.012) & (0.001) & (0.012) \\
-%   % [1ex]
-%   % Female & 0.524 & 0.562 & 0.520 & 0.428 \\
-%   % & (0.001) & (0.019) & (0.001) & (0.019) \\
-%   % [1ex]
-%   % Age & 20.945 & 20.501 & 20.961 & 20.490 \\
-%   % & (0.006) & (0.104) & (0.006) & (0.099) \\
-%   \midrule
-%   Observations & 128,174 & 673 & 127,481 & 669 \\
-%   \bottomrule
-%   \end{tabular*}
-%   \begin{tablenotes}[flushleft]
-%   \footnotesize
-%   \item[] \textit{Note:} Standard errors in parentheses.
-GPA, test scores, and tie strength are standardized at the network level.
-For each referrer's network, we first calculated the mean and standard deviation of each measure.
-We then computed the average of these means and standard deviations across all referrers.
-Each individual's score was standardized using these network-level statistics.
-The standardization formula is $z = (x - \bar{x}_{network}) / \sigma_{network}$, where $\bar{x}_{network}$ and $\sigma_{network}$ are the average of network means and standard deviations, respectively.
-Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively.
-Tie strength measures the number of connections between individuals.
-%   \end{tablenotes}
-%   \label{tab:stats_by_nomination}
-%   \end{threeparttable}
-% \end{table}
-
-\subsection{Ex post referral choice sets}
-
-We now shed more light on the referral behavior after having characterized how referrals were made.
-Particularly interesting is that referrals go to peers with whom the median participant took 12 courses, with an average of 14.
-By restricting the networks for courses taken above the median, we can get a snapshot of how the referral choice set actually looked for participants before making referral decisions.
-As discussed in Section \ref{s:ses-diversity}, taking more courses with network members increases the share of same-SES individuals for both low- and high-SES students, and we had explored program selection as a potential mechanism.
-In Figure \ref{t15availability}, we show the effects of network segregation on \textit{ex post} referral choice sets for each SES group.
-Network compositions above the median number of courses taken reveal strong segregation effects: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
-Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
-At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
-High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% population share ($+12.5$ pp.).
-Middle-SES networks remain relatively balanced and closely track population proportions across all SES groups.
-Taken together, these confirm that the observed referral rates of SES groups follow the network compositions above median number of courses taken together, except for the low-SES.
-We conclude that the referral choices in our setting are mainly driven by availability and performance.
-
-\begin{figure}[H]
-  \centering
-  \caption{Network size and courses taken together by courses taken}\label{t15availability}
-  \includegraphics[width=0.6\linewidth]{../figures/t15availability.png}
-  \begin{tablenotes}
-    \footnotesize
-    \item[] \textit{Note:} This figure compares the network shares of SES groups in the networks of low-, middle-, and high-SES participants above the median number of courses taken together with peers.
-Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
-Low- and high-SES networks both become same-SES dominated at the expense of each other while middle-SES networks remain balanced.
-Error bars represent 95\% confidence intervals.
-  \end{tablenotes}
-\end{figure}
-
-\section{Robustness check} \label{Robustness}
+\subsection{Robustness check: Contact intensity and sharing academic programs} \label{Robustness}
 
@@
 
+\begin{figure}[H]
+  \centering
+  \caption{Network shares by SES}\label{connections_by_ses_app}
+  \includegraphics[width=0.6\linewidth]{../figures/availability_lses.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average network shares of SES groups respectively for low-, middle-, and high-SES referrers.
+Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+While the share of low-SES peers in the network decreases as the SES of the referrers increases, the share of high-SES peers in the network increases.
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Network shares by SES at courses taken above 12}\label{t15availability}
+  \includegraphics[width=0.6\linewidth]{../figures/t15availability.png}
+  \begin{tablenotes}
+    \footnotesize
+    \item[] \textit{Note:} This figure displays the average network shares of SES groups respectively for low-, middle-, and high-SES referrers above the median number of courses taken together.
+Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+Low- and high-SES networks both become same-SES dominated at the expense of each other while middle-SES networks remain balanced.
+Error bars represent 95\% confidence intervals.
+  \end{tablenotes}
+\end{figure}
+
 \pagebreak
@@
   \footnotesize
-  \item[] \textit{Note:} This table shows average (Math and Reading) standardized entry exam scores for individuals of different SES levels (rows) when connected to peers of specific SES levels (columns).
+  \item[] \textit{Note:} This table shows average (math and critical reading) standardized entry exam scores for individuals of different SES levels (rows) when connected to peers of specific SES levels (columns).
 The ``All'' row shows the overall average scores across all participant SES levels when connected to each network SES type.

### 2025-08-04 writing/manuscript.tex
v1.1.5

@@
 
-Referral hiring—the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities—is a common labor market practice that makes differences in social capital evident.\footnote{Referrals solve some frictions in the search and matching process and benefit both job-seekers and employers.
+Research on economic connectivity has focused on the relationship between individual choice and chance in meeting high-SES individuals.
+The prevailing hypothesis emerging from the seminal work of \citet{chetty2022n} is that increasing exposure to high-SES individuals under favorable inter-group contact conditions will lead low-SES individuals to connect with them at higher rates.
+Universities, in this regard, represent a particularly promising setting since they attract higher-than-population shares of high-SES students, and create more opportunities for cross-SES connections.
+However, credible evidence on biases in individual choices to connect across SES groups remains limited.
+One important reason for this gap is the challenge of creating controlled environments that isolate SES biases while accounting for natural variations in social network compositions.
+
+We overcome this challenge through a lab-in-the-field experiment at a Colombian university.
+We recruited 734 undergraduate students to make incentivized referrals among peers they encountered during their coursework.
+Referrals were made for the math and critical reading areas of the national university entry exam, and to incentivize performance-based referral selection, participants earned payments up to \$60 per referral based on their nominee's percentile ranking at the university.
+This setup provided an objective performance benchmark for referrals while SES biases in referral selection could still play a role.
+
+Referrals originated from each participant's unique course enrollment network that we constructed using extensive administrative data.
+The enrollment network covered each course the referrer had taken with all other undergraduate students at the university (more than 4500 individuals).
+It allowed us to observe both characteristics of every potential referral candidate, and the number of courses taken together as a measure of the intensity of interaction between the referrer and the candidate.
+Referrals from the enrollment networks enabled us to separate network composition (i.e., chance of meeting during coursework and frequency of contact) from SES biases in referral selection (i.e., individual choice in picking a referral).
+By doing so, we were able to control for naturally varying network compositions with referral candidates at the individual level, and could identify group-level SES biases in referral selection that go beyond mere opportunities to interact at the university.
+
+We randomized participants into two conditions.
+In the \textbf{Baseline} condition participants made referrals with performance-based incentives only, where their earnings depended on the actual performance of their referrals.
+In the \textbf{Bonus} condition, participants made referrals with performance-based incentives and an additional fixed bonus (\$25) going to their referral of choice.
+We designed the \textbf{Bonus} condition to make SES biases in referral selection even more salient.
+The fixed bonus provided more incentives to refer someone who performs less well, but is better connected with the referrer in terms of contact intensity which could correlate with SES.
+
+We find that referrals consistently go to higher-performing peers with strong contact intensity (14 vs.
+4 courses taken together), regardless of the incentive conditions and the exam area.
+Pooling across conditions and exam areas, we find that SES bias in referrals is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
+In contrast, middle- and high-SES referrers show no in-group biases and also no biases against low-SES peers.
+
+With 93\% of referrals within the same academic program to peers with high numbers of courses taken together, we find that chances to interact during coursework explains most of the observed referral patterns in terms of SES: at the contact intensity where referrals occur (median 12 courses together), low-SES networks contain 44.5\% low-SES peers versus 35\% university-wide (increase of 27\%), while high-SES networks contain only 15.7\% low-SES peers (decrease of 55\%).
+Even in the absence of a bias against low-SES, this intense network segregation makes it clear that in the range where high-SES referrers consider candidates, low-SES are practically not even in the choice sets for consideration.
+
+Looking for potential mechanisms driving the segregation in enrollment networks, we identify program selection as key.
+Program fees at the partner university are fixed on a cost basis, and with less than 5\% of undergraduates qualifying for scholarships.
+The consequence of these institutional policies is that SES groups end up sorting into programs on the basis of their costs, where some programs cost up to six times more on a yearly basis.
+To sum, even though low-SES are exposed to higher-than-population shares of high-SES students, and high-SES are not biased toward other SES groups, meaningful interaction opportunities are limited due to institutional and organizational factors.
+
+% One potential concern in interpreting our results is that referrals in our scenario have no real consequences in terms of job opportunities.
+While it is true that the referrals made in our setting do not result in job opportunities, our findings replicate the typical results from the experimental literature studying referrals where performance-based incentives brings in qualified candidates \citep{beaman_who_2012,pallais_why_2016,witte2021workers}, with potential biases in referral selection in play \citep{beaman_job_2018,hederos2025gender}.
+Moreoever, referral hiring captures a wide range of practices spanning from formal referral programs within hiring firms to informal sharing of job opportunities between two candidates \citep{topa2019social}.
+The lower-stakes referral environment with objective performance benchmarks could actually provide a lower-bound in SES biases in referral selection.
+
+% Another potential concern is about the nature of the enrollment network.
+One could question what exactly the enrollment network captures and whether it overlaps with the actual university social network of students.
+These are tough questions with no way to test in our date.
+What we can do is comapre our approach with other methods.
+While there are other ways to elicit networks by simply asking participants for a list of friends, these may be prone to biases in recall, could bias referral decisions, and are limited in the size of networks they elicit.
+Another solution to this problem could involve collecting participant data from social media platforms (e.g., Facebook) but this would also at best remain a proxy for actual social interactions.
+Our approach takes advantage of extensive administrative data which is not affected by biases in recall, and arguably overlaps with university social networks that could be collected through social media platforms.
+
+% A final related concern is our measure of contact intensity.
+One could question whether the number of courses taken together captures the true intensity of social interactions.
+Our data provides key insights into what this measure actually captures: In a robustness exercise, we find that beyond identifying peers in the same academic programs, the number of courses taken is a significant predictor of who gets a referral.
+This indactes that the number of courses taken together is a meaningful indicator of social contact between the referrer and the referral.
+
+Our findings contribute to understanding SES biases in referral selection with some important scope conditions.
+First, while our referrals have no direct job consequences, the performance-based incentive structure replicates typical findings from earler referral experiments \citep{beaman_who_2012,pallais_why_2016}, and the lower-stakes environment may actually provide a lower bound on SES biases compared to high-stakes hiring contexts.
+
+Second, our enrollment networks capture classroom-based interactions rather than broader social networks.
+This approach offers advantages over self-reported friendship networks, which suffer from recall bias and size limitations, or social media networks, which may not reflect meaningful interactions.
+The administrative data reveals that course-taking intensity predicts referral selection even beyond program affiliation, suggesting it captures meaningful social contact.
+
+Finally, our setting examines SES bias within a single institution where cross-SES contact is possible.
+The generalizability to contexts with less SES diversity or different institutional structures remains an open question for future research.
+
+—is a common labor market practice that makes differences in social capital evident.\footnote{Referrals solve some frictions in the search and matching process and benefit both job-seekers and employers.
 As a consequence, referral candidates get hired more often, have lower turnover, and earn higher wages \citep{brown2016informal,dustmann2016referral,friebel2023employee}.} Since referrals originate from the networks of referrers, the composition of referrer networks becomes a crucial channel that propagates inequality.
@@
 To incentivize participants to refer qualified candidates during the experiment, we set earnings to depend on referred candidates' actual university entry exam scores.
-
-Referral hiring in the labor market can range from firm-level formal referral programs asking employees to bring candidates to simply passing on job opportunities between network members \citep{topa2019social}.
-Since our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
-Our setting instead resembles situations where contacts share opportunities with each other without requiring the referred candidate to take any action and without revealing the referrer's identity.
-This eliminates reputational concerns since there is no hiring employer.
-It also establishes a lower bound on the expected reciprocity for the referrer when combined with pay-for-performance incentives \citep{witte2021workers,bandiera2009social}.
-At the same time, referring based on university entry exam scores is still an objective, widely accepted measure of ability.
-We show evidence that referrers in our setting not only possess accurate information about these signals but can also screen more productive individuals from their university network.
 
@@
 The identifying variation comes from within-network differences in referral decisions, holding constant the pool of available candidates.
-
 We estimate separate models for each referrer SES group to estimate aggregate SES biases across socioeconomic groups.

### 2025-08-05 writing/manuscript.tex
v1.1.6
Chapter 3 to-do: re-read and send

--- 2025-08-01 writing/manuscript.tex
@@
 \section*{Abstract}
-Economic connectivity, defined as the share of high-SES connections in one's network, is a strong correlate of labor market income.
-Yet, low-SES individuals are typically at a disadvantage when it comes to knowing the right people.
-Referral hiring leverages networks and make explicit the role of economic connectivity where taste-based biases could further exacerbate low-SES outcomes.
-We conduct a field experiment with 734 university students to study the network compositions of different SES groups.
-We leverage enrollment networks to identify all potential referral candidates and conduct an incentivized referral exercise to reveal SES biases within these choice sets.
-We find that the university enrollment networks are highly segregated, with low-SES and high-SES individuals having a higher share of same-SES connections in their networks due to program selection (12\% and 31\% respectively).
-When considering ex post actualized choice sets for the observed referrals, the segregation becomes worse: Low-SES individuals connect with other low-SES individuals at rates 30\% higher than the university share, while high-SES individuals connect with other high-SES individuals at rates 55\% higher than the university share.
-Yet, we find no bias against low-SES individuals once we account for network structures.
-We randomly assign half of the participants to a condition where their referral candidate receives a fixed bonus on top of pay-for-performance referral incentives.
-We find that additional incentives for the referral candidate do not change connection intensity with the referral nor the referral quality.
-Our findings suggest that systematic segregation patterns in networks that alter choice sets matter more than taste-based SES biases in referrals, and highlight the potential for institutional action in promoting SES diversity.
+The share of high-SES connections in one's network is a strong correlate of labor market income.
+We investigate whether differences in high-SES connection shares are exacerbated by SES biases in referral selection.
+We conduct a lab-in-the-field experiment with 734 Colombian university students making incentivized referrals from their enrollment networks.
+Randomizing participants between performance-only incentives and performance plus a fixed \$25 bonus for referral recipients, we find no effect of the treatment on referral choices: Referrals consistently go to high-performing peers with whom they take many courses together.
+We find that while low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no bias toward other groups.
+Network segregation, driven by students selecting into programs based on their SES, limits cross-SES referral opportunities even without an explicit SES bias.
+These suggest institutional policies promoting cross-SES contact are key for reducing SES-based inequalities.
 \medskip \\
 \textbf{JEL Classification:} C93, J71, D85, Z13 \\
-\textbf{Keywords:} social capital, social networks, referral hiring, socioeconomic status, field experiment
+\textbf{Keywords:} inequality, economic mobility, peer networks, class discrimination, homophily
 
@@
 
-Referral hiring—the formal or informal process where firms ask workers to recommend qualified candidates for job opportunities—is a common labor market practice that makes differences in social capital evident.\footnote{Referrals solve some frictions in the search and matching process and benefit both job-seekers and employers.
-As a consequence, referral candidates get hired more often, have lower turnover, and earn higher wages \citep{brown2016informal,dustmann2016referral,friebel2023employee}.} Since referrals originate from the networks of referrers, the composition of referrer networks becomes a crucial channel that propagates inequality.
-Similar individuals across socio-demographic characteristics form connections at higher rates \citep{mcpherson2001birds}, making across-SES (low-to-high) connections less likely than same-SES connections \citep{chetty2022na}.
-Referrals will thus reflect similarities in socio-demographic characteristics present in networks even in the absence of biases in the referral procedure—that is, even when referring randomly from one's network according to some productivity criteria.
-
-Yet, experimental evidence shows referrals can be biased even under substantial pay-for-performance incentives beyond what is attributable to differences in network compositions, at least in the case of gender \citep{beaman_job_2018,hederos2025gender}.
-A similar bias against low-SES individuals may further exacerbate their outcomes.
-If job information is in the hands of a select few high-SES individuals to whom low-SES individuals already have limited network access due to their lack of economic connectivity, and high-SES referrers are biased against low-SES individuals—referring other high-SES individuals at higher rates than their network composition would suggest—we should expect referral hiring to further disadvantage low-SES individuals.
-
-The empirical question we answer in this paper is whether referrers exhibit bias against low-SES peers after accounting for differences in network SES composition.
-We also evaluate the causal impact of two different incentive structures on referral behavior.
-
-In this study, we examine inequalities related to SES by curating a university-wide network dataset comprising over 4,500 students for whom classroom interactions are recorded along with individual attributes.
-We focus on the role of SES in referrals by experimentally investigating whether individuals who are asked to refer a peer tend to refer a same-SES candidate.
-We also explore potential mechanisms behind referral patterns by randomizing participants into two different incentive structures.
-To this end, we conducted a lab-in-the-field experiment with 734 students at a Colombian university.
-We instructed participants to refer a qualified student for tasks similar to the math and reading parts of the national university entry exam (equivalent to the SAT in the US system).
-To incentivize participants to refer qualified candidates during the experiment, we set earnings to depend on referred candidates' actual university entry exam scores.
-
-Referral hiring in the labor market can range from firm-level formal referral programs asking employees to bring candidates to simply passing on job opportunities between network members \citep{topa2019social}.
-Since our participants are students at the university and refer based on exam scores, we abstract away from formal referral programs with defined job openings.
-Our setting instead resembles situations where contacts share opportunities with each other without requiring the referred candidate to take any action and without revealing the referrer's identity.
-This eliminates reputational concerns since there is no hiring employer.
-It also establishes a lower bound on the expected reciprocity for the referrer when combined with pay-for-performance incentives \citep{witte2021workers,bandiera2009social}.
-At the same time, referring based on university entry exam scores is still an objective, widely accepted measure of ability.
-We show evidence that referrers in our setting not only possess accurate information about these signals but can also screen more productive individuals from their university network.
-
-In a university setting, class attendance provides essential opportunities for face-to-face interaction between students.
-This is a powerful force that reduces network segregation by providing ample opportunities to meet across SES groups, because of exposure to an equal or higher level of high-SES individuals compared to the general population \citep{chetty2022n}.\footnote{In a different sample from the same university population, \citet{diaz_peer_2025} show this holds true for the highest-SES individuals at this institution, accounting for about 6\% of their sample but less than 5\% of Colombian high-school graduates \citep{fergusson2021desigualdad}.} The very high level of income inequality in Colombia makes SES differences extremely visible in access to tertiary education, where rich and poor typically select into different institutions \citep{jaramillo-echeverri2023}.
-However, in the particular institutional setting we have chosen for this study, different SES groups mix at this university, allowing us to focus on SES diversity within the institution.
-At the same time, as students take more classes together, their similarities across all observable characteristics tend to increase \citep{kossinets_origins_2009}.
-This is an opposite force that drives high- and low-SES networks to segregate.
-We observe the net effect of these two opposing forces using administrative data and construct class attendance (enrollment) networks for 734 participants based on the number of common courses they have taken together with other students.
-This allows us to directly identify aggregate characterizations of different SES groups' network compositions as a function of courses taken (e.g., in same-SES share), as well as the individual characteristics of network members who receive referrals among all possible candidates.
-
-We find strong evidence that networks of high- and low-SES participants exhibit same-SES bias.
-On average, both groups connect with their own SES group at higher rates than would occur randomly given actual group shares at the university (12\% for low-SES and 31\% for high-SES).
-As students take more courses together within the same program, their networks dwindle in size and become even more homogeneous in SES shares.
-At 12 courses together (the median number of courses taken together among referrals), the same-SES share increases to 30\% above the university share for low-SES students and 55\% above for high-SES students.
-We identify selection into academic programs as a key mechanism explaining this phenomenon: The private university where our study took place implements exogenous cost-based program pricing and does not offer SES-based price reductions.
-This results in programs with very large cost differences within the same university, with some programs costing up to six times the cheapest one.
-We find that the average yearly fee paid per student increases with SES, and the high-SES share in the most expensive program at the university—medicine—drives a large part of the network segregation across SES groups.
-
-Do segregated networks account for the differences in SES referral rates across SES groups?
-Same-SES referrals are 17\% more common than referrer networks suggest.
-Controlling for differences in network compositions, we find that the entirety of the bias is driven by low-SES referrers.
-We find no bias against low-SES peers beyond what is attributable to differences in network composition.
-Regardless of SES, participants refer productive individuals, and referred candidates are characterized by a very high number of courses taken together.
-The latter underlies the impact of program selection on the intensity of social interaction, where participants activate smaller and more homogeneous parts of their networks for making referrals.
-Our treatment randomized participants across two different incentive schemes by adding a substantial monetary bonus (\$25) for the referred candidate on top of the pay-for-performance incentives.
-We provide evidence that treatment incentives did not change referral behavior across the same-SES referral rate, the number of courses taken together with the referral candidate, and the candidate's exam scores.
-We interpret the lack of differences in the number of courses taken together as further evidence that referrals go to strong social ties across both treatments regardless of the incentive structure.\footnote{This follows directly from earlier evidence showing that referrals tend to go to strong ties, i.e., close friends and/or family members \citep{gee2017social,kramarz2014strong,wang2013marriage}.}
-
-Our main empirical contribution to the experimental referral literature is our observation of the entire network that characterizes the referral choice set.
-Earlier research compares referrals made across different incentive structures and makes inferences about the counterfactual.
-For example, \citet{beaman_who_2012} compared referrers paid based on their referred candidate's productivity instead of receiving a fixed finder's fee, and \citet{beaman_job_2018} compared referrers who were restricted to refer either a male or female candidate instead of choosing freely.
-While \citet{pallais_why_2016} recruited a random sample of non-referred workers for comparison with referred ones, none of the previous studies could identify the entire referral choice set and provide a direct comparison to those who were referred by the participants.
-Observing the entire network allows us to identify biases in referrals in a more natural way, without imposing restrictions on the choice sets.
-A similar approach to ours is \citet{hederos2025gender}, who elicited friendship networks by asking referrers to name 5 close friends.
-Their findings suggest only half of those who were referred were from the elicited friendship network, and thus represent an incomplete observation of the entire referral choice set.
-We take our analysis one step further by requesting referrals from the enrollment network, where we have complete information on every single connection that may or may not receive a referral.
-This allows us to neatly separate the effect of network composition from any potential biases stemming from the referral procedure itself.
-
-Second, we build upon the earlier work on inequalities in referrals and the role of SES differences.
-The reliance of labor markets on referrals, coupled with homophily in social networks, can lead to persistent inequalities in wages and employment \citep{montgomery_social_1991,calvo2004effects,bolte_role_2021}.
-The premise of these models is that referrals exhibit homophily, so that employees are more likely to refer workers of their own race, gender, SES, etc.
-Supporting evidence shows that low-SES individuals have networks with lower shares of high-SES individuals, which partly explains why they have worse labor market outcomes \citep{stansbury2024class,chetty2022na}.
-We contribute by separately identifying the role of network homophily (the tendency to connect with similar others) and referral homophily (the tendency to refer similar others).
-Our results suggest that network homophily, rather than referral homophily, drives SES inequality in our setting.
-
-To our knowledge, \citet{diaz_peer_2025} are the first to study SES biases in referrals, and our study is conceptually the closest to theirs.
-Drawing from a similar sample at the same institution, \citet{diaz_peer_2025} focus on referrals from first-year students made within mixed-program classrooms and find no evidence for an aggregate bias against low-SES individuals.
-We also find no aggregate bias against low-SES individuals in referrals beyond what is attributable to differences in network structure.
-Our setup differs as we sample from students who completed their first year and impose no limits on referring from a classroom.
-This has several implications: We find that referrals in our setup go to individuals within the same program, and that programs have different SES shares which become even more accentuated as students take more courses together.
-While networks drive inequality in referral outcomes because of the institutional environment in our sample, we have no reason to believe first-year student networks in \citet{diaz_peer_2025} have similar levels of segregation to begin with.
-Our findings suggest that implementing more mixed-program courses that allow for across-SES mixing should be a clear policy goal to reduce segregation \citep{alan2023troeasa,rohrer2021po}.
+Research on economic connectivity has focused on two distinct mechanisms that shape cross-SES connections: network composition (who you have the chance to meet inside an institutional environment) versus individual preference (who you choose to connect with among those available).
+The prevailing hypothesis emerging from the seminal work of \citet{chetty2022n} is that increasing exposure to high-SES individuals under favorable intergroup contact conditions will lead low-SES individuals to connect with them at higher rates.
+Universities, in this regard, represent a particularly promising setting as they attract higher-than-population shares of high-SES students, and create more opportunities for cross-SES connections.
+However, credible evidence on biases in individual preferences to connect across SES groups remains limited.
+One important reason for this gap is the challenge of creating controlled environments that isolate SES biases while accounting for natural variations in social network compositions.
+
+We overcome this challenge through a lab-in-the-field experiment at a Colombian university.
+Focusing on the role of SES in referral selection, we studied whether individuals who were asked to refer a peer tended to refer a same-SES candidate.
+We recruited 734 undergraduate students to make incentivized referrals among peers they encountered during their coursework.
+Referrals were made for the math and critical reading areas of the national university entry exam, and to incentivize performance-based referral selection, participants earned payments up to \$60 per referral based on their nominee's percentile ranking at the university.
+This setup provided an objective performance benchmark for referrals while SES biases in referral selection could still play a role.
+
+Referrals originated from each participant's unique course enrollment network that we constructed using extensive administrative data.
+The enrollment network covered each course the referrer had taken with all other undergraduate students at the university (more than 4,500 individuals).
+It allowed us to observe both characteristics of every potential referral candidate, and the number of courses taken together as a measure of the intensity of interaction between the referrer and the candidate.
+Referrals from the enrollment networks enabled us to separate network composition (i.e., chance of meeting during coursework and frequency of contact) from SES biases in referral selection (i.e., individual choice in picking a referral).
+By doing so, we were able to control for naturally varying network compositions with referral candidates at the individual level, and could identify group-level SES biases in referral selection that go beyond mere opportunities to interact at the university.
+
+We randomized participants into two conditions.
+In the \textbf{Baseline} condition participants made referrals with performance-based incentives only, where their earnings depended on the actual performance of their referrals.
+In the \textbf{Bonus} condition, participants made referrals with performance-based incentives and an additional fixed bonus (\$25) going to their referral of choice.
+We designed the \textbf{Bonus} condition to make SES biases in referral selection even more salient.
+The fixed bonus created incentives to refer peers with high connection intensity (many courses taken together) even if they performed less well, potentially amplifying SES bias since connection intensity and SES background are correlated.
+
+We find that referrals consistently go to higher-performing peers with strong connection intensity (14 vs.
+4 courses taken together), regardless of the incentive conditions and the exam area.
+Pooling across conditions and exam areas, we find that SES bias in referrals is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
+In contrast, middle- and high-SES referrers show no bias toward other groups.
+
+With 93\% of referrals going to peers within the same academic program with whom referrers have taken many courses together, we find that network composition rather than SES biases explain most observed referral patterns.
+At the connection intensity where referrals typically occur (median 12 courses together), network segregation becomes stark: low-SES networks contain 44.5\% low-SES peers versus 35\% university-wide (27\% increase), while high-SES networks contain only 15.7\% low-SES peers (55\% decrease from the university average).
+This segregation means that even without any bias against low-SES peers, high-SES referrers rarely encounter low-SES candidates in their practical choice sets.
+
+Looking for potential mechanisms driving the segregation in enrollment networks, we identify program selection as key.
+Program fees at the partner university are fixed on a cost basis, and with less than 5\% of undergraduates qualifying for scholarships.
+The consequence of these institutional policies is that SES groups end up sorting into programs on the basis of their costs, where some programs cost up to six times more on a yearly basis.
+To sum, even though low-SES are exposed to higher-than-population shares of high-SES students, and high-SES are not biased toward other SES groups, meaningful interaction opportunities are limited due to institutional and organizational factors.
+
+Our findings should be interpreted with some scope conditions.
+First, our referrals have no direct job consequences, and referring under anonymity presents a lower stake environment with no potential reputational concerns.
+Nevertheless, we replicate typical findings from earlier referral experiments where performance-based incentives brings in qualified candidates (e.g., \citet{witte2021workers,beaman_who_2012}).
+
+Second, our enrollment networks capture classroom-based interactions and a measure for their intensity rather than broader social networks and close friendships.
+This approach offers advantages over self-reported friendship network elicitation methods, which suffers from censoring due to size limitations \citep{griffith2022jle}, or social media networks, which may not overlap with actual interactions at the university.
+We find that courses taken together predicts referral selection beyond program affiliation, suggesting it does capture meaningful variation in connection intensity.
+
+Finally, our setting examines SES bias within a single institution where cross-SES contact is possible, but where the networks of different SES groups are separated due to program selection.
+The generalizability to contexts with different institutional structures remains an open question for future research.
+
+We contribute to several strands of literature.
+First, a burgeoning literature studies the effects of SES on labor market outcomes \citep{stansbury2024class,FriedmanLaurison2019GettingOn,laurison2024sf}, with mechanisms including cultural matching and SES-based discrimination in the hiring processes \citep{rivera2012asr,rivera2016asr,galos2024esr,nunez2004class}.
+We extend this literature by examining the role of referral networks as a specific mechanism through which SES could affect economic opportunities.
+
+A subset of the literature focuses on SES-based differences in social capital and network formation \citep{chetty2022na,engzell2025ajos,michelman2022tqjoe}, with connection intensity \citep{gee2017jole,kramarz2014res,wang2013aejae,sterling2014ms} and homophily \citep{mcpherson2001birds,currarini2009e,jackson2022,bolte2024jle,montgomery_social_1991} driving differences across groups.
+Based on the pioneering work of \citet{currarini2010pnas}, we contribute by identifying two different types of homophily, and separate whether differential outcomes stem from network composition (who you know) versus taste-based biases (who you choose to interact with).
+Our findings suggest that rather than focusing on taste-based biases,  implementing mixed-program courses to increase across-SES connection intensity should be a clear policy goal in order to reduce SES-based network segregation (see e.g., for a similar institutional intervention \citet{rohrer2021po}).
+
+Methodologically, we contribute to the literature on job referral experiments.
+This literature provides causal evidence on why referrals in the labor market are prevalent,\footnote{Referrals solve frictions in the search and matching process and benefit both job-seekers and employers \citep{topa2019social}.
+Referral candidates tend to get hired more often, have lower turnover, and earn higher wages \citep{obukhova2013ms,brown2016informal,dustmann2016referral}.} and their consequences.
+Performance-based incentives bring in qualified candidates otherwise not identified by demographics \citep{beaman_who_2012,pallais_why_2016,friebel2023employee,witte2021workers}, at the cost of disadvantaging certain groups \citep{beaman_job_2018,hederos2025gender}.
+We extend this literature by a simple referral framework where we replicate the earlier findings and causally evaluate the effect of a sizeable monetary bonus for the referral candidate.
 
@@
 Undergraduate students at the university choose among 32 different academic programs.
-Students take between 5 to 7 courses per semester, and programs last anywhere between 4 to 12 semesters (2 to 6 years).
+Students take between 5 and 7 courses per semester, and programs last anywhere between 4 and 12 semesters (2 to 6 years).
 The majority (64\%) of students are enrolled in the 10 programs described in Appendix Figure \ref{program_share}.
@@
 For each participant, we identify all other undergraduate students with whom they have taken at least one course and create their individual network of university connections.
-The size of this network depends on how many different students a participant has encountered through coursework, while the intensity of connection is measured by the number of courses taken together.
+The size of this network depends on how many students a participant has encountered through coursework, while the connection intensity is measured by the number of courses taken together.
 This approach provides a complete picture of each participant's social environment at the university, including detailed characteristics (i.e., SES, academic program, performance) for both the participant and every person in their network.
@@
 \begin{align} \label{eq1}
-Y_{ij} = \alpha_i + \beta_{1} SES_{ij} + \beta_{2} X_{ij} + \varepsilon_{ij}
+Y_{ij} = \alpha_i + \beta_{1} SES_{ij} + \beta X_{ij} + \varepsilon_{ij}
 \end{align}
@@
 The exam consists of five areas (critical reading, mathematics, natural sciences, social sciences, and English).
-We focus on critical reading and mathematics as these represent two independent and fundemental skills.
+We focus on critical reading and mathematics as these represent two independent and fundamental skills.
 Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history).
@@
 In the \textbf{Baseline} treatment, only the participants can earn money based on their referral's performance.
-The \textbf{Bonus} treatment adds an additional fixed payment of \$25 to the peer who gets the referral.
+The \textbf{Bonus} treatment adds a fixed payment of \$25 to the peer who gets the referral.
 This payment is independent of the referral's actual performance (see Table \ref{tab:treatments}).
@@
 Table \ref{tab:balance} presents key demographic characteristics and academic performance indicators across treatments (see Appendix Table \ref{tab:selection} for selection).
-The sample is well-balanced between the \textbf{Baseline} and \textbf{Bonus} conditions and we observe no statistically significant differences in any of the reported variables (all \textit{p} values $> 0.1$).
+The sample is well-balanced between the \textbf{Baseline} and \textbf{Bonus} conditions, and we observe no statistically significant differences in any of the reported variables (all \textit{p} values $> 0.1$).
 Our sample is characterized by a majority of middle-SES students with about one-tenth of the sample being high-SES students.
@@
 GPA is grade point average out of 5.
-Connections refers to the average number of network members.
+Connections refer to the average number of network members.
 Low-SES, Med-SES, and High-SES indicate SES categories based on strata.
@@
     \item[] \textit{Note:} 
-    This figure displays the average number of connections in blue and the average number of courses taken together with connections in grey across semesters completed.
+    This figure displays the average number of connections in blue and the average number of courses taken together with connections in gray across semesters completed.
 Network size (nb.
@@
 We compare the performance and the number of courses taken together with the referrer between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
-We find that the the number of courses taken together with referrer, as well as performance measures across Reading, Math, and GPA are similar across treatments.
-Taken together, the similarities in academic performance and contact intensity suggest these two factors drive referrals regardless of treatment.
+We find that the number of courses taken together with referrer, as well as performance measures across Reading, Math, and GPA are similar across treatments.
+Taken together, the similarities in academic performance and connection intensity suggest these two factors drive referrals regardless of treatment.
 For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
@@
 How do enrollment networks differ across SES groups?
-We look at how the number of connections (network size) and number of courses taken together (contact intensity) change across SES groups in Figure \ref{connections_by_ses}.
+We look at how the number of connections (network size) and number of courses taken together (connection intensity) change across SES groups in Figure \ref{connections_by_ses}.
 Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, denser networks.
@@
 In terms of network compositions, participants could connect with other SES groups at different rates than would occur randomly depending on their own SES.
-We illustrate the average network shares conditional on referrer SES for low-SES in Figure \ref{connections_to_low_ses} and for high-SES in Figure \ref{connections_to_high_ses}.\footnote{For sake of brevity we omit middle-SES from this exposition.
+Figure \ref{connections_to_low_ses} and Figure \ref{connections_to_high_ses} illustrate the average network shares conditional on referrer SES respectively for low- and high-SES.\footnote{For sake of brevity we omit middle-SES from this exposition.
 For the complete relationship, see Appendix Figure \ref{connections_by_ses_app}.} We observe modest deviations from university-wide SES shares in enrollment networks: Low-SES referrers have on average 38.4\% low-SES peers compared to the university average of 34.3\%, while high-SES referrers have 20.4\% high-SES connections compared to the university average of 15.3\%.
@@
     \item[] \textit{Note:} This figure illustrates the distribution of each SES group across programs sorted by fee.
-the majority of low-SES select into programs with below average cost, while high-SES select into programs with above average cost.
+The majority of low-SES select into programs with below average cost, while high-SES select into programs with above average cost.
 Medicine accounts for a third of all high-SES students at this university.
@@
 
-\subsection{Robustness check: Contact intensity and sharing academic programs} \label{Robustness}
+\subsection{Robustness check: Connection intensity and sharing academic programs} \label{Robustness}
 
@@
 The persistence of statistical significance (all $p < 0.001$) suggests that the number of courses taken together has an independent effect on referral decisions.
-To sum, our measure of contact intensity seems to capture meaningful social interaction patterns that lead to referrals, and go beyond simply identifying matching academic programs.
+To sum, our measure of connection intensity seems to capture meaningful social interaction patterns that lead to referrals, and go beyond simply identifying matching academic programs.
 
@@
 \section{Conclusion} \label{Conclusion}
-In this paper, we study whether SES groups are biased toward one another beyond what is attributable to differences in their networks, and the effects of different incentive structures on referral behavior.
-Through a lab-in-the-field experiment that leverages enrollment networks at a socially diverse university, we find that the SES biases in referrals originate mostly from network structures, and referrals under performance-pay incentives do not exacerbate existing SES inequalities.
-
-Our findings reveal that enrollment networks are surprisingly segregated and referrals from these networks reflect closely the choice sets of the referrers.
-We identify program selection as the key mechanism driving this segregation.
-Low-SES students select into more affordable programs, and program selection plays a major part in segregating SES groups where low- and high-SES take more courses with their own SES group.
-Consequently, referrals come almost exclusively from the same academic program as the referrer, limiting the SES-diversity of their choice sets.
-Regardless of the bonus for the referral candidate, participants also pick higher performing peers with whom they have taken many courses together.
-We find that only low-SES referrers exhibit a same-SES bias.
-These findings suggest that the underlying network structure plays a crucial role in referrals, where institutional action can remedy the network segregation.
-
-These results complement the broader literature where much of the bias in referrals can be attributable to the ``practical'' choice sets of the referrers.
-While previous work demonstrates that about half of referrals come from a smaller, elicited network of close friends \citep{hederos2025gender}, we go the other way and use administrative data to construct a complete network which presumably includes close social relationships at the institutional level.
-Having access to the complete network thus eliminates any potential for under or overestimating taste-based biases \citep{griffith2022jle}.
-Under performance-pay incentives, referrers identify productive others regardless of additional financial rewards for the referral candidate.
-Still, the lack of a treatment effect suggests that in both incentive structures referrers pick close ties, shifting the responsibility to institutional actors to create diverse environments where cross-SES social interaction can take place more frequently and allow more diversity in networks.
-
-These findings have policy implications.
-Looking forward, institutions can play a crucial role in achieving SES equality of opportunity in higher education.
-Universities are already a setting in which low-SES get exposed to typically a higher than population share of higher-SES individuals than at other settings \citep{chetty2022n}.
-Yet, segregation within the higher education institutions remain a source for SES inequality.
-If low-SES peers never get to interact in meaningful ways with higher-SES, e.g., by taking courses together, the premise of social mobility through social channels remains severely underexploited.
-Future studies should work on ways to reduce SES segregation in collaboration with institutions, where having access to complete enrollment networks in addition to the typical friendship elicitation methods could help identifying the exact overlap between the two distinct approaches.
+We investigate whether SES biases in referral selection stem from taste-based preferences in choosing an SES group over others or network segregation.
+Through a lab-in-the-field experiment with 734 university students making incentivized referrals from complete enrollment networks, we find that institutional factors dominate individual preferences.
+
+Our key findings are threefold.
+First, referral patterns remain unchanged across different incentive structures: participants consistently select high-performing peers with a high number of courses taken together regardless of whether referral recipients receive additional compensation.
+Second, we find an SES bias is that is asymmetric and limited.
+While low-SES referrers exhibit strong in-group preferences,  middle- and high-SES referrers show no bias toward other groups.
+Third, network segregation driven by cost-based program selection explains most referral patterns.
+At typical referral range measured by the number of courses taken together, low-SES and high-SES students have dramatically different choice sets, with high-SES networks containing only 15.7\% low-SES peers compared to 35\% university-wide.
+
+These results have important policy implications.
+While universities expose low-SES students to higher-than-population shares of high-SES peers, segregation within institutions limits meaningful cross-SES interaction.
+Our findings suggest that institutional interventions promoting mixed-SES classrooms, rather than addressing individual biases, represent the most promising approach to reducing SES-based inequality in opportunity transmission.
+Future research should explore the causal effect of specific institutional interventions that aim to increase cross-SES interactions.
 

### 2025-08-06 writing/manuscript.tex
v1.1.7
Chapter 3 to-do: finish re-read and send

@@
 
-\title{Class differences in social networks: Evidence from a referral experiment}
+\title{When Proximity Isn't Enough: Network Segregation and SES Bias in Referrals}
 % \\ \large Experimental Design \\
@@
 The share of high-SES connections in one's network is a strong correlate of labor market income.
-We investigate whether differences in high-SES connection shares are exacerbated by SES biases in referral selection.
-We conduct a lab-in-the-field experiment with 734 Colombian university students making incentivized referrals from their enrollment networks.
-Randomizing participants between performance-only incentives and performance plus a fixed \$25 bonus for referral recipients, we find no effect of the treatment on referral choices: Referrals consistently go to high-performing peers with whom they take many courses together.
-We find that while low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no bias toward other groups.
-Network segregation, driven by students selecting into programs based on their SES, limits cross-SES referral opportunities even without an explicit SES bias.
+We investigate whether SES biases in referral selection exacerbate differences high-SES connection shares.
+We conduct a lab-in-the-field experiment with 734 Colombian university students who make incentivized referrals from their enrollment networks.
+Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of incentives.
+While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no bias toward other groups and refer along the network shares of each SES groups.
+We find that network segregation, driven by program selection based on SES, limits cross-SES referral opportunities for even without an explicit SES bias.
 These suggest institutional policies promoting cross-SES contact are key for reducing SES-based inequalities.
@@
 \section{Introduction}
-Equally qualified individuals in terms of productivity face different labor market outcomes based on their socioeconomic status \citep{stansbury2024class}.
+Equally qualified individuals face different labor market outcomes based on their socioeconomic status \citep{stansbury2024class}.
 This persistent inequality undermines meritocratic ideals and represents a substantial barrier to economic mobility.
-A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectivity, defined as the share of high-SES connections among low-SES individuals, is the most important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
+A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectivity, defined as the share of high-SES connections among low-SES individuals, is an important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
 In this sense, a lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.
@@
 Research on economic connectivity has focused on two distinct mechanisms that shape cross-SES connections: network composition (who you have the chance to meet inside an institutional environment) versus individual preference (who you choose to connect with among those available).
-The prevailing hypothesis emerging from the seminal work of \citet{chetty2022n} is that increasing exposure to high-SES individuals under favorable intergroup contact conditions will lead low-SES individuals to connect with them at higher rates.
+The prevailing hypothesis emerging from the seminal work of \citet{chetty2022n} is that increasing exposure to high-SES individuals will lead low-SES individuals to connect with them at higher rates.
 Universities, in this regard, represent a particularly promising setting as they attract higher-than-population shares of high-SES students, and create more opportunities for cross-SES connections.
 However, credible evidence on biases in individual preferences to connect across SES groups remains limited.
-One important reason for this gap is the challenge of creating controlled environments that isolate SES biases while accounting for natural variations in social network compositions.
+One important reason for this gap is the challenge of creating controlled environments that isolate SES biases while accounting for natural variations in network compositions.
 
@@
 Referrals were made for the math and critical reading areas of the national university entry exam, and to incentivize performance-based referral selection, participants earned payments up to \$60 per referral based on their nominee's percentile ranking at the university.
-This setup provided an objective performance benchmark for referrals while SES biases in referral selection could still play a role.
+This setup provided an objective performance benchmark for referrals where SES biases in referral selection could still play a role.
 
@@
 The enrollment network covered each course the referrer had taken with all other undergraduate students at the university (more than 4,500 individuals).
-It allowed us to observe both characteristics of every potential referral candidate, and the number of courses taken together as a measure of the intensity of interaction between the referrer and the candidate.
+It allowed us to observe both characteristics of every potential referral candidate, and the intensity of interaction between the two, which we measured by the number of courses taken together.
 Referrals from the enrollment networks enabled us to separate network composition (i.e., chance of meeting during coursework and frequency of contact) from SES biases in referral selection (i.e., individual choice in picking a referral).
@@
 We designed the \textbf{Bonus} condition to make SES biases in referral selection even more salient.
-The fixed bonus created incentives to refer peers with high connection intensity (many courses taken together) even if they performed less well, potentially amplifying SES bias since connection intensity and SES background are correlated.
-
-We find that referrals consistently go to higher-performing peers with strong connection intensity (14 vs.
-4 courses taken together), regardless of the incentive conditions and the exam area.
-Pooling across conditions and exam areas, we find that SES bias in referrals is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
+The fixed bonus created incentives to refer peers even if they performed less well, potentially amplifying the relevance of other factors like the SES bias and the connection intensity.
+
+We find that referrals consistently go to higher-performing peers with high connection intensity (14 vs.
+4 courses), regardless of the conditions and the exam area.
+Pooling across these, we find that SES bias in referral selection is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
 In contrast, middle- and high-SES referrers show no bias toward other groups.
 
-With 93\% of referrals going to peers within the same academic program with whom referrers have taken many courses together, we find that network composition rather than SES biases explain most observed referral patterns.
+With 93\% of referrals going to peers within the same academic program with whom referrers have taken many courses together, we find that network composition rather than SES biases better explain the observed referral patterns.
 At the connection intensity where referrals typically occur (median 12 courses together), network segregation becomes stark: low-SES networks contain 44.5\% low-SES peers versus 35\% university-wide (27\% increase), while high-SES networks contain only 15.7\% low-SES peers (55\% decrease from the university average).
@@
 Looking for potential mechanisms driving the segregation in enrollment networks, we identify program selection as key.
-Program fees at the partner university are fixed on a cost basis, and with less than 5\% of undergraduates qualifying for scholarships.
-The consequence of these institutional policies is that SES groups end up sorting into programs on the basis of their costs, where some programs cost up to six times more on a yearly basis.
-To sum, even though low-SES are exposed to higher-than-population shares of high-SES students, and high-SES are not biased toward other SES groups, meaningful interaction opportunities are limited due to institutional and organizational factors.
+Program fees at our partner university are fixed on a cost basis, and less than 5\% of undergraduates qualify for scholarships.
+One consequence of these policies is that SES groups end up sorting into programs on the basis of their costs, where some programs cost up to six times more on a yearly basis.
+To sum, even though low-SES are exposed to higher-than-population shares of high-SES students, and high-SES are not biased toward other SES groups, meaningful interaction opportunities at the university are genuinely limited.
 
 Our findings should be interpreted with some scope conditions.
-First, our referrals have no direct job consequences, and referring under anonymity presents a lower stake environment with no potential reputational concerns.
-Nevertheless, we replicate typical findings from earlier referral experiments where performance-based incentives brings in qualified candidates (e.g., \citet{witte2021workers,beaman_who_2012}).
-
-Second, our enrollment networks capture classroom-based interactions and a measure for their intensity rather than broader social networks and close friendships.
-This approach offers advantages over self-reported friendship network elicitation methods, which suffers from censoring due to size limitations \citep{griffith2022jle}, or social media networks, which may not overlap with actual interactions at the university.
-We find that courses taken together predicts referral selection beyond program affiliation, suggesting it does capture meaningful variation in connection intensity.
-
-Finally, our setting examines SES bias within a single institution where cross-SES contact is possible, but where the networks of different SES groups are separated due to program selection.
+First, our referrals have no direct job consequences, and participants refer under anonymity.
+These may represent a lower stake environment for referrers with no potential reputational concerns.
+Nevertheless, we replicate typical findings from earlier referral experiments where performance-based incentives brings in qualified candidates from participant networks (e.g., \citet{witte2021workers,beaman_who_2012}).
+
+Second, enrollment networks capture classroom-based interactions and their intensity rather than broader networks of close friendships.
+While our approach has clear advantages over self-reported friendship network elicitation which suffers from censoring due to limitations in size \citep{griffith2022jle}, triangulating it with an additional method (e.g., social media friendship data) could provide useful for better identifying actual interactions at the university.
+Still, we find that connection intensity predicts referral selection well beyond same program affiliation, suggesting it does capture meaningful variation in social interactions in some dimension.
+
+Finally, our setting examines SES bias within a single institution where cross-SES contact is possible, and the networks of different SES groups are separated due to program selection.
 The generalizability to contexts with different institutional structures remains an open question for future research.
@@
 Based on the pioneering work of \citet{currarini2010pnas}, we contribute by identifying two different types of homophily, and separate whether differential outcomes stem from network composition (who you know) versus taste-based biases (who you choose to interact with).
-Our findings suggest that rather than focusing on taste-based biases,  implementing mixed-program courses to increase across-SES connection intensity should be a clear policy goal in order to reduce SES-based network segregation (see e.g., for a similar institutional intervention \citet{rohrer2021po}).
+Our findings suggest that rather than focusing on taste-based biases,  implementing mixed-program courses to increase across-SES connection intensity should be a clear policy goal in order to reduce SES-based network segregation (see e.g., for an institutional intervention by \citet{rohrer2021po}).
 
@@
 This literature provides causal evidence on why referrals in the labor market are prevalent,\footnote{Referrals solve frictions in the search and matching process and benefit both job-seekers and employers \citep{topa2019social}.
-Referral candidates tend to get hired more often, have lower turnover, and earn higher wages \citep{obukhova2013ms,brown2016informal,dustmann2016referral}.} and their consequences.
-Performance-based incentives bring in qualified candidates otherwise not identified by demographics \citep{beaman_who_2012,pallais_why_2016,friebel2023employee,witte2021workers}, at the cost of disadvantaging certain groups \citep{beaman_job_2018,hederos2025gender}.
-We extend this literature by a simple referral framework where we replicate the earlier findings and causally evaluate the effect of a sizeable monetary bonus for the referral candidate.
+Referral candidates tend to get hired more often, have lower turnover, and earn higher wages \citep{obukhova2013ms,brown2016informal,dustmann2016referral}.} finding that performance-based incentives bring in qualified candidates otherwise not identified by demographic characteristics \citep{beaman_who_2012,pallais_why_2016,friebel2023employee,witte2021workers}, and the consequences of relying upon referral hiring, which come at the cost of disadvantaging certain groups \citep{beaman_job_2018,hederos2025gender}.
+We extend this literature by causally evaluate the effect of a sizeable monetary bonus for the referral candidate and exploring SES biases in referral selection.
 
@@
 Section \ref{BS} begins with the background and setting in Colombia.
-In Section \ref{ES} we present the empirical strategy and in Section \ref{Design} we present the design of the experiment.
+Section \ref{ES} presents the empirical strategy and Section \ref{Design} presents the design of the experiment.
 In Section \ref{SID} we describe the experimental sample, incentives and the procedure.
@@
 This economic disparity creates profound differences in outcomes across SES groups in terms of education, geographic residence, language, manners, and social networks \citep{garciavillegas2021dimension, angulo2012movilidad,garcia2015loteria}.
-While these patterns are not atypical and exist elsewhere, Colombia's pronounced inequality makes economic, educational, and cultural differences across SES particularly visible.
+While similar patterns also exist elsewhere, Colombia's pronounced economic inequality makes educational and cultural differences across SES groups particularly visible.
+
+In higher education, Colombia's pronounced economic equality manifests itself by preventing meaningful interaction between SES groups.
+Wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
+Taken together, the unique ways in which economic inequality manifests itself in the Colombian higher educational setting provides the ideal conditions to study biases related to SES in referral selection.
 
@@
 Designed for utility subsidies from higher strata to support lower strata, the system aligns with and reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.
-It is widely used by policymakers and in official statistics \citep{fergusson2021desigualdad}.
+It is also widely used by policymakers and in official statistics \citep{fergusson2021desigualdad} and well known to by the public.
 Using the estrato system, we categorize students in strata 1-2 as low-SES, strata 3-4 as middle-SES, and strata 5-6 as high-SES.
-
-In higher education, Colombia's pronounced economic equality manifests itself by preventing meaningful interaction between SES groups.
-Wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
-Taken together, the unique ways in which economic inequality manifests itself in the Colombian higher educational setting provides the ideal conditions to study biases related to SES in referral selection.
 
@@
     \item[] \textit{Note:} This figure shows the average score national university entry exam by monthly family income and type of higher education institution.
-With average student scores in the 65-70 band (see Appendix Figures \ref{math_hist} and \ref{reading_hist}), the private university where we conducted this experiment caters to low-, middle- and high-SES students.
+With average student scores in the 65-70 band, the private university where we conducted this study caters to both low- and high-income students.
 Figure reproduced from \citet{fergusson2021distincion}.
@@
 Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
-
-To map social connections at the university, we construct enrollment networks using administrative data.
+Academic program choice thus shapes students' connections at the university, influencing both who they encounter in classes and the frequency of these interactions.
+
+To map these social connections, we construct enrollment networks using administrative data.
 For each participant, we identify all other undergraduate students with whom they have taken at least one course and create their individual network of university connections.
-The size of this network depends on how many students a participant has encountered through coursework, while the connection intensity is measured by the number of courses taken together.
-This approach provides a complete picture of each participant's social environment at the university, including detailed characteristics (i.e., SES, academic program, performance) for both the participant and every person in their network.
+The size of this network depends on how many students a participant has encountered through coursework, while the intensity of connection is measured by the number of courses taken together.
+This approach provides a complete picture of each participant's social environment at the university, and includes detailed characteristics (i.e., SES, academic program, performance) for both the participant and every person in their network.
 
@@
 
-where $Y_{ij} = 1$ if referrer $i$ selects candidate $j$, and 0 otherwise.
+where $Y_{ij} = 1$ if referrer $i$ chooses referral candidate $j$, and 0 otherwise.
 We set middle-SES as the base category, so $\beta_1$ is the log-odds estimate for referring low- and high-SES candidates relative to middle-SES.
-$X_{ij}$ includes the remaining characteristics of referral candidates in the enrollment network that improve model fit such as  entry exams scores and the number of courses taken together with the referrer.
+$X_{ij}$ includes the remaining characteristics of referral candidates in the enrollment network that improve model fit such as entry exam scores and the number of courses taken together with the referrer.
 These continuous variables are standardized using means and standard deviations calculated by first computing network-level statistics for each referrer, then averaging across all 734 networks.\footnote{Each referral candidate's entry exam score and the number of courses they have taken with the referrer is standardized using these sample-level statistics.
-The standardization formula is $z_{i} = (x_{i} - \bar{X}) / \sigma$, where $\bar{X}$ and $\sigma$ are the average mean and standard deviation across participant networks for the measure.} The individual fixed effects $\alpha_i$ control for all referrer-specific factors that might influence both network formation and referral decisions.
-Because we observe two referrals from each referrer, we cluster standard errors at the referrer level to account for the potential correlation within these referral decisions.
+The standardization formula is $z_{i} = (x_{i} - \bar{X}) / \sigma$, where $\bar{X}$ and $\sigma$ are the average mean and standard deviation across participant networks for the measure.} The individual fixed effects $\alpha_i$ control for referrer-specific factors that might influence both network formation and referral decisions.
+Because we observe two referrals (one per exam area) from each referrer, we cluster standard errors at the referrer level and account for the potential correlation in the error terms.
 
@@
 This assumption could be violated if peers within the same SES group are viewed as close substitutes, where adding similar alternatives distorts choice probabilities.
-While this concern may have some validity in our setting,\footnote{Among participants making referrals to two different individuals, half refer to someone else from the same SES, suggesting potential substitutability within SES groups.} Alternative discrete choice models that relax IIA are computationally prohibitive given our large dataset.\footnote{Models such as nested logit become computationally intractable with over 250,000 observations across 734 individuals.} We therefore proceed with the conditional logit framework while acknowledging this limitation.
+While this concern may have some validity in our setting,\footnote{Among participants making referrals to two different individuals, half refer to someone else from the same SES, suggesting potential substitutability within SES groups.} alternative discrete choice models that relax IIA are computationally prohibitive given our large dataset.\footnote{Models such as nested logit become computationally intractable with over 250,000 observations across 734 individuals.} We therefore proceed with the conditional logit framework while acknowledging its limitations.
 
 \section{Design} \label{Design}
-We designed an online experiment to assess peer referral selection from an SES perspective and to evaluate the causal effect of providing a bonus to referral candidates.
+We designed an experiment to assess SES biases in referral selection and to evaluate the causal effect of providing a bonus to referral candidates.
 The experimental design consisted of two incentivized tasks administered in the following sequence: First, participants completed belief elicitation tasks about their own performance on the national university entry exam.
@@
 Finally, participants reported beliefs about their referrals' performance and provided demographic information.
-This structure allowed us to measure both the accuracy of participants' beliefs and their referral behavior under controlled incentive conditions.
+This structure allowed us to measure the accuracy of participants' beliefs and observe their referral decisions in a controlled setting.
 Figure \ref{timeline} shows the experimental timeline, and detailed instructions are provided in Appendix \ref{instructions}.
@@
 The scores from this exam provide pre-existing, comparable measures of performance.
-By using existing administrative data, we also ensure that all eligible students have comparable performance measures.
 
 The exam consists of five areas (critical reading, mathematics, natural sciences, social sciences, and English).
-We focus on critical reading and mathematics as these represent two independent and fundamental skills.
+We focus on critical reading and mathematics as these represent independent and overarching skills.
 Critical reading evaluates competencies necessary to understand, interpret, and evaluate texts found in everyday life and broad academic fields (e.g., history).
-Mathematics assesses students' competency in using undergraduate level mathematical tools (e.g., reasoning in proportions, financial literacy).
+Mathematics assesses students' competency in using high school level mathematical tools (e.g., reasoning in proportions, financial literacy).
 These together capture performance in comprehending and critically evaluating written material as well as reasoning and problem-solving abilities.
@@
 To examine how different incentive structures affect referral selection, we randomly assign a fixed bonus payment for students who get a referral.
-In the \textbf{Baseline} treatment, only the participants can earn money based on their referral's performance.
+In the \textbf{Baseline} treatment, only the participants, i.e., those who make referrals, can earn money based on their referral's performance.
 The \textbf{Bonus} treatment adds a fixed payment of \$25 to the peer who gets the referral.
@@
 Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together (88\% success rate).
-We randomly allocated participants to either \textbf{Baseline} or \textbf{Bonus} treatments.
 
@@
 We plot this relationship in Figure \ref{conns_by_tie}: As students take more than 5 courses together, the size of their enrollment network drops dramatically from above 210 to below 50.
-These patterns reveal that while participants' overall networks are large with relatively few courses taken together on average, they spend most of their time at the university within smaller, more intensive groups of peers from the same academic program.
+These patterns reveal that while participants' overall networks are large with relatively few courses taken together on average, they are more frequently in contact within a much smaller group of peers from the same academic program.
 
@@
 We compare the outcomes across exam areas for referrals only going to separate individuals in Appendix Table \ref{tab:referral_by_area} and all referrals in Appendix Table \ref{tab:referral_area}.
-In both cases, we find no meaningful differences between referrals made for Math or Reading areas of the entry exam.
-As referrals in both exam areas come from the same enrollment network, we pool referrals per participant and report their averages in our main analysis to avoid inflating statistical power in our comparisons.
+In both cases, we find no meaningful differences between referrals made for math or critical reading areas of the entry exam.
+As referrals in both exam areas come from the same enrollment network, we group referrals per participant and report average outcomes.
 
@@
 First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
-This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have stronger ties.
+This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have higher contact intensity.
 While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
@@
   \begin{threeparttable}
-  \caption{Characteristics of referrals by treatment condition}
+  \caption{Characteristics of referrals by treatment}
   \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
@@
 
-To motivate the SES related biases in referral selection, we now examine the overall SES composition of referrals compared to the average network availability.
+To motivate the SES biases in referral selection, we now examine the overall SES composition of referrals compared to the average network availability.
 Descriptively, referral patterns largely mirror underlying network structure.\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
@@
 Pooling over SES groups who are connected with similar others systematically reduces variance (similar to resampling in bootstrapping).
-For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Referrals to low-SES peers constitute 37.9\% of all referrals compared to 33.7\% network representation, middle-SES referrals account for 51.0\% versus 51.4\% network share, and high-SES referrals represent 11.1\% compared to 14.9\% network availability (see Figure \ref{fig:all_referral_rates}).
+For this reason we choose not reporting test results in certain sections including this one and focus on describing the relationships between SES groups.} Referrals to low-SES peers constitute 37.9\% of all referrals compared to 33.7\% network share, middle-SES referrals account for 51.0\% versus 51.4\%, and high-SES referrals represent 11.1\% compared to 14.9\% (see Figure \ref{fig:all_referral_rates}).
 The largest deviation is less than 5 percentage points for any SES group.
@@
 Low-SES referrers have the largest same-SES deviation, referring 12.9 percentage points more to low-SES students than their network composition suggests, while high-SES referrers under-refer to low-SES students by 10.9 percentage points (see Figure \ref{fig:all_ses_referral_rates}).
-These descriptive findings suggest that referral behavior diverges most from underlying network structure when SES differences are most pronounced and motivate our formal analysis.
+These descriptive findings suggest that referral selection in SES terms diverges most from underlying network structure when SES groups are further apart, and motivate our formal analysis.
 
@@
     \footnotesize
-    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray) for each SES group.
+    \item[] \textit{Note:} This figure compares the average SES composition of referrers' networks (dark gray) to the SES composition of referrals (light gray) for low-, middle- and high-SES referrers (left to right).
 Error bars represent 95\% confidence intervals.
@@
 
-We now analyze the results of the regression specification in Equation \ref{eq1} and describe our findings in Table \ref{tab:ses-heterogeneity}.
-We run three separate regressions, one for each referrer SES group, with a single regressor which is the referral candidate's SES.
+We now describe our findings using the regression specification (see Equation \ref{eq1}) in Table \ref{tab:ses-heterogeneity}.
+We first run three separate regressions, one for each referrer SES group, with a single regressor which is the referral candidate's SES.
 Controlling for network composition, we find that low-SES participants are more likely to refer other low-SES, and are less likely to refer high-SES relative to the probability of referring middle-SES peers.
@@
 We proceed by adding the standardized number of courses taken together as a control in our specification and describe the results in Table \ref{tab:ses-heterogeneity-extended}.
-A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that intensity of contact substantially increase the probability of referral.
-The high $\chi^2$ statistics suggest that the model with this regressor provides a better fit than a model without.
-Nevertheless, low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
+A one standard deviation increase in the number of courses taken together proves to be highly significant across all models, with coefficients ranging from 0.856 to 1.049, indicating that connection intensity substantially increases the probability of referral.
+The high $\chi^2$ statistics suggest that the model with this regressor provides a better fit than previous models.
+We find that low-SES participants still show a strong same-SES bias relative to referring middle-SES peers at the average number of courses taken together.
 This same-SES bias is not observed among middle-SES or high-SES referrers, who also display no statistically significant bias toward low-SES candidates.
@@
 Middle- and high-SES referrers show no systematic discrimination against other SES groups once we account for network composition and other relevant factors contributing to the referral decision.
-We will explore potential mechanisms that help explain this unexpected result.
+We will next explore potential mechanisms that help explain this unexpected result.
 
@@
 
-\section{Potential Mechanisms and Robustness Checks } \label{MandRC}
+\section{Potential Mechanisms and Robustness Checks} \label{MandRC}
 \subsection{SES diversity in networks} \label{s:ses-diversity}
@@
 We look at how the number of connections (network size) and number of courses taken together (connection intensity) change across SES groups in Figure \ref{connections_by_ses}.
-Low- and middle-SES students have larger networks but take fewer courses together with network members, while high-SES students have smaller, denser networks.
-Specifically, both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03$, $p = 0.003$ and $t = 2.49$, $p = 0.013$, respectively), but high-SES students take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20$, $p < .001$).
+Both low- and middle-SES students have significantly larger networks than high-SES students ($t = 3.03$, $p = 0.003$ and $t = 2.49$, $p = 0.013$, respectively), while high-SES students take significantly more courses with their network members than both low- ($t = -3.70, p < .001$) and middle-SES ($t = -4.20$, $p < .001$).
 
@@
 
-While same-SES students are connected more often with each other, so far we did not look at the consequences in terms of number of courses taken together with network members.
+While same-SES students are connected more often with each other, so far we only consider the average the number of courses taken together with network members.
 What are the diversity implications of increased connection intensity between students?
 As students take more courses together with peers, the share of same-SES peers in the networks of low- and high-SES increases while the share of middle-SES declines (see Figure \ref{share_same_ses_by_tie}).
-Both increases are substantial, amounting to 50\% for high-, and 30\% for low-SES.
-Considering that beyond 5 courses taken together network members are almost entirely within the same program, these suggest program selection may have strong consequences for SES diversity in our setting.
+Both increases are substantial, amounting to 50\% for high-, and 30\% for low-SES beyond 15 courses together.
+Considering that beyond 5 courses taken together network members are almost entirely within the same program, program selection may have strong consequences for explaining the network segregation in our setting.
 
@@
 How did the referrer choice sets look like in practice?
-We combine our findings from network diversity and its relationship with connection intensity, together with referral selection.
+We now combine our findings about network segregation with referral selection.
 In Section \ref{RC}, we found that referrals went to peers with whom the median participant took 12 courses (average 14).
@@
 We show the average network shares conditional on referrer SES and above median number of courses taken together for low-SES in Figure \ref{connections_to_low_ses_tie12} and for high-SES in Figure \ref{connections_to_high_ses_tie12}.\footnote{In Appendix Figure \ref{t15availability} we present the complete relationship including middle-SES.} Network compositions above the median number of courses taken reveal strong segregation effects in referral choice sets: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
-Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% population share ($-5.4$ pp.).
+Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% university share ($-5.4$ pp.).
 At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
-High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% population share ($+12.5$ pp.).
-Middle-SES networks remain relatively balanced and closely track population proportions.
+High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% university share ($+12.5$ pp.).
+Middle-SES networks remain relatively balanced and closely track university proportions.
 
 Put differently, in an environment where 1 out of 3 students are low-SES, the chance that low-SES are considered for a referral by high-SES at random is already less than 1/6.
-This confirms that low-SES and high-SES practically have non-overlapping networks despite having opportunities to meet on equal status students at the university.
+This stark disparity reveals that low-SES and high-SES students operate in practically separate social worlds within the same university, despite formal contact opportunities to meet as equal-status students.
 While referral selection being driven by availability and performance is positive, network segregation has such a large impact on diversity.

### 2025-08-07 writing/manuscript.tex
v1.2

@@
 Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of incentives.
-While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no bias toward other groups and refer along the network shares of each SES groups.
+While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no biases towards their own and other groups, referring along their network shares.
 We find that network segregation, driven by program selection based on SES, limits cross-SES referral opportunities for even without an explicit SES bias.
@@
 Pooling across these, we find that SES bias in referral selection is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
-In contrast, middle- and high-SES referrers show no bias toward other groups.
+In contrast, middle- and high-SES referrers show no biases toward their own or other groups.
 
@@
 A subset of the literature focuses on SES-based differences in social capital and network formation \citep{chetty2022na,engzell2025ajos,michelman2022tqjoe}, with connection intensity \citep{gee2017jole,kramarz2014res,wang2013aejae,sterling2014ms} and homophily \citep{mcpherson2001birds,currarini2009e,jackson2022,bolte2024jle,montgomery_social_1991} driving differences across groups.
-Based on the pioneering work of \citet{currarini2010pnas}, we contribute by identifying two different types of homophily, and separate whether differential outcomes stem from network composition (who you know) versus taste-based biases (who you choose to interact with).
-Our findings suggest that rather than focusing on taste-based biases,  implementing mixed-program courses to increase across-SES connection intensity should be a clear policy goal in order to reduce SES-based network segregation (see e.g., for an institutional intervention by \citet{rohrer2021po}).
+Based on the pioneering work of \citet{currarini2010pnas}, we contribute by identifying two different types of homophily, and separate whether differential referral outcomes stem from network composition (who you know) versus taste-based biases (who you choose to interact with).
+Our findings suggest that structural factors impacting network composition, rather than taste-based SES biases, drive the differences in referral outcomes.
+Under this light, implementing mixed-program courses to increase across-SES connection intensity should be a clear policy goal in order to reduce SES-based network segregation.
 
@@
 Referral candidates tend to get hired more often, have lower turnover, and earn higher wages \citep{obukhova2013ms,brown2016informal,dustmann2016referral}.} finding that performance-based incentives bring in qualified candidates otherwise not identified by demographic characteristics \citep{beaman_who_2012,pallais_why_2016,friebel2023employee,witte2021workers}, and the consequences of relying upon referral hiring, which come at the cost of disadvantaging certain groups \citep{beaman_job_2018,hederos2025gender}.
-We extend this literature by causally evaluate the effect of a sizeable monetary bonus for the referral candidate and exploring SES biases in referral selection.
+We extend this literature by causally evaluating the effect of a sizeable monetary bonus for the referral candidate and exploring SES biases in referral selection.
 
@@
 
-What are the diversity-related consequences of SES-driven differences across networks?
+What are the diversity consequences of SES-driven differences across networks?
 In terms of network compositions, participants could connect with other SES groups at different rates than would occur randomly depending on their own SES.
@@
   \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES.
-Horizontal lines plot the university-wide shares of SES groups (Low: 35\%, High: 14\%).
+Horizontal lines plot the university-wide shares of SES groups (Low: 34\%, High: 15\%).
 While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
@@
 Both increases are substantial, amounting to 50\% for high-, and 30\% for low-SES beyond 15 courses together.
-Considering that beyond 5 courses taken together network members are almost entirely within the same program, program selection may have strong consequences for explaining the network segregation in our setting.
+While it is known that students who take courses together have similar characteristics \citep{kossinets_origins_2009}, it is important to understand how increasing similarities in SES reflects on referral choice sets.
 
@@
 
-Put differently, in an environment where 1 out of 3 students are low-SES, the chance that low-SES are considered for a referral by high-SES at random is already less than 1/6.
-This stark disparity reveals that low-SES and high-SES students operate in practically separate social worlds within the same university, despite formal contact opportunities to meet as equal-status students.
-While referral selection being driven by availability and performance is positive, network segregation has such a large impact on diversity.
-We now explore program selection as a key driver.
+Put differently, in an environment where 1 out of 3 students are low-SES, the chance that a low-SES peer is considered for a referral by high-SES is already less than 1/6.
+This stark disparity reveals that low-SES and high-SES students practically have separate networks within the same university, despite  the opportunities to meet as equal-status students.
+The network segregation makes cross-SES referrals structurally unlikely even without any taste-based SES biases.
+We now explore program selection that emerges as a key driver of this segregation.
 
@@
   \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES above the median number of courses taken together.
-Horizontal lines plot the university-wide shares of SES groups (Low: 35\%, High: 14\%).
+Horizontal lines plot the university-wide shares of SES groups (Low: 34\%, High: 15\%).
 While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
@@
 
-\subsection{Program selection and SES diversity}
-
-Academic programs at this university use cost-based pricing, and typically less than 5\% of students receive any kind of scholarship.
+\subsection{Program selection as a mechanism}
+
+Academic programs at this university have cost-based pricing, and typically less than 5\% of students receive any kind of scholarship.
 Based on this, we first calculate how much every undergraduate program at the university is expected to cost students per year (see Figure \ref{fees_with_boxplot}).
@@
 
-We then examine how SES groups are distributed across programs to identify evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
+To answer, we examine how SES groups are distributed across programs to identify evidence of SES-based selection (see Figure \ref{ses_distribution_by_fees}).
 Indeed, low-SES students select into more affordable programs, followed by middle-SES students.
@@
 high-SES ($D=31.31$, $p<0.001$).
-With this finding, program selection could be the reason why low- and high-SES networks tend to segregate as the number of courses taken increases.
-The next section characterizes the referrals, and we will return to the diversity implications of program selection once we propose an understanding of how referrals were made.
+These findings support the idea that program selection could be the reason why low- and high-SES networks tend to segregate as the number of courses taken increases.
+Financial constraints channel students into different academic programs, which in turn determine their classroom interactions and university social networks.
 
@@
 Being in the same academic program has a substantial positive effect on referral likelihood, with coefficients ranging from 1.257 to 2.198 across all referrer SES groups.
-This confirms that program affiliation serves as a strong predictor of referral decisions, reflecting increased familiarity.
+This confirms that program affiliation serves as a strong predictor of referral decisions.
 Our comparison of interest is the point estimate for the standardized number of courses taken.
@@
 We investigate whether SES biases in referral selection stem from taste-based preferences in choosing an SES group over others or network segregation.
-Through a lab-in-the-field experiment with 734 university students making incentivized referrals from complete enrollment networks, we find that institutional factors dominate individual preferences.
+Through a lab-in-the-field experiment with 734 university students making incentivized referrals from their unique enrollment networks, we find that institutional factors dominate individual preferences.
 
@@
 Second, we find an SES bias is that is asymmetric and limited.
-While low-SES referrers exhibit strong in-group preferences,  middle- and high-SES referrers show no bias toward other groups.
+While low-SES referrers exhibit strong in-group preferences,  middle- and high-SES referrers show no bias toward their own and other groups.
 Third, network segregation driven by cost-based program selection explains most referral patterns.
-At typical referral range measured by the number of courses taken together, low-SES and high-SES students have dramatically different choice sets, with high-SES networks containing only 15.7\% low-SES peers compared to 35\% university-wide.
+At typical referral range measured by the number of courses taken together, low-SES and high-SES students have dramatically different choice sets, with high-SES networks containing only 15.7\% low-SES peers compared to 34\% university-wide.
 
 These results have important policy implications.
-While universities expose low-SES students to higher-than-population shares of high-SES peers, segregation within institutions limits meaningful cross-SES interaction.
-Our findings suggest that institutional interventions promoting mixed-SES classrooms, rather than addressing individual biases, represent the most promising approach to reducing SES-based inequality in opportunity transmission.
-Future research should explore the causal effect of specific institutional interventions that aim to increase cross-SES interactions.
+While universities expose low-SES students to higher-than-population shares of high-SES peers, segregation within institutions limits meaningful interaction across SES.
+Our findings suggest that institutional interventions promoting cross-SES contact, represents a promising approach to reduce SES-based inequality in opportunity transmission.
+Future research should explore the causal effects of specific institutional interventions such as mixed seating \citep{rohrer2021po}, or cross-SES mentoring programs \citep{alan2025aer}, that increase interactions between with SES groups.
 

### 2025-08-12 writing/manuscript.tex
v1.2.1
todo: reviews from Sophie

@@
 \section*{Abstract}
-The share of high-SES connections in one's network is a strong correlate of labor market income.
-We investigate whether SES biases in referral selection exacerbate differences high-SES connection shares.
+
+The share of high-SES connections in one's network strongly correlates with labor market income.
+Understanding whether network-based inequalities stem from who people can meet versus whom they choose to connect with requires separating network composition from individual preferences.
+We achieve this separation through a lab-in-the-field experiment where 734 Colombian university students make incentivized referrals from their complete enrollment networks.
+
 We conduct a lab-in-the-field experiment with 734 Colombian university students who make incentivized referrals from their enrollment networks.
-Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of incentives.
+Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of the treatment.
 While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no biases towards their own and other groups, referring along their network shares.
@@
 This persistent inequality undermines meritocratic ideals and represents a substantial barrier to economic mobility.
-A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectivity, defined as the share of high-SES connections among low-SES individuals, is an important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
+A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectedness, defined as the share of high-SES connections among low-SES individuals, is an important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
 In this sense, a lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.

### 2025-08-13 writing/manuscript.tex
v1.2.2

--- 2025-08-07 writing/manuscript.tex
@@
 
-\title{When Proximity Isn't Enough: Network Segregation and SES Bias in Referrals}
+\title{When Proximity Isn't Enough: Network Segregation and Class Bias in Referrals}
 % \\ \large Experimental Design \\
@@
 \section*{Abstract}
-The share of high-SES connections in one's network is a strong correlate of labor market income.
-We investigate whether SES biases in referral selection exacerbate differences high-SES connection shares.
+The share of high-socioeconomic status (SES) connections in one's network is a strong correlate of labor market income.
+While universities provide ample opportunities for cross-SES contact, it remains unclear whether this exposure translates into meaningful connections.
+We investigate this question by exploring SES biases in referral selection.
 We conduct a lab-in-the-field experiment with 734 Colombian university students who make incentivized referrals from their enrollment networks.
-Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of incentives.
-While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no biases towards their own and other groups, referring along their network shares.
-We find that network segregation, driven by program selection based on SES, limits cross-SES referral opportunities for even without an explicit SES bias.
-These suggest institutional policies promoting cross-SES contact are key for reducing SES-based inequalities.
+Randomizing participants between performance-only incentives and performance plus a fixed bonus for referral recipients, we find that referrals go to high-performing peers with whom they take many courses together, regardless of condition.
+While low-SES referrers exhibit strong in-group preferences, middle- and high-SES referrers show no biases toward their own and other groups.
+Network segregation, driven by cost-based program selection, limits cross-SES referral opportunities even without an explicit SES bias.
+Our results imply that institutional policies promoting cross-SES contact are key for reducing SES-based inequalities.
 \medskip \\
@@
 
-\pagebreak
 \section{Introduction}
-Equally qualified individuals face different labor market outcomes based on their socioeconomic status \citep{stansbury2024class}.
+Equally qualified individuals face different labor market outcomes based on their SES \citep{stansbury2024class}.
 This persistent inequality undermines meritocratic ideals and represents a substantial barrier to economic mobility.
-A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectivity, defined as the share of high-SES connections among low-SES individuals, is an important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
-In this sense, a lack of social capital means lack of access to individuals with influential (higher paid) jobs and job opportunities.
+A key driver of SES-based inequality in the labor market stems from differences in social capital.\footnote{See for example \citet{loury_dynamic_1977,bourdieu_forms_1986} for pioneering work on the relationship between social position and human capital acquisition.} Economic connectedness, defined as the share of high-SES connections in one's network, is an important facet of social capital because it correlates strongly with labor market income \citep{chetty2022na}.
+In this sense, a lack of social capital means lack of access to individuals with influential (higher paid) jobs and related job opportunities.
 It implies having worse outcomes when using one's network to find jobs conditional on the capacity to leverage one's social network.\footnote{See for example \citet{lin1981asr,mouw2003asr} for differential outcomes while using contacts in job search, and \citet{smith2005ajs,Pedulla2019RaceAN} specifically for the effects of race conditional on network use.}
 
-Research on economic connectivity has focused on two distinct mechanisms that shape cross-SES connections: network composition (who you have the chance to meet inside an institutional environment) versus individual preference (who you choose to connect with among those available).
-The prevailing hypothesis emerging from the seminal work of \citet{chetty2022n} is that increasing exposure to high-SES individuals will lead low-SES individuals to connect with them at higher rates.
+Research on economic connectedness has focused on two distinct mechanisms that shape cross-SES connections: network composition (who you have the chance to meet inside an institutional environment) versus individual preference (who you choose to connect with among those available).
+A prevailing hypothesis is that increasing exposure to high-SES individuals will lead to higher rates of cross-SES connections in networks \citep{chetty2022n}.
 Universities, in this regard, represent a particularly promising setting as they attract higher-than-population shares of high-SES students, and create more opportunities for cross-SES connections.
-However, credible evidence on biases in individual preferences to connect across SES groups remains limited.
-One important reason for this gap is the challenge of creating controlled environments that isolate SES biases while accounting for natural variations in network compositions.
-
-We overcome this challenge through a lab-in-the-field experiment at a Colombian university.
-Focusing on the role of SES in referral selection, we studied whether individuals who were asked to refer a peer tended to refer a same-SES candidate.
+However, whether these cross-SES connection opportunities turn into meaningful contacts, and the role of SES biases in the process has not yet been explored.
+
+We address these questions through a referral experiment in a university setting.
+Focusing on the role of SES in referral selection, we studied whether individuals tended to refer same-SES peers.
 We recruited 734 undergraduate students to make incentivized referrals among peers they encountered during their coursework.
-Referrals were made for the math and critical reading areas of the national university entry exam, and to incentivize performance-based referral selection, participants earned payments up to \$60 per referral based on their nominee's percentile ranking at the university.
+Referrals were made for the math and critical reading areas of the national university entry exam.
+To incentivize performance-based referral selection, participants (referrers) earned payments up to \$60 per referral based on their nominee's percentile ranking at the university.
 This setup provided an objective performance benchmark for referrals where SES biases in referral selection could still play a role.
@@
 Referrals originated from each participant's unique course enrollment network that we constructed using extensive administrative data.
-The enrollment network covered each course the referrer had taken with all other undergraduate students at the university (more than 4,500 individuals).
-It allowed us to observe both characteristics of every potential referral candidate, and the intensity of interaction between the two, which we measured by the number of courses taken together.
+The enrollment network covered each course that the participant had taken with all other undergraduate students at the university (more than 4,500 individuals).
+It allowed us to observe every potential referral candidate, and the connection intensity between the candidate and the referrer, which we measured by the number of courses they took together.
 Referrals from the enrollment networks enabled us to separate network composition (i.e., chance of meeting during coursework and frequency of contact) from SES biases in referral selection (i.e., individual choice in picking a referral).
@@
 We randomized participants into two conditions.
-In the \textbf{Baseline} condition participants made referrals with performance-based incentives only, where their earnings depended on the actual performance of their referrals.
+In the \textbf{Baseline} condition, participants made referrals with performance-based incentives only, where their earnings depended on the actual performance of their referrals.
 In the \textbf{Bonus} condition, participants made referrals with performance-based incentives and an additional fixed bonus (\$25) going to their referral of choice.
-We designed the \textbf{Bonus} condition to make SES biases in referral selection even more salient.
 The fixed bonus created incentives to refer peers even if they performed less well, potentially amplifying the relevance of other factors like the SES bias and the connection intensity.
 
-We find that referrals consistently go to higher-performing peers with high connection intensity (14 vs.
-4 courses), regardless of the conditions and the exam area.
-Pooling across these, we find that SES bias in referral selection is primarily driven by low-SES participants exhibiting in-group preferences: Controlling for network composition, low-SES referrers are 45\% more likely to refer other low-SES peers  and 44\% less likely to refer high-SES relative to middle-SES peers.
+We find that referrals consistently go to higher-performing peers with high connection intensity, regardless of conditions and exam areas.
+Pooling across these, we find that SES bias in referral selection is primarily driven by low-SES participants exhibiting in-group preferences.
+In our preferred specification, low-SES referrers are 27\% more likely to refer other low-SES peers and 36\% less likely to refer high-SES relative to middle-SES peers.
 In contrast, middle- and high-SES referrers show no biases toward their own or other groups.
 
-With 93\% of referrals going to peers within the same academic program with whom referrers have taken many courses together, we find that network composition rather than SES biases better explain the observed referral patterns.
-At the connection intensity where referrals typically occur (median 12 courses together), network segregation becomes stark: low-SES networks contain 44.5\% low-SES peers versus 35\% university-wide (27\% increase), while high-SES networks contain only 15.7\% low-SES peers (55\% decrease from the university average).
-This segregation means that even without any bias against low-SES peers, high-SES referrers rarely encounter low-SES candidates in their practical choice sets.
+With 93\% of referrals going to peers within the same academic program with whom referrers have taken many courses together, we find that network composition rather than SES biases better explains the observed referral patterns.
+At the connection intensity where referrals typically occur (median 12 courses together), network segregation becomes stark: low-SES students comprise 44.5\% of low-SES referrers' networks compared to only 15.7\% of high-SES referrers' networks, despite representing 34\% of the university population.
+This segregation means that even without bias against low-SES peers, high-SES referrers rarely encounter low-SES candidates among their close university connections.
 
@@
 First, our referrals have no direct job consequences, and participants refer under anonymity.
-These may represent a lower stake environment for referrers with no potential reputational concerns.
-Nevertheless, we replicate typical findings from earlier referral experiments where performance-based incentives brings in qualified candidates from participant networks (e.g., \citet{witte2021workers,beaman_who_2012}).
+These may represent a lower stake environment for referrers.
+Nevertheless, we replicate typical findings from earlier referral experiments where performance-based incentives brings in qualified candidates from referrer networks (e.g., \citet{witte2021workers,beaman_who_2012}).
 
 Second, enrollment networks capture classroom-based interactions and their intensity rather than broader networks of close friendships.
-While our approach has clear advantages over self-reported friendship network elicitation which suffers from censoring due to limitations in size \citep{griffith2022jle}, triangulating it with an additional method (e.g., social media friendship data) could provide useful for better identifying actual interactions at the university.
-Still, we find that connection intensity predicts referral selection well beyond same program affiliation, suggesting it does capture meaningful variation in social interactions in some dimension.
+Unlike self-reported friendship networks that must limit the number of connections surveyed \citep{griffith2022jle}, administrative data captures all classroom interactions without artificial size constraints.
+Combining enrollment networks with  additional network data (e.g., from social media) could be useful for better identifying interactions at the university.
+Still, we find that connection intensity predicts referral selection well beyond same program affiliation, suggesting it does capture meaningful variation in social interactions.
 
@@
 
-Methodologically, we contribute to the literature on job referral experiments.
+Third, we contribute to the literature on job referral experiments.
 This literature provides causal evidence on why referrals in the labor market are prevalent,\footnote{Referrals solve frictions in the search and matching process and benefit both job-seekers and employers \citep{topa2019social}.
 Referral candidates tend to get hired more often, have lower turnover, and earn higher wages \citep{obukhova2013ms,brown2016informal,dustmann2016referral}.} finding that performance-based incentives bring in qualified candidates otherwise not identified by demographic characteristics \citep{beaman_who_2012,pallais_why_2016,friebel2023employee,witte2021workers}, and the consequences of relying upon referral hiring, which come at the cost of disadvantaging certain groups \citep{beaman_job_2018,hederos2025gender}.
-We extend this literature by causally evaluating the effect of a sizeable monetary bonus for the referral candidate and exploring SES biases in referral selection.
+We extend this literature by causally evaluating the effects of a sizeable monetary bonus for referral candidates and exploring SES biases in referral selection.
 
@@
 This economic disparity creates profound differences in outcomes across SES groups in terms of education, geographic residence, language, manners, and social networks \citep{garciavillegas2021dimension, angulo2012movilidad,garcia2015loteria}.
-While similar patterns also exist elsewhere, Colombia's pronounced economic inequality makes educational and cultural differences across SES groups particularly visible.
-
-In higher education, Colombia's pronounced economic equality manifests itself by preventing meaningful interaction between SES groups.
+
+In higher education, economic inequality manifests itself by preventing meaningful interaction between SES groups.
 Wealthy families attend exclusive private schools while poorer families access lower-quality public or ``non-elite'' private institutions (see Figure \ref{school_quality_income}).
-Taken together, the unique ways in which economic inequality manifests itself in the Colombian higher educational setting provides the ideal conditions to study biases related to SES in referral selection.
+While similar patterns also exist elsewhere, differences in educational outcomes across SES groups are particularly visible in Colombia.
 
@@
 Designed for utility subsidies from higher strata to support lower strata, the system aligns with and reinforces existing social class divisions \citep{uribe2008estratificacion, guevara2019spatializing}.
-It is also widely used by policymakers and in official statistics \citep{fergusson2021desigualdad} and well known to by the public.
+It is also widely used by policymakers and in official statistics \citep{fergusson2021desigualdad}.
 Using the estrato system, we categorize students in strata 1-2 as low-SES, strata 3-4 as middle-SES, and strata 5-6 as high-SES.
@@
 
-Our study takes place in a non-elite private university which attracts students across the socioeconomic spectrum: The university's undergraduate student body comprises 35\% low-SES, 50\% middle-SES, and 15\% high-SES students.\footnote{Government statistics reveal less than 5\% of the population is high-SES \citep[p.
+Our study takes place in a non-elite private university which attracts students across the socioeconomic spectrum: the university's undergraduate student body comprises 34\% low-SES, 51\% middle-SES, and 15\% high-SES students.\footnote{Government statistics reveal less than 5\% of the population is high-SES \citep[p.
 103]{hudson_colombia_2010}.} This diversity provides opportunities for different SES groups to meet and interact within the same institutional framework.
 
-The opportunities for contact at the university are on equal status.
+The contact at the university is on equal status.
 All undergraduate students pay the same fees based on their program choices, and less than 5\% of undergraduate students receive scholarships.
-The student body is mostly urban ($>70$\%), not part of an ethnic minority ($>95$\%), and has comparable university entry exam scores (see Appendix Figures \ref{math_hist} and \ref{reading_hist}).
+The student body is mostly urban ($>70$\%), not part of an ethnic minority ($>95$\%), and has similar university entry exam scores (see Appendix Figures \ref{math_hist} and \ref{reading_hist}).
 These make our setting appropriate to study the effects of contact on intergroup discrimination.
@@
 Undergraduate students at the university choose among 32 different academic programs.
-Students take between 5 and 7 courses per semester, and programs last anywhere between 4 and 12 semesters (2 to 6 years).
+Students take between 5 and 7 courses per semester, and programs last between 4 and 12 semesters (2 to 6 years).
 The majority (64\%) of students are enrolled in the 10 programs described in Appendix Figure \ref{program_share}.
-Medicine, the largest program by size at the university, lasts for 12 semesters, followed by engineering programs at 10 semesters.
-Most remaining programs last for about 8 to 10 semesters, with specialized programs for immediate entry into the workforce lasting only 4 semesters.
+While medicine, the largest program by size at the university lasts for 12 semesters, specialized programs for immediate entry into the workforce last only 4 semesters.
 Academic program choice thus shapes students' connections at the university, influencing both who they encounter in classes and the frequency of these interactions.
@@
 
-For causal identification, we require two assumptions.
+For identification, we require two assumptions.
 First, conditional exogeneity.
 SES and the number of courses taken together could be endogenous due to program selection.
-High-SES students sort into expensive programs while low-SES students choose affordable programs, creating SES variation across enrollment networks.
+High-SES students may sort into expensive programs while low-SES students choose affordable programs, creating SES variation across enrollment networks.
 Similarly, the number of courses taken together reflects program selection decisions that may correlate with unobserved referral preferences.
@@
 \section{Design} \label{Design}
-We designed an experiment to assess SES biases in referral selection and to evaluate the causal effect of providing a bonus to referral candidates.
-The experimental design consisted of two incentivized tasks administered in the following sequence: First, participants completed belief elicitation tasks about their own performance on the national university entry exam.
-Second, they completed the main referral task, nominating peers based on exam performance in two academic areas.
-Finally, participants reported beliefs about their referrals' performance and provided demographic information.
-This structure allowed us to measure the accuracy of participants' beliefs and observe their referral decisions in a controlled setting.
-Figure \ref{timeline} shows the experimental timeline, and detailed instructions are provided in Appendix \ref{instructions}.
-
-\begin{figure}[H]
-\centering
-\caption{Experimental Timeline}\label{timeline}
+We designed an experiment to assess SES biases in referral selection and evaluate the causal effect of providing bonuses to referral candidates.
+The 30-minute experiment consisted of three sequential tasks: initial belief elicitation about participants' own performance on the national university entry exam, referral tasks where they nominated peers for two exam areas (math and critical reading), and another belief elicitation about their nominees' performance.
+This structure allowed us to collected incentivized measures for the accuracy of participants' performance beliefs and their referral decisions.
+Figure \ref{timeline} shows the experiment overview, and detailed instructions are provided in Appendix \ref{instructions}.
+
+\begin{figure}[H]
+\centering
+\caption{Experiment Overview}\label{timeline}
 \includegraphics[width=\linewidth]{../figures/timeline.jpg}
@@
 \footnotesize
-\item[] \textit{Note:} Participants first reported beliefs about their own university entry exam performance, then made referrals for each academic area, and finally reported beliefs about their referrals' performance and provided demographics.
+\item[] \textit{Note:} Participants first reported beliefs about their university entry exam performance in two areas, then made referrals for those, and finally reported beliefs about their referrals' performance and provided demographics.
 \end{tablenotes}
@@
 
-Participants can only refer students with whom they have taken at least one class during their university studies.
-This requirement ensures that referrals are based on actual peer interactions.
+Participants are required to only refer students with whom they have taken at least one class during their university studies.
+Referrals to students without any classes taken together are possible, but not valid.
+This condition ensures that referrals are based on actual peer interactions.
 We randomize the order in which participants make referrals across the two exam areas.
@@
 \subsection{Bonus Treatment}
-To examine how different incentive structures affect referral selection, we randomly assign a fixed bonus payment for students who get a referral.
-In the \textbf{Baseline} treatment, only the participants, i.e., those who make referrals, can earn money based on their referral's performance.
-The \textbf{Bonus} treatment adds a fixed payment of \$25 to the peer who gets the referral.
+To examine how different incentive structures affect referral selection, we randomly assign a fixed bonus payment for students who get a referral (receiver).
+In the \textbf{Baseline} treatment, only the participants, i.e., those who make referrals (sender), can earn money based on their referral's performance.
+The \textbf{Bonus} treatment adds a fixed payment of \$25  uniquely to the peer who gets the referral.
 This payment is independent of the referral's actual performance (see Table \ref{tab:treatments}).
@@
 \subsection{Belief elicitation}
-We collect two sets of incentivized beliefs to assess the accuracy of participants' knowledge about exam performance.
-Participants first report beliefs about their own percentile ranking in the university for each exam area.
+We collect two sets of beliefs to assess the accuracy of participants' knowledge about exam performance.
+Participants first report beliefs about their own percentile ranking in the university for math and critical reading areas.
 After making referrals, participants report their beliefs about their referrals' percentile ranking in the university.
@@
 \section{Sample, Incentives, and Procedure} \label{SID}
-We invited all 4,417 undergraduate students who had completed their first year at the university at the time of recruitment to participate in our experiment.
+We invited all 4,417 undergraduate students who had completed their first semester at the university at the time of recruitment to participate in our experiment.
 A total of 837 students participated in the data collection (19\% response rate).
-Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together (88\% success rate).
+Our final sample consists of 734 individuals who referred peers with whom they had taken at least one class together, excluding 12\% of participants who made two non-valid referrals.
 
@@
 Our sample is characterized by a majority of middle-SES students with about one-tenth of the sample being high-SES students.
-The test scores and GPA distributions are balanced.
+The test scores and grade distributions are balanced.
 On average, participants had taken 3.8 courses together with members of their network, and the average network consisted of 175 peers.
@@
 
-The experiment was conducted online through Qualtrics, with participants recruited from active students.
+The experiment was conducted online through Qualtrics, and we recruited participants by sending invitations to their student emails.
 To ensure data quality while managing costs, we randomly selected one in ten participants for payment.
@@
 This structure resulted in maximum total earnings of \$82.
-The average time to complete the survey was 30 minutes, with an average compensation of \$80 for the one in ten participants randomly selected for payment.
+The average time to complete the survey was 30 minutes, with an average compensation of \$80 for one in ten participants randomly selected for payment.
 Payment processing occurred through bank transfer within 15 business days of participation.
@@
 We begin by describing the key features of the enrollment networks.
-On average, participants connect with 175 other students, and take an average of 3.62 courses together.
+On average, participants connect with 175 other students, and take an average of 3.8 courses together.
 Figure \ref{connections_class} shows how network characteristics vary by students' time at the university: both the number of connections (network size) and the number of courses taken together (connection intensity) change as participants progress through their studies.
@@
     \item[] \textit{Note:} 
-    This figure displays the average number of connections in blue and the average number of courses taken together with connections in gray across semesters completed.
+    This figure displays the average number of connections in gray and the average number of courses taken together with connections in blue across semesters completed.
 Network size (nb.
@@
   \end{subfigure}
-  \caption*{\footnotesize\textit{Note:} The left panel illustrates the share of connections within the same program as a function of the number of courses taken together.
-The right panel shows the average network size as a function of the number of courses taken together.
+  \caption*{\footnotesize\textit{Note:} Panel (a) illustrates the share of connections within the same program as a function of the number of courses taken together.
+Panel (b) shows the average network size as a function of the number of courses taken together.
 Taking more than 5 courses together with a network member means on average 90\% chance to be in the same program.
@@
 Participants made one referral for math and one referral for the reading part of the university entry exam from their enrollment networks.
-We observe 1,342 referrals from 734 participants in our final dataset.
+We collected 1,342 valid referrals from 734 participants in our final dataset.
 More than 90\% of these consist of participants referring for both exam areas (see Appendix Table \ref{tab:referral_distribution}).
@@
 First, referrals go to peers with whom the referrer has taken around 14 courses with on average, compared to almost 4 on average with others in their network (see Figure \ref{tie_hist}).
-This difference of 10.1 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have higher contact intensity.
+This difference of 10 courses is significant ($t = 34.98$, $p < 0.001$), indicating that referrers choose individuals with whom they have higher contact intensity.
 While the median referral recipient has taken 12 courses together with the referrer, the median network member has shared only 2.8 courses.
@@
 The interquartile range for referrals spans from 65.5 to 75 points, compared to 63.5 to 66.9 points for the broader network, highlighting the  concentration of referrals among higher performing peers.
+Participant beliefs regarding their referral's and own performance rank at the university also support these findings (see Appendix Figures \ref{own_belief} and \ref{other_belief}).
 
@@
     \footnotesize
-    \item[] \textit{Note:} This figure compares the distributions of entry exam scores (Math and Reading average) between referrers' network members (orange) versus their chosen referral recipients (dark blue) for all 734 participants.
+    \item[] \textit{Note:} This figure compares the distributions of entry exam scores (math and critical reading average) between referrers' network members (orange) versus their chosen referral recipients (dark blue) for all 734 participants.
 75\% of referral recipients score above 65.5 points compared to only 25\% of network members scoring above 66.9 points.
@@
 We compare the performance and the number of courses taken together with the referrer between the \textbf{Baseline} and \textbf{Bonus} treatments in Table \ref{tab:referral_by_treatment}.
-We find that the number of courses taken together with referrer, as well as performance measures across Reading, Math, and GPA are similar across treatments.
-Taken together, the similarities in academic performance and connection intensity suggest these two factors drive referrals regardless of treatment.
+Contrary to our expectations, we find that the number of courses taken together with referrer, as well as performance measures across critical reading and math (including grades) are similar across treatments.
+Taken together, the results on academic performance and connection intensity suggest these two factors drive referrals regardless of treatment.
 For this reason, in the remainder of the paper, we report pooled results combining the averages of referral outcomes across treatments.
@@
   \footnotesize
-  \item[] \textit{Note:} This table compares the characteristics of network members who were referred under baseline vs bonus treatment conditions.
+  \item[] \textit{Note:} This table compares the characteristics of network members who were referred under baseline vs.
+bonus treatments.
 $p$-values for binary outcomes are from two-sample tests of proportions; for continuous variables, from two-sample $t$-tests with unequal variances.
@@
 Courses taken is the number of courses participant has taken  with their referral.
-Both columns only include network members who were referred in each treatment.
+Both columns only include the average outcomes of network members who were referred in each treatment.
   \end{tablenotes}
@@
 To motivate the SES biases in referral selection, we now examine the overall SES composition of referrals compared to the average network availability.
-Descriptively, referral patterns largely mirror underlying network structure.\footnote{Because we estimate the share of SES groups in every individual network, we get very precise estimates of the actual means.
+Descriptively, referral patterns largely mirror underlying network structure.\footnote{Because we calculate the share of SES groups in every individual network, we get very precise estimates of the actual means.
 However, it is important to note that these are not independent observations.
@@
 The bias was underestimated as high-SES candidates' better performance relative to middle-SES increased referrals.
-Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias towards one another that operates independently of -- and counter to -- performance-based considerations.
-What makes a symmetric bias interpretation difficult is that while biased against low-SES, high-SES referrers do not (under any specification) display a positive bias towards their in-group.
+Controlling for exam scores reveal that both high- and low-SES referrers have negative SES bias toward one another that operates independently of -- and counter to -- performance-based considerations.
+What makes a symmetric bias interpretation difficult is that while biased against low-SES, high-SES referrers do not (under any specification) display a positive bias toward their in-group.
 
@@
 Middle- and high-SES referrers show no systematic discrimination against other SES groups once we account for network composition and other relevant factors contributing to the referral decision.
-We will next explore potential mechanisms that help explain this unexpected result.
+We will next explore potential mechanisms that help explain the unexpected direction of the SES bias.
 
@@
 
-We find larger differences when studying connections between SES groups: Low-SES referrers connect with other low-SES at much higher rates than high-SES referrers (38.4\% vs 25.1\%).
-Conversely, high-SES referrers connect more with other high-SES than low-SES referrers (20.4\% vs 12.6\%).
-Middle-SES referrers are in between the two extreme patterns, connecting with middle-SES at higher rates than low-SES referrers (52.9\% vs 49.0\%) but lower rates than high-SES referrers (52.9\% vs 54.5\%).
+We find larger differences when studying connections between SES groups: Low-SES referrers connect with other low-SES at much higher rates than high-SES referrers (38.4\% vs.
+25.1\%).
+Conversely, high-SES referrers connect more with other high-SES than low-SES referrers (20.4\% vs.
+12.6\%).
+Middle-SES referrers are in between the two extreme patterns, connecting with middle-SES at higher rates than low-SES referrers (52.9\% vs.
+49.0\%) but lower rates than high-SES referrers (52.9\% vs.
+54.5\%).
 These findings indicate SES-based segregation in networks, with same-SES homophily across groups.
@@
   \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES.
-Horizontal lines plot the university-wide shares of SES groups (Low: 34\%, High: 15\%).
+Horizontal lines plot the university-wide shares of SES groups (low-SES: 34\%, high-SES: 15\%).
 While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
@@
 
-We show the average network shares conditional on referrer SES and above median number of courses taken together for low-SES in Figure \ref{connections_to_low_ses_tie12} and for high-SES in Figure \ref{connections_to_high_ses_tie12}.\footnote{In Appendix Figure \ref{t15availability} we present the complete relationship including middle-SES.} Network compositions above the median number of courses taken reveal strong segregation effects in referral choice sets: Low-SES networks contain 44.5\% low-SES peers, higher than the 35\% university-wide share by 9.5 percentage points.
+We show the average network shares conditional on referrer SES and above median number of courses taken together for low-SES in Figure \ref{connections_to_low_ses_tie12} and for high-SES in Figure \ref{connections_to_high_ses_tie12}.\footnote{In Appendix Figure \ref{t15availability} we present the complete relationship including middle-SES.} Network compositions above the median number of courses taken reveal strong segregation effects in referral choice sets: Low-SES networks contain 44.5\% low-SES peers, higher than the 34\% university-wide share by 9.5 percentage points.
 Conversely, high-SES students are under-represented in low-SES networks at only 8.6\% average share, compared to the 14\% university share ($-5.4$ pp.).
-At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to just 15.7\%, a 19.3 percentage point decrease relative to the university average.
-High-SES students have a same-SES concentration at 26.5\%, doubling their 14\% university share ($+12.5$ pp.).
+At the other extreme, high-SES networks show the reverse pattern with average low-SES share dropping to 15.7\%, a 19.3 percentage point decrease relative to the university average.
+High-SES students have a same-SES concentration at 26.5\% ($+12.5$ pp.).
 Middle-SES networks remain relatively balanced and closely track university proportions.
@@
   \caption*{\footnotesize\textit{Note:} Figures illustrate the average network shares of low- and high- SES peers conditional on referrer SES above the median number of courses taken together.
-Horizontal lines plot the university-wide shares of SES groups (Low: 34\%, High: 15\%).
+Horizontal lines plot the university-wide shares of SES groups (low-SES: 34\%, high-SES: 15\%).
 While the share of low-SES peers in the network decreases as referrer SES increases, the share of high-SES peers in the network increases.
@@
 Does the number of courses taken together have an independent effect that goes beyond identifying peers in the same academic program?
-To evaluate this question we leverage our administrative data, and identify peers within the same program: In each individual network we observe the participant-specific academic program for the participant making the referral and alternative-specific academic program for each referral candidate.
+To evaluate this question we leverage our administrative data, and identify peers within the same program: In each individual network we observe the participant-specific academic program for the referrer and alternative-specific academic program for each referral candidate.
 We add this new variable in our specification and describe our findings in Table \ref{tab:ses-heterogeneity-program}.
@@
 Our comparison of interest is the point estimate for the standardized number of courses taken.
-Across all three referrer groups, the standardized number of courses taken together maintains its statistical significance after controlling for same program membership.
+Across all three referrer SES groups, the standardized number of courses taken together maintains its statistical significance after controlling for same program membership.
 The coefficient magnitudes are expectedly smaller compared to specifications without program controls (ranging from 0.688 to 0.930) as the newly added variable is a moderator: Matching academic programs leads to taking more courses together.
-The remaining estimates in our model remain robust to the inclusion of the same-program variable with little change in point estimates.
+The remaining estimates in our model are robust to the inclusion of the same-program variable with little change in point estimates.
 The persistence of statistical significance (all $p < 0.001$) suggests that the number of courses taken together has an independent effect on referral decisions.
@@
 \section{Conclusion} \label{Conclusion}
-We investigate whether SES biases in referral selection stem from taste-based preferences in choosing an SES group over others or network segregation.
-Through a lab-in-the-field experiment with 734 university students making incentivized referrals from their unique enrollment networks, we find that institutional factors dominate individual preferences.
+We investigate whether SES biases in referral selection stem from individual preferences in choosing an SES group over others or network segregation.
+Through a lab-in-the-field experiment with 734 university students making incentivized referrals from their enrollment networks, we find that institutional factors dominate individual preferences.
 
@@
 Our findings suggest that institutional interventions promoting cross-SES contact, represents a promising approach to reduce SES-based inequality in opportunity transmission.
-Future research should explore the causal effects of specific institutional interventions such as mixed seating \citep{rohrer2021po}, or cross-SES mentoring programs \citep{alan2025aer}, that increase interactions between with SES groups.
+Future research should explore the causal effects of specific institutional interventions such as mixed seating \citep{rohrer2021po}, or cross-SES mentoring programs \citep{alan2025aer}, that increase interactions between  SES groups.
 
@@
 Students cluster around certain programs.
-The top 5 most popular programs (Medicine, Law, Biomedical Engineering, Pharmacy Technology, and Business Administration) account for 43\% of all undergraduates, and the top 10 most popular programs account for 63\% of students.
-  \end{tablenotes}
+The top 5 most popular programs (Medicine, Law, Biomedical Engineering, Pharmacy Technology, and Business Administration) account for 43\% of all undergraduates, and the top 10 most popular programs account for 64\% of students.
+  \end{tablenotes}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{Distribution of participant beliefs}
+  \begin{subfigure}[t]{0.49\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/own_belief.png}
+      \caption{Beliefs about own performance rank}  
+      \label{own_belief}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.49\textwidth} 
+    \centering
+      \includegraphics[width=\linewidth]{../figures/other_belief.png}
+      \caption{Beliefs about referral performance rank}
+      \label{other_belief}
+  \end{subfigure}
+  \caption*{\footnotesize\textit{Note:} Panel (a) illustrates participant's own rank belief minus their actual rank at the university.
+Panel (b) illustrates participant's rank belief of their referral minus their actual rank at the university.
+While participants accurately assess their own rank, they slightly overestimate their referral's rank.
+  }
 \end{figure}
@@
     \item[] \textit{Note:} This figure displays the average network shares of SES groups respectively for low-, middle-, and high-SES referrers.
-Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+Horizontal lines plot the university-wide shares of each SES group (Low: 34\%, Mid: 51\%, High: 15\%).
 While the share of low-SES peers in the network decreases as the SES of the referrers increases, the share of high-SES peers in the network increases.
@@
     \item[] \textit{Note:} This figure displays the average network shares of SES groups respectively for low-, middle-, and high-SES referrers above the median number of courses taken together.
-Horizontal lines plot the university-wide shares of each SES group (Low: 35\%, Mid: 51\%, High: 14\%).
+Horizontal lines plot the university-wide shares of each SES group (Low: 34\%, Mid: 51\%, High: 15\%).
 Low- and high-SES networks both become same-SES dominated at the expense of each other while middle-SES networks remain balanced.
@@
 If not, your answer will not be considered for payment.
-The person you recommend will not be contacted or receive any benefit from your recommendation.
+\textbf{The person you recommend will not be contacted or receive any benefit from your recommendation.} [Only seen if assigned to the treatment]
 
